### 2018-01-02 NewTexFile/GopinathArgall_RSS2018.tex
First Commit

\documentclass[conference]{IEEEtran}
\usepackage{times}
% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage[normalem]{ulem} % underline
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{balance}
\usepackage{color}
\usepackage{url}
\usepackage{booktabs}
\usepackage{pifont}
\newcommand{\argmax}{\arg\!\max}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\pdfinfo{
	/Author (Deepak Gopinath, Brenna D. Argall)
	/Title  (Mode Switch Assistance to Human Intent Disambiguation)
	/CreationDate (January 31 2017)
	/Subject (Robots)
	/Keywords (Robots)
}
% numbers option provides compact numerical references in the text.

\pdfinfo{
   /Author (Homer Simpson)
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}

\begin{document}

% paper title
\title{Fisher Information based Disambiguation of Human Intent - An Experimental Evaluation}
\author{Author Names Omitted for Anonymous Review. Paper-ID [\textbf{163}]}
% You will get a Paper-ID when submitting a pdf file to the conference system
%\author{Deepak Gopinath and Brenna D. Argall}

%\author{\authorblockN{Deepak Gopinath}
%\authorblockA{Department of Mechanical\\Engineering,
%Northwestern University\\
%Evanston, Illinois 30332\\
%Email: deepakedakkattilgopinath2015\\@u.northwestern.edu}
%\and
%\authorblockN{Brenna D. Argall}
%\authorblockA{Department of Mechanical\\Engineering,
%		Northwestern University\\
%		Evanston, Illinois 30332\\
%		Email: brenna.argall@northwestern.edu}
%	}

%\author{Deepak Gopinath$^{1}$ and Brenna D. Argall$^{2}$
%	\thanks{Manuscript received: March, 1, 2016; Revised June,
%		7, 2016; Accepted June, 29, 2016.}
%}
% avoiding spaces at the end of the author lines is not a problem with
% conference papers because we don't use \thanks or \IEEEmembership

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\authorblockN{Deepak E. Gopinath\authorrefmark{1}\authorrefmark{2},
%		Brenna D. Argall\authorrefmark{1}\authorrefmark{2}\authorrefmark{3}\authorrefmark{4}
%	}
%	\authorblockA{
%		\authorrefmark{1}Department of Mechanical Engineering, Northwestern University, Evanston, IL}
%	
%	\authorblockA{\authorrefmark{2}Rehabilitation Institute of Chicago, Chicago, IL}
%	
%	\authorblockA{\authorrefmark{3}Department of Physical Medicine and Rehabilitation, Northwestern University, Chicago, IL}
%	
%	\authorblockA{\authorrefmark{4}Department of Electrical Engineering and Computer Science, Northwestern University, Evanston, IL}
%	
%	\authorblockA{{\tt\small deepakgopinath@u.northwestern.edu}}
%	\authorblockA{{\tt\small brenna.argall@northwestern.edu}}
%}

\maketitle

\begin{abstract}
The abstract goes here.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}
This demo file is intended to serve as a ``starter file" for the
Robotics: Science and Systems conference papers produced under \LaTeX\
using IEEEtran.cls version 1.7a and later.

\section{Related Work}

Section text here.

\section{Mathematical Formalism}
\subsection{Disambiguation Schemes}
\subsubsection{Fisher Information Based Metric}
\subsubsection{Entropy-based Metric}
\subsubsection{Heuristic-based Metric}

\subsection{Intent inference}
\subsubsection{Dynamic Field Theory Based}
\subsubsection{Bayesian Inference}
\subsubsection{Confidence Functions}

\subsection{Shared Control}

\section{Experimental Evaluation}

\section{RSS citations}

Please make sure to include \verb!natbib.sty! and to use the
\verb!plainnat.bst! bibliography style. \verb!natbib! provides additional
citation commands, most usefully \verb!\citet!. For example, rather than the
awkward construction

{\small
\begin{verbatim}
\cite{kalman1960new} demonstrated...
\end{verbatim}
}

\noindent
rendered as ``\cite{kalman1960new} demonstrated...,''
or the
inconvenient

{\small
\begin{verbatim}
Kalman \cite{kalman1960new} 
demonstrated...
\end{verbatim}
}

\noindent
rendered as 
``Kalman \cite{kalman1960new} demonstrated...'', 
one can
write

{\small
\begin{verbatim}
\citet{kalman1960new} demonstrated... 
\end{verbatim}
}
\noindent
which renders as ``\citet{kalman1960new} demonstrated...'' and is 
both easy to write and much easier to read.

\subsection{RSS Hyperlinks}

This year, we would like to use the ability of PDF viewers to interpret
hyperlinks, specifically to allow each reference in the bibliography to be a
link to an online version of the reference. 
As an example, if you were to cite ``Passive Dynamic Walking''
\cite{McGeer01041990}, the entry in the bibtex would read:

{\small
\begin{verbatim}
@article{McGeer01041990,
  author = {McGeer, Tad}, 
  title = {\href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic Walking}}, 
  volume = {9}, 
  number = {2}, 
  pages = {62-82}, 
  year = {1990}, 
  doi = {10.1177/027836499000900206}, 
  URL = {http://ijr.sagepub.com/content/9/2/62.abstract}, 
  eprint = {http://ijr.sagepub.com/content/9/2/62.full.pdf+html}, 
  journal = {The International Journal of Robotics Research}
}
\end{verbatim}
}
\noindent
and the entry in the compiled PDF would look like:

\def\tmplabel#1{[#1]}

\begin{enumerate}
\item[\tmplabel{1}] Tad McGeer. \href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic
Walking}. {\em The International Journal of Robotics Research}, 9(2):62--82,
1990.
\end{enumerate}
%
where the title of the article is a link that takes you to the article on IJRR's website.

Linking cited articles will not always be possible, especially for
older articles. There are also often several versions of papers
online: authors are free to decide what to use as the link destination
yet we strongly encourage to link to archival or publisher sites
(such as IEEE Xplore or Sage Journals).  We encourage all authors to use this feature to
the extent possible.

\section{Conclusion} 
\label{sec:conclusion}

The conclusion goes here.

\section*{Acknowledgments}

%% Use plainnat to work nicely with natbib.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}

### 2018-01-02 TexFile/GopinathArgallRSS2018/GopinathArgallRSS2018.tex
First Commit

--- 2018-01-02 NewTexFile/GopinathArgall_RSS2018.tex
@@
 \usepackage{times}
+
 % numbers option provides compact numerical references in the text. 
@@
 \usepackage[bookmarks=true]{hyperref}
-\usepackage{graphics} % for pdf, bitmapped graphics files
+%
+%\smartqed  % flush right qed marks, e.g. at end of proof
+%
 \usepackage{graphicx}
-\usepackage[numbers]{natbib}
-\usepackage{multicol}
-\usepackage[bookmarks=true]{hyperref}
+\usepackage{amssymb}
+\usepackage{graphicx}
 \usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
+\usepackage{mathtools, bbm}
 \usepackage{amsmath} % assumes amsmath package installed
@@
 \usepackage{url}
-\usepackage{booktabs}
-\usepackage{pifont}
-\newcommand{\argmax}{\arg\!\max}
-\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+\usepackage{microtype}
+\usepackage{algorithm, algorithmic}
+\usepackage{breqn}
+\usepackage[bottom]{footmisc}
 \pdfinfo{
-	/Author (Deepak Gopinath, Brenna D. Argall)
-	/Title  (Mode Switch Assistance to Human Intent Disambiguation)
-	/CreationDate (January 31 2017)
-	/Subject (Robots)
-	/Keywords (Robots)
-}
-% numbers option provides compact numerical references in the text.
-
-\pdfinfo{
-   /Author (Homer Simpson)
+   /Author ()
    /Title  (Robots: Our new overlords)
@@
 % paper title
-\title{Fisher Information based Disambiguation of Human Intent - An Experimental Evaluation}
-\author{Author Names Omitted for Anonymous Review. Paper-ID [\textbf{163}]}
+\title{Intent Clarification using Fisher Information Metric}
+
 % You will get a Paper-ID when submitting a pdf file to the conference system
-%\author{Deepak Gopinath and Brenna D. Argall}
+\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}
 
-%\author{\authorblockN{Deepak Gopinath}
-%\authorblockA{Department of Mechanical\\Engineering,
-%Northwestern University\\
-%Evanston, Illinois 30332\\
-%Email: deepakedakkattilgopinath2015\\@u.northwestern.edu}
+%\author{\authorblockN{Michael Shell}
+%\authorblockA{School of Electrical and\\Computer Engineering\\
+%Georgia Institute of Technology\\
+%Atlanta, Georgia 30332--0250\\
+%Email: mshell@ece.gatech.edu}
 %\and
-%\authorblockN{Brenna D. Argall}
-%\authorblockA{Department of Mechanical\\Engineering,
-%		Northwestern University\\
-%		Evanston, Illinois 30332\\
-%		Email: brenna.argall@northwestern.edu}
-%	}
+%\authorblockN{Homer Simpson}
+%\authorblockA{Twentieth Century Fox\\
+%Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\and
+%\authorblockN{James Kirk\\ and Montgomery Scott}
+%\authorblockA{Starfleet Academy\\
+%San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212\\
+%Fax: (888) 555--1212}}
 
-%\author{Deepak Gopinath$^{1}$ and Brenna D. Argall$^{2}$
-%	\thanks{Manuscript received: March, 1, 2016; Revised June,
-%		7, 2016; Accepted June, 29, 2016.}
-%}
 % avoiding spaces at the end of the author lines is not a problem with
@@
 % 
-%\author{\authorblockN{Deepak E. Gopinath\authorrefmark{1}\authorrefmark{2},
-%		Brenna D. Argall\authorrefmark{1}\authorrefmark{2}\authorrefmark{3}\authorrefmark{4}
-%	}
-%	\authorblockA{
-%		\authorrefmark{1}Department of Mechanical Engineering, Northwestern University, Evanston, IL}
-%	
-%	\authorblockA{\authorrefmark{2}Rehabilitation Institute of Chicago, Chicago, IL}
-%	
-%	\authorblockA{\authorrefmark{3}Department of Physical Medicine and Rehabilitation, Northwestern University, Chicago, IL}
-%	
-%	\authorblockA{\authorrefmark{4}Department of Electrical Engineering and Computer Science, Northwestern University, Evanston, IL}
-%	
-%	\authorblockA{{\tt\small deepakgopinath@u.northwestern.edu}}
-%	\authorblockA{{\tt\small brenna.argall@northwestern.edu}}
-%}
+%\author{\authorblockN{Michael Shell\authorrefmark{1},
+%Homer Simpson\authorrefmark{2},
+%James Kirk\authorrefmark{3}, 
+%Montgomery Scott\authorrefmark{3} and
+%Eldon Tyrell\authorrefmark{4}}
+%\authorblockA{\authorrefmark{1}School of Electrical and Computer Engineering\\
+%Georgia Institute of Technology,
+%Atlanta, Georgia 30332--0250\\ Email: mshell@ece.gatech.edu}
+%\authorblockA{\authorrefmark{2}Twentieth Century Fox, Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\authorblockA{\authorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212, Fax: (888) 555--1212}
+%\authorblockA{\authorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
 
@@
 
-\section{Related Work}
+\section{Section}
 
@@
 
-\section{Mathematical Formalism}
-\subsection{Disambiguation Schemes}
-\subsubsection{Fisher Information Based Metric}
-\subsubsection{Entropy-based Metric}
-\subsubsection{Heuristic-based Metric}
+\subsection{Subsection Heading Here}
+Subsection text here.
 
-\subsection{Intent inference}
-\subsubsection{Dynamic Field Theory Based}
-\subsubsection{Bayesian Inference}
-\subsubsection{Confidence Functions}
-
-\subsection{Shared Control}
-
-\section{Experimental Evaluation}
+\subsubsection{Subsubsection Heading Here}
+Subsubsection text here.
 

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/AutoDiff/Supplements/example1.m

@@ -1,0 +1,50 @@
+%% Example 1: Functions, derivatives, and Newton's method
+%
+% The audi class provides access to derivatives of arbitrary
+% order after initializing arguments accordingly.
+
+%%
+% *Univariate case:*
+%%
+
+% define univariate function as usual
+f = @(x) (sin(x)-atan(x))./x;
+
+% initialize audi variable of order 2
+x = ainit(linspace(0,6),2);   
+
+% plot function and first two derivatives
+figure(1), clf, hold on, grid on
+y = f(x);                                
+plot(x{0},[y{0};y{1}],x{0},y{2},'--')     
+
+% Five iterations of Newton's method starting from x=2.0 yield a zero 
+% of f, which is accurate up to machine precision. The requested 
+% derivative f' is computed automatically.
+x = ainit(2.0,1);                         % only first derivatives needed
+for i = 1:5
+  y = f(x);                               
+  x = x - y{0}/y{1};                      % audi syntax for x = x - f(x)/f'(x)
+end
+plot(x{0},f(x{0}),'ro')
+title(['f(' num2str(x{0},16) ')  =  ' num2str(f(x{0}))])
+
+%%
+% *Bivariate case:*
+
+%%
+
+% define bivariate function
+% f = @(u,v) u.*exp(v-u.^2-v.^2);
+f = @(u,v) u.^2 + v.^2;
+
+% initialize audi grid and evaluate
+[u,v] = ndgrid(linspace(-2,2,50));
+[u,v] = ainit(u,v,1);                        
+z = f(u,v);
+
+% plot function f and partial derivative f_uvv
+figure(2), clf, mesh(u{0},v{0},z{0})  
+title('Function f')
+figure(3), clf, mesh(u{0},v{0},z{1,2}) 
+title('Partial derivative f_{uvv}')

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/Numerical_Fisher_3D_2d.m

@@ -1,0 +1,125 @@
+clear all; clc; close all;
+%%
+global num_modes ng nd xg xr sig;
+ng = 4; %number of goals. is a fixed parameter
+nd = 3; %dimensionality of the problem.
+num_modes = 2;
+sig = 0.1; %std deviation for the entropy measurement.
+% xg = [randsample(-4:4, ng);rand(1,ng)*8 - 4; randsample(-4:4, ng)] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+xg= [3, -3, 3;
+    3, 3, 3;
+    -3, 3, 3;
+    3, -3, -3]';
+% xr = [randsample(-4:4, 1);randsample(-4:4, 1); randsample(-4:4, 1) ] + rand(nd,1) - rand(nd,1); %random current robot position. FIM would be evaluated at this robot position
+xr = [0,0,0]';
+uh = [1,0, 0]'; % user control command
+%%
+%PLOT GOALS AND ROBOT and UH
+figure;
+scatter3(xg(1,1:ng), xg(2,1:ng), xg(3,1:ng), 180, 'k', 'filled'); grid on; hold on;
+xlabel('X'); ylabel('Y'); zlabel('Z');
+scatter3(xr(1), xr(2), xr(3), 140, 'r', 'filled');
+quiver3(xr(1), xr(2), xr(3), uh(1), uh(2), uh(3), 0, 'LineWidth', 2, 'MaxHeadSize', 2); %current robot velocity arrow
+for i=1:ng %vectors connecting robot and goals.
+    quiver3(xr(1), xr(2), xr(3), xg(1,i) - xr(1), xg(2,i) - xr(2), xg(3,i) - xr(3), 'LineWidth', 1.5, 'LineStyle', '-.');
+end
+xrange = [-5,5]; %set axis limits
+yrange = [-5,5];
+zrange = [-5,5];
+line(xrange, [0,0], [0,0], 'Color', 'k', 'LineWidth', 1.5); %draw x and y axes.
+line([0,0], yrange, [0,0], 'Color', 'k','LineWidth', 1.5);
+line([0,0], [0,0], zrange, 'Color', 'k','LineWidth', 1.5);
+axis([xrange, yrange, zrange]);
+axis square;
+view([32,16]);
+%%
+%%
+%2D interface with two modes. xy and xz
+%THe prior is uniform. p(uh) = 1 for uh
+dtheta = 0.4;
[…]

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/Numerical_Fisher_3D_Id_CONF.m

@@ -1,0 +1,177 @@
+clear all; clc; close all;
+% close all;
+%%
+global num_modes ng nd xg xr sig;
+ng = 2;
+nd = 3;
+num_modes = 3;
+% xg = [rand(1,ng)*4 - 2;rand(1,ng)* 4- 2; rand(1,ng)*8 - 4] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+xg = [randsample(-2:2, ng); rand(1,ng)*4 - 2; randsample(-4:4, ng)] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+% xg = [2.345585086756016,  -0.654414913243983,   3.345585086756016;
+%    0.068458668712525,  -0.931541331287475,   2.068458668712525;
+%   -2.389203961866748,   1.610796038133252,  -3.389203961866748;];
+% xg= [-3, 0, 0.01;
+%     -1, 0.5, 0;
+%     3, -0.2, 0.01;
+%     1, 0.1, -0.01]';
+% xg = [0.45, -0.438, 0.23;
+%       -0.45, -0.330, 0.2;
+%       0.1, -0.45, 0.3]';
+xg = [0.45, -0.438, 0.23;
+      -0.45, -0.330, 0.2;
+      0.1, -0.45, 0.3]';
+% xr = [0.2, -0.1, 0.3]';
+% xr = [0.405, -0.128, 0.287]';
+xr =[-0.083077724768694, %robot pos at traj time stamp 501; 
+  -0.649295673560288,
+   0.288730342677929]';
+
+% xr = [0,0,0]';
+uh = [-1,0,0]';
+sig = 0.01;
+% 1.0e+08 *
+% 
+%    1.615703233093601
+%    0.000000001561469
+%    0.000000000000063
+%%
+
+%PLOT GOALS AND ROBOT and UH
+figure;
+scatter3(xg(1,1:ng), xg(2,1:ng), xg(3,1:ng), 180, 'k', 'filled'); grid on; hold on;
+xlabel('X'); ylabel('Y'); zlabel('Z');
+scatter3(xr(1), xr(2), xr(3), 140, 'r', 'filled');
+quiver3(xr(1), xr(2), xr(3), uh(1), uh(2), uh(3), 0, 'LineWidth', 2, 'MaxHeadSize', 2); %current robot velocity arrow
[…]

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/Numerical_Fisher_3D_Id_DFT.m

@@ -1,0 +1,260 @@
+% clear all; clc; close all;
+% close all;
+%%
+global num_modes ng nd xg xr sig delta_t;
+ng = 2;
+nd = 3;
+num_modes = 3;
+% xg = [rand(1,ng)*4 - 2;rand(1,ng)* 4- 2; rand(1,ng)*8 - 4] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+% xg = [rand(1,ng)*8 - 4; rand(1,ng)* 8 - 4 ; rand(1,ng)*8 - 4] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+% xg = [2.345585086756016,  -0.654414913243983,   3.345585086756016;
+%    0.068458668712525,  -0.931541331287475,   2.068458668712525;
+%   -2.389203961866748,   1.610796038133252,  -3.389203961866748;];
+% xg= [-3, 0, 0.01;
+%     -1, 0.5, 0;
+%     3, -0.2, 0.01;
+%     1, 0.1, -0.01]';
+% xg = circshift(xg, 1);
+% xg = circshift(xg, 1);
+% xg = [0.45, -0.438, 0.23;
+%       -0.45, -0.330, 0.2;
+%       0.1, -0.45, 0.3]';
+% xg = [0.45, -0.438, 0.23;
+%       -0.45, -0.330, 0.2;
+%       0.1, -0.45, 0.3]';
+% xr = [0.2, -0.1, 0.3]';
+% xr = [0.405, -0.128, 0.287]';
+xg= [3, -3, 3;
+    3, 3, 3;
+    3, 3, -3;
+    3, -3, -3]';
+% xr =[-0.083077724768694, %robot pos at traj time stamp 501; 
+%   -0.649295673560288,
+%    0.288730342677929]';
+
+xr = [0,0,0];
+uh = [-1,0,0]';
+sig = 0.01;
+delta_t = 0.1;
+%%
+
+%PLOT GOALS AND ROBOT and UH
+figure;
+scatter3(xg(1,1:ng), xg(2,1:ng), xg(3,1:ng), 180, 'k', 'filled'); grid on; hold on;
+xlabel('X'); ylabel('Y'); zlabel('Z');
+scatter3(xr(1), xr(2), xr(3), 140, 'r', 'filled');
[…]

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/Simulate_Robot.m

@@ -1,0 +1,123 @@
+clear all; clc; close all;
+
+%%
+global num_modes ng nd xg xr sig delta_t;
+ng = 2;
+nd = 3;
+num_modes = 3;
+% xg = [rand(1,ng)*4 - 2;rand(1,ng)* 4- 2; rand(1,ng)*8 - 4] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+% xg = [randsample(-1:1, ng); -rand(1,ng)*2; randsample(-1:1, ng)] + rand(nd,1)*0.2 - rand(nd,1)*0.2; %random goal positions. These will be treated as fixed parameters.
+% xg = [2.345585086756016,  -0.654414913243983,   3.345585086756016;
+%    0.068458668712525,  -0.931541331287475,   2.068458668712525;
+%   -2.389203961866748,   1.610796038133252,  -3.389203961866748;];
+% xg= [-3, 0, 0.01;
+%     -1, 0.5, 0;
+%     3, -0.2, 0.01;
+%     1, 0.1, -0.01]';
+xg = [0.45, -0.438, 0.23;
+      -0.45, -0.330, 0.2;
+      0.1, -0.45, 0.3]';
+% xr = [0.2, -0.1, 0.3]';
+xr = [0.405, -0.128, 0.287]';
+uh = [-1,0,0]';
+sig = 0.1;
+%%
+
+%PLOT GOALS AND ROBOT and UH
+% figure;
+% scatter3(xg(1,1:ng), xg(2,1:ng), xg(3,1:ng), 180, 'k', 'filled'); grid on; hold on;
+% xlabel('X'); ylabel('Y'); zlabel('Z');
+% scatter3(xr(1), xr(2), xr(3), 140, 'r', 'filled');
+% quiver3(xr(1), xr(2), xr(3), uh(1), uh(2), uh(3), 0, 'LineWidth', 2, 'MaxHeadSize', 2); %current robot velocity arrow
+% for i=1:ng %vectors connecting robot and goals.
+%     quiver3(xr(1), xr(2), xr(3), xg(1,i) - xr(1), xg(2,i) - xr(2), xg(3,i) - xr(3), 'LineWidth', 1.5, 'LineStyle', '-.');
+% end
+% xrange = 0.5*[-2,2]; %set axis limits
+% yrange = 0.5*[-2,2];
+% zrange = 0.5*[-2,2];
[…]

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/compute_entropy.m

@@ -1,0 +1,39 @@
+function [ Upsilon ] = compute_entropy(uh, varargin)
+%UNTITLED4 Summary of this function goes here
+%   Detailed explanation goes here
+global delta_t ng;
+intent_type = varargin{1};
+curr_x = varargin{2};
+if strcmp(intent_type, 'conf')
+    pg = compute_conf(uh, curr_x); %confidence function does not care of what the current pg is and therefore ignores pg0
+elseif strcmp(intent_type, 'dft')
+    %For every 'uh' let the pg system evolve from the 'current' p(g). At
+    %the time of intervention store the p(g) away in a variable that will
+    %be used for each iteration. And the resulting p(g) is the one for which the entropy will be calculated. 
+    
+    pg0 = varargin{3}; %pg at the time of optimal mode computation
+    projection_time = 1; %let the DS evolve for projection_time seconds
+    t_stamps = 0:delta_t:projection_time; %time stamps for projection. 
+    pgs_project = zeros(ng, length(t_stamps)); %array to store evolved probabilities. 
+    pgs_project(:, 1) = pg0; %init pg0
+    for i=1:length(t_stamps)-1
+        pgs_project(:, i+1) = compute_p_of_g_dft(uh, curr_x, pgs_project(:, i));
+        curr_x = sim_dyn(curr_x, uh);
+    end
+    pg = pgs_project(:, end); %pg after the projected DS evolution. 
+elseif strcmp(intent_type, 'bayes')
+    pg0 = varargin{3};
+    projection_time = 1;
+    t_stamps = 0:delta_t:projection_time; %time stamps for projection. 
+    pgs_project = zeros(ng, length(t_stamps)); %array to store evolved probabilities.
+    pgs_project(:, 1) = pg0; %init pg0 at the time of assistance. 
+    for i=1:length(t_stamps)-1
+        pgs_project(:, i+1) = compute_bayes(uh, curr_x, pgs_project(:, i));
+        curr_x = sim_dyn(curr_x, uh);
+    end
+    pg = pgs_project(:, end);
+end
+% pg = compute_p_of_g(uh, xr);
+Upsilon = nansum(pg.*log2(pg));
+end
+

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/compute_upsilon_pg.m

@@ -1,0 +1,6 @@
+function [ Upsilon ] = compute_upsilon_pg( pg )
+%UNTITLED4 Summary of this function goes here
+%   Detailed explanation goes here
+Upsilon = nansum(pg.*log2(pg));
+end
+

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/computepg.m

@@ -1,0 +1,25 @@
+function pg = computepg( uh, xr )
+%UNTITLED3 Summary of this function goes here
+%   Detailed explanation goes here
+global ng xg;
+if size(xr, 2) > 1
+    xr = xr';
+end
+pg = (1/ng)*zeros(ng, 1);
+for i=1:ng
+    normxs = (xg(:, i) - xr)/(norm((xg(:, i) - xr)) + realmin); %ith goal position;
+    normuh = uh/(norm(uh) +realmin); %add realmin to avoid divide by zero errors. 
+    costh = dot(normxs, normuh);
+%     if costh < 0
+%         pg(i) = 0;
+%         pg(i) = (1 + dot(normxs, normuh))/2; %This is where ANY kind of method to generate P(g) can be used. 
+% 
+%     else
+%         pg(i) = (1 + dot(normxs, normuh))/2; %This is where ANY kind of method to generate P(g) can be used. 
+%     end
+    pg(i) = (1 + dot(normxs, normuh))/2;
+end
+pg = pg/sum(pg);
+
+end
+

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/func.m

@@ -1,0 +1,4 @@
+function y = func(x ,p1, p2)
+     x1 = x(1); x2 = x(2); x3 = x(3);
+     y = (p1+p2)*(x1)^4 + (x2)^3 + x3^3;
+end

### 2018-01-02 Code/Numerical_Fisher/FisherInfo/sim_dyn.m

@@ -1,0 +1,4 @@
+function xr_new = sim_dyn(xr, uh) %all args are considered to be column vectors. 
+    global delta_t;    
+    xr_new = xr + uh.*delta_t + normrnd(0, 0.000, length(xr), 1); %add stochasticity to the dynamics. 
+end

### 2018-01-02 Code/Numerical_Fisher/Robotics_Library_Matlab/AxisAng_Quat.m

@@ -1,0 +1,33 @@
+function [ q ] = AxisAng_Quat( r, varargin)
+%UNTITLED Summary of this function goes here
+%   Detailed explanation goes here
+
+% Usage
+% Input - r = exponential coordinates for rotation r = w*theta. Varargin is
+% a flag used to change the output representation from [x,y,z,w] to [w,x,y,z]
+% Output - Unit Quaternion representing the same rotations = [ qx, qy,
+% qz, qw]
+
+%Example
+% Input - r = [pi/2, 0, 0]
+% Output q = [0.707, 0.707, 0, 0]
+
+q = [];
+if(size(r,2) > 1) %Make it a column vector if a row vector
+    r = r';
+end
+if(size(r,2) > 1) % if a matrix
+    disp('r is not a vector');
+elseif(size(r, 1) ~= 3)
+    disp('r is not a 3d vector');
+else
+    [w,theta] = AxisAng3(r);
+    qw = cos(theta/2);
+    qv = sin(theta/2)*w;
+    q = [qv;qw];
+    if length(varargin) == 1
+        q = circshift(q, 1);
+    end
+end
+end
+

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/R2/SimulateTraj_R2_With_Blending.m

@@ -1,0 +1,332 @@
+% clear all; close all; clc;
+
+%% SPAWN GOAL CONFIGURATION AND ROBOT POSITION. RANDOMLY IN THE WORKSPACE. 
+
+%Define workspace limits. All in metres. 
+xrange = [-0.5, 0.5];
+yrange = [-0.5, 0.5];
+
+global cm num_modes ng nd xg xr sig delta_t conf_thresh conf_max alpha_max;
+
+%workspace parameters
+max_ng = 6;
+% ng = 4; %num of goals
+ng = datasample(2:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
+nd = 2; %num of dimensions. by definition R^2
+cm = {1,2}; %only control mode settings. 
+num_modes = length(cm); %or 1 depending on whether the modes are [x, y] or [{x,y}]
+
+%spawn random goals and random robot positoin
+xg = [rand(1,ng)*range(xrange) + xrange(1); rand(1,ng)*range(yrange) + yrange(1)]; %random goal positions. These will be treated as fixed parameters.
+xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1)];
+xr_true = xr; %store away random position in a variable for reuse.
+
+
+%disambiguation related params
+sig = 0.01; %For Fisher information
+delta_t = 0.1; %For compute projections. 
+
+%arbitrartion function parameters - Fixed parameters for shared control. 
+conf_thresh = (1.2/ng);
+conf_max = (1.4/ng);
+alpha_max = 0.7;
+
+%% PLOT GOALS AND CURRENT ROBOT POSITION. 
+
+% figure;
+% scatter(xg(1,1:ng), xg(2,1:ng), 180, 'k', 'filled'); grid on; hold on;
+% scatter(xr(1), xr(2), 140, 'r', 'filled');
+% offset = [-0.1, 0.1];
+% line(xrange+offset, [0,0], 'Color', 'r'); %draw x and y axes.
+% line([0,0], yrange+offset, 'Color', 'g');
+% axis([xrange + offset, yrange + offset]);
+% axis square;
+
+%% START SIMULATING A HUMAN CONTROLLING THE ROBOT FROM THE CURRENT POSITION ALWAYS IN THE DISAMBIGUATING MODE, TOWARDS A RANDOMLY PICKED GOAL FROM 
+%% THE LIST OF GOALS.
+
+% generate random user goal index. change color to magenta. 
[…]

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/R2/compute_bayes_R2.m

@@ -1,0 +1,37 @@
+function [ posterior ] = compute_bayes_R2( uh, xr, prior )
+%UNTITLED Summary of this function goes here
+%   Detailed explanation goes here
+    global ng
+    ll = likelihood_func(uh, xr);
+    prior = prior + 0.01*rand(ng, 1); %to avoid collapse of posterior. 
+    prior = prior/sum(prior);
+    posterior = ll.*prior;
+    posterior = posterior/sum(posterior); %make sure that the posterior is always normalized. 
+end
+
+function likelihood = likelihood_func(uh, xr)
+    global ng xg;
+    likelihood = zeros(ng, 1);
+    if norm(uh)~=0
+        uh = uh/norm(uh);
+    else
+        likelihood = ones(ng, 1);
+        return;
+    end
+    for i=1:ng
+        dir_vec = xg(:, i) - xr; %vector joining the robot position and the goal_x. 
+        dir_vec = dir_vec/norm(dir_vec); %as long as xr is not xg, this would be nonzero;
+        likelihood(i) = p_of_u_given_g(uh, dir_vec);
+    end
+end
+
+function [q] = p_of_u_given_g(uh, dir_vec) %assumes that the uh that is expected to see for a goal is the one which is directly pointing at it. 
+%     q = prob(uh(1) - dir_vec(1))*prob(uh(2) - dir_vec(2))*prob(uh(3) - dir_vec(3)); %p(ux, uy, uz) = p(ux)p(uy)p(uz);
+    ang = acos(round(dot(uh, dir_vec), 5));
+    q = prob(ang);
+end
+
+function p = prob(a) %zero mean gaussian, 
+    sigma = pi/2; %for the time being use this std dev
+    p = (1/sqrt(2*pi*sigma^2))*exp((-1/2.0)*(a^2/sigma^2));
+end

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/R2/compute_projected_entropy_R2.m

@@ -1,0 +1,9 @@
+function [ Upsilon ] = compute_projected_entropy_R2( uh, varargin )
+%UNTITLED8 Summary of this function goes here
+%   Detailed explanation goes here
+projection_time = 1;
+projected_pg = compute_pg_projection_R2(uh, projection_time, varargin{:});
+Upsilon = compute_pg_entropy(projected_pg);
+
+end
+

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/R3/SimulateTraj_R3_With_Blending.m

@@ -1,0 +1,331 @@
+% clear all; close all; clc;
+%% 
+%workspace limits
+xrange = [-0.5, 0.5];
+yrange = [-0.5, 0.5];
+zrange = [-0.5, 0.5];
+
+%global variables. 
+global num_modes cm ng nd xg xr sig delta_t conf_thresh conf_max alpha_max;
+
+%workspace params.
+% ng = 3; %num of goals
+max_ng = 6;
+% ng = 4; %num of goals
+ng = datasample(2:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
+nd = 3; %num of dimensions. by definition R^3
+cm_options = {{1,2,3}, {[1,2], 3}};
+max_nm = length(cm_options);
+cm = cm_options{datasample(1:max_nm, 1)};
+% cm = {1,2,3}; %{1,2,3}, %{[1,3], 2} %{[2,3], 1};
+num_modes = length(cm); %
+
+%spawn random goals and robot position. 
+xg = [rand(1,ng)*range(xrange) + xrange(1); rand(1,ng)*range(yrange) + yrange(1); rand(1,ng)*range(zrange) + zrange(1)]; %random goal positions. These will be treated as fixed parameters.
+xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1); rand(1,1)*range(zrange) + zrange(1)];
+xr_true = xr;
+
+%disamb parameters.
+sig = 0.01; %For Fisher information
+delta_t = 0.1; %For compute projections. 
+
+%arbitration function parameters
+conf_thresh = (1.2/ng);
+conf_max = (1.4/ng);
+alpha_max = 0.7;
+
+%% plot the goals and robot
+% figure;
+% scatter3(xg(1,1:ng), xg(2,1:ng), xg(3,1:ng), 230, 'k', 'filled'); grid on; hold on;
+% xlabel('X'); ylabel('Y'); zlabel('Z');
+% scatter3(xr(1), xr(2), xr(3), 230, 'r', 'filled');
+% offset = [-0.3, 0.3];
+% line(xrange+offset, [0,0], [0,0], 'Color', 'r', 'LineWidth', 1.5); %draw x and y axes.
+% line([0,0], yrange+offset, [0,0], 'Color', 'g','LineWidth', 1.5);
+% line([0,0], [0,0], zrange+offset, 'Color', 'b','LineWidth', 1.5);
[…]

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/R3/compute_p_of_g_dft_R3.m

@@ -1,0 +1,38 @@
+function [pg] = compute_p_of_g_dft_R3( uh, xr, pg )
+%UNTITLED3 Summary of this function goes here
+%   Detailed explanation goes here
+    global ng delta_t;
+    tau = 5;
+    h = 1/ng;
+    %%%%%%%%%%%%%%%%
+    %only for ad mode
+%     uh = aeval(uh);
+    %%%%%%%%%%%%%%%%%%
+    curr_pg = compute_curr_input_R3(uh, xr);
+    lambda = 0*ones(ng,ng);
+    lambda(1: ng+1: ng*ng) = 0;
+    lambda = 1*eye(ng) + lambda;
+    dpgdt = (-1/tau)*eye(ng)*pg ++ (h/tau)*ones(ng,1) + lambda*sigmoid(curr_pg); %ODE - Dynamics neural field. 
+    pg = pg + dpgdt*delta_t; %Euler integration;
+    pg(pg <= 0) = realmin;
+    pg = pg/sum(pg); %normalize, so that the inidividual values are alwyas between 0 and 1. 
+end
+
+function out = sigmoid(u)
+    out = 1./(1 + exp(-u));
+    out = out - 0.5;
+end
+
+function curr_input = compute_curr_input_R3(uh, xr)
+    global ng xg;
+    if size(xr, 2) > 1
+        xr = xr';
+    end
+    curr_input = zeros(ng, 1);
+    for i=1:ng %directedness based confidence function. 
+        normxs = (xg(:, i) - xr)/(norm((xg(:, i) - xr)) + realmin); %ith goal position;
+        normuh = uh/(norm(uh) +realmin); %add realmin to avoid divide by zero errors. 
+        costh = dot(normxs, normuh);
+        curr_input(i) = (1 + costh)/2;
+    end
+end

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/R3/compute_pg_entropy.m

@@ -1,0 +1,6 @@
+function [ Upsilon ] = compute_pg_entropy( pg )
+%UNTITLED4 Summary of this function goes here
+%   Detailed explanation goes here
+Upsilon = nansum(pg.*log2(pg));
+end
+

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/SE2/SimulateTraj_SE2_With_Blending.m

@@ -1,0 +1,373 @@
+% clear all; close all; clc;
+
+
+%% SPAWN GOAL CONFIGURATION AND ROBOT POSITION. RANDOMLY IN THE WORKSPACE. 
+
+%Define workspace limits. All in metres. 
+xrange = [-0.5, 0.5];
+yrange = [-0.5, 0.5];
+th_range = [0, 2*pi];
+
+global num_modes cm ng nd xg xr sig delta_t conf_thresh conf_max alpha_max;
+max_ng = 6;
+% ng = 4; %num of goals
+ng = datasample(2:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
+nd = 3; %num of dimensions. by definition R^3
+cm_options = {{1,2,3}, {[1,2], 3}};
+max_nm = length(cm_options);
+cm = cm_options{datasample(1:max_nm, 1)};
+num_modes = length(cm);
+
+xg = [rand(1,ng)*range(xrange) + xrange(1); rand(1,ng)*range(yrange) + yrange(1); rand(1,ng)*range(th_range) + th_range(1)]; %random goal positions. These will be treated as fixed parameters.
+xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1); rand(1,1)*range(th_range) + th_range(1)];
+xr_true = xr;
+
+sig = 0.01; %For Fisher information
+delta_t = 0.1; %For compute projections. 
+
+%arbitration function parameters
+conf_thresh = (1.2/ng);
+conf_max = (1.4/ng);
+alpha_max = 0.7;
+
+%% plot positions and body rotation axis. 
+% figure;
+% scatter(xg(1,1:ng), xg(2,1:ng), 230, 'k', 'filled'); grid on; hold on;
+% scatter(xr(1), xr(2), 140, 'r', 'filled');
+% % for i=1:ng %vectors connecting robot and goals.
+% %     quiver(xr(1), xr(2), xg(1,i) - xr(1), xg(2,i) - xr(2), 'LineWidth', 1.5, 'LineStyle', '-.');
+% % end
+% offset = [-0.1, 0.1];
+% line(xrange+offset, [0,0], 'Color', 'r'); %draw x and y axes.
+% line([0,0], yrange+offset, 'Color', 'g');
+% axis([xrange + offset, yrange + offset]);
+% axis square;
+% 
+% % draw orientations:
+% l_axis = 0.05; % length of axis 
[…]

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/SE3/compute_p_of_g_dft_SE3.m

@@ -1,0 +1,75 @@
+function [pg] = compute_p_of_g_dft_SE3( uh, xr_T, pg )
+%UNTITLED3 Summary of this function goes here
+%   Detailed explanation goes here
+    global ng delta_t;
+    tau = 5;
+    h = 1/ng;
+    %%%%%%%%%%%%%%%%
+    %only for ad mode
+%     uh = aeval(uh);
+    %%%%%%%%%%%%%%%%%%
+    curr_pg = compute_curr_input_SE3(uh, xr_T);
+    lambda = 0*ones(ng,ng);
+    lambda(1: ng+1: ng*ng) = 0;
+    lambda = 1*eye(ng) + lambda;
+    dpgdt = (-1/tau)*eye(ng)*pg ++ (h/tau)*ones(ng,1) + lambda*sigmoid(curr_pg); %ODE - Dynamics neural field. 
+    pg = pg + dpgdt*delta_t; %Euler integration;
+    pg(pg <=0) = realmin;
+    pg = pg/sum(pg); %normalize, so that the inidividual values are alwyas between 0 and 1. 
+end
+
+function out = sigmoid(u)
+    out = 1./(1 + exp(-u));
+    out = out - 0.5;
+end
+
+function curr_input = compute_curr_input_SE3(uh, xr_T)
+    global ng xg_T;
+    xr_pos = xr_T(1:3, 4); %robot position
+
+    curr_input = zeros(ng, 1); %initialize
+    if norm(uh(1:3)) > 0.000001 % if translation uh is nonzero. directedness
+        for i=1:ng
+            curr_gT = xg_T(:,:,i);
+            xg_pos = curr_gT(1:3, 4);
+            normxs = (xg_pos - xr_pos)/(norm(xg_pos - xr_pos) + realmin);
+            normuh = uh(1:3)/(norm(uh(1:3)) + realmin);
+            costh = dot(normxs, normuh);
+            curr_input(i) = (1 + costh)/2;
+        end
+    end
+    if norm(uh(4:6)) > 0.000001 %rotational agreement. 
+        for i=1:ng
+            goal_vel = generate_R_autonomy(xg_T(:,:,i), xr_T);
+            if norm(goal_vel(4:6)) > 0.0001
+                rot_vel = goal_vel(4:6);
+                rot_align = dot(uh(4:6), rot_vel)/(norm(uh(4:6)) * norm(rot_vel) +  realmin);
+                rot_align = (1 + rot_align)*0.5;
[…]

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/SE3/compute_projected_entropy_SE3.m

@@ -1,0 +1,12 @@
+function [ Upsilon ] = compute_projected_entropy_SE3( uh, varargin )
+%UNTITLED8 Summary of this function goes here
+%   Detailed explanation goes here
+
+projection_time = 1;
+projected_pg = compute_pg_projection_SE3(uh, projection_time, varargin{:});
+% disp(projected_pg);
+Upsilon = compute_pg_entropy(projected_pg);
+% disp(Upsilon);
+
+end
+

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/Utils/compute_best_mode.m

@@ -1,0 +1,26 @@
+function best_mode = compute_best_mode(EID_AR)
+     %threshold within which two modes are considered to be disambiguate equally. 
+    global cm;
+    eq_modes = compute_equivalent_modes(EID_AR); %eq modes contain the indices of the cm that arae equivalent mode. 
+    if ~isempty(eq_modes) %there are equivalent modes. 
+        if length(eq_modes) == 1 &&  length(eq_modes{1}) == length(cm)
+            fprintf('All modes disambiguate equally. Dont change current mode \n');
+            best_mode = -1;
+        elseif length(eq_modes) >= 1
+            best_mode = find(EID_AR == max(EID_AR));
+            for i=1:length(eq_modes)
+                if ~isempty(find(best_mode == eq_modes{i}, 1))
+                    best_mode = eq_modes{i};
+                    for j=1:length(eq_modes{i})
+                        fprintf('Mode %d\n',eq_modes{i}(j));
+                    end
+                    break;
+                end
+            end
+            fprintf('Control mode %d disambiguates best\n', best_mode);
+        end
+    else
+        best_mode = find(EID_AR == max(EID_AR));
+        fprintf('The Control mode %d disambiguates best - last\n', best_mode);
+    end
+end

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/Utils/plot_script.m

@@ -1,0 +1,62 @@
+figure; 
+subplot(3,4,1);
+plot(pgs_ENT','LineWidth', 1.5); grid on;
+ylim([0.0, 1.0]);
+title('ENTROPY PG'); xlabel('Time Steps'); ylabel('PG');
+
+subplot(3,4,2);
+plot(pgs_FI', 'LineWidth', 1.5); grid on;
+title('FI PG'); xlabel('Time Steps'); ylabel('PG')
+ylim([0.0, 1.0]);
+
+subplot(3,4,3);
+plot(pgs_DISAMB', 'LineWidth', 1.5); grid on;
+title('DISAMB PG'); xlabel('Time Steps'); ylabel('PG')
+ylim([0.0, 1.0]);
+
+subplot(3,4,4);
+plot(pgs_POT', 'LineWidth', 1.5); grid on;
+title('POT PG'); xlabel('Time Steps'); ylabel('PG')
+ylim([0.0, 1.0]);
+
+subplot(3,4,5);
+scatter(1:length(optimal_modes_ENT), optimal_modes_ENT, 'r', 'filled'); 
+title('ENTROPY MODES');
+% 
+subplot(3,4,6);
+scatter(1:length(optimal_modes_FI), optimal_modes_FI, 'b', 'filled');
+title('FI MODES');
+
+subplot(3,4,7);
+scatter(1:length(optimal_modes_DISAMB), optimal_modes_DISAMB, 'g', 'filled');
+title('DISAMB MODES');
+
+subplot(3,4,8);
+scatter(1:length(optimal_modes_POT), optimal_modes_POT, 'k', 'filled');
+title('POT MODES');
+%%
+color_scheme = {'b', 'r', 'y', 'pur', 'green', 'm', 'k'};
+fprintf('THE RANDOM GOAL IS %d and COLOR is %s\n', random_goal_index, color_scheme{random_goal_index});
+fprintf('THE NUMBER OF MODES SWITCHES POT %d, ENT %d, FI %d and DISAMB %d\n',sum(abs(diff(optimal_modes_POT))), sum(abs(diff(optimal_modes_ENT))), sum(abs(diff(optimal_modes_FI))), sum(abs(diff(optimal_modes_DISAMB))));
+%b,r,y, purple, green
+
+subplot(3,4,9);
[…]

### 2018-01-02 Code/Numerical_Fisher/SimulationCode/data_analysis_test.m

@@ -1,0 +1,144 @@
+clear all; clc; close all;
+
+%%
+spaceList = {'R22', 'R33', 'SE2', 'SE3'}; %R2, R3, SE2, SE3
+condList = {'POT', 'ENT', 'FI', 'DISAMB'};
+delta_t = 0.1;
+total_subjects = 50;
+total_time_all = zeros(total_subjects, length(condList), length(spaceList)); %by deciding how soon does the chatter begin?
+initial_alpha = -999*ones(total_subjects, length(condList), length(spaceList)); %initialize the alpha time as big negative. If it stays like this it means that the assistance was never triggered. 
+percentage_alpha = zeros(total_subjects, length(spaceList)); %for this the chattering has to be detected and snipped. 
+final_dist_to_goal = -999*ones(total_subjects, length(condList), length(spaceList)); %for all spaces. 
+final_angle_to_goal = -999*ones(total_subjects, length(condList), length(spaceList)); %only SE2 and SE3
+ng_array = zeros(total_subjects, length(spaceList)); %number of goals for each conditions. 
+
+for i=1:length(spaceList) %type of World
+    dirname = strcat(spaceList{i}, '_DATA');
+    fnames = dir(dirname);
+    numfids = length(fnames);
+    for k=3:3 + (total_subjects-1)  %50 samples from each WORLD. First two files in the directory are . and ..
+        n = fnames(k).name;
+        disp(n);
+        load(n);
+        
+%%  compute fraction of distance remaining to the goal. 
+        if i == 1 || i == 2
+            final_dist_to_goal(k, 1, i) = norm(traj_POT(:,end) - xg(:, random_goal_index))/norm(traj_POT(:, 1) - xg(:, random_goal_index));
+            final_dist_to_goal(k, 2, i) = norm(traj_ENT(:,end) - xg(:, random_goal_index))/norm(traj_ENT(:, 1) - xg(:, random_goal_index));
+            final_dist_to_goal(k, 3, i) = norm(traj_FI(:,end) - xg(:, random_goal_index))/norm(traj_FI(:, 1) - xg(:, random_goal_index));
[…]

### 2018-01-02 Code/Numerical_Fisher/dft.m

@@ -1,0 +1,39 @@
+% function dydt = dft(t,y,h, tau, c)
+% %UNTITLED3 Summary of this function goes here
+% %   Detailed explanation goes here
+% 
+% dydt = (1.0/tau)*(-y + h + inputs(t) + c*sigmoid(y));
+% end
+
+function dydt = dft(t,y,h,tau,c,ng)
+   dydt = zeros(ng,1);
+   inp = inputs(t, ng); %2 d array. containing 
+   lambda = -2*ones(ng,ng);
+   lambda(1: ng+1: ng*ng) = 0;
+   lambda = 4*eye(ng) + lambda;
+   dydt = (-1/tau)*eye(ng)*y + (h/tau)*ones(ng,1) + lambda*sigmoid(inp);
+end
+
+
+function out = inputs(t, ng)
+    if t < 1.0  || (t >= 6.0 && t < 10.0) || t >= 11.0 %control command has not been issued. 
+        out = zeros(ng, 1);
+    elseif t >= 1.0 && t < 3.0 %control command towards goal 1 and away from goal 2
+        out = [0.9, 0.05, 0.1, 0.1]';
+    elseif t >= 3.0 && t < 6.0
+        out = [0.05, 0.9, 0.01, 0.1]';
+%         out = zeros(ng, 1);
+    elseif t >=10.0 && t < 11
+         out = [0.1, 0.1, 0.9, 0.8]';
+%         out = zeros(ng, 1);
+    end
+%     out = zeros(ng, 1);
+%     fprintf('%f\t%f\n', out, t);
+end
+
+function out = sigmoid(u)
+    out = 1./(1 + exp(-u));
+    out = out - 0.5;
+%     out = out';
+%     fprintf('%f\n', out);
+end

### 2018-01-02 Code/Numerical_Fisher/num_grad.m

@@ -1,0 +1,47 @@
+% num_grad.m
+%
+% [df, NFV] = num_grad(func, X, NFV, h)
+%
+% Function to compute the numerical gradient of an arbitrary objective
+% function.
+%
+% Inputs:
+%	-> func: Function handle for which numerical derivative is to 
+%		be obtained.
+%	-> X: Point of interest about which derivative is to be
+%		obtained.
+%	-> NFV: Accumulator to keep track of number of function
+%		evaluations.
+%	-> h: Tolerance for differentiation.
+%
+% Outputs:
+%	-> df: Numerical derivative of function func (vector of size
+%		n=length(X)).
+%	-> NFV: Accumulator incremented by the number of function
+%		evaluations which have taken place.
+%
+% Created by: Brendan C. Wood
+% Created on: February 14, 2011
+%
+% Copyright (c) 2011, Brendan C. Wood <b.wood@unb.ca>
+%
+
+function [df] = num_grad(func, X, h)
+
+df = zeros(length(X), 1);
+
+% for each dimension of objective function
+for i=1:length(X)
+    % vary variable i by a small amount (left and right)
+    x1 = X;
+    x2 = X;
+    x1(i) = X(i) - h;
+    x2(i) = X(i) + h;
+    
+    % evaluate the objective function at the left and right points
+    y1 = func(x1);
+    y2 = func(x2);
+    
+    % calculate the slope (rise/run) for dimension i
+    df(i) = (y2 - y1) / (2*h);
+end

### 2018-01-02 Code/Numerical_Fisher/process_bag/process_bag.m

@@ -1,0 +1,19 @@
+function [u, t] = process_bag(bagfile)
+%UNTITLED2 Summary of this function goes here
+%   Detailed explanation goes here
+
+clear rosbag_wrapper;
+clear ros.Bag;
+bag = ros.Bag.load(bagfile);
+% bag.info()
+topic1 = '/control_input';
+[msgs, meta] = bag.readAll({topic1});
+u = zeros(3, length(meta));
+t = zeros(length(meta), 1);
+for i=1:length(meta)
+    u(:, i) = msgs{i}.data(1:3);
+    t(i) = meta{i}.time.time;
+end
+t = t - t(1);
+end
+

### 2018-01-02 Code/Sym_Fisher/FisherInfo/BetaDistribution.m

@@ -1,0 +1,30 @@
+clc; clear; close all; 
+
+x = 0:0.01:1;
+% a = 14.12; b = 7.76;
+% y = betapdf(x, a, b);
+% 
+% m = (a - 1)/(a + b -2);
+% var = (a*b)/(((a + b)^2)*(a + b + 1));
+% fprintf('The mode and variance are %f and %f\n', m, var);
+% plot(x, y, 'r'); grid on; hold on;
+
+m = 0.98;
+var = 0.001;
+
+syms a b m var;
+
+eq1 = (a - 1)/(a + b -2) == m;
+eq2 = (a*b)/(((a + b)^2)*(a + b + 1)) == var;
+
+[sola, solb] = solve(eq1, eq2, [a,b]);
+% fprintf('The shape params are %f and %f\n', sola, solb);
+a_list = eval(vpa(sola)); %evaluate symbolic solution.
+b_list = eval(vpa(solb));
+
+a = a_list(a_list > 1);
+b = b_list(b_list > 1);
+fprintf('The shape params are %f and %f\n', a, b);
+y = betapdf(x, real(a), real(b));
+plot(x, y, 'b'); grid on;
+

### 2018-01-02 Code/Sym_Fisher/FisherInfo/FIsherInfo_Entropy_UH_EID_3D.m

@@ -1,0 +1,232 @@
+%% 
+clear all; clc; close all;
+
+global num_modes;
+ng = 3; %number of goals. is a fixed parameter
+nd = 3; %dimensionality of the problem.
+num_modes = 3;
+sig_t = 0.1; %std deviation for the entropy measurement.
+xg_t = [randsample(-4:4, ng);randsample(-4:4, ng); randsample(-4:4, ng)] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+% xg_t= [-3, 0, 0.01;
+%     -1, 0.5, 0;
+%     3, -0.2, 0.01;
+%     1, 0.1, -0.01]';
+% xr_t = [randsample(-4:4, 1);randsample(-4:4, 1); randsample(-4:4, 1) ] + rand(nd,1) - rand(nd,1); %random current robot position. FIM would be evaluated at this robot position
+xr_t = [0,0,0]';
+uh_t = [1,0, 0]'; % user control command
+%%
+
+%PLOT GOALS AND ROBOT and UH
+figure;
+scatter3(xg_t(1,1:ng), xg_t(2,1:ng), xg_t(3,1:ng), 180, 'k', 'filled'); grid on; hold on;
+xlabel('X'); ylabel('Y'); zlabel('Z');
+scatter3(xr_t(1), xr_t(2), xr_t(3), 140, 'r', 'filled');
+quiver3(xr_t(1), xr_t(2), xr_t(3), uh_t(1), uh_t(2), uh_t(3), 0, 'LineWidth', 2, 'MaxHeadSize', 2); %current robot velocity arrow
+for i=1:ng %vectors connecting robot and goals.
+    quiver3(xr_t(1), xr_t(2), xr_t(3), xg_t(1,i) - xr_t(1), xg_t(2,i) - xr_t(2), xg_t(3,i) - xr_t(3), 'LineWidth', 1.5, 'LineStyle', '-.');
+end
+xrange = [-5,5]; %set axis limits
+yrange = [-5,5];
+zrange = [-5,5];
+line(xrange, [0,0], [0,0], 'Color', 'k', 'LineWidth', 1.5); %draw x and y axes.
+line([0,0], yrange, [0,0], 'Color', 'k','LineWidth', 1.5);
+line([0,0], [0,0], zrange, 'Color', 'k','LineWidth', 1.5);
+axis([xrange, yrange, zrange]);
+axis square;
[…]

### 2018-01-02 Code/Sym_Fisher/FisherInfo/FIsherInfo_Entropy_UH_EID_3D_2dInt.m

@@ -1,0 +1,280 @@
+%% 
+clear all; clc; close all;
+global num_modes;
+ng = 4; %number of goals. is a fixed parameter
+nd = 3; %dimensionality of the problem.
+num_modes = 2;
+sig_t = 0.1; %std deviation for the entropy measurement.
+% xg_t = [randsample(-4:4, ng);rand(1,ng)*4 - 2; randsample(1:4, ng)] + rand(nd,1) - rand(nd,1); %random goal positions. These will be treated as fixed parameters.
+xg_t= [3, -3, 3;
+    3,3, -3;
+    3, 3, 3;
+    3, -3, -3]';
+% xr_t = [randsample(-4:4, 1);randsample(-4:4, 1); randsample(-4:4, 1) ] + rand(nd,1) - rand(nd,1); %random current robot position. FIM would be evaluated at this robot position
+xr_t = [0,0,0]';
+uh_t = [1,0, 0]'; % user control command
+%%
+
+%PLOT GOALS AND ROBOT and UH
+figure;
+scatter3(xg_t(1,1:ng), xg_t(2,1:ng), xg_t(3,1:ng), 180, 'k', 'filled'); grid on; hold on;
+xlabel('X'); ylabel('Y'); zlabel('Z');
+scatter3(xr_t(1), xr_t(2), xr_t(3), 140, 'r', 'filled');
+quiver3(xr_t(1), xr_t(2), xr_t(3), uh_t(1), uh_t(2), uh_t(3), 0, 'LineWidth', 2, 'MaxHeadSize', 2); %current robot velocity arrow
+for i=1:ng %vectors connecting robot and goals.
+    quiver3(xr_t(1), xr_t(2), xr_t(3), xg_t(1,i) - xr_t(1), xg_t(2,i) - xr_t(2), xg_t(3,i) - xr_t(3), 'LineWidth', 1.5, 'LineStyle', '-.');
+end
+xrange = [-5,5]; %set axis limits
+yrange = [-5,5];
+zrange = [-5,5];
+line(xrange, [0,0], [0,0], 'Color', 'r', 'LineWidth', 3.5); %draw x and y axes.
+line([0,0], yrange, [0,0], 'Color', 'g','LineWidth', 3.5);
+line([0,0], [0,0], zrange, 'Color', 'b','LineWidth', 3.5);
+axis([xrange, yrange, zrange]);
+axis square;
+view([32,16]);
+
+%%
[…]

### 2018-01-02 Code/Sym_Fisher/FisherInfo/MLE_Tests.m

@@ -1,0 +1,20 @@
+clear; clc; close all;
+
+%Jay Myung MLE Tutorial. Likelihood Functions
+
+w = 0:0.01:1;
+
+w = w + (w == 0)*10^-5 - (w == 1)*10^-5;
+
+%for y = 7, n=10
+L = (factorial(10)/(factorial(7)*factorial(3))).*(w.^7).*((1 - w).^3);
+logL = log((factorial(10)/(factorial(7)*factorial(3)))) + 7*log(w) + 3*log(1 - w);
+% plot(w, L); grid on; 
+% figure;
+% plot(w, logL); grid on;
+
+syms w;
+
+L = (factorial(10)/(factorial(7)*factorial(3)))*(w^7)*((1 - w)^3);
+logL = log(L);
+score = diff(logL, w);

### 2018-01-02 Code/Sym_Fisher/FisherInfo/fisher_info_entropy.py

@@ -1,0 +1,53 @@
+from sympy import *
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+
+
+from IPython import embed
+
+class FisherInfo(object):
+    """docstring forFisherInfo."""
+    def __init__(self):
+        super(FisherInfo, self).__init__()
+        self.arg = arg
+        self.ng = 3 #number of goals.
+        self.nd = 2 #dimensionality of the problem
+        self.num_modes = 3 #number of control modes
+        self.sig_t = 0.1 # standard deviation for the measurement model
+
+        self.xg_t =  np.random.choice(np.arange(-3,3), size=(self.nd, self.ng)) + np.random.rand(self.nd, 1) - np.random.rand(self.nd, 1)
+        # self.xg_t = np.array([[-3, 3, 2], [3, 3, 4]]); # hardcoded goal position for ng = 3
+        self.xr_t =  np.random.choice(np.arange(-3,3), size=(self.nd, 1)) + np.random.rand(self.nd, 1) - np.random.rand(self.nd, 1)
+        self.xr_t = np.array([[1], [0]]); #hardcoded robot position
+        self.uh_t = np.array([[1], [0]]); #hardcoded control command
+
+        #Plot the goals.
+        fig, ax = plt.subplots()
+        ax.scatter(self.xg_t[0, :], self.xg_t[1, :], s=100)
+        ax.hold(True)
+        ax.scatter(self.xr_t[0,0], self.xr_t[1,0], s = 100, c='r')
+        ax.set_xlabel('X')
+        ax.set_ylabel('Y')
+        ax.set_title('Goal configuration')
+        ax.grid(True)
+        plt.show()
+
+        # ax.scatter()
+        embed()
+
+        #Symbolic variables. Vector of variables for 3D robot position and 3D control command.
+
+        self.xr = MatrixSymbol('xr', self.nd, 1)
+        self.uh = MatrixSymbol('uh', self.nd, 1)
+        self.sig = Symbol('sig')
+        self.normuh = self.uh
+
+
+
+    def compute_best_mode(self):
+        pass
+
+if __name__ == '__main__':
+    FI = FisherInfo()
+    # FI.compute()

### 2018-01-02 Code/Sym_Fisher/FisherInfo/measurement_model_tests.m

@@ -1,0 +1,5 @@
+clear all; clc; close all;
+
+% nG = 4; %number of goals;
+
+

### 2018-01-02 Code/Sym_Fisher/FisherInfo/plot_conf_surface.m

@@ -1,0 +1,13 @@
+
+uh = [0,-1];
+xg = [2,1];
+[x_xr, y_xr] = meshgrid(-5:0.5:5, -5:1:5);
+
+den = (sqrt((xg(1) - x_xr).^2 + (xg(2) - y_xr).^2))*(norm(uh));
+num = uh(1).*(xg(1) - x_xr) + uh(2).*(xg(2) - y_xr);
+costh = num./den;
+cg = (1 + costh)./2;
+surf(x_xr, y_xr, cg); hold on;
+scatter3(xg(1), xg(2), 0, 100, 'filled', 'k');
+xlabel('XPos');ylabel('YPos');zlabel('Confidence value');
+quiver3(0,0, 0, uh(1), uh(2), 0,'LineWidth', 2, 'MaxHeadSize', 2);

### 2018-01-02 Code/Sym_Fisher/FisherInfo/test.m

@@ -1,0 +1,9 @@
+F = scatteredInterpolant
+%the steps of tx and ty will allow you change smoothness
+tx = min(X):max(X);
+ty = mix(Y):max(Y);
+[qx,qy] = meshgrid(tx,ty);
+qz = F(qx,qy);
+mesh(qx,qy,qz);
+hold on;
+plot3(x,y,z,'o');

### 2018-01-02 Code/Sym_Fisher/UI_Tests/createSlidersAndButtons.m

@@ -1,0 +1,43 @@
+function createSlidersAndButtons
+%UNTITLED7 Summary of this function goes here
+%   Detailed explanation goes here
+sld1 = uicontrol('Style', 'slider',...
+    'Min',-5,'Max',5,'Value',0,...
+    'Position', [450 20 80 20],...
+    'Callback', @xr_z); 
+txt1 = uicontrol('Style','text',...
+    'Position',[525 20 40 20],...
+    'String','ZVal');
+
+sld2 = uicontrol('Style', 'slider',...
+    'Min',-5,'Max',5,'Value',0,...
+    'Position', [450 50 80 20],...
+    'Callback', @xr_y); 
+txt2 = uicontrol('Style','text',...
+    'Position',[525 50 40 20],...
+    'String','YVal');
+
+sld3 = uicontrol('Style', 'slider',...
+    'Min',-5,'Max',5,'Value',0,...
+    'Position', [450 80 80 20],...
+    'Callback', @xr_x); 
+txt3 = uicontrol('Style','text',...
+    'Position',[525 80 40 20],...
+    'String','XVal');
+btn = uicontrol('Style', 'pushbutton', 'String', 'Disamb',...
+    'Position', [20 40 120 20],...
+    'Callback', @set_rob_pos);       
+
+btn = uicontrol('Style', 'pushbutton', 'String', 'Resample Goals',...
+    'Position', [20 10 150 20],...
+    'Callback', @set_goal_pos);   
+
+popup = uicontrol('Style', 'popup',...
+           'String', {'2','3','4','5','6'},...
+           'Position', [20 340 100 50],...
+           'Callback', @set_num_goals); 
+txt3 = uicontrol('Style','text',...
+    'Position',[20 390 100 20],...
+    'String','NumGoals');
+end
+

### 2018-01-02 Code/Sym_Fisher/UI_Tests/plot_xr_xg.m

@@ -1,0 +1,9 @@
+function plot_xr_xg(xr_color)
+%UNTITLED8 Summary of this function goes here
+%   Detailed explanation goes here
+    global xr_t;
+    delete(findobj(gcf, 'type', 'Scatter'))
+    scatter3(xr_t(1), xr_t(2), xr_t(3), 100, xr_color, 'filled'); grid on; hold on;
+    plot_xgs;
+end
+

### 2018-01-02 Code/Sym_Fisher/UI_Tests/set_num_goals.m

@@ -1,0 +1,14 @@
+function set_num_goals( source, events )
+%UNTITLED11 Summary of this function goes here
+%   Detailed explanation goes here
+
+global ng;
+val = source.Value;
+maps = source.String;
+fprintf('The number of goals is %d\n', str2double(maps{val}));
+disp('In set num of goals. ');
+ng = str2double(maps{val});
+reset_sym_math;
+set_goal_pos(source, events);
+end
+

### 2018-01-02 Code/Sym_Fisher/UI_Tests/set_rob_pos.m

@@ -1,0 +1,9 @@
+function set_rob_pos(source, event)
+    global xr_t;
+    fprintf('New Robot position is %f, %f, %f\n', xr_t(1), xr_t(2), xr_t(3));
+%     plot_xr;
+    best_mode = compute_disamb;
+    colors = {[1,0,0], [0,1,0], [0,0,1], [1,1,0], [1,0,1], [0,1,1], [0.08,0.08,0.08]};
+    plot_xr_xg(colors{best_mode});
+end
+

### 2018-01-02 Code/Sym_Fisher/UI_Tests/xr_x.m

@@ -1,0 +1,8 @@
+function xr_x(source, event)
+    
+    global xr_t;
+    xr_t(1) = source.Value;
+%     fprintf('The X pos of robot is %f \n', xr_t(1));
+    plot_xr_xg([0.4, 0.4, 0.4]);
+end
+

### 2018-01-02 Code/Sym_Fisher/UI_Tests/xr_y.m

@@ -1,0 +1,8 @@
+function xr_y(source, event)
+    
+    global xr_t;
+    xr_t(2) = source.Value;
+%     fprintf('The Y pos of robot is %f \n', xr_t(2));
+    plot_xr_xg([0.4, 0.4, 0.4]);
+end
+

### 2018-01-02 Code/Sym_Fisher/UI_Tests/xr_z.m

@@ -1,0 +1,7 @@
+function xr_z(source, event)
+    global xr_t;
+    xr_t(3) = source.Value;
+%     fprintf('The X pos of robot is %f \n', xr_t(3));
+    plot_xr_xg([0.4, 0.4, 0.4]);
+end
+

### 2018-01-05 NewTexFile/GopinathArgall_RSS2018.tex
Commit from laptop

@@
 \begin{abstract}
-The abstract goes here.
+In this paper, we treat the problem of intent disambiguation in terms of information theoretic principles.
+The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions and provide appropriate types of assistance quickly, confidently and accurately.
+We propose two different control mode selection schemes for intent disambiguation using notions of entropy and Fisher information in the context of assistive robotic manipulation.
+The proposed algorithms characterize the disambiguation capabilities of different control modes by the forward projection of probability distributions over goals and computing the relevant information theoretic measures.
+Our previous exploratory pilot studies revealed that the success of the disambiguation system depends on a variety of factors and choice of parameters.
+In order to thoroughly investigate the impact of the choice of various parameters and components, we present extensive simulation results both for point-robots that reside in different spaces as well as on the simulated robotic arm.
+Our results indicate that with the disambiguation algorithm the robot is able to assist earlier during task execution.
+Furthermore, the goal inferences are more accurate when operating in the disambiguating modes.
 \end{abstract}
@@
 \section{Introduction}
-This demo file is intended to serve as a ``starter file" for the
-Robotics: Science and Systems conference papers produced under \LaTeX\
-using IEEEtran.cls version 1.7a and later.
+Assistive shared-control machines such as robotic arms and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result of spinal cord injuries or brain traumas.
+These machines can promote independence, enhance the quality of lives and revolutionize the way they interact with society.
+These machines help to extend the mobility and manipulation capabilities of individuals thereby helping them perform activities of daily living in a more effective manner.
+
+The efficacy of assistive machines rely on their ability to infer the users' needs and intentions and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately.
+Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, the users' are typically constrained to produce control commands that do not reveal the intent more expressively.
+Therefore, intent inference is a necessary and crucial component to ensure appropriate assistance.
+Specifically, in assistive robotic manipulation, often the first step of a task is to reach for and grasp discrete objects in the environment.
+Therefore in this context, intent inference can be cast as a problem of maintaining the probability distribution over all possible discrete goals (objects) in the workspace.
+
+Our insight is that the information contained in control command issued in certain control modes is more useful for accurate inference and thereby will help the robot in providing the appropriate kind of assistance.
+In this work, we rely on information theoretic principles to quantify the information regarding intent disambiguation contained in different control modes and select control modes that maximize intent disambiguation.
 
@@
 
-Section text here.
-
 \section{Mathematical Formalism}
+\subsection{Set Theoretic Treatment of Control Modes}
 \subsection{Disambiguation Schemes}
@@
 \subsection{Intent inference}
-\subsubsection{Dynamic Field Theory Based}
+\subsubsection{Dynamic Field Theory}
 \subsubsection{Bayesian Inference}
@@
 
-\section{RSS citations}
-
-Please make sure to include \verb!natbib.sty! and to use the
-\verb!plainnat.bst! bibliography style. \verb!natbib! provides additional
-citation commands, most usefully \verb!\citet!. For example, rather than the
-awkward construction
-
-{\small
-\begin{verbatim}
-\cite{kalman1960new} demonstrated...
-\end{verbatim}
-}
-
-\noindent
-rendered as ``\cite{kalman1960new} demonstrated...,''
-or the
-inconvenient
-
-{\small
-\begin{verbatim}
-Kalman \cite{kalman1960new} 
-demonstrated...
-\end{verbatim}
-}
-
-\noindent
-rendered as 
-``Kalman \cite{kalman1960new} demonstrated...'', 
-one can
-write
-
-{\small
-\begin{verbatim}
-\citet{kalman1960new} demonstrated... 
-\end{verbatim}
-}
-\noindent
-which renders as ``\citet{kalman1960new} demonstrated...'' and is 
-both easy to write and much easier to read.
-
-\subsection{RSS Hyperlinks}
-
-This year, we would like to use the ability of PDF viewers to interpret
-hyperlinks, specifically to allow each reference in the bibliography to be a
-link to an online version of the reference. 
-As an example, if you were to cite ``Passive Dynamic Walking''
-\cite{McGeer01041990}, the entry in the bibtex would read:
-
-{\small
-\begin{verbatim}
-@article{McGeer01041990,
-  author = {McGeer, Tad}, 
-  title = {\href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic Walking}}, 
-  volume = {9}, 
-  number = {2}, 
-  pages = {62-82}, 
-  year = {1990}, 
-  doi = {10.1177/027836499000900206}, 
-  URL = {http://ijr.sagepub.com/content/9/2/62.abstract}, 
-  eprint = {http://ijr.sagepub.com/content/9/2/62.full.pdf+html}, 
-  journal = {The International Journal of Robotics Research}
-}
-\end{verbatim}
-}
-\noindent
-and the entry in the compiled PDF would look like:
-
-\def\tmplabel#1{[#1]}
-
-\begin{enumerate}
-\item[\tmplabel{1}] Tad McGeer. \href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic
-Walking}. {\em The International Journal of Robotics Research}, 9(2):62--82,
-1990.
-\end{enumerate}
-%
-where the title of the article is a link that takes you to the article on IJRR's website.
-
-Linking cited articles will not always be possible, especially for
-older articles. There are also often several versions of papers
-online: authors are free to decide what to use as the link destination
-yet we strongly encourage to link to archival or publisher sites
-(such as IEEE Xplore or Sage Journals).  We encourage all authors to use this feature to
-the extent possible.
-
+\section{Results}
+\section{Discussion}
 \section{Conclusion}
-\label{sec:conclusion}
-
-The conclusion goes here.
+\section{References}
 

### 2018-01-05 Code/Numerical_Fisher/SimulationCode/R3/SimulateTraj_R3_With_Blending.m

@@ -55,7 +55,7 @@ random_goal = xg(:, random_goal_index);
 
 %%
 intent_types = {'dft', 'conf', 'bayes'};
-intent_type = intent_types{datasample(length(intent_types), 1)}; % or conf or bayes
+intent_type = intent_types{datasample(1:length(intent_types), 1)}; % or conf or bayes
 
 %% BASELINE
 total_time_steps = 120; %with delta_t of 0.1, this amounts to 10 seconds. We will assume that "mode switches" don't take time. 
@@ -71,7 +71,7 @@ traj_POT(:, 1) = xr;
 pgs_POT(:, 1) = (1/ng)*ones(ng, 1);%uniform probability to start off with. This is the true pg distribution during the course of the trajectory
 %internally projection
 current_optimal_mode_POT = 1;
-mode_comp_timesteps = 5;
+mode_comp_timesteps = 4;
 
 for i=1:total_time_steps-1
     curr_goal_index_POT = datasample(find(pgs_POT(:, i) == max(pgs_POT(:, i))), 1);

### 2018-01-05 Code/Numerical_Fisher/SimulationCode/SE2/SimulateTraj_SE2_With_Blending.m

@@ -58,10 +58,10 @@ random_goal = xg(:, random_goal_index);
 
 %%
 intent_types = {'dft', 'conf', 'bayes'};
-intent_type = intent_types{datasample(length(intent_types), 1)}; % or conf or bayes
+intent_type = intent_types{datasample(1:length(intent_types), 1)}; % or conf or bayes
 
 %% BASELINE
-total_time_steps = 100; %with delta_t of 0.1, this amounts to 10 seconds. We will assume that "mode switches" don't take time. 
+total_time_steps = 120; %with delta_t of 0.1, this amounts to 10 seconds. We will assume that "mode switches" don't take time. 
 pgs_POT = zeros(ng, total_time_steps);
 optimal_modes_POT = zeros(total_time_steps-1, 1);
 alpha_POT = zeros(total_time_steps-1, 1);
@@ -93,16 +93,20 @@ for i=1:total_time_steps-1
     end
     %gotta determine uh. Assumes human is executes the "straightest
     %possible motion in the current mode towards the specified goal". 
-    uh = generate_full_uh(random_goal, xr);
+    uh = generate_full_uh(random_goal, xr); 
     zero_dim = setdiff(1:nd,current_optimal_mode_POT);
     for jj=1:length(zero_dim)
         uh(zero_dim(jj)) = 0;
     end
     uh = 0.2*(uh./(abs(uh) + realmin));
+    
     ur = generate_autonomy(curr_goal_index_POT); %autonomy command in full 2D space toward what it thinks is the current goal
     alpha_POT(i) = alpha_from_confidence(pgs_POT(curr_goal_index_POT, i)); %linear belnding param
     blend_vel = (1-alpha_POT(i))*uh + alpha_POT(i)*ur; %blended vel
     uh_POT(:, i) = uh; ur_POT(:, i) = ur; blend_vel_POT(:, i) = blend_vel;
+    
+    %forward propragate belief based on one of the three intent inference
+    %mechanisms. 
     if strcmp(intent_type, 'dft')
         pgs_POT(:, i+1) = compute_p_of_g_dft_SE2(uh, xr, pgs_POT(:, i));
     elseif strcmp(intent_type, 'bayes')
@@ -110,8 +114,13 @@ for i=1:total_time_steps-1
     elseif strcmp(intent_type, 'conf')
         pgs_POT(:, i+1) = compute_conf_SE2(uh, xr);
[…]

### 2018-01-05 Code/Numerical_Fisher/SimulationCode/data_analysis_test.m

@@ -4,23 +4,28 @@ clear all; clc; close all;
 spaceList = {'R22', 'R33', 'SE2', 'SE3'}; %R2, R3, SE2, SE3
 condList = {'POT', 'ENT', 'FI', 'DISAMB'};
 delta_t = 0.1;
-total_subjects = 50;
+total_subjects = 400;
+
 total_time_all = zeros(total_subjects, length(condList), length(spaceList)); %by deciding how soon does the chatter begin?
 initial_alpha = -999*ones(total_subjects, length(condList), length(spaceList)); %initialize the alpha time as big negative. If it stays like this it means that the assistance was never triggered. 
-percentage_alpha = zeros(total_subjects, length(spaceList)); %for this the chattering has to be detected and snipped. 
+percentage_correct_inference = zeros(total_subjects, length(condList), length(spaceList));
+percentage_alpha = zeros(total_subjects, length(condList), length(spaceList)); %for this the chattering has to be detected and snipped. 
+
 final_dist_to_goal = -999*ones(total_subjects, length(condList), length(spaceList)); %for all spaces. 
 final_angle_to_goal = -999*ones(total_subjects, length(condList), length(spaceList)); %only SE2 and SE3
+
 ng_array = zeros(total_subjects, length(spaceList)); %number of goals for each conditions. 
+intent_type_array = cell(total_subjects, length(spaceList));
 
 for i=1:length(spaceList) %type of World
     dirname = strcat(spaceList{i}, '_DATA');
     fnames = dir(dirname);
     numfids = length(fnames);
-    for k=3:3 + (total_subjects-1)  %50 samples from each WORLD. First two files in the directory are . and ..
-        n = fnames(k).name;
+    for index=3:3 + (total_subjects-1)  %50 samples from each WORLD. First two files in the directory are . and ..
+        n = fnames(index).name;
         disp(n);
         load(n);
-        
+        k = index - 2;
 %%  compute fraction of distance remaining to the goal. 
         if i == 1 || i == 2
[…]

### 2018-01-05 Code/Numerical_Fisher/SimulationCode/script_simulate.m

@@ -1,13 +1,13 @@
 clear all; clc; close all;
 
-N = 300; %number of simulations
+N = 400; %number of simulations
 vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
 types = {'POT', 'ENT', 'FI', 'DISAMB'};
 %for R2 case
-for ii=1:0
+for ii=1:N
     %define global variables
    SimulateTraj_R2_With_Blending;
-   filename = strcat('R2_DATA/DATAR22_', num2str(ii), '.mat');
+   filename = strcat('R22_DATA/DATAR22_', num2str(ii), '.mat');
    save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
    for jj=1:length(vars)
         for kk=1:length(types)
@@ -15,20 +15,20 @@ for ii=1:0
         end
    end
    clear all; clc; close all;
-   N = 300; %number of simulations
+   N = 400; %number of simulations
    vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
    types = {'POT', 'ENT', 'FI', 'DISAMB'};
 end
 
 %% R3 simulation.
 
-N = 300; %number of simulations
+
 vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
 types = {'POT', 'ENT', 'FI', 'DISAMB'};
-for ii=1:0
+for ii=1:N
     %define global variables
    SimulateTraj_R3_With_Blending;
-   filename = strcat('R3_DATA/DATAR33_', num2str(ii), '.mat');
+   filename = strcat('R33_DATA/DATAR33_', num2str(ii), '.mat');
    save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
    for jj=1:length(vars)
         for kk=1:length(types)
@@ -37,17 +37,16 @@ for ii=1:0
    end
    
    clear all; clc; close all;
-   N = 300; %number of simulations
+   N = 400; %number of simulations
[…]

### 2018-01-16 NewTexFile/GopinathArgall_RSS2018.tex
Added KL DIV

@@
 \usepackage{pifont}
+\usepackage{algorithm, algorithmic}
 \newcommand{\argmax}{\arg\!\max}
@@
 \begin{abstract}
-In this paper, we treat the problem of intent disambiguation in terms of information theoretic principles.
-The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions and provide appropriate types of assistance quickly, confidently and accurately.
-We propose two different control mode selection schemes for intent disambiguation using notions of entropy and Fisher information in the context of assistive robotic manipulation.
+In this paper, we tackle the problem of intent disambiguation in terms of information theoretic principles.
+The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions and provide appropriate types of assistance quickly and accurately.
+We propose two different control mode selection schemes for intent disambiguation using notions of entropy and Fisher information for an assistive robotic manipulator.
 The proposed algorithms characterize the disambiguation capabilities of different control modes by the forward projection of probability distributions over goals and computing the relevant information theoretic measures.
 Our previous exploratory pilot studies revealed that the success of the disambiguation system depends on a variety of factors and choice of parameters.
-In order to thoroughly investigate the impact of the choice of various parameters and components, we present extensive simulation results both for point-robots that reside in different spaces as well as on the simulated robotic arm.
+In order to thoroughly investigate the impact of various components, we present results from an extensive simulation-based study both for point-robots that reside in different spaces as well as on the simulated robotic arm.
 Our results indicate that with the disambiguation algorithm the robot is able to assist earlier during task execution.
@@
 \section{Introduction}
-Assistive shared-control machines such as robotic arms and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result of spinal cord injuries or brain traumas.
+Assistive shared-control machines such as robotic arms, smart wheelchairs  and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result injuries to the central nervous system.
 These machines can promote independence, enhance the quality of lives and revolutionize the way they interact with society.
-These machines help to extend the mobility and manipulation capabilities of individuals thereby helping them perform activities of daily living in a more effective manner.
+They can also help to extend the mobility and manipulation capabilities of individuals thereby helping motor-impaired people perform activities of daily living in a more effective manner.
 
+An assistive robotic machine is typically controlled using a control interface.
+These interfaces are low-dimensional, low-bandwidth and discrete, and can operate only in subsets of the entire control space.
+These subsets are referred to as \textit{control modes}.
 The efficacy of assistive machines rely on their ability to infer the users' needs and intentions and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately.
-Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, the users' are typically constrained to produce control commands that do not reveal the intent more expressively.
-Therefore, intent inference is a necessary and crucial component to ensure appropriate assistance.
-Specifically, in assistive robotic manipulation, often the first step of a task is to reach for and grasp discrete objects in the environment.
-Therefore in this context, intent inference can be cast as a problem of maintaining the probability distribution over all possible discrete goals (objects) in the workspace.
+Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, the users are constrained to produce control commands that do not reveal the intent more expressively.
+In other words, these control interfaces act like filters that restrict the amount of information regarding intent that passes through.
+Sparsity and noise in these control commands make the inference task even harder, prompting the need for robust intent inference formalisms.
+In the context of assistive robotic manipulation, often the first step of a task is to reach for and grasp discrete objects in the environment.
+Therefore, intent inference can be cast as a problem of maintaining the probability distribution over all possible discrete goals (objects) in the workspace.
+Intent inference mechanisms typically rely on various environmental cues and task-relevant features such as robot and goal positions, human control commands and biometric measures for estimating the most probably goal.
+More the number of sensor modalities, it is likely that the inference becomes more accurate.
+However, due to cost considerations and user acceptance issues, we design our assistance add-ons to be as invisible as possible.
+Therefore, our system tries to infer intent primarily based on the information contained in the constrained control commands issues to the assistive machine.
 
-Our insight is that the information contained in control command issued in certain control modes is more useful for accurate inference and thereby will help the robot in providing the appropriate kind of assistance.
-In this work, we rely on information theoretic principles to quantify the information regarding intent disambiguation contained in different control modes and select control modes that maximize intent disambiguation.
+Our insight is that the information contained in control commands issued in certain control modes will clarify human's underlying intent unambiguously and is more useful for the robot to perform accurate intent inference.
+This, in turn will help the robot to appropriate kinds of assistance more effectively.
+In this paper, we tackle the problem intent disambiguation using information theoretic principles.
+More specifically, we rely on information theoretic notions of \textit{entropy} and \textit{Fisher information} characterize and quantify the intent disambiguation capabilities of a control mode.
+We utilize this characterization of control modes to develop a mode switch assistance paradigm that enhances the robot's intent inference capabilities, by selecting the control mode in which a user-initiated motion will \textit{maximally disambiguate} human intent.
+The disambiguation layer elicits more \textit{intent expressive} commands from the user by placing the user control in certain control modes.
 
-\section{Related Work}
+In Section~\ref{sec:related_work} we present an overview of relevant research in the areas of shared autonomy in assistive robotics, types of shared autonomy assistance paradigms and use of information theoretic tools in information acquisition.
+Section~\ref{sec:math} presents the set theoretic treatment of control modes mathematical formalism for the intent disambiguation and intent inference.
+Section~\ref{sec:shared-control} focuses on the implementation details of the shared control system.
+The study design and experimental methods are discussed in Section~\ref{sec:ed} followed by results in Section~\ref{sec:results}.
+Discussion and conclusions are presented in Sections~\ref{sec:discussions} and~\ref{sec:conclusions} respectively.
 
-\section{Mathematical Formalism}
+\section{Related Work}\label{sec:related_work}
+
+SHARED CONTROL
+NEED FOR INFERENCE.
+MODE SWITCHING SCHEMES
+
+INTENT CLARIFICATION
+FISHER INFO BASED INFORMATION ACQUISITION.
+
+\section{Mathematical Formalism}\label{sec:math}
+This section describes the mathematical details of the intent disambiguation algorithm that computes a control mode that can maximally disambiguate between the various goals.
+Section~\ref{ssec:notation} outlines the mathematical notation used in this paper.
+Section ~\ref{ssec:disamb} describes the disambiguation algorithm.
+The mathematical details of the intent inference paradigms is outlined in detail in Section~\ref{ssec:inference}.
+\subsection{Notation}\label{ssec:notation}
+ In assistive robotic manipulation, since the robot is mainly used for reaching toward and grasping of discrete objects in the environment, intent inference is the estimation of the probability distribution over all possible goals (objects) in the environment.
+The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$ and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$.
+%A \textit{goal} represents the human's underlying intent. Specifically,
+At any time $t$, the system actively maintains a probability distribution over goals denoted by $\boldsymbol{p}(t)$ such that $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots, p^{n_g}(t)]^{T}$ where $p^i(t)$ denotes the probability associated with goal $g^i$.
+The probability $p^i(t)$ represent the robot's \textit{confidence} that goal $g^i$ is the human's intended goal.
+
+possibly change this into a categorical distribution. Identify the random variable properly.
+
+Let $\mathcal{K}$ be the set of all controllable dimensions of the robot and $k^i$ represent the $i^{th}$ control dimension where $i \in [1,2,\dots,n_k]$ with $n_k = \vert\mathcal{K}\vert$.
+The number of controllable dimensions ($n_k$) depends on the robotic platform used.
+Let $\boldsymbol{x_r}$ denote the position of the robot's end-effector position with respect to the world frame.
+The coordinate space to which $\boldsymbol{x_r}$ belongs depends on the robotic platform.
+For example, a 2D point robot that operates has $\boldsymbol{x_r} \in \mathbb{R}^2$, whereas a 6DOF robotic manipulator has $\boldsymbol{x_r} \in \mathbb{SE}(3)$.
+Lastly, let $\boldsymbol{u_h} \in \mathbb{R}^{n_k}$ denotes the human control command issued via the control interface and $\boldsymbol{u_r} \in \mathbb{R}^{n_k}$ denote the robot autonomy command.
+
 \subsection{Set Theoretic Treatment of Control Modes}
-\subsection{Disambiguation Schemes}
-\subsubsection{Fisher Information Based Metric}
-\subsubsection{Entropy-based Metric}
-\subsubsection{Heuristic-based Metric}
 
-\subsection{Intent inference}
+The limitations of the control interfaces necessitate the control space $\mathcal{K}$ to be partitioned into control modes.
+Let $\mathcal{M}$ denote the set of all control modes with $n_m = \vert\mathcal{M}\vert$.
+Additionally, let $m^i$ refer to the $i^{th}$ control mode where $i \in [1,2,\dots,n_m]$.
+Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i$ spans all of the controllable dimensions.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Let $\boldsymbol{e}^i$ be the standard basis vectors that denote the unit velocity vector along the $i^{th}$ control dimension.\footnote{For the rotational control dimensions, the velocity is specified with respect to the end-effector of the robotic frame.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+Therefore, the user can only access smaller subsets of $\mathbb{R}^{n_k}$ via the control interface with $\mathcal{U}_{m^i}$ denoting the subset of $\mathbb{R}^{n_k}$ accessible from control mode $m^i$.
+Figure 1 represents this in a pictorial fashion for a robot residing in $\mathbb{R}^2$.
+
+% The disambiguation formalism developed in Section~\ref{ssec:disamb} is agnostic to the particular form of intent inference.
+However, the algorithm assumes that $\boldsymbol{p}(t)$ can be forward projected in time by iteratively applying the intent inference algorithm.
+\subsection{Disambiguation Schemes}\label{ssec:disamb}
+
+The need for intent disambiguation arises from the manner in which the probability distribution over goals evolves as the user controls the robot and performs the task.
+The evolution of the probability distribution is closely related to the choice of intent inference mechanism as well as the features that contribute to it.
+If the evolution is sensitive to the user control command, then it is likely that the goal probabilities evolve in different ways as the user operates the robot in different control modes.
+Our aim is to develop a metric that will estimate the ``disambiguation capability'' of control dimension/mode.
+The hypothesis is that subsequent user operation of the robot in the control mode with maximum disambiguation capability will ``help'' the robot to perform better intent inference and likely will result in providing appropriate kinds of assistance.
+
+The first step towards the computation of the disambiguation metric $D_m$ is the forward projection of the probability distribution $\boldsymbol{p}(t)$ from current time $t_a$ to $t_b$ such that $t_a < t_b$, Algorithm~\ref{alg1}, lines 3-10.
+The exact computation of the projected probability distribution will depend on the underlying intent inference computation---for example, whether it depends on $\boldsymbol{x_r}$ (which can be computed from $\boldsymbol{u}_h$ applied to the robot kinematics model) or $\boldsymbol{u}_h$ (which can be taken as $\boldsymbol{e}^k$).
+All parameters and features which affect the computation of $\boldsymbol{p}(t)$ are denoted as $\boldsymbol{\Theta}$.
+For the purposes of forward projection of probabilities and the computation of the disambiguation metric $D_m$ for each control mode $m \in \mathcal{M}$ we only consider the direction of the control command.
+We assume that the human always generates control commands of maximum magnitude when operating in a control mode.
+For a given control mode $m$, we consider $2^{\mathcal{U}_{m}}$ possible control commands.
+The probabilities are forward projected for each of the possible control commands and a weighted average of all disambiguation metric computations is used to characterize the control mode $m$.
+In the following sub-sections we present two different methods to compute the disambiguation metric.
+
+\begin{algorithm}[t]
+	\caption{Calculate $\boldsymbol{p}(t_b)$, $\boldsymbol{p}(t_c)$}
+	\label{alg1}
+	\begin{algorithmic}[1]
+		\REQUIRE $\boldsymbol{p}(t_a), \boldsymbol{x}_r(t_a), \Delta t, t_a < t_b, \boldsymbol{\Theta}$
+		\FOR{$m=1\dots n_m$}
+		\STATE Initialize $D_m = 0$, $t = t_a$
+
+		\WHILE{$t \leq t_b$}
+		\STATE $\boldsymbol{p}_k(t + \Delta t) \leftarrow \text{UpdateIntent}(\boldsymbol{p}_k(t), \boldsymbol{u}_h; \boldsymbol{\Theta})$
+		\STATE $\boldsymbol{x}_r(t + \Delta t) \leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r(t), \boldsymbol{u}_h)$
+		\IF{$t = t_b$} \STATE {$Compute \; D_m$} 
+		\ENDIF
+		\STATE $t \leftarrow t + \Delta t$
+		\ENDWHILE
+
+		\ENDFOR
+
+	\end{algorithmic}
+\end{algorithm}
+
+\subsubsection{Entropy Based Disambiguation Metric}
+The entropy of the probability distribution is reflective of the average information content of a stochastic source of data.
+For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$ with probability mass distribution denoted by $p(X)$, the Shannon entropy is defined as
+
+\begin{equation*}
+H(X) = -\Sigma_{i = 1}^{n} P(x_i)log_{2}P(x_i)
+\end{equation*}
+
+Lower entropy indicates higher certainty in the value of the random variable and vice-versa.
+Therefore, entropy of the projected probability distribution, $\boldsymbol{p}(t_b)$, can be used as a measure of how confident the system is in its prediction of human intent.
+That is, entropy can be used a measure of disambiguation.
+Lower the entropy better the disambiguation due to higher certainty in the human's intended goal.
+The entropy of the probability distribution is affected by the same factors that determine the time evolution of the probability distribution.
+Therefore, 
+\begin{equation}
+D_m = \Sigma_{i=1}^{2^{\vert\mathcal{U}_{m}\vert}} \boldsymbol{p}(t_b)
+\end{equation}
+
+\subsubsection{KL-Divergence based Metric}
+KL divergence is used as a measure of information gain between two distributions.
+Widely used in the context of Bayesian inference, KL divergence measures the information gain when the prior is updated to the posterior in the light of new evidence.
+In the context of disambiguation we can treat the projected probability distributions as the posterior and dostribution at time t to be the prior.
+KL divergence can then be used to caracterize the information gain capabilities of each control mode.
+
+Include figure. 
+%\subsubsection{Fisher Information Based Metric}
+%What is Fisher information
+%Treat entropy as a Gaussain random variable. The noise in the entropy estimate can be due to the fact that the true intent gets distorted in the control interface. 
+%\subsubsection{Heuristic-based Metric}
+
+\subsection{Intent inference}\label{ssec:inference}
 \subsubsection{Dynamic Field Theory}
@@
 
-\subsection{Shared Control}
+\section{Shared Control}\label{sec:shared-control}
 
-\section{Experimental Evaluation}
+\section{Experimental Evaluation}\label{sec:ed}
 
-\section{Results}
-\section{Discussion}
-\section{Conclusion}
+\section{Results}\label{sec:results}
+\section{Discussion}\label{sec:discussions}
+\section{Conclusion}\label{sec:conclusions}
 \section{References}

### 2018-01-16 Code/Numerical_Fisher/FisherInfo/Numerical_Fisher_2D_Id.m

@@ -80,13 +80,15 @@ step_size = (max_ws - min_ws)/num_steps;
 ax_p = (min_ws:step_size:max_ws)' +0.001;
 [X,Y] = meshgrid(ax_p);
 ws_points = [X(:) Y(:)];
-disamb_modes = zeros(size(ws_points, 1), 1);
+disamb_modes_ENT = zeros(size(ws_points, 1), 1);
+disamb_modes_FI = zeros(size(ws_points, 1), 1);
 pg0 = (1/ng)*ones(ng,1);
 % pg0 = [0.4, 0.2, 0.4];
 %%
 for i=1:size(ws_points,1)
     xr = ws_points(i, :)';
-    disamb_modes(i) = compute_optimal_mode_ENT_2D('dft', xr, pg0, '1d');
+    disamb_modes_ENT(i) = compute_optimal_mode_ENT_2D('dft', xr, pg0, '1d');
+    disamb_modes_FI(i) = compute_optimal_mode_FI_2D('dft', xr, pg0, '1d');
 end
 
 %%
@@ -94,10 +96,9 @@ figure;grid on; hold on;
 colors = {[1,0,0], [0,1,0], [0,0,1]};
 
 for i=1:length(colors)
-    scatter(ws_points(disamb_modes == i, 1), ws_points(disamb_modes == i, 2), 70, colors{i}, 'filled'); hold on;
+    scatter(ws_points(disamb_modes_ENT == i, 1), ws_points(disamb_modes_ENT == i, 2), 70, colors{i}, 'filled'); hold on;
 end
 scatter(xg(1,1:ng), xg(2,1:ng), 180, 'k', 'filled');
-
 xrange = [-5.5,5.5]; %set axis limits
 yrange = [-5.5,5.5];
 line(xrange, [0,0], 'Color', 'r'); %draw x and y axes.
@@ -106,6 +107,26 @@ axis([xrange, yrange]);
 legend('Mode 1', 'Mode 2', 'Equivalent');
 axis square;
 xlabel('Spatial X'); ylabel('Spatial Y'); title('Best Disamb Control Modes');
+title('ENTROPY BASED METRIC')
+
+%%
+figure;grid on; hold on;
+colors = {[1,0,0], [0,1,0], [0,0,1]};
+
+for i=1:length(colors)
+    scatter(ws_points(disamb_modes_FI == i, 1), ws_points(disamb_modes_FI == i, 2), 70, colors{i}, 'filled'); hold on;
+end
[…]

### 2018-01-16 Code/Numerical_Fisher/FisherInfo/Numerical_Fisher_3D_Id_DFT.m

@@ -146,7 +146,7 @@ view([32,16]);
 
 min_ws = -5;
 max_ws = 5;
-num_steps = 8;
+num_steps = 5;
 step_size = (max_ws - min_ws)/num_steps;
 ax_p = (min_ws:step_size:max_ws)' +0.001;
 [X,Y,Z] = meshgrid(ax_p);
@@ -167,7 +167,7 @@ scatter3(xg(1,1:ng), xg(2,1:ng), xg(3,1:ng), 580, 'k', 'filled');
 % xrange = [-1,1]; %set axis limits
 % yrange = [-1,1];
 % zrange = [-1,1];
-sf = 2;
+sf = 1.5;
 xrange = sf*[-5,5]; %set axis limits
 yrange = sf*[-5,5];
 zrange = sf*[-5,5];
@@ -175,7 +175,7 @@ line(xrange, [0,0], [0,0], 'Color', 'r', 'LineWidth', 3.5); %draw x and y axes.
 line([0,0], yrange, [0,0], 'Color', 'g','LineWidth', 5.5);
 line([0,0], [0,0], zrange, 'Color', 'b','LineWidth', 3.5);
 axis([xrange, yrange, zrange]);
-axis square;xlabel('X'); ylabel('Y'); zlabel('Z');
+axis square;xlabel('\bf X'); ylabel('\bf Y'); zlabel('\bf Z');
 view([32,16]);
 grid on; hold on;
 scatter3(ws_points(disamb_modes == 1, 1), ws_points(disamb_modes == 1, 2),  ws_points(disamb_modes == 1, 3), 70, 'r', 'filled');

### 2018-01-16 Code/Numerical_Fisher/FisherInfo/compute_bayes.m

@@ -3,7 +3,7 @@ function [ posterior ] = compute_bayes( uh, xr, prior )
 %   Detailed explanation goes here
     global ng
     ll = likelihood_func(uh, xr);
-    prior = prior + 0.01*rand(ng, 1); %to avoid collapse of posterior. 
+    prior = prior + 0.001*rand(ng, 1); %to avoid collapse of posterior. 
     prior = prior/sum(prior);
     posterior = ll.*prior;
     posterior = posterior/sum(posterior); %make sure that the posterior is always normalized. 
@@ -27,11 +27,12 @@ end
 
 function [q] = p_of_u_given_g(uh, dir_vec) %assumes that the uh that is expected to see for a goal is the one which is directly pointing at it. 
 %     q = prob(uh(1) - dir_vec(1))*prob(uh(2) - dir_vec(2))*prob(uh(3) - dir_vec(3)); %p(ux, uy, uz) = p(ux)p(uy)p(uz);
-    ang = acos(dot(uh, dir_vec));
+    ang = acos(round(dot(uh, dir_vec), 5));
     q = prob(ang);
 end
 
-function p = prob(a) %zero mean gaussian, 
-    sigma = pi/2; %for the time being use this std dev
+function p = prob(a) %zero mean gaussian,  % MAKE this into von Misner
+    sigma = 1.5*pi; %for the time being use this std dev
     p = (1/sqrt(2*pi*sigma^2))*exp((-1/2.0)*(a^2/sigma^2));
+    
 end

### 2018-01-16 Code/Numerical_Fisher/FisherInfo/compute_p_of_g_dft.m

@@ -2,7 +2,7 @@ function [pg] = compute_p_of_g_dft( uh, xr, pg )
 %UNTITLED3 Summary of this function goes here
 %   Detailed explanation goes here
     global ng delta_t;
-    tau = 5;
+    tau = 3.8;
     h = 1/ng;
     %%%%%%%%%%%%%%%%
     %only for ad mode
@@ -11,7 +11,7 @@ function [pg] = compute_p_of_g_dft( uh, xr, pg )
     curr_pg = compute_curr_input(uh, xr);
     lambda = 0*ones(ng,ng);
     lambda(1: ng+1: ng*ng) = 0;
-    lambda = 1*eye(ng) + lambda;
+    lambda = 2*eye(ng) + lambda;
     dpgdt = (-1/tau)*eye(ng)*pg + (h/tau)*ones(ng,1) + lambda*sigmoid(curr_pg); %ODE - Dynamics neural field. 
     pg = pg + dpgdt*delta_t; %Euler integration;
     pg(pg <=0) = realmin;

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/R2/WorkspaceSim/SimulateR2_Workspace.m

@@ -1,0 +1,129 @@
+clear all; clc; close all;
+%%
+%Define workspace limits. All in metres. 
+xrange = [-0.5, 0.5];
+yrange = [-0.5, 0.5];
+
+global cm num_modes ng nd xg xr sig delta_t conf_thresh conf_max alpha_max;
+
+%workspace parameters
+max_ng = 6;
+ng = datasample(2:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
+nd = 2; %num of dimensions. by definition R^2
+cm = {1,2}; %only control mode settings. 
+num_modes = length(cm); %or 1 depending on whether the modes are [x, y] or [{x,y}]
+
+%spawn random goals and random robot positions
+xg = [rand(1,ng)*range(xrange) + xrange(1); rand(1,ng)*range(yrange) + yrange(1)]; %random goal positions. These will be treated as fixed parameters.
+xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1)];
+xr_true = xr; %store away random position in a variable for reuse.
+
+
+%disambiguation related params
+sig = 0.01; %For Fisher information
+delta_t = 0.1; %For compute projections. 
+
+%arbitrartion function parameters - Fixed parameters for shared control. 
+conf_thresh = (1.2/ng);
+conf_max = (1.4/ng);
+alpha_max = 0.7;
+
+%%
+
+%% PLOT GOALS AND CURRENT ROBOT POSITION. 
+
+figure;
+scatter(xg(1,1:ng), xg(2,1:ng), 180, 'k', 'filled'); grid on; hold on;
+scatter(xr(1), xr(2), 140, 'r', 'filled');
+offset = [-0.1, 0.1];
+line(xrange+offset, [0,0], 'Color', 'r'); %draw x and y axes.
+line([0,0], yrange+offset, 'Color', 'g');
+axis([xrange + offset, yrange + offset]);
+axis square;
+
+%%
+intent_type = 'dft';
+
+%%
+min_ws = -0.5;
+max_ws = 0.5;
+num_steps = 20;
+step_size = (max_ws - min_ws)/num_steps;
+ax_p = (min_ws:step_size:max_ws)'; %so that it doesnt align exactly with the goals?
+[X,Y] = meshgrid(ax_p);
+ws_points = [X(:) Y(:)];
+disamb_modes_ENT = zeros(size(ws_points, 1), 1);
[…]

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/R2/compute_optimal_mode_ENT_R2.m

@@ -33,7 +33,6 @@ for i=1:length(cm)
 end
 
 best_mode = compute_best_mode(EID_AR);
-
 end
 
 

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/R2/compute_optimal_mode_FI_R2.m

@@ -1,4 +1,4 @@
-function [ best_mode ] = compute_optimal_mode_FI_R2(intent_type, xr_T, pg)
+function [ best_mode, EID_AR ] = compute_optimal_mode_FI_R2(intent_type, xr_T, pg)
 %UNTITLED6 Summary of this function goes here
 %   Detailed explanation goes here
 % global delta_t;

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/R2/compute_projected_kl_R2.m

@@ -1,0 +1,9 @@
+function [ Upsilon ] = compute_projected_kl_R2( uh, varargin )
+%UNTITLED8 Summary of this function goes here
+%   Detailed explanation goes here
+projection_time = 1.5;
+projected_pg = compute_pg_projection_R2(uh, projection_time, varargin{:});
+Upsilon = compute_kl_div(projected_pg, varargin{3});
+
+end
+

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/R3/compute_bayes_R3.m

@@ -31,6 +31,6 @@ function [q] = p_of_u_given_g(uh, dir_vec) %assumes that the uh that is expected
 end
 
 function p = prob(a) %zero mean gaussian, 
-    sigma = pi/2; %for the time being use this std dev
+    sigma = 1.5*pi; %for the time being use this std dev
     p = (1/sqrt(2*pi*sigma^2))*exp((-1/2.0)*(a^2/sigma^2));
 end

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/R3/compute_p_of_g_dft_R3.m

@@ -12,7 +12,7 @@ function [pg] = compute_p_of_g_dft_R3( uh, xr, pg )
     lambda = 0*ones(ng,ng);
     lambda(1: ng+1: ng*ng) = 0;
     lambda = 1*eye(ng) + lambda;
-    dpgdt = (-1/tau)*eye(ng)*pg ++ (h/tau)*ones(ng,1) + lambda*sigmoid(curr_pg); %ODE - Dynamics neural field. 
+    dpgdt = (-1/tau)*eye(ng)*pg + (h/tau)*ones(ng,1) + lambda*sigmoid(curr_pg); %ODE - Dynamics neural field. 
     pg = pg + dpgdt*delta_t; %Euler integration;
     pg(pg <= 0) = realmin;
     pg = pg/sum(pg); %normalize, so that the inidividual values are alwyas between 0 and 1. 

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/R3/compute_pg_entropy.m

@@ -1,6 +1,0 @@
-function [ Upsilon ] = compute_pg_entropy( pg )
-%UNTITLED4 Summary of this function goes here
-%   Detailed explanation goes here
-Upsilon = nansum(pg.*log2(pg));
-end
-

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/SE2/SimulateTraj_SE2_With_Blending.m

@@ -1,4 +1,4 @@
-% clear all; close all; clc;
+clear all; close all; clc;
 
 
 %% SPAWN GOAL CONFIGURATION AND ROBOT POSITION. RANDOMLY IN THE WORKSPACE. 
@@ -31,30 +31,30 @@ conf_max = (1.4/ng);
 alpha_max = 0.7;
 
 %% plot positions and body rotation axis. 
-% figure;
-% scatter(xg(1,1:ng), xg(2,1:ng), 230, 'k', 'filled'); grid on; hold on;
-% scatter(xr(1), xr(2), 140, 'r', 'filled');
-% % for i=1:ng %vectors connecting robot and goals.
-% %     quiver(xr(1), xr(2), xg(1,i) - xr(1), xg(2,i) - xr(2), 'LineWidth', 1.5, 'LineStyle', '-.');
-% % end
-% offset = [-0.1, 0.1];
-% line(xrange+offset, [0,0], 'Color', 'r'); %draw x and y axes.
-% line([0,0], yrange+offset, 'Color', 'g');
-% axis([xrange + offset, yrange + offset]);
-% axis square;
-% 
-% % draw orientations:
-% l_axis = 0.05; % length of axis 
-% line([xr(1), xr(1) + l_axis*cos(xr(3))], [xr(2), xr(2) + l_axis*sin(xr(3))], 'Color', 'r', 'LineWidth', 2);
-% line([xr(1), xr(1) - l_axis*sin(xr(3))], [xr(2), xr(2) + l_axis*cos(xr(3))], 'Color', 'g', 'LineWidth', 2);
-% for i=1:ng
-%     line([xg(1, i), xg(1, i) + l_axis*cos(xg(3, i))], [xg(2, i), xg(2, i) + l_axis*sin(xg(3, i))], 'Color', 'r', 'LineWidth', 2);
-%     line([xg(1, i), xg(1, i) - l_axis*sin(xg(3, i))], [xg(2, i), xg(2, i) + l_axis*cos(xg(3, i))], 'Color', 'g', 'LineWidth', 2);
+figure;
+scatter(xg(1,1:ng), xg(2,1:ng), 230, 'k', 'filled'); grid on; hold on;
+scatter(xr(1), xr(2), 140, 'r', 'filled');
+% for i=1:ng %vectors connecting robot and goals.
[…]

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/SE2/compute_bayes_SE2.m

@@ -74,6 +74,6 @@ end
 
 %%
 function p = prob(a) %zero mean gaussian, 
-    sigma = pi/2; %for the time being use this std dev
+    sigma = 1.5*pi; %for the time being use this std dev
     p = (1/sqrt(2*pi*sigma^2))*exp((-1/2.0)*(a^2/sigma^2));
 end

### 2018-01-16 Code/Numerical_Fisher/SimulationCode/Utils/plot_goal_match.m

@@ -3,28 +3,36 @@ figure;
 
 subplot(4,2,1);
 scatter(1:length(curr_goal_ENT), curr_goal_ENT == random_goal_index, 'r', 'filled'); grid on;
-title('ENT GOAL MATCH'); xlabel('Time Steps'); ylabel('Matched/Unmatched'); ylim([0.0, 1.0]);
+title('ENT GOAL MATCH'); xlabel('Time Steps'); ylabel('Matched/Unmatched'); ylim([0.0, 1.0]); xlim([0, 120]);
+xlim([0, 120])
 subplot(4,2,2);
 scatter(1:length(curr_goal_ENT), curr_goal_ENT, 'r', 'filled'); grid on;
-title('ENT GOAL INFERENCE'); xlabel('Time Steps'); ylabel('Goal Index');ylim([1, ng]);
+title('ENT GOAL INFERENCE'); xlabel('Time Steps'); ylabel('Goal Index');ylim([1, ng]);xlim([0, 120]);
 
 subplot(4,2,3);
-scatter(1:length(curr_goal_FI), curr_goal_FI == random_goal_index, 'b', 'filled'); grid on;
-title('FI GOAL MATCH'); xlabel('Time Steps'); ylabel('Matched/Unmatched');ylim([0.0, 1.0]);
+scatter(1:length(curr_goal_KL), curr_goal_KL == random_goal_index, 'b', 'filled'); grid on;
+title('KL GOAL MATCH'); xlabel('Time Steps'); ylabel('Matched/Unmatched');ylim([0.0, 1.0]);xlim([0, 120]);
 subplot(4,2,4);
-scatter(1:length(curr_goal_FI), curr_goal_FI, 'b', 'filled'); grid on;
-title('FI GOAL INFERENCE'); xlabel('Time Steps'); ylabel('Goal Index');ylim([1, ng]);
+scatter(1:length(curr_goal_KL), curr_goal_KL, 'b', 'filled'); grid on;
+title('KL GOAL INFERENCE'); xlabel('Time Steps'); ylabel('Goal Index');ylim([1, ng]);xlim([0, 120]);
+
+% subplot(4,2,3);
+% scatter(1:length(curr_goal_FI), curr_goal_FI == random_goal_index, 'b', 'filled'); grid on;
+% title('FI GOAL MATCH'); xlabel('Time Steps'); ylabel('Matched/Unmatched');ylim([0.0, 1.0]);
[…]

### 2018-01-23 NewTexFile/GopinathArgall_RSS2018.tex
First Draft - with figures, without robot sim

--- 2018-01-05 NewTexFile/GopinathArgall_RSS2018.tex
@@
 \usepackage{multicol}
+\usepackage{tabularx}
 \usepackage[bookmarks=true]{hyperref}
@@
 \usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
-\usepackage{amsmath} % assumes amsmath package installed
-\usepackage{amssymb}  % assumes amsmath package installed
+\usepackage{amsmath} % assumes amsmath package installed  % assumes amsmath package installed
+\usepackage{mathtools, bbm}
 \usepackage{lipsum}
@@
 \usepackage{pifont}
-\newcommand{\argmax}{\arg\!\max}
+\usepackage{algorithm, algorithmic}
+\DeclareMathOperator*{\argmax}{argmax}
+%\newcommand{\argmax}{\arg\!\max}
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
@@
 % paper title
-\title{Fisher Information based Disambiguation of Human Intent - An Experimental Evaluation}
+\title{Information Theoretic Formulation of Intent Disambiguation}
 \author{Author Names Omitted for Anonymous Review. Paper-ID [\textbf{163}]}
@@
 \begin{abstract}
-In this paper, we treat the problem of intent disambiguation in terms of information theoretic principles.
-The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions and provide appropriate types of assistance quickly, confidently and accurately.
-We propose two different control mode selection schemes for intent disambiguation using notions of entropy and Fisher information in the context of assistive robotic manipulation.
-The proposed algorithms characterize the disambiguation capabilities of different control modes by the forward projection of probability distributions over goals and computing the relevant information theoretic measures.
+In this paper, we formulate the problem of intent disambiguation in information theoretic terms.
+We propose two different control mode selection schemes for intent disambiguation using information theoretic ideas of \textit{entropy} and \textit{Kullback-Leibler Divergence} for an assistive robotic manipulator.
+The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions and provide appropriate types of assistance quickly and accurately.
+The proposed algorithms characterize the disambiguation capabilities of different control modes by the forward projection of probability distributions over goals and computing the average information gain and content.
 Our previous exploratory pilot studies revealed that the success of the disambiguation system depends on a variety of factors and choice of parameters.
-In order to thoroughly investigate the impact of the choice of various parameters and components, we present extensive simulation results both for point-robots that reside in different spaces as well as on the simulated robotic arm.
+In order to thoroughly investigate the impact of various components, we present results from an extensive simulation-based study both for point-robots that reside in different spaces as well as on the simulation of a real robotic arm.
 Our results indicate that with the disambiguation algorithm the robot is able to assist earlier during task execution.
-Furthermore, the goal inferences are more accurate when operating in the disambiguating modes.
+Furthermore, the goal inferences are more accurate and the total amount of assistance greater when operating in the disambiguating modes compared to the baseline.
 \end{abstract}
@@
 \section{Introduction}
-Assistive shared-control machines such as robotic arms and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result of spinal cord injuries or brain traumas.
+Assistive shared-control machines such as robotic arms, smart wheelchairs  and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result injuries to the central nervous system~\citep{laplante1992assistive}.
 These machines can promote independence, enhance the quality of lives and revolutionize the way they interact with society.
-These machines help to extend the mobility and manipulation capabilities of individuals thereby helping them perform activities of daily living in a more effective manner.
+They can also help to extend the mobility and manipulation capabilities of individuals thereby helping motor-impaired people perform activities of daily living in a more effective manner.
 
+An assistive robotic machine is typically controlled using control interfaces such as joysticks, switch-based head arrays and sip-and-puffs.
+These interfaces are low-dimensional, low-bandwidth and occasionally discrete, and can operate only in subsets of the entire control space.
+These subsets are referred to as \textit{control modes}.
 The efficacy of assistive machines rely on their ability to infer the users' needs and intentions and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately.
-Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, the users' are typically constrained to produce control commands that do not reveal the intent more expressively.
-Therefore, intent inference is a necessary and crucial component to ensure appropriate assistance.
-Specifically, in assistive robotic manipulation, often the first step of a task is to reach for and grasp discrete objects in the environment.
-Therefore in this context, intent inference can be cast as a problem of maintaining the probability distribution over all possible discrete goals (objects) in the workspace.
+Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, the users are constrained to produce control commands that likely does not reveal the true intent in an unambiguous and expressive manner.
+That is, the control interfaces act like filters that restrict the amount of information regarding intent that gets passed through.
+%Furthermore, sparsity and noise in the control commands make the inference process even harder prompting the need for robust intent inference formalisms.
 
-Our insight is that the information contained in control command issued in certain control modes is more useful for accurate inference and thereby will help the robot in providing the appropriate kind of assistance.
-In this work, we rely on information theoretic principles to quantify the information regarding intent disambiguation contained in different control modes and select control modes that maximize intent disambiguation.
+In the context of assistive robotic manipulation, often the first step of a task is to reach for and grasp discrete objects in the environment.
+Therefore, intent inference can be cast as a problem of maintaining the probability distribution over all possible discrete goals (objects) in the workspace.
+Intent inference mechanisms typically rely on various environmental cues and task-relevant features such as robot and goal positions, human control commands and biometric measures for estimating the most probable goal.
+However, due to cost considerations and user acceptance issues, our system tries to infer intent primarily based on the information contained in the constrained control commands issued to the assistive machine.
 
-\section{Related Work}
+Our insight is that the information contained in control commands issued in certain control modes will clarify human's underlying intent unambiguously and is likely to be more useful for the robot to perform accurate intent inference.
+This, in turn will help the robot to appropriate kinds of assistance more effectively.
+In this paper, we formulate the problem of intent disambiguation in information-theoretic terms.
+More specifically, we rely on information theoretic notions of \textit{entropy} and \textit{Kullback-Leibler Divergence} to characterize and quantify the intent disambiguation capabilities of a control mode.
+We utilize this characterization of control modes to develop a mode switch assistance paradigm that enhances the robot's intent inference capabilities, by selecting the control mode in which a user-initiated motion will \textit{maximally disambiguate} human intent.
+%The disambiguation system will likely elicit more \textit{intent expressive} commands from the user by placing the user control in certain control modes.
 
-\section{Mathematical Formalism}
-\subsection{Set Theoretic Treatment of Control Modes}
-\subsection{Disambiguation Schemes}
-\subsubsection{Fisher Information Based Metric}
-\subsubsection{Entropy-based Metric}
-\subsubsection{Heuristic-based Metric}
+In Section~\ref{sec:related_work} we present an overview of relevant research in the areas of shared autonomy in assistive robotics, types of shared autonomy assistance paradigms and use of information theoretic tools in information acquisition.
+Section~\ref{sec:math} presents the set theoretic treatment of control modes mathematical formalism for the intent disambiguation and intent inference.
+Section~\ref{sec:shared-control} focuses on the implementation details of the shared control system.
+The study design and experimental methods are discussed in Section~\ref{sec:ed} followed by results in Section~\ref{sec:results}.
+Discussion and conclusions are presented in Sections~\ref{sec:discussions} and~\ref{sec:conclusions} respectively.
 
-\subsection{Intent inference}
-\subsubsection{Dynamic Field Theory}
-\subsubsection{Bayesian Inference}
-\subsubsection{Confidence Functions}
+\section{Related Work}\label{sec:related_work}
+This section presents an overview of related works in the areas of shared autonomy in assistive robotics, robot assistance for modal control, intent inference in human-robot interaction and information acquisition in robotics.
 
-\subsection{Shared Control}
+Shared-autonomy in assistive machines aims to reduce the human's physical and cognitive burden during task execution without having the user completely cede manual control~\citep{philips2007adaptive, demeester2008user}.
+Some of the common shared-autonomy approaches include (a) hierarchical paradigms in which the higher level goals are entrusted with the user and the autonomy generates low-level control~\citep{kim2012autonomy}, (b) control allocation in distinct partitions of the control space~\citep{driessen2005collaborative} and (c) blending user controls and robot autonomy commands~\citep{muelling2017autonomy}.
 
-\section{Experimental Evaluation}
+Due to the limitations of the control interfaces, users typically have to shift their focus from the task at hand to switching between various control modes during task execution and results in a higher cognitive load.
+Various mode switching assistance paradigms have been proposed to alleviate task effort.
+For example, a time-optimal mode switch assistance~\citep{herlant2016assistive} and heuristic based mode switch assistance to maximize intent disambiguation~\citep{gopinath2017mode}.
 
-\section{Results}
-\section{Discussion}
-\section{Conclusion}
-\section{References}
+For an assistive machine to provide appropriate kinds of assistance accurately and at the right time, it needs to have a good estimate of the human's underlying intent.
+Intent inference algorithms, therefore, play a vital role in the success of a shared-control assistive system.
+Intent inference and recognition can be classified into two broad categories: heuristic approaches and model-based approaches.
+Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features such as motion cues and the human's underlying intention~\citep{baker2007goal, baker2009action}.
+On the other hand, in model-based approaches, the human is modeled within the Partially Observable Markov Decision Process (MDP)~\citep{taha2011pomdp, dragan2013policy} framework and is assumed to behave according to a control policy that maps states to actions.
+However, in Bayesian schemes, incorporating the entire history of states requires estimation of joint probability distributions that can become quickly intractable.
+
+Robot assistance schemes that seeks to elicit more informative cues from the human to clarify the underlying intent can be thought of as an information acquisition problem.
+Intent acquisition can leverage the underlying synergies and shared intentionality~\citep{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions (for example, selecting a control mode or executing a robot motion) that will nudge the human to reveal her/his intent more clearly~\cite{sadigh2016information, sadigh2016planning}.
+More generally, in the field of machine learning and experimental design, active learning is widely used for improving the efficiency of estimating unknown model parameters from data.
+Data collection is time consuming and expensive; therefore, it is necessary to obtain data samples that contain the greatest amount of information regarding the unknown parameters.
+In parameter estimation problems, researchers usually start with a prior distribution on the parameters which then gets updated upon the arrival of new data samples.
+Information theoretic metrics such as a KL-divergence can be utilized to identify regions of the sample space that will maximize information gain~\citep{tong2001active} and subsequently guide the data sampling process.
+Sensing robots designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\citep{atanasov2014information}.
+If the spatial distribution of information density is known \textit{a priori}, information maximization can be accomplished by maximizing the ergodicity of the robot's trajectory with respect to the underlying information density map~\citep{miller2016ergodic, miller2013trajectory}.
+
+\section{Mathematical Formalism}\label{sec:math}
+This section describes the mathematical details of the intent disambiguation algorithm that computes a control mode that can maximally disambiguate between the various goals.
+Section~\ref{ssec:notation} outlines the mathematical notation used in this paper.
+Section~\ref{ssec:set_modes} presents a set-theoretic treatment of control modes and Section ~\ref{ssec:disamb} describes the disambiguation algorithm.
+The mathematical details of the intent inference paradigms are outlined in detail in Section~\ref{ssec:inference}.
+\subsection{Notation}\label{ssec:notation}
+ In assistive robotic manipulation, as the robot is mainly used for reaching toward and grasping of discrete objects in the environment, intent inference is process of estimating the user's intended goal.
+The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$ and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$.
+At any time $t$, the unknown goal $g$ follows a categorical probability distribution whose sample space is $\mathcal{G}$.
+ That is, 
+ \begin{equation*}
+ g \sim \textbf{Cat}(n_g | \boldsymbol{p}(t)) = \prod_{i=1}^{n_g}p^{i}(t)^{[g = g^i]}
+ \end{equation*}
+where, $[g = g^i]$ is the Iverson bracket and evaluates to 1 if $g = g^i$, 0 otherwise.
+$\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots, p^{n_g}(t)]^{T}$ where $p^i(t)$ denotes the probability associated with goal $g^i$.
+The probability $p^i(t)$ represent the robot's \textit{confidence} that goal $g^i$ is the human's intended goal.
+
+Let $\mathcal{K}$ be the set of all controllable dimensions of the robot and $k^i$ represent the $i^{th}$ control dimension where $i \in [1,2,\dots,n_k]$ with $n_k = \vert\mathcal{K}\vert$.
+The number of controllable dimensions ($n_k$) depends on the robotic platform used.
+Let $\boldsymbol{x_r}$ denote the position of the robot's end-effector position with respect to the world frame.
+The mathematical space in which $\boldsymbol{x_r}$ resides and the number of controllable dimensions depends on the robotic platform.
+For example, a 2D point robot that operates has $\boldsymbol{x_r} \in \mathbb{R}^2$, whereas a 6DOF robotic manipulator has $\boldsymbol{x_r} \in \mathbb{SE}(3)$.
+Lastly, let $\boldsymbol{u_h} \in \mathbb{R}^{n_k}$ denotes the human control command issued via the control interface and $\boldsymbol{u_r} \in \mathbb{R}^{n_k}$ denote the robot autonomy command\footnote{For the rotational control dimensions, the velocity is specified with respect to the end-effector of the robotic frame.}.
+
+\subsection{Set Theoretic Treatment of Control Modes}\label{ssec:set_modes}
+%
+%The limitations of the control interfaces necessitate the control space $\mathcal{K}$ to be partitioned into control modes.
+Let $\mathcal{M}$ denote the set of all control modes with $n_m = \vert\mathcal{M}\vert$.
+Additionally, let $m^i$ refer to the $i^{th}$ control mode where $i \in [1,2,\dots,n_m]$.
+Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i$ spans all of the controllable dimensions.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Let $\boldsymbol{e}^i$ be the standard basis vectors that denote the unit velocity vector along the $i^{th}$ control dimension.\footnote{For the rotational control dimensions, the velocity is specified with respect to the end-effector of the robotic frame.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+Therefore, the user can only access smaller subsets of $\mathbb{R}^{n_k}$ via the control interface with $\mathcal{U}_{m^i}$ denoting the subset of $\mathbb{R}^{n_k}$ accessible from control mode $m^i$.
+Figure 1 represents this in a pictorial fashion for a robot residing in $\mathbb{R}^2$.
+
+The low dimensionality of the control interfaces necessitates the control space $\mathcal{K}$ to be partitioned into control modes.
+Let $\mathcal{M}$ denote the set of all control modes with $n_m = \vert\mathcal{M}\vert$.
+Additionally, let $m^i$ refer to the $i^{th}$ control mode where $i \in [1,2,\dots,n_m]$.
+Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i$ spans all of the controllable dimensions.
+The cardinality of each mode denoted by $\vert m \vert$ indicates the number of dimensions that can be controlled when operating in $m$.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+That is, for each $m \in \mathcal{M}$, the subspace of $\mathcal{R}^{n_k}$ that is accessible corresponds to $\mathcal{R}^{\vert m \vert}$ whose basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
+Maximum velocity limits along each dimension imposes further constraints on the set of control commands that are available in each mode.
+The set of control commands denoted by $\mathcal{U}^m$, can be written as
+\begin{equation*}
+\mathcal{U}^m = \{\boldsymbol{u} \in \mathcal{R}^{\vert m \vert}, s.t \norm{\boldsymbol{u}}_{\infty} \leq c \} 
+\end{equation*}
+where $c$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm.
+Therefore, the set $\mathcal{U}^m$ corresponds to a hypercube of dimensionality $\vert m \vert$ embedded in $\mathcal{R}^{n_k}$.
+In other words $\mathcal{U}^m$ is a $\vert m \vert$-cube with edge length equals $2c$.
+Without loss of generality, the velocity limits can be different for different control dimensions in which case $\mathcal{U}^m$ will correspond to a hypercuboid.
+Figure 1 represents this in a pictorial fashion for a robot residing in $\mathbb{R}^2$.
+ \begin{figure}[h]
+	\centering
+	\includegraphics[width= 0.8\hsize, height=0.2\vsize]{./figures/R2_ControlModes.eps}
+	\vspace{-0.35cm}
+	\caption{Illustration of 1D and 2D control modes in a two-dimensional control space, $\mathbb{R}^2$.
+Note that this space can be embedded in a higher dimensional space such as $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
+The 1D control modes are shown in blue and orange and the 2D control mode is shown as the green shaded area within the red square.
+The vertex set denotes the maximum magnitude control commands that can be issued when operating in a control mode.
+}
+	\label{fig:r2_modes}
+\end{figure}
+
+% The disambiguation formalism developed in Section~\ref{ssec:disamb} is agnostic to the particular form of intent inference.
+However, the algorithm assumes that $\boldsymbol{p}(t)$ can be forward projected in time by iteratively applying the intent inference algorithm.
+\subsection{Disambiguation Schemes}\label{ssec:disamb}
+
+The need for intent disambiguation arises from the manner in which the probability distribution over goals evolves as the user controls the robot and performs the task.
+The evolution of the probability distribution is closely related to the choice of intent inference mechanism as well as the features that contribute to it.
+If the evolution is sensitive to the user control command, then it is likely that the goal probabilities evolve in different ways as the user operates the robot in different control modes.
+Our aim is to develop a metric that will estimate the ``disambiguation capability'' of control dimension/mode.
+The hypothesis is that subsequent user operation of the robot in the control mode with maximum disambiguation capability will ``help'' the robot to perform better intent inference and likely will result in providing appropriate kinds of assistance.
+
+The first step towards the computation of the disambiguation metric $D_m$ is the forward projection of the probability distribution $\boldsymbol{p}(t)$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
+The exact computation of the projected probability distribution will depend on the underlying intent inference computation---for example, whether it depends on $\boldsymbol{x_r}$ (which can be computed from $\boldsymbol{u}_h$ applied to the robot kinematics model) or $\boldsymbol{u}_h$.
+All parameters and features which affect the computation of $\boldsymbol{p}(t)$ are denoted as $\boldsymbol{\Theta}$.
+If the inference mechanism depend on the control command, the projected probability distribution at time $t_b$ given by $\boldsymbol{p}(t_b)$ depends on $\boldsymbol{u_h}$.
+For the purposes of computation of the disambiguation metric, in each mode $m \in \mathcal{M}$, we only consider the set containing the ``vertices'' of the $\vert m \vert$-cube, denoted by $Vert(\mathcal{U}^m)$.
+The probabilities are forward projected for each of the possible control commands available in $Vert(\mathcal{U}^m)$ (Algorithm~\ref{alg:disamb}, Lines 5-9) and a weighted average of all disambiguation metric computations on each of the projected probabilities is used to characterize the control mode $m$.
+In the following sub-sections we present two different methods to compute the disambiguation metric for a given mode $m$.
+
+ \begin{figure}[h]
+	\centering
+	\includegraphics[width= 1.\hsize, height=0.3\vsize]{./figures/Disamb_Compute.eps}
+	\vspace{-0.35cm}
+	\caption{Illustration of computation of $D_m$ in $\mathbb{R}^2$.
+The goals are shown in red, green and blue and the robot is depicted in black.
+The probability distributions are forward projected for all $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
+The change in the overall shape of the probability distribution upon evolving from $\boldsymbol{p}(t_a)$ to $\boldsymbol{p}(t_b)$ amounts to the information `gain' and is captured by the \textit{KL-Divergence}.
+The entropy of $\boldsymbol{p}(t_b)$ captures the information `content' present in the distribution.}
+	\label{fig:disamb_compute}
+\end{figure}
+
+\subsubsection{Entropy Based Disambiguation Metric}\label{sssec:ent}
+The entropy of the probability distribution is reflective of the average information content of a stochastic source of data.
+For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$, the Shannon entropy is defined as
+
+\begin{equation*}
+ENT(P(X)) = -\sum_{i = 1}^{n} P(x_i)log_{2}P(x_i)
+\end{equation*}
+where $P(X)$ denotes the probability mass function.
+
+Lower entropy indicates higher certainty in the value of the random variable and vice-versa.
+Therefore, entropy of the projected probability distribution, $\boldsymbol{p}(t_b)$, can be used as a measure of how confident the system is in its prediction of human intent.
+That is, entropy can be used a measure of disambiguation.
+Lower the entropy better the disambiguation due to higher certainty in the human's intended goal.
+The disambiguation capability of a control mode $m$ is characterized by computing a weighted average of the entropies of projected probability distributions for all possible control commands $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
+That is
+\begin{equation}
+D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)}  ENT(\boldsymbol{p}(t_b; \boldsymbol{u_h}))
+\end{equation}
+where $\boldsymbol{p}(t_b; \boldsymbol{u_h})$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is $\boldsymbol{u_h}$.
+\subsubsection{KL-Divergence Based Metric}\label{sssec:kl}
+KL-Divergence, also known relative entropy, measures how one probability distribution differ from another distribution.
+KL-Divergence is widely used in the context of Bayesian inference to compute the information gain when the prior is updated to the posterior in the light of new evidence.
+For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$ the KL-Divergence is defined by
+\begin{equation*}
+KL(P||Q) = -\sum_{i=1}^{n}P(x_i)log_2\frac{Q(x_i)}{P(x_i)}
+\end{equation*}
+where $P(X)$ and $Q(X)$ are two different probability mass distributions. 
+In the context of disambiguation we can treat the projected probability distribution as the posterior and distribution at time $t_a$ to be the prior.
+KL-Divergence can then be used to characterize the information gain regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
+More specifically, the disambiguation capability of control mode $m$ is computed by averaging the information gain for all possible control commands $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
+That is the disambiguation metric can be computed as
+\begin{equation*}
+D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)} KL(\boldsymbol{p}(t_b; \boldsymbol{u_h})||\boldsymbol{p}(t_a))~~~~.
+\end{equation*}
+\begin{algorithm}[t]
+	\caption{Calculate $\boldsymbol{p}(t_b)$, $D_m$}
+	\label{alg:disamb}
+	\begin{algorithmic}[1]
+		\REQUIRE $\boldsymbol{p}(t_a), \boldsymbol{x}_r(t_a), \Delta t, t_a < t_b, \boldsymbol{\Theta}$
+		\FOR{$m=1\dots n_m$}
+		\STATE Initialize $D_m = 0$
+
+		\FOR{$\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$}
+		\STATE Initialize $t = t_a, \boldsymbol{x_r}(t) = \boldsymbol{x_r}(t_a), \boldsymbol{p}(t) = \boldsymbol{p}(t_a)$
+		\WHILE{$t \leq t_b$}
+		\STATE $\boldsymbol{p}(t + \Delta t) \leftarrow \text{UpdateIntent}(\boldsymbol{p}(t), \boldsymbol{u}_h; \boldsymbol{\Theta})$
+		\STATE $\boldsymbol{x}_r(t + \Delta t) \leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r(t), \boldsymbol{u}_h)$
+		\STATE $t \leftarrow t + \Delta t$
+		\ENDWHILE
+
+		\STATE $D_m \leftarrow D_m + \frac{1}{\vert Vert(\mathcal{U}^m) \vert} ENT(\boldsymbol{p}(t_b)) $
+
+		or
+
+		\STATE $D_m \leftarrow D_m + \frac{1}{\vert Vert(\mathcal{U}^m) \vert} KL(\boldsymbol{p}(t_b) \vert\vert \boldsymbol{p}(t_a)) $
+
+		\ENDFOR
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+The control mode with highest disambiguation capability $m^*$ is given by $\argmax_m D_m$.
+Disambiguation mode $m^*$ is the control mode that system chooses \textit{for} the human to better estimate their intent.
+Any control command issued by the human when operating in $m^*$ is likely to be more beneficial for the robot to determine the human's intended goal.
+
+\subsection{Intent inference}\label{ssec:inference}
+This section describes the different types of intent inference schemes used in this paper.
+Our preliminary pilot studies indicated that the disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms.
+%This is because, during the forward projection step, different intent update schemes result in different projections and affects the computation of the disambiguation metric.
+
+\subsubsection{Heuristic Approaches}
+Heuristic approaches based on \textit{confidence} functions seek to find direct mappings between instantaneous cues and underlying human intentions.
+For every goal $g \in \mathcal{G}$, the system maintains an associated set of confidences denoted by $\mathcal{C}$.
+The system designer has the freedom to choose the set of features that will inform the confidences.
+For example, a simple proximity-based confidence function used extensively in literature is
+\begin{equation}
+c(\boldsymbol{x_r}, \boldsymbol{x_g}) = max\Big(0, 1 - \frac{\norm{\boldsymbol{x_r} - \boldsymbol{x_g}}}{r}\Big)
+\end{equation}
+where $\boldsymbol{x_r}$ is the robot position, $\boldsymbol{x_g}$ is the goal position, $r$ is the radius beyond which the confidence function is always 0 and $\norm{\cdot}$ is an appropriate distance metric.
+%A confidence function that relies purely on proximity features, however, ignores all information regarding human intent contained in the control command itself. 
+A slightly more information-rich variant that aims to capture the ``directedness'' of the human control command to a particular goal position is
+\begin{equation*}
+c({\boldsymbol{x_r},\boldsymbol{x_g}, \boldsymbol{u}_{h}}) = \boldsymbol{u}_h\cdot(\boldsymbol{x}_{g} - \boldsymbol{x_r})
+\end{equation*}
+where $\boldsymbol{u_h}$ is the human control command.
+
+The drawback of heuristic approaches is that information contained in the history of states is typically ignored.
+As a result, the inference is not robust to external noise and can exhibit chatter behavior.
+\subsubsection{Bayesian Approaches}
+Bayesian approaches to intent inference consists of iterative updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
+The Bayesian update equation for the probability distribution over goals is given by
+\begin{equation*}
+\underbrace{p(g_t| \boldsymbol{u}^{1:t}_{\boldsymbol{h}}, \boldsymbol{\Theta})}_{posterior} = \eta \underbrace{p(\boldsymbol{u}^{1:t}_{\boldsymbol{h}} | g_t, \boldsymbol{\Theta})}_{likelihood}\underbrace{p(g_{t-1})}_{prior}
+\end{equation*}
+where $\eta$ is the normalization factor, $\boldsymbol{u}^{1:t}_{\boldsymbol{h}}$ is the entire history of control commands and $\boldsymbol{\Theta}$ denoted all other task-relevant and environment features that informs the inference process.
+Under first-order Markovian assumption the equation can be simplified by only considering the control command at the current time step $t$.
+The likelihood function captures how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed based on certain heuristics.
+Incorporating past history of states becomes cumbersome in Bayesian schemes as estimating the joint likelihood of control commands becomes intractable.
+\subsubsection{Dynamic Neural Field Based Approaches}
+In this approach, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$~\citep{gopinath2017disamb}.
+Recurrent interaction between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
+Historically, dynamic neural fields were conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner1995dynamics, schoner2008dynamical}.
+
+ The dynamical system that governs the time evolution of goal probabilities can be generically written as 
+\begin{equation*}
+\dot{\boldsymbol{p}}(t) = F(\boldsymbol{p}(t), \boldsymbol{u}_h ; \boldsymbol{\Theta})
+\end{equation*}
+where $F$ represents the nonlinear vector field, $\boldsymbol{u}_h$ is the human control input and $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters that affect the time-evolution of the probability distribution.
+The full specification of the neural field is given by
+\begin{multline}\label{eq:dft}
+\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} + \\ \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
+\end{multline}
+where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector containing all ones of dimension $n_g \times 1$, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
+%In the absence of any information or cues, the probability distribution settles to a resting state which is a uniform distribution, that is whenever $\boldsymbol{u}_h = 0$, $\boldsymbol{\xi} = \vec{0}$.
+Given the initial probability distribution at time $t_a$ Equation~\ref{eq:dft} can be solved numerically from $t \in [t_a, t_b]$ using a simple Euler algorithm with a fixed time-step $\Delta t$.
+The design of $\boldsymbol{\xi}$ is informed by what features of the human control input and environment capture the human's underlying intent most effectively.
+We rely on the \textit{directedness} of the human control commands towards a goal, the \textit{proximity} to a goal and the \textit{agreement} between the human commands and robot autonomy.
+
+\section{Shared Control}\label{sec:shared-control}
+In our system, control sharing is achieved with a blending-based paradigm in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
+\subsection{Blending Paradigm}\label{ssec:blending}
+The autonomous control policy generates control command
+$\boldsymbol{u}_r \leftarrow f_{r}(\boldsymbol{x})$
+where $f_{r}(\cdot) \in \mathcal{F}_{r}$, and $\mathcal{F}_{r}$ is the set of all control behaviors corresponding to different tasks. 
+Specifically, let $\boldsymbol{u}_{r,g}$ be the autonomy command associated with goal $g$. The final control command $\boldsymbol{u}$ issued to the robot then is given by
+\begin{equation*}
+\boldsymbol{u} = \alpha\cdot \boldsymbol{u}_{r,g^*} + (1 - \alpha)\cdot \boldsymbol{u}_h
+\end{equation*}
+where $g^*$ is the most confident goal and corresponds to the mode of $\boldsymbol{p}(t)$. The blending parameter, $\alpha$ is a piecewise linear function of the $p(g^*)$ and is specified as
+$$
+\alpha = \left\{
+\begin{array}{ll}
+0 & \quad\quad~~~ p(g^*) \leq \rho_1 \\
+\frac{\rho_3}{\rho_2 - \rho_1}\cdot p(g^*) &  \quad \text{if}\quad \rho_1 < p(g^*) \leq \rho_2  \\
+\rho_3 & \quad\quad~~~ p(g^*) > \rho_2 	
+\end{array}
+\right.
+$$
+with $\rho_i \in [0, 1] \;\forall\; i \in [1,2,3]$ and $ \rho_2 > \rho_1$. 
+In our implementation, we empirically set $\rho_1 = \frac{1.2}{n_g}, \rho_2 = \frac{1.4}{n_g}$ and $ \rho_3 = 0.7$.
+
+The robot control command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field which is defined in all parts of the state space~\citep{khatib1986real}.
+Every goal $g$ is associated with a potential field $\gamma_g$ which treats $g$ as an attractor and all the other goals in the scene as repellers.
+\begin{equation*}
+\dot{\boldsymbol{x}}_r^{attract} = \boldsymbol{x}_{g} - \boldsymbol{x_r}
+\end{equation*}
+where $\boldsymbol{x}_{g}$ is the location of goal $g$.
+Each dimension of $\dot{\boldsymbol{x}}_r^{attract}$ can be interpreted as the magnitude of the attractive \textit{pull} towards the goal along that dimension.
+The repeller velocity is given by
+\begin{equation*}
+\dot{\boldsymbol{x}}_r^{repel} = \sum_{i \in \mathcal{G} \setminus g} \frac{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}{\mu(\norm{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}^2)}
+\end{equation*}
+where $\dot{\boldsymbol{x}}_r$ indicates the velocity of the robot in the world frame, $\mu$ controls the magnitude of the repeller velocity.
+The autonomy command is computed as a summation of these attractor and repeller velocities.
+\begin{equation*}
+\boldsymbol{u}_{r,g} = \dot{\boldsymbol{x}}_r^{attract} + \dot{\boldsymbol{x}}_r^{repel} 
+\end{equation*}
+$\gamma_g$ operates in the full six dimensional Cartesian space, and treats position and orientation as independent potential fields.
+
+\subsection{Maximum Potential Mode Switch Assistance}\label{ssec:maxpot}
+As a baseline for the simulation experiments described in Section~\ref{sec:ed} we also propose a simple greedy mode switch assistance scheme.
+At any given time $t$, the system selects the control mode which has the \textit{maximum attractive pull} towards the goal.
+For each control dimension $k$, the magnitude of the $k^{th}$ dimension of $\dot{\boldsymbol{x}}_r^{attract}$ is a measure of the attractive pull along $k$.
+Each control mode $m \in \mathcal{M}$ is summarized by the total attractive potential of all control dimensions $k$ such that $k \in m$.
+\section{Experimental Evaluation}\label{sec:ed}
+In this section we describe simulation experiments conducted on point-like robots and the simulated robot environment to evaluate the effectiveness of our disambiguation algorithm.
+\subsection{Point Robot Simulation Setup}
+\subsubsection{Robot Workspace}
+Our simulations were performed on point-like robots that reside in $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$ spaces.
+The translational workspace limits were set at $[-0.4m, 0.4m]$ along each translational dimension and the orientation limits were set at $[0, 2\pi]$ along each rotational axis.
+Table~\ref{tbl:manip} lists all the factors there were randomized and manipulated for each trial.
+\begin{table}[t]
+	\centering
+	\begin{tabular}{|p{3cm}|p{3cm}|}
+		\hline
+		\textbf{Variable} &\textbf{Range}  \\ \hline
+		$n_g$ &  $[2,6]$ \\ \hline
+		$\mathcal{M}$ & Randomly selected from Table~\ref{tbl:cmp} conditioned on the space\\ \hline
+		Intent Inference & ['Conf', 'Bayes', 'DFT] \\ \hline
+		Initial Robot Position & Randomized within workspace limits \\ \hline
+		Goal Positions & Randomized within workspace limits \\ \hline
+		Intended Goal & Randomly chosen from $\mathcal{G}$ \\ \hline
+	\end{tabular}
+	\vspace{.2cm}
+	\caption{Randomized Factors for Each Simulation Trial} 
+	\label{tbl:manip}
+	\vspace{-.5cm}
+\end{table}
+
+\subsubsection{Mode Switch Schemes}
+Four different mode switching schemes were activated during each simulation trial, three of which performed intent disambiguation and one which served as a baseline for comparison.
+The disambiguation algorithms were entropy-based (Section~\ref{sssec:ent}), KL-Divergence based (Section~\ref{sssec:kl}) and a heuristic-based approach which was developed in an earlier work~\citep{gopinath2017mode}.
+We used the mode switching scheme described in Section~\ref{ssec:maxpot} as the baseline for comparison.
+\subsubsection{Simulated $\boldsymbol{u_r}$ and $\boldsymbol{u_h}$}
+The simulated robot autonomy $\boldsymbol{u^{sim}_r}$ is generated using a repeller-free potential field.
+In a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u^{sim}_h}$ is given by
+\begin{equation*}
+\boldsymbol{u^{sim}_h} = \argmax_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)} \boldsymbol{u_h}\cdot(\boldsymbol{x_g}^{intended} - \boldsymbol{x_r})
+\end{equation*}
+where $\boldsymbol{x_g}^{intended}$ is the position of the human's intended goal which is known only to the human and the system tries to infer using the inference scheme.
+This model of simulated human control command assumes that the user issues control commands at all times and always tries to optimize for distance and time.
+The final control command issued to the point robot was determined by the blending-based shared control scheme described in Section~\ref{sec:shared-control}.
+\subsubsection{Metrics}
+The following metrics were used to evaluate the efficacy of the disambiguation algorithm compared to the baseline mode switch assistance:
+\begin{itemize}
+%	\item \textit{Task Completion Time (s)}: The amount of time for a successful trial to reach the goal. 
+%	\item \textit{Number of Mode Switches}: This metric refers to the number of times the control mode switch from the current mode to a different mode. 
+	\item \textit{Initial Onset of Assistance (s)}: Earliest time at which assistance towards the intended goal was triggered.
+This measure captures how \textit{quickly} the robot was able to infer the correct goal  \textit{and} provide assistance.
+	\item \textit{Total Amount of Assistance (\%)}: Fraction of the total trial time for which assistance towards the intended goal was present.  
+	\item \textit{Inference Accuracy (\%)}: Fraction of the total trial time for which the intent inference mechanism correctly inferred the human's intended goal.
+This is a measure of overall confidence of the system.
+\end{itemize}
+
+\subsubsection{Simulation Protocol}
+5000 simulation runs were performed for each of the scenarios. 
+The maximum trial duration was set at $12s$ or equivalently $120$ time-steps with $\Delta t = 0.1$.
+The mode switch assistance algorithm was activated once every $4$ time-steps.
+The trial was ended prematurely if the robot reached within the intended goal as determined by a pre-specified distance threshold.
+ \begin{figure}[h!]
+	\centering
+	\includegraphics[width= 0.8\hsize, height=0.26\vsize]{./figures/WS_SIM.eps}
+	\vspace{-0.35cm}
+	\caption{Example of point-like robot simulation in $\mathbb{R}^2$.
+The goals are represented in black, the initial robot position in red and the human's intended goal in magenta.
+The different colored trajectories correspond to different mode switching schemes.
+Potential-based (Black), Entropy-based (Red), KL Divergence-based (Blue) and Heuristic-based (Green).}
+	\label{fig:ws_sim}
+\end{figure}
+ \begin{figure}[t!]
+	\centering
+	\includegraphics[width= 1.\hsize, height=0.45\vsize]{./figures/initial_alpha.eps}
+	\vspace{-0.75cm}
+	\caption{Group differences for initial onset of assistance for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\label{fig:initial_alpha}
+\end{figure}
+
+\begin{table}[t]
+	\centering
+	\begin{tabular}{|p{1cm}|p{0.5cm}|p{3cm}|}
+		\hline
+		\textbf{Space} & $n_k$ &\textbf{Control Mode Sets}  \\ \hline
+		$\mathbb{R}^2$ & $2$ & $\{[1],[2]\}$ \\ \hline
+		$\mathbb{R}^3$ & $3$ & $\{[1],[2]\}$, $\{[1,2], [3]\}$ \\ \hline
+		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
+		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
+	\end{tabular}
+	\vspace{.2cm}
+	\caption{Predefined control space partition sets for each of the simulation spaces.} 
+	\label{tbl:cmp}
+	\vspace{-.5cm}
+\end{table}
+
+\subsection{MICO Robot Simulation Setup}
+We also evaluated our system in a real robot simulation environment (MICO robotic arm from Kinova Robotics).
+The end effector of the robot lives in $\mathbb{SE}(3)$; however, the physical constraints of the robot make the kinematics highly nonlinear compared to that of a point robot in $\mathbb{SE}(3)$.
+We evaluated the system on two tasks: 1) Four goals with same orientation and 2) five goals with different orientations.
+Two mode switching schemes were tested: KL-divergence based disambiguation and the maximum potential based mode switching.
+For every trial, the robot autonomy was generated using a potential field as described in Section~\ref{ssec:blending}.
+However, unlike the point robot simulation in $\mathbb{SE}(3)$, the simulated human control command was made more realistic by adding noise to the magnitude and direction of the signal.
+
+\section{Results}\label{sec:results}
+
+In this section we present the results from the simulation studies conducted on point-like robots in different spaces.
+One way analysis of variance was performed using Kruskal-Wallis test and post-hoc analysis between groups was conducted using a multiple comparison test that used Tukey's HSD criterion.
+All analysis was performed in MATLAB.
+In all the data plots, (*) indicates $p < 0.05$, (**) indicates $p < 0.01$ and (***) indicates $p < 0.001$.
+\subsection{Initial Onset of Assistance}
+
+Kruskal-Wallis test reveals that the group ranks are different for all simulation scenarios.
+Post-hoc analysis also reveals statistically significant differences between the baseline mode switch assistance scheme and at least one disambiguation scheme for all simulation scenarios (Figure~\ref{fig:initial_alpha}).
+This shows that when the disambiguation scheme is used, the system is able to provide assistance \textit{quicker} and \textit{earlier} during task execution.
+
+\subsection{Amount of Total Assistance}
+%\vspace*{-0.7cm}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width= 1.\hsize, height=0.6\vsize]{./figures/total_assistance.eps}
+	\vspace{-0.8cm}
+	\caption{Group differences for total amount of assistance for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\label{fig:total_assistance}
+\end{figure}
+For all simulation scenarios, Figure~\ref{fig:total_assistance} shows a statistically significant increase in the total amount of assistance when disambiguation schemes are active compared to the baseline.
+This is possibly because disambiguation modes help to \textit{reveal} the intent more clearly \textit{to} the robot.
+As a result the overall confidence in the system's prediction of intended goal increases, thereby resulting in more assistance.
+%\subsection{Number of Mode Switches}
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width= 1.\hsize, height=0.53\vsize]{./figures/num_mode.eps}
+%	\vspace{-0.35cm}
+%	\caption{Group differences for total amount of assistance for different simulation scenarios. Box plots show the median and the quartiles.} 
+%	\label{fig:num_mode}
+%\end{figure}
+%The results in Figure~\ref{fig:num_mode} shows that the number of mode switches is significantly lower for the disambiguation paradigms.
+Furthermore, for all simulation scenarios except $\mathbb{R}^2$, using KL-divergence based disambiguation resulted in the lowest number of mode switches.
+
+\subsection{Inference Accuracy}
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width= 1.\hsize, height=0.35\vsize]{./figures/correct_inference.eps}
+	\vspace{-0.75cm}
+	\caption{Group differences for fractional time for correct goal inference for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\label{fig:correct_inference}
+\end{figure}
+As shown in Figure~\ref{fig:correct_inference}, for all simulation scenarios, except $\mathbb{SE}(2)$, the accuracy of intent inference was higher for the disambiguation schemes compared to the baseline.
+This is likely because of the fact that, disambiguating modes elicit control commands that carry more information regarding the intended goal thereby helping the system to perform accurate intent inference.
+\section{Discussion}\label{sec:discussions}
+\section{Conclusion}\label{sec:conclusions}
 
 \section*{Acknowledgments}
-
+Funding source omitted for review. 
 %% Use plainnat to work nicely with natbib. 
-
+\balance
 \bibliographystyle{plainnat}

### 2018-01-23 Code/Numerical_Fisher/SimulationCode/R2/SimulateTraj_R2_With_Blending.m

@@ -33,7 +33,7 @@ alpha_max = 0.7;
 
 %% PLOT GOALS AND CURRENT ROBOT POSITION. 
 % 
-figure;
+% figure;
 scatter(xg(1,1:ng), xg(2,1:ng), 180, 'k', 'filled'); grid on; hold on;
 scatter(xr(1), xr(2), 140, 'r', 'filled');
 offset = [-0.1, 0.1];
@@ -48,11 +48,13 @@ axis square;
 % generate random user goal index. change color to magenta. 
 random_goal_index = randsample(ng, 1); 
 random_goal = xg(:, random_goal_index);
+%%
 scatter(random_goal(1), random_goal(2), 180, 'm', 'filled'); grid on; hold on;
 
 %%
 intent_types = {'dft', 'conf', 'bayes'};
 intent_type = intent_types{datasample(1:length(intent_types), 1)}; % or conf or bayes
+intnent_type = 'dft';
 
 %% %% USING MAX POTENTIAL AS BASE LINE
 total_time_steps = 120; %with delta_t of 0.1, this amounts to 10 seconds. We will assume that "mode switches" don't take time. 
@@ -373,8 +375,8 @@ scatter(traj_KL(1, :)', traj_KL(2, :)', 'b', 'filled');
 scatter(traj_DISAMB(1, :)', traj_DISAMB(2, :)', 'g', 'filled');
 
 %% PLOT PROBABILITIES AND THE DISAMB MODES. 
-plot_script;
-plot_goal_match;
+% plot_script;
+% plot_goal_match;
 
 %% generate u_h
 function uh = generate_full_uh(xg, xr) %full unnomralized uh

### 2018-01-23 Code/Numerical_Fisher/SimulationCode/R2/WorkspaceSim/SimulateR2_Workspace.m

@@ -55,7 +55,7 @@ ws_points = [X(:) Y(:)];
 disamb_modes_ENT = zeros(size(ws_points, 1), 1);
 disamb_modes_KL = zeros(size(ws_points, 1), 1);
 pg0 = (1/ng)*ones(ng,1); %at every workspace point the starting probability distribution is uniform. 
-pg0 = rand(ng, 1); pg0 = pg0/sum(pg0);
+% pg0 = rand(ng, 1); pg0 = pg0/sum(pg0);
 current_optimal_mode_ENT = cm{datasample(1:num_modes, 1)};
 current_optimal_mode_KL = cm{datasample(1:num_modes, 1)};
 %%

### 2018-01-23 Code/Numerical_Fisher/SimulationCode/R2/compute_projected_entropy_R2.m

@@ -1,7 +1,7 @@
 function [ Upsilon ] = compute_projected_entropy_R2( uh, varargin )
 %UNTITLED8 Summary of this function goes here
 %   Detailed explanation goes here
-projection_time = 1.5;
+projection_time = 1;
 projected_pg = compute_pg_projection_R2(uh, projection_time, varargin{:});
 Upsilon = compute_pg_entropy(projected_pg);
 % Upsilon = compute_kl_div(projected_pg, varargin{3});

### 2018-01-23 Code/Numerical_Fisher/SimulationCode/R2/compute_projected_kl_R2.m

@@ -1,7 +1,7 @@
 function [ Upsilon ] = compute_projected_kl_R2( uh, varargin )
 %UNTITLED8 Summary of this function goes here
 %   Detailed explanation goes here
-projection_time = 1.5;
+projection_time = 1;
 projected_pg = compute_pg_projection_R2(uh, projection_time, varargin{:});
 Upsilon = compute_kl_div(projected_pg, varargin{3});
 

### 2018-01-23 Code/Numerical_Fisher/SimulationCode/SE3/SimulateTraj_SE3_With_Blending.m

@@ -236,7 +236,7 @@ pgs_KL(:, 1) = (1/ng)*ones(ng, 1);%uniform probability to start off with. This i
 current_optimal_mode_KL_index = 1;
 current_optimal_mode_KL = cm{current_optimal_mode_KL_index};
 
-for i=1:total_time_steps
+for i=1:total_time_steps-1
     if compute_dist_to_goal(random_goal_T, xr_T_true)
         fprintf('Within 10 percent of the original separation from goal. Stopping simulation\n');
         break;
@@ -365,7 +365,7 @@ current_optimal_mode_DISAMB_index = 1;
 current_optimal_mode_DISAMB = cm{current_optimal_mode_DISAMB_index};
 mode_comp_timesteps = 4;
 
-for i=1:total_time_steps
+for i=1:total_time_steps-1
     if compute_dist_to_goal(random_goal_T, xr_T_true)
         fprintf('Within 10 percent of the original separation from goal. Stopping simulation\n');
         break;

### 2018-01-23 Code/Numerical_Fisher/SimulationCode/analysis_script.m

@@ -1,0 +1,205 @@
+%%
+% data_parser_new;
+before_timeout_trials = ~(trajectory_time == 11.9); %all trials that did not time out. 
+%% Trajectory Time Analysis. Almost Normal Distribution. Therefore use ANOVA. 
+title_list = {'R^2', 'R^3', 'SE(2)', 'SE(3)'};
+bins = 20;
+sps = cell(4,1);
+% for i=1:length(spaceList)
+%     data = trajectory_time(:, :, i);
+%     fprintf('*****************\n');
+%     fprintf('THE SPACE IS %s\n', spaceList{i});
+% %     close all;
+%      x = []; cond = {};
+%     for j=1:length(condList)
+%         fprintf('THE COND IS %s\n', condList{j});
+%         col = data(before_timeout_trials(:,j,i) == 1, j); %only those trials that did not timeout.
+%         x = [x; col(:)]; cond = cat(1, cond, cellstr(repmat(condList{j}, length(col), 1 )));
+% %         histogram(col, bins); hold on;
+% %         pause;
+%     end
+%     [p, tbl, stats] = anova1(x, cond, 'off');
+%     c = multcompare(stats, 'Display', 'off');
+%     sps{i} = subplot(2,2,i);
+%     bh1 = boxplot(x, cond); 
+%     set(bh1(:,1),'linewidth',2); set(bh1(:,2),'linewidth',2); set(bh1(:,3),'linewidth',2); set(bh1(:,4),'linewidth',2);
+%     title(sps{i}, title_list{i}); 
+%     grid on; xlabel('Mode Switch Assistance'); ylabel('Trial Completion Time');
+%     pvalues = c(:, 6);
+% %     [p,tbl,stats] = kruskalwallis(x, cond);
+%     
+%     
+% end
+
+%% Kruskal Wallis on Initial Alpha Distribution (R2 has no difference...R3, SE2, SE3 showing some difference). 
+% R2
+% for i=1:length(spaceList) %R2, R3, SE2, SE3
+%     data = initial_alpha(:, :, i);
+%     fprintf('*****************\n');
+%     fprintf('THE SPACE IS %s\n', spaceList{i});
+% %     close all;
+%     x = []; cond = {}; maxx = zeros(length(condList), 1);
+%     for j=1:length(condList)
[…]

### 2018-02-01 TexStuff/FirstDraft_TexFile/GopinathArgall_RSS2018.tex
Second draft

--- 2018-01-23 NewTexFile/GopinathArgall_RSS2018.tex
@@
 In order to thoroughly investigate the impact of various components, we present results from an extensive simulation-based study both for point-robots that reside in different spaces as well as on the simulation of a real robotic arm.
-Our results indicate that with the disambiguation algorithm the robot is able to assist earlier during task execution.
-Furthermore, the goal inferences are more accurate and the total amount of assistance greater when operating in the disambiguating modes compared to the baseline.
+Our results indicate that compared to the baseline, with the disambiguation algorithm active the robot is able to assist earlier during task execution, the goal inferences are more accurate and, the total amount of assistance to be higher.
 \end{abstract}
@@
 In this paper, we formulate the problem of intent disambiguation in information-theoretic terms.
-More specifically, we rely on information theoretic notions of \textit{entropy} and \textit{Kullback-Leibler Divergence} to characterize and quantify the intent disambiguation capabilities of a control mode.
+More specifically, we rely on information theoretic notions of \textit{entropy} and \textit{Kullback-Leibler Divergence} (KL-Divergence) to characterize and quantify the intent disambiguation capabilities of a control mode.
 We utilize this characterization of control modes to develop a mode switch assistance paradigm that enhances the robot's intent inference capabilities, by selecting the control mode in which a user-initiated motion will \textit{maximally disambiguate} human intent.
@@
 Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features such as motion cues and the human's underlying intention~\citep{baker2007goal, baker2009action}.
-On the other hand, in model-based approaches, the human is modeled within the Partially Observable Markov Decision Process (MDP)~\citep{taha2011pomdp, dragan2013policy} framework and is assumed to behave according to a control policy that maps states to actions.
+On the other hand, in model-based approaches, the human is modeled within the Partially Observable Markov Decision Process (POMDP)~\citep{taha2011pomdp, dragan2013policy} framework and is assumed to behave according to a control policy that maps states to actions.
 However, in Bayesian schemes, incorporating the entire history of states requires estimation of joint probability distributions that can become quickly intractable.
@@
 Section~\ref{ssec:notation} outlines the mathematical notation used in this paper.
-Section~\ref{ssec:set_modes} presents a set-theoretic treatment of control modes and Section ~\ref{ssec:disamb} describes the disambiguation algorithm.
+Section~\ref{ssec:set_modes} presents a set-theoretic treatment of control modes and Section~\ref{ssec:disamb} describes the disambiguation algorithm.
 The mathematical details of the intent inference paradigms are outlined in detail in Section~\ref{ssec:inference}.
@@
 Let $\mathcal{K}$ be the set of all controllable dimensions of the robot and $k^i$ represent the $i^{th}$ control dimension where $i \in [1,2,\dots,n_k]$ with $n_k = \vert\mathcal{K}\vert$.
-The number of controllable dimensions ($n_k$) depends on the robotic platform used.
 Let $\boldsymbol{x_r}$ denote the position of the robot's end-effector position with respect to the world frame.
-The mathematical space in which $\boldsymbol{x_r}$ resides and the number of controllable dimensions depends on the robotic platform.
+The mathematical space in which $\boldsymbol{x_r}$ resides and the number of controllable dimensions ($n_k$) depends on the robotic platform.
 For example, a 2D point robot that operates has $\boldsymbol{x_r} \in \mathbb{R}^2$, whereas a 6DOF robotic manipulator has $\boldsymbol{x_r} \in \mathbb{SE}(3)$.
@@
 Additionally, let $m^i$ refer to the $i^{th}$ control mode where $i \in [1,2,\dots,n_m]$.
-Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i$ spans all of the controllable dimensions.
+Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i = \mathcal{K}$.
 The cardinality of each mode denoted by $\vert m \vert$ indicates the number of dimensions that can be controlled when operating in $m$.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
-That is, for each $m \in \mathcal{M}$, the subspace of $\mathcal{R}^{n_k}$ that is accessible corresponds to $\mathcal{R}^{\vert m \vert}$ whose basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
+That is, for each $m \in \mathcal{M}$, the subspace of $\mathcal{R}^{n_k}$ that is accessible corresponds to $\mathcal{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
 Maximum velocity limits along each dimension imposes further constraints on the set of control commands that are available in each mode.
@@
 Without loss of generality, the velocity limits can be different for different control dimensions in which case $\mathcal{U}^m$ will correspond to a hypercuboid.
-Figure 1 represents this in a pictorial fashion for a robot residing in $\mathbb{R}^2$.
+Figure 1 represents this in a pictorial fashion for $\mathbb{R}^2$.
  \begin{figure}[h]
@@
 
-The first step towards the computation of the disambiguation metric $D_m$ is the forward projection of the probability distribution $\boldsymbol{p}(t)$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
+The first step towards the computation of the disambiguation metric $D_m$ for each $m \in \mathcal{M}$ is the forward projection of the probability distribution $\boldsymbol{p}(t)$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
 The exact computation of the projected probability distribution will depend on the underlying intent inference computation---for example, whether it depends on $\boldsymbol{x_r}$ (which can be computed from $\boldsymbol{u}_h$ applied to the robot kinematics model) or $\boldsymbol{u}_h$.
@@
 For the purposes of computation of the disambiguation metric, in each mode $m \in \mathcal{M}$, we only consider the set containing the ``vertices'' of the $\vert m \vert$-cube, denoted by $Vert(\mathcal{U}^m)$.
-The probabilities are forward projected for each of the possible control commands available in $Vert(\mathcal{U}^m)$ (Algorithm~\ref{alg:disamb}, Lines 5-9) and a weighted average of all disambiguation metric computations on each of the projected probabilities is used to characterize the control mode $m$.
+The probabilities are forward projected for each of the possible control commands available in $Vert(\mathcal{U}^m)$ and a weighted average of all disambiguation metric computations on each of the projected probabilities is used to characterize the control mode $m$ (Algorithm~\ref{alg:disamb}, Lines 3-11).
 In the following sub-sections we present two different methods to compute the disambiguation metric for a given mode $m$.
@@
 	\caption{Illustration of computation of $D_m$ in $\mathbb{R}^2$.
-The goals are shown in red, green and blue and the robot is depicted in black.
+The goals are shown in red, green and blue and the robot in black.
 The probability distributions are forward projected for all $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
 The change in the overall shape of the probability distribution upon evolving from $\boldsymbol{p}(t_a)$ to $\boldsymbol{p}(t_b)$ amounts to the information `gain' and is captured by the \textit{KL-Divergence}.
-The entropy of $\boldsymbol{p}(t_b)$ captures the information `content' present in the distribution.}
+The entropy of $\boldsymbol{p}(t_b)$ captures the information `content' in the projected distribution.}
 	\label{fig:disamb_compute}
@@
 \subsubsection{Entropy Based Disambiguation Metric}\label{sssec:ent}
-The entropy of the probability distribution is reflective of the average information content of a stochastic source of data.
+The entropy of the probability distribution is captures the average information content of a stochastic source of data.
 For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$, the Shannon entropy is defined as
@@
 \subsubsection{KL-Divergence Based Metric}\label{sssec:kl}
-KL-Divergence, also known relative entropy, measures how one probability distribution differ from another distribution.
+KL-Divergence, also known as relative entropy, measures how one probability distribution differ from another distribution.
 KL-Divergence is widely used in the context of Bayesian inference to compute the information gain when the prior is updated to the posterior in the light of new evidence.
@@
 In the context of disambiguation we can treat the projected probability distribution as the posterior and distribution at time $t_a$ to be the prior.
-KL-Divergence can then be used to characterize the information gain regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
+KL-Divergence can then be used to characterize the \textit{information gain} regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
 More specifically, the disambiguation capability of control mode $m$ is computed by averaging the information gain for all possible control commands $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
@@
 For every goal $g \in \mathcal{G}$, the system maintains an associated set of confidences denoted by $\mathcal{C}$.
-The system designer has the freedom to choose the set of features that will inform the confidences.
+The system designer has the freedom to choose the set of features that will inform the confidence functions.
 For example, a simple proximity-based confidence function used extensively in literature is
@@
 
-The drawback of heuristic approaches is that information contained in the history of states is typically ignored.
+One of the drawbacks of heuristic approaches is that information contained in the history of states is typically ignored.
 As a result, the inference is not robust to external noise and can exhibit chatter behavior.
@@
 where $\eta$ is the normalization factor, $\boldsymbol{u}^{1:t}_{\boldsymbol{h}}$ is the entire history of control commands and $\boldsymbol{\Theta}$ denoted all other task-relevant and environment features that informs the inference process.
+The likelihood function is related to how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed based on certain heuristics.
+Incorporating past history of states becomes cumbersome in Bayesian schemes as estimating the joint likelihood of control commands becomes intractable.
 Under first-order Markovian assumption the equation can be simplified by only considering the control command at the current time step $t$.
-The likelihood function captures how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed based on certain heuristics.
-Incorporating past history of states becomes cumbersome in Bayesian schemes as estimating the joint likelihood of control commands becomes intractable.
 \subsubsection{Dynamic Neural Field Based Approaches}
 In this approach, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$~\citep{gopinath2017disamb}.
-Recurrent interaction between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
+Recurrent interactions between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
 Historically, dynamic neural fields were conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner1995dynamics, schoner2008dynamical}.

### 2018-02-01 TexStuff/SecondDraft_TexFile/GopinathArgall_SecondDraftRSS2018.tex
Second draft

--- 2018-02-01 TexStuff/FirstDraft_TexFile/GopinathArgall_RSS2018.tex
@@
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+\def\bibfont{\footnotesize}
 \pdfinfo{
@@
 \title{Information Theoretic Formulation of Intent Disambiguation}
-\author{Author Names Omitted for Anonymous Review. Paper-ID [\textbf{163}]}
+\author{Author Names Omitted for Anonymous Review.}
 % You will get a Paper-ID when submitting a pdf file to the conference system
@@
 \begin{abstract}
+The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately.
 In this paper, we formulate the problem of intent disambiguation in information theoretic terms.
-We propose two different control mode selection schemes for intent disambiguation using information theoretic ideas of \textit{entropy} and \textit{Kullback-Leibler Divergence} for an assistive robotic manipulator.
-The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions and provide appropriate types of assistance quickly and accurately.
-The proposed algorithms characterize the disambiguation capabilities of different control modes by the forward projection of probability distributions over goals and computing the average information gain and content.
-Our previous exploratory pilot studies revealed that the success of the disambiguation system depends on a variety of factors and choice of parameters.
-In order to thoroughly investigate the impact of various components, we present results from an extensive simulation-based study both for point-robots that reside in different spaces as well as on the simulation of a real robotic arm.
-Our results indicate that compared to the baseline, with the disambiguation algorithm active the robot is able to assist earlier during task execution, the goal inferences are more accurate and, the total amount of assistance to be higher.
+We propose two different methods for intent disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}.
+The proposed algorithms characterize the disambiguation capabilities of the system by the forward projection of probability distributions over goals utilizing an intent inference scheme and a kinematics model and computing the average information gain and content.
+Previous studies have shown that the success of a disambiguation algorithm depends on a variety of factors and parameters.
+To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for point-like robots and a simulated robotic arm.
+Our results indicate that, compared to a baseline, the proposed disambiguation algorithms allow the robot to assist earlier during task execution.
+Additionally, we find that goal inference is more accurate and the total amount of assistance provided is higher.
 \end{abstract}
@@
 \section{Introduction}
-Assistive shared-control machines such as robotic arms, smart wheelchairs  and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result injuries to the central nervous system~\citep{laplante1992assistive}.
-These machines can promote independence, enhance the quality of lives and revolutionize the way they interact with society.
-They can also help to extend the mobility and manipulation capabilities of individuals thereby helping motor-impaired people perform activities of daily living in a more effective manner.
+Assistive machines such as robotic arms, smart wheelchairs  and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result injuries to the central nervous system~\citep{laplante1992assistive}.
+These machines can promote independence, enhance the quality of lives and revolutionize the way people interact with society.
+They can also help extend the mobility and manipulation capabilities of individuals thereby helping motor-impaired people perform activities of daily living in a more effective manner.
 
-An assistive robotic machine is typically controlled using control interfaces such as joysticks, switch-based head arrays and sip-and-puffs.
-These interfaces are low-dimensional, low-bandwidth and occasionally discrete, and can operate only in subsets of the entire control space.
+An assistive robotic machine is typically controlled using a control interface such as a joystick, a switch-based head array or a sip-and-puff.
+These interfaces are low-dimensional, low-bandwidth and occasionally discrete.
+For this reason, they can often only operate in a subset of the entire control space.
 These subsets are referred to as \textit{control modes}.
 The efficacy of assistive machines rely on their ability to infer the users' needs and intentions and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately.
-Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, the users are constrained to produce control commands that likely does not reveal the true intent in an unambiguous and expressive manner.
-That is, the control interfaces act like filters that restrict the amount of information regarding intent that gets passed through.
+Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, users are constrained to produce control commands that likely do not reveal their true intent.
+That is, the control interfaces act like filters that restrict the amount of information regarding the user's intent that gets passed through.
 %Furthermore, sparsity and noise in the control commands make the inference process even harder prompting the need for robust intent inference formalisms. 
+In the context of assistive robotic manipulation, the first step of a task is often to reach for, and grasp, discrete objects in the environment.
+Therefore, \textit{intent inference} can be cast as a problem of computing the probability distributions over all possible discrete goals (objects) in the workspace.
+To estimate the most probable goal, intent inference mechanisms typically rely on various environmental cues and task-relevant features such as the robot and goal positions, human control commands and biometric measures.
+In contrast, our system infers intent primarily based on the information contained in the constrained control commands issued to the assistive machine.
+This approach is more cost effective and more likely to be accepted by the users.
 
-In the context of assistive robotic manipulation, often the first step of a task is to reach for and grasp discrete objects in the environment.
-Therefore, intent inference can be cast as a problem of maintaining the probability distribution over all possible discrete goals (objects) in the workspace.
-Intent inference mechanisms typically rely on various environmental cues and task-relevant features such as robot and goal positions, human control commands and biometric measures for estimating the most probable goal.
-However, due to cost considerations and user acceptance issues, our system tries to infer intent primarily based on the information contained in the constrained control commands issued to the assistive machine.
+Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the robot than others.
+Therefore, by having the human provide input in these modes, the robot can possibly infer the human's underlying intent unambiguously.
+This, in turn, allows the robot to \textit{help assist the human achieve their desired goal earlier}.
+This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating.
+This can likely result lower user satisfaction often with significantly worse performance then either the human or robot could produce on their own.
+In this paper, we address this problem by utilizing our characterization of control modes to develop a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
+To formulate the problem of \textit{intent disambiguation}, we use information theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the intent disambiguation capabilities of each control mode.
 
-Our insight is that the information contained in control commands issued in certain control modes will clarify human's underlying intent unambiguously and is likely to be more useful for the robot to perform accurate intent inference.
-This, in turn will help the robot to appropriate kinds of assistance more effectively.
+%Our insight is that the information contained in control commands issued by the human when operating in certain control modes will be more useful \textit{for} the robot to perform intent inference more accurately.
+This in turn, will clarify the human's underlying intent unambiguously and help the robot to appropriately select the necessary kinds of assistance more effectively.
 In this paper, we formulate the problem of intent disambiguation in information-theoretic terms.
-More specifically, we rely on information theoretic notions of \textit{entropy} and \textit{Kullback-Leibler Divergence} (KL-Divergence) to characterize and quantify the intent disambiguation capabilities of a control mode.
-We utilize this characterization of control modes to develop a mode switch assistance paradigm that enhances the robot's intent inference capabilities, by selecting the control mode in which a user-initiated motion will \textit{maximally disambiguate} human intent.
+Specifically, we rely on information theoretic notions of \textit{entropy} and \textit{Kullback-Leibler divergence} (KL divergence) to characterize and quantify the intent disambiguation capabilities of a control mode.
+We utilize this characterization of control modes to develop a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
 %The disambiguation system will likely elicit more \textit{intent expressive} commands from the user by placing the user control in certain control modes.
 
-In Section~\ref{sec:related_work} we present an overview of relevant research in the areas of shared autonomy in assistive robotics, types of shared autonomy assistance paradigms and use of information theoretic tools in information acquisition.
-Section~\ref{sec:math} presents the set theoretic treatment of control modes mathematical formalism for the intent disambiguation and intent inference.
-Section~\ref{sec:shared-control} focuses on the implementation details of the shared control system.
+In Section~\ref{sec:related_work} we present an overview of relevant research.
+Section~\ref{sec:math} presents set theoretic treatment of control modes followed by intent disambiguation and intent inference in Section~\ref{sec:disamb}.
 The study design and experimental methods are discussed in Section~\ref{sec:ed} followed by results in Section~\ref{sec:results}.
@@
 \section{Related Work}\label{sec:related_work}
-This section presents an overview of related works in the areas of shared autonomy in assistive robotics, robot assistance for modal control, intent inference in human-robot interaction and information acquisition in robotics.
-
-Shared-autonomy in assistive machines aims to reduce the human's physical and cognitive burden during task execution without having the user completely cede manual control~\citep{philips2007adaptive, demeester2008user}.
+This section presents an overview of related works in information acquisition in robotics, intent inference in human-robot interaction and robot assistance for modal control. 
+%
+%Shared-autonomy in assistive machines aims to reduce the human's physical and cognitive burden during task execution without having the user completely cede manual control~\citep{philips2007adaptive, demeester2008user}.
 Some of the common shared-autonomy approaches include (a) hierarchical paradigms in which the higher level goals are entrusted with the user and the autonomy generates low-level control~\citep{kim2012autonomy}, (b) control allocation in distinct partitions of the control space~\citep{driessen2005collaborative} and (c) blending user controls and robot autonomy commands~\citep{muelling2017autonomy}.
 
-Due to the limitations of the control interfaces, users typically have to shift their focus from the task at hand to switching between various control modes during task execution and results in a higher cognitive load.
-Various mode switching assistance paradigms have been proposed to alleviate task effort.
-For example, a time-optimal mode switch assistance~\citep{herlant2016assistive} and heuristic based mode switch assistance to maximize intent disambiguation~\citep{gopinath2017mode}.
+Information theoretic approaches are widely utilized in the field of machine learning and robotics for optimal experiment design, for efficient data collection processes and for informing search strategies.
+Robot assistance schemes that seek to elicit more informative cues \textit{from} the human to clarify the underlying intent can be thought of as an information acquisition problem.
+Intent acquisition can leverage the underlying synergies and shared intentionality~\citep{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions (for example, selecting a control mode or executing a robot motion) that will nudge the human to reveal her/his intent more clearly~\cite{sadigh2016information, sadigh2016planning}.
+Information theoretic metrics such as a KL divergence can be utilized to identify regions of the sample space that will maximize information gain~\citep{tong2001active} and subsequently guide the data sampling process.
+Sensing robots designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\citep{atanasov2014information}.
+If the spatial distribution of information density is known \textit{a priori}, information maximization can be accomplished by maximizing the ergodicity of the robot's trajectory with respect to the underlying information density map~\citep{miller2013trajectory, miller2016ergodic}.
 
 For an assistive machine to provide appropriate kinds of assistance accurately and at the right time, it needs to have a good estimate of the human's underlying intent.
-Intent inference algorithms, therefore, play a vital role in the success of a shared-control assistive system.
+Intent inference algorithms, therefore, play a vital role in the success of a assistive system.
 Intent inference and recognition can be classified into two broad categories: heuristic approaches and model-based approaches.
-Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features such as motion cues and the human's underlying intention~\citep{baker2007goal, baker2009action}.
-On the other hand, in model-based approaches, the human is modeled within the Partially Observable Markov Decision Process (POMDP)~\citep{taha2011pomdp, dragan2013policy} framework and is assumed to behave according to a control policy that maps states to actions.
-However, in Bayesian schemes, incorporating the entire history of states requires estimation of joint probability distributions that can become quickly intractable.
+Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features (such as motion cues) and the human's underlying intention~\citep{baker2007goal, baker2009action}.
+On the other hand, in model-based approaches the system maintains a model of how a human maps states to control actions.
+The model can either be learned from data or can be hand-designed based on domain knowledge.
+For example, the human can be modeled within the Partially Observable Markov Decision Process (POMDP)~\citep{dragan2013policy, taha2011pomdp} framework and is assumed to behave according to a control policy that maps states to actions.
+However, in model-based approaches incorporating the entire history of states requires estimation of joint probability distributions over past states which can become computationally expensive and intractable quickly.
 
-Robot assistance schemes that seeks to elicit more informative cues from the human to clarify the underlying intent can be thought of as an information acquisition problem.
-Intent acquisition can leverage the underlying synergies and shared intentionality~\citep{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions (for example, selecting a control mode or executing a robot motion) that will nudge the human to reveal her/his intent more clearly~\cite{sadigh2016information, sadigh2016planning}.
-More generally, in the field of machine learning and experimental design, active learning is widely used for improving the efficiency of estimating unknown model parameters from data.
-Data collection is time consuming and expensive; therefore, it is necessary to obtain data samples that contain the greatest amount of information regarding the unknown parameters.
-In parameter estimation problems, researchers usually start with a prior distribution on the parameters which then gets updated upon the arrival of new data samples.
-Information theoretic metrics such as a KL-divergence can be utilized to identify regions of the sample space that will maximize information gain~\citep{tong2001active} and subsequently guide the data sampling process.
-Sensing robots designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\citep{atanasov2014information}.
-If the spatial distribution of information density is known \textit{a priori}, information maximization can be accomplished by maximizing the ergodicity of the robot's trajectory with respect to the underlying information density map~\citep{miller2016ergodic, miller2013trajectory}.
+When there is a mismatch between the dimensionality of the problem and the control interface users have to continuously shift their focus from the task at hand to the choice of control mode during task execution, thereby resulting in a higher cognitive load.
+To solve this problem, various mode switching assistance paradigms have been proposed to alleviate task effort.
+For example, an automatic time-optimal mode switch assistance has been proposed which has shown to significantly improve user satisfaction~\citep{herlant2016assistive}.
+In the area of myoelectric prosthetics, dynamic switching approaches that learn the most effective control option during task execution using temporal difference and reinforcement learning have also been proposed~\cite{pilarski2012dynamic}.
 
-\section{Mathematical Formalism}\label{sec:math}
-This section describes the mathematical details of the intent disambiguation algorithm that computes a control mode that can maximally disambiguate between the various goals.
-Section~\ref{ssec:notation} outlines the mathematical notation used in this paper.
+\section{Mathematical Notation}\label{sec:math}
+This section describes the mathematical notation used in our intent disambiguation algorithm that computes a control mode that maximally disambiguates between the various goals.
+We develop this algorithm specifically for robotic manipulation scenarios in which the user is controlling a robotic arm to reach for and interact with various discrete objects in the environment.
+
+% Section~\ref{ssec:notation} outlines the mathematical notation used in this paper.
 Section~\ref{ssec:set_modes} presents a set-theoretic treatment of control modes and Section~\ref{ssec:disamb} describes the disambiguation algorithm.
 The mathematical details of the intent inference paradigms are outlined in detail in Section~\ref{ssec:inference}.
-\subsection{Notation}\label{ssec:notation}
- In assistive robotic manipulation, as the robot is mainly used for reaching toward and grasping of discrete objects in the environment, intent inference is process of estimating the user's intended goal.
+\subsection{Probability Distribution Over Goals}\label{ssec:notation}
+ In assistive robotic manipulation, intent inference is most commonly process of estimating the user's intended goal out of a set of discrete objects in the environment~\citep{calli2015ycb}.
 The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$ and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$.
-At any time $t$, the unknown goal $g$ follows a categorical probability distribution whose sample space is $\mathcal{G}$.
+At any time $t$, the likelihood of goal $g$ being the desired goal follows a categorical probability distribution whose sample space is $\mathcal{G}$.
  That is, 
@@
 The probability $p^i(t)$ represent the robot's \textit{confidence} that goal $g^i$ is the human's intended goal.
-
-Let $\mathcal{K}$ be the set of all controllable dimensions of the robot and $k^i$ represent the $i^{th}$ control dimension where $i \in [1,2,\dots,n_k]$ with $n_k = \vert\mathcal{K}\vert$.
-Let $\boldsymbol{x_r}$ denote the position of the robot's end-effector position with respect to the world frame.
-The mathematical space in which $\boldsymbol{x_r}$ resides and the number of controllable dimensions ($n_k$) depends on the robotic platform.
-For example, a 2D point robot that operates has $\boldsymbol{x_r} \in \mathbb{R}^2$, whereas a 6DOF robotic manipulator has $\boldsymbol{x_r} \in \mathbb{SE}(3)$.
-Lastly, let $\boldsymbol{u_h} \in \mathbb{R}^{n_k}$ denotes the human control command issued via the control interface and $\boldsymbol{u_r} \in \mathbb{R}^{n_k}$ denote the robot autonomy command\footnote{For the rotational control dimensions, the velocity is specified with respect to the end-effector of the robotic frame.}.
 
@@
 Figure 1 represents this in a pictorial fashion for a robot residing in $\mathbb{R}^2$.
+The low dimensionality of the control interfaces necessitates the control space to be partitioned into control modes.
+Let $\mathcal{K}$ be the set of all controllable dimensions of the robot and $k^i$ represent the $i^{th}$ control dimension where $i \in [1,2,\dots,n_k]$ with $n_k = \vert\mathcal{K}\vert$.
+the number of controllable dimensions ($n_k$) depends on the robotic platform; for example, a 2D point robot that operates in $\mathbb{R}^2$ has $n_k = 2$ whereas $n_k =6$ for a 6DoF robotic manipulator.
+%Lastly, let $\boldsymbol{u_h} \in \mathbb{R}^{n_k}$ denotes the human control command issued via the control interface and $\boldsymbol{u_r} \in \mathbb{R}^{n_k}$ denote the robot autonomy command.
 
-The low dimensionality of the control interfaces necessitates the control space $\mathcal{K}$ to be partitioned into control modes.
  Let $\mathcal{M}$ denote the set of all control modes with $n_m = \vert\mathcal{M}\vert$.
@@
 \begin{equation*}
-\mathcal{U}^m = \{\boldsymbol{u} \in \mathcal{R}^{\vert m \vert}, s.t \norm{\boldsymbol{u}}_{\infty} \leq c \} 
+\mathcal{U}^m = \{\boldsymbol{u} | \boldsymbol{u} \in \mathcal{R}^{\vert m \vert} ~ and ~ \norm{\boldsymbol{u}}_{\infty} \leq c \} 
 \end{equation*}
 where $c$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm. 
-Therefore, the set $\mathcal{U}^m$ corresponds to a hypercube of dimensionality $\vert m \vert$ embedded in $\mathcal{R}^{n_k}$.
+%Therefore, the set $\mathcal{U}^m$ corresponds to a hypercube of dimensionality $\vert m \vert$ embedded in $\mathcal{R}^{n_k}$.
 In other words $\mathcal{U}^m$ is a $\vert m \vert$-cube with edge length equals $2c$.
@@
 Figure 1 represents this in a pictorial fashion for $\mathbb{R}^2$.
- \begin{figure}[h]
-	\centering
-	\includegraphics[width= 0.8\hsize, height=0.2\vsize]{./figures/R2_ControlModes.eps}
-	\vspace{-0.35cm}
-	\caption{Illustration of 1D and 2D control modes in a two-dimensional control space, $\mathbb{R}^2$.
+% \begin{figure}[h]
+%	\centering
+%	\includegraphics[width= 0.8\hsize, height=0.2\vsize]{./figures/R2_ControlModes.eps}
+%	\vspace{-0.35cm}
+%	\caption{Illustration of 1D and 2D control modes in a two-dimensional control space, $\mathbb{R}^2$.
 Note that this space can be embedded in a higher dimensional space such as $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
@@
 }
-	\label{fig:r2_modes}
-\end{figure}
+%	\label{fig:r2_modes}
+%\end{figure}
 
@@
 However, the algorithm assumes that $\boldsymbol{p}(t)$ can be forward projected in time by iteratively applying the intent inference algorithm.
-\subsection{Disambiguation Schemes}\label{ssec:disamb}
+\section{Intent Disambiguation}\label{sec:disamb}
 
-The need for intent disambiguation arises from the manner in which the probability distribution over goals evolves as the user controls the robot and performs the task.
-The evolution of the probability distribution is closely related to the choice of intent inference mechanism as well as the features that contribute to it.
-If the evolution is sensitive to the user control command, then it is likely that the goal probabilities evolve in different ways as the user operates the robot in different control modes.
-Our aim is to develop a metric that will estimate the ``disambiguation capability'' of control dimension/mode.
-The hypothesis is that subsequent user operation of the robot in the control mode with maximum disambiguation capability will ``help'' the robot to perform better intent inference and likely will result in providing appropriate kinds of assistance.
+This section describes our two proposed approaches for intent disambiguation using information theoretic concepts and the different intent inference schemes that work in conjunction with the disambiguation algorithms.
 
+\subsection{Need For Intent Disambiguation}
+
+Our aim is to develop a metric that will capture the ``disambiguation capability'' of a control dimension/mode.
+Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely ``help'' the robot to perform better intent inference and may result in the robot providing appropriate kinds of assistance.
+
+At any given time $t$, the probability distributions over goals encodes the human's underlying intent.
+The time evolution of the probability distribution, however, depends on the choice of the intent inference scheme and the various task relevant features and parameters that contribute to it.
+If the evolution is sensitive to the user control command (denoted by $\boldsymbol{u_h}$) then it is likely that the goal probabilities evolve differently as the user operates the robot in different control modes.
+User generated motion along certain control dimensions may reveal the human's intent with less ambiguity.
+That is, intent disambiguation serves as a mechanism that will enhance the accuracy of intent inference.
+Various types of intent inference schemes used in conjunction with the proposed disambiguation algorithms in our paper are described in detail in Section~\ref{ssec:inference}.
+
+\subsection{Forward Projection of $\boldsymbol{p}(t)$}
 The first step towards the computation of the disambiguation metric $D_m$ for each $m \in \mathcal{M}$ is the forward projection of the probability distribution $\boldsymbol{p}(t)$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
-The exact computation of the projected probability distribution will depend on the underlying intent inference computation---for example, whether it depends on $\boldsymbol{x_r}$ (which can be computed from $\boldsymbol{u}_h$ applied to the robot kinematics model) or $\boldsymbol{u}_h$.
+The exact computation of the projected probability distribution will depend on the underlying intent inference computation---for example, whether it depends on the robot position ($\boldsymbol{x_r}$), which can be computed from the human control command (denoted by $\boldsymbol{u}_h$) applied to the robot kinematics model or $\boldsymbol{u}_h$.
 All parameters and features which affect the computation of $\boldsymbol{p}(t)$ are denoted as $\boldsymbol{\Theta}$.
 If the inference mechanism depend on the control command, the projected probability distribution at time $t_b$ given by $\boldsymbol{p}(t_b)$ depends on $\boldsymbol{u_h}$.
-For the purposes of computation of the disambiguation metric, in each mode $m \in \mathcal{M}$, we only consider the set containing the ``vertices'' of the $\vert m \vert$-cube, denoted by $Vert(\mathcal{U}^m)$.
-The probabilities are forward projected for each of the possible control commands available in $Vert(\mathcal{U}^m)$ and a weighted average of all disambiguation metric computations on each of the projected probabilities is used to characterize the control mode $m$ (Algorithm~\ref{alg:disamb}, Lines 3-11).
+For the purposes of computation of the disambiguation metric, in each mode $m \in \mathcal{M}$, we only consider a subset of control commands from $\mathcal{U}^m$, and is denoted by $Vert(\mathcal{U}^m)$.
+The set $Vert(\mathcal{U}^m)$ is given by
+\begin{equation*}
+Vert(\mathcal{U}^m) = \{\boldsymbol{u} \in \mathcal{U}^m ~|~ \boldsymbol{u} = \argmax_{\boldsymbol{u} \in \mathcal{U}^m} \norm{\boldsymbol{u}}_{2}\}
+\end{equation*}
+where $\norm{\cdot}_2$ is the Euclidean norm.\footnote{$Vert(\mathcal{U}^m)$ corresponds to the ``vertices'' of the $|m|$-dimensional hypercube that is the space of control commands accessible from mode $m$.}
+
+The probabilities are forward projected for each of the possible control commands available in $Vert(\mathcal{U}^m)$ and a weighted average of the disambiguation metric computations on each of the projected probabilities is used to characterize the control mode $m$ (Algorithm~\ref{alg:disamb}, Lines 3-11).
 In the following sub-sections we present two different methods to compute the disambiguation metric for a given mode $m$.
@@
 The probability distributions are forward projected for all $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
-The change in the overall shape of the probability distribution upon evolving from $\boldsymbol{p}(t_a)$ to $\boldsymbol{p}(t_b)$ amounts to the information `gain' and is captured by the \textit{KL-Divergence}.
-The entropy of $\boldsymbol{p}(t_b)$ captures the information `content' in the projected distribution.}
+The change in the overall shape of the probability distribution upon evolving from $\boldsymbol{p}(t_a)$ to $\boldsymbol{p}(t_b)$ amounts to the information \textit{gain} and is captured by the \textit{KL divergence}.
+The entropy of $\boldsymbol{p}(t_b)$ captures the information \textit{content} in the projected distribution.}
 	\label{fig:disamb_compute}
@@
 
-\subsubsection{Entropy Based Disambiguation Metric}\label{sssec:ent}
-The entropy of the probability distribution is captures the average information content of a stochastic source of data.
+\subsection{Entropy Based Disambiguation Metric}\label{sssec:ent}
+The entropy of the probability distribution captures the average information content of a stochastic source of data.
+Lower entropy indicates higher certainty in the value of the random variable and vice-versa.
+Therefore, in the context of intent disambiguation entropy of the projected probability distribution, $\boldsymbol{p}(t_b)$, can be used as a measure of how confident the system is in its prediction of human intent.
+That is, entropy can be used a measure of disambiguation.
+Lower the entropy better the disambiguation due to higher certainty in the human's intended goal.
 For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$, the Shannon entropy is defined as
-
 \begin{equation*}
@@
 where $P(X)$ denotes the probability mass function.
-
-Lower entropy indicates higher certainty in the value of the random variable and vice-versa.
-Therefore, entropy of the projected probability distribution, $\boldsymbol{p}(t_b)$, can be used as a measure of how confident the system is in its prediction of human intent.
-That is, entropy can be used a measure of disambiguation.
-Lower the entropy better the disambiguation due to higher certainty in the human's intended goal.
 The disambiguation capability of a control mode $m$ is characterized by computing a weighted average of the entropies of projected probability distributions for all possible control commands $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
@@
 where $\boldsymbol{p}(t_b; \boldsymbol{u_h})$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is $\boldsymbol{u_h}$.
-\subsubsection{KL-Divergence Based Metric}\label{sssec:kl}
-KL-Divergence, also known as relative entropy, measures how one probability distribution differ from another distribution.
-KL-Divergence is widely used in the context of Bayesian inference to compute the information gain when the prior is updated to the posterior in the light of new evidence.
-For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$ the KL-Divergence is defined by
+\subsection{KL divergence Based Metric}\label{sssec:kl}
+Although entropy can capture information \textit{content}, intent disambiguation can likely benefit from the quantification of the information \textit{gain} regarding the human's intended goal as a result of user-initiated motion in a control mode $m$.
+KL divergence, also known as relative entropy, measures how one probability distribution differs from another distribution.
+KL divergence is widely used in the context of Bayesian inference to compute the information gain when the prior is updated to the posterior in the light of new evidence.
+In the context of disambiguation we can treat the projected probability distribution as the posterior and distribution at time $t_a$ to be the prior.
+KL divergence can then be used to characterize the \textit{information gain} regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
+For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$ the KL divergence is defined by
 \begin{equation*}
@@
 where $P(X)$ and $Q(X)$ are two different probability mass distributions. 
-In the context of disambiguation we can treat the projected probability distribution as the posterior and distribution at time $t_a$ to be the prior.
-KL-Divergence can then be used to characterize the \textit{information gain} regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
   More specifically, the disambiguation capability of control mode $m$ is computed by averaging the information gain for all possible control commands $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
@@
 \subsection{Intent inference}\label{ssec:inference}
-This section describes the different types of intent inference schemes used in this paper.
-Our preliminary pilot studies indicated that the disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms.
+  The disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms.
+The update rule for the probability distribution over goals is determined by the choice of inference schemes (Algorithm~\ref{alg:disamb}, Line 6) as a result of which the projected probability distributions, $\boldsymbol{p}(t_b)$ and the disambiguation metric $D_m$, likely are going to be different.
+This section describes the different types of intent inference schemes that work in conjunction with the disambiguation algorithms proposed in Section~\ref{sec:disamb}.
 %This is because, during the forward projection step, different intent update schemes result in different projections and affects the computation of the disambiguation metric.
@@
 \subsubsection{Heuristic Approaches}
-Heuristic approaches based on \textit{confidence} functions seek to find direct mappings between instantaneous cues and underlying human intentions.
+Heuristic approaches based on \textit{confidence} functions~\citep{dragan2013policy} seek to find direct mappings between instantaneous cues and underlying human intentions.
 For every goal $g \in \mathcal{G}$, the system maintains an associated set of confidences denoted by $\mathcal{C}$.
@@
 where $\boldsymbol{x_r}$ is the robot position, $\boldsymbol{x_g}$ is the goal position, $r$ is the radius beyond which the confidence function is always 0 and $\norm{\cdot}$ is an appropriate distance metric.
-%A confidence function that relies purely on proximity features, however, ignores all information regarding human intent contained in the control command itself. 
 A slightly more information-rich variant that aims to capture the ``directedness'' of the human control command to a particular goal position is
@@
 where $\boldsymbol{u_h}$ is the human control command.
+These confidence functions rely on instantaneous features and therefore are amnesic and can exhibit chatter behavior~\citep{dragan2012formalizing}.
 
-One of the drawbacks of heuristic approaches is that information contained in the history of states is typically ignored.
+%One of the drawbacks of heuristic approaches is that information contained in the history of states is typically ignored.
 As a result, the inference is not robust to external noise and can exhibit chatter behavior.
 \subsubsection{Bayesian Approaches}
-Bayesian approaches to intent inference consists of iterative updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
+Bayesian approaches to intent inference consists of iteratively updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
 The Bayesian update equation for the probability distribution over goals is given by
@@
 where $\eta$ is the normalization factor, $\boldsymbol{u}^{1:t}_{\boldsymbol{h}}$ is the entire history of control commands and $\boldsymbol{\Theta}$ denoted all other task-relevant and environment features that informs the inference process.
-The likelihood function is related to how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed based on certain heuristics.
-Incorporating past history of states becomes cumbersome in Bayesian schemes as estimating the joint likelihood of control commands becomes intractable.
+The likelihood function is related to how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed utilizing domain knowledge.
 Under first-order Markovian assumption the equation can be simplified by only considering the control command at the current time step $t$.
 \subsubsection{Dynamic Neural Field Based Approaches}
-In this approach, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$~\citep{gopinath2017disamb}.
-Recurrent interactions between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
-Historically, dynamic neural fields were conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner1995dynamics, schoner2008dynamical}.
+Dynamic neural fields are differential equations in time that governs the time evolution of dynamical state variables, with some specific properties such as recurrent interactions between the state variables, robustness to external noise and memory.
+Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner2008dynamical, schoner1995dynamics}.
+When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$~\citep{gopinath2017disamb}.
+%Recurrent interactions between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
 
- The dynamical system that governs the time evolution of goal probabilities can be generically written as 
-\begin{equation*}
-\dot{\boldsymbol{p}}(t) = F(\boldsymbol{p}(t), \boldsymbol{u}_h ; \boldsymbol{\Theta})
-\end{equation*}
-where $F$ represents the nonlinear vector field, $\boldsymbol{u}_h$ is the human control input and $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters that affect the time-evolution of the probability distribution.
+% The dynamical system that governs the time evolution of goal probabilities can be generically written as 
+%\begin{equation*}
+%\dot{\boldsymbol{p}}(t) = F(\boldsymbol{p}(t), \boldsymbol{u}_h ; \boldsymbol{\Theta})
+%\end{equation*}
+%where $F$ represents the nonlinear vector field, $\boldsymbol{u}_h$ is the human control input and $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters that affect the time-evolution of the probability distribution.
 The full specification of the neural field is given by
@@
 \end{multline}
-where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector containing all ones of dimension $n_g \times 1$, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
+where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector containing all ones of dimension $n_g \times 1$, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters that affect the time-evolution of the probability distribution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
 %In the absence of any information or cues, the probability distribution settles to a resting state which is a uniform distribution, that is whenever $\boldsymbol{u}_h = 0$, $\boldsymbol{\xi} = \vec{0}$.
@@
 
-\section{Shared Control}\label{sec:shared-control}
-In our system, control sharing is achieved with a blending-based paradigm in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
-\subsection{Blending Paradigm}\label{ssec:blending}
-The autonomous control policy generates control command
-$\boldsymbol{u}_r \leftarrow f_{r}(\boldsymbol{x})$
-where $f_{r}(\cdot) \in \mathcal{F}_{r}$, and $\mathcal{F}_{r}$ is the set of all control behaviors corresponding to different tasks. 
-Specifically, let $\boldsymbol{u}_{r,g}$ be the autonomy command associated with goal $g$. The final control command $\boldsymbol{u}$ issued to the robot then is given by
+\section{Experimental Evaluation}\label{sec:ed}
+We evaluate the efficacy of the proposed disambiguation algorithm on simulated point-like robots and a simulated robotic manipulator that operates in a \textit{shared-control} setting.
+This section describes the shared-control paradigm used in our experiments and the details of the simulation experiment protocol.
+%In this section we describe our simulation experiments conducted on simulated point-like robots and a simulated robotic manipulator to evaluate the effectiveness of our disambiguation algorithm. 
+\subsection{Shared Control}\label{ssec:shared-control}
+Shared autonomy in assistive robotics aims to reduce the human's physical and cognitive burden during task execution without having the user to completely cede manual control.
+Some common shared-control approaches include (a) hierarchical paradigms in which the choice of a high-level goal is entrusted to the user and the autonomy generates low-level control~\citep{kim2012autonomy} and (b) signal-level paradigms in which the user and robot's control commands are blended together~\citep{muelling2017autonomy}.
+Shared control systems often require a good estimate of the human's intent to determine when and how to share control.
+Therefore, intent inference and disambiguation play a vital role in the seamless operation and success of a shared control system.
+In our experimental evaluation, control-sharing is achieved with a blending-based paradigm in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
+\subsubsection{Robot Autonomy}\label{sssec:autonomy}
+%The autonomous control policy generates control command
+%$\boldsymbol{u}_r \leftarrow f_{r}(\boldsymbol{x})$
+%where $f_{r}(\cdot) \in \mathcal{F}_{r}$, and $\mathcal{F}_{r}$ is the set of all control behaviors corresponding to different tasks. 
+%Specifically, let $\boldsymbol{u}_{r,g}$ be the autonomy command associated with goal $g$.
+
+The robot control command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field which is defined in all parts of the state space~\citep{khatib1986real}.
+Every goal $g$ is associated with a potential field $\gamma_g$ which treats $g$ as an attractor and all the other goals in the scene as repellers.
+That is,
 \begin{equation*}
-\boldsymbol{u} = \alpha\cdot \boldsymbol{u}_{r,g^*} + (1 - \alpha)\cdot \boldsymbol{u}_h
+\dot{\boldsymbol{x}}_r^{attract} = \boldsymbol{x}_{g} - \boldsymbol{x_r}
+\end{equation*}
+ where $\dot{\boldsymbol{x}}_r$ indicates the velocity of the robot, $\boldsymbol{x}_{g}$ is the location of goal $g$.
+Each dimension of $\dot{\boldsymbol{x}}_r^{attract}$ can be interpreted as the magnitude of the \textit{attractive pull} towards the goal along that dimension.
+The repeller velocity is given by
+\begin{equation*}
+\dot{\boldsymbol{x}}_r^{repel} = \sum_{i \in \mathcal{G} \setminus g} \frac{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}{\mu(\norm{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}^2)}
+\end{equation*}
+ $\mu$ controls the magnitude of the repeller velocity. The autonomy command $\boldsymbol{u}_{r,g}$ is computed as a summation of the attractor and repeller velocities.
+%\begin{equation*}
+%\boldsymbol{u}_{r,g} = \dot{\boldsymbol{x}}_r^{attract} + \dot{\boldsymbol{x}}_r^{repel} 
+%\end{equation*}
+%$\gamma_g$ operates in the full six dimensional Cartesian space, and treats position and orientation as independent potential fields. 
+\subsubsection{Blending Paradigm}\label{sssec:blending}
+The final control command $\boldsymbol{u_f}$ issued to the robot then is given by
+\begin{equation*}
+\boldsymbol{u_f} = \alpha\cdot \boldsymbol{u}_{r,g^*} + (1 - \alpha)\cdot \boldsymbol{u}_h
 \end{equation*}
@@
 In our implementation, we empirically set $\rho_1 = \frac{1.2}{n_g}, \rho_2 = \frac{1.4}{n_g}$ and $ \rho_3 = 0.7$.
+\subsubsection{Baseline Mode Switch Assistance}\label{sssec:baseline}
+As a baseline for the simulation experiments described in Section~\ref{sec:ed} we also propose a simple greedy mode switch assistance scheme.
+At any given time $t$, the system selects the control mode which has the \textit{maximum attractive pull} or \textit{maximum potential} towards the goal.
+For each control dimension $k$, the magnitude of the $k^{th}$ dimension of $\dot{\boldsymbol{x}}_r^{attract}$ is a measure of the attractive potential along $k$.
+Each control mode $m \in \mathcal{M}$ is summarized by the total attractive potential of all control dimensions $k \in m$.
 
-The robot control command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field which is defined in all parts of the state space~\citep{khatib1986real}.
-Every goal $g$ is associated with a potential field $\gamma_g$ which treats $g$ as an attractor and all the other goals in the scene as repellers.
-\begin{equation*}
-\dot{\boldsymbol{x}}_r^{attract} = \boldsymbol{x}_{g} - \boldsymbol{x_r}
-\end{equation*}
-where $\boldsymbol{x}_{g}$ is the location of goal $g$.
-Each dimension of $\dot{\boldsymbol{x}}_r^{attract}$ can be interpreted as the magnitude of the attractive \textit{pull} towards the goal along that dimension.
-The repeller velocity is given by
-\begin{equation*}
-\dot{\boldsymbol{x}}_r^{repel} = \sum_{i \in \mathcal{G} \setminus g} \frac{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}{\mu(\norm{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}^2)}
-\end{equation*}
-where $\dot{\boldsymbol{x}}_r$ indicates the velocity of the robot in the world frame, $\mu$ controls the magnitude of the repeller velocity.
-The autonomy command is computed as a summation of these attractor and repeller velocities.
-\begin{equation*}
-\boldsymbol{u}_{r,g} = \dot{\boldsymbol{x}}_r^{attract} + \dot{\boldsymbol{x}}_r^{repel} 
-\end{equation*}
-$\gamma_g$ operates in the full six dimensional Cartesian space, and treats position and orientation as independent potential fields.
-
-\subsection{Maximum Potential Mode Switch Assistance}\label{ssec:maxpot}
-As a baseline for the simulation experiments described in Section~\ref{sec:ed} we also propose a simple greedy mode switch assistance scheme.
-At any given time $t$, the system selects the control mode which has the \textit{maximum attractive pull} towards the goal.
-For each control dimension $k$, the magnitude of the $k^{th}$ dimension of $\dot{\boldsymbol{x}}_r^{attract}$ is a measure of the attractive pull along $k$.
-Each control mode $m \in \mathcal{M}$ is summarized by the total attractive potential of all control dimensions $k$ such that $k \in m$.
-\section{Experimental Evaluation}\label{sec:ed}
-In this section we describe simulation experiments conducted on point-like robots and the simulated robot environment to evaluate the effectiveness of our disambiguation algorithm.
 \subsection{Point Robot Simulation Setup}
@@
 		$\mathcal{M}$ & Randomly selected from Table~\ref{tbl:cmp} conditioned on the space\\ \hline
-		Intent Inference & ['Conf', 'Bayes', 'DFT] \\ \hline
+		Intent Inference & [`Confidence', `Bayes', `DFT'] \\ \hline
 		Initial Robot Position & Randomized within workspace limits \\ \hline
@@
 Four different mode switching schemes were activated during each simulation trial, three of which performed intent disambiguation and one which served as a baseline for comparison.
-The disambiguation algorithms were entropy-based (Section~\ref{sssec:ent}), KL-Divergence based (Section~\ref{sssec:kl}) and a heuristic-based approach which was developed in an earlier work~\citep{gopinath2017mode}.
-We used the mode switching scheme described in Section~\ref{ssec:maxpot} as the baseline for comparison.
+The disambiguation algorithms were entropy-based (Section~\ref{sssec:ent}), KL divergence based (Section~\ref{sssec:kl}) and a heuristic-based approach developed in an earlier work~\citep{gopinath2017mode}.
+We used the mode switching scheme described in Section~\ref{sssec:baseline} as the baseline for comparison.
 \subsubsection{Simulated $\boldsymbol{u_r}$ and $\boldsymbol{u_h}$}
@@
 This model of simulated human control command assumes that the user issues control commands at all times and always tries to optimize for distance and time.
-The final control command issued to the point robot was determined by the blending-based shared control scheme described in Section~\ref{sec:shared-control}.
+The final control command issued to the point robot was determined by the blending-based shared control scheme described in Section~\ref{sssec:blending}.
 \subsubsection{Metrics}
@@
 	\item \textit{Initial Onset of Assistance (s)}: Earliest time at which assistance towards the intended goal was triggered.
-This measure captures how \textit{quickly} the robot was able to infer the correct goal  \textit{and} provide assistance.
+This measure captures how \textit{early} the robot was able to infer the correct goal  \textit{and} provide assistance.
 	\item \textit{Total Amount of Assistance (\%)}: Fraction of the total trial time for which assistance towards the intended goal was present.  
@@
 \end{itemize}
-
+\begin{table}[t]
+	\centering
+	\begin{tabular}{|p{1cm}|p{0.5cm}|p{3cm}|}
+		\hline
+		\textbf{Space} & $n_k$ &\textbf{Control Mode Sets}  \\ \hline
+		$\mathbb{R}^2$ & $2$ & $\{[1],[2]\}$ \\ \hline
+		$\mathbb{R}^3$ & $3$ & $\{[1],[2], [3]\}$, $\{[1,2], [3]\}$ \\ \hline
+		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
+		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
+	\end{tabular}
+	\vspace{.2cm}
+	\caption{Predefined control space partition sets for each of the simulation spaces.} 
+	\label{tbl:cmp}
+	\vspace{-.5cm}
+\end{table}
 \subsubsection{Simulation Protocol}
@@
 The trial was ended prematurely if the robot reached within the intended goal as determined by a pre-specified distance threshold.
+Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point-like robot in $\mathbb{R}^2$.
  \begin{figure}[h!]
 	\centering
-	\includegraphics[width= 0.8\hsize, height=0.26\vsize]{./figures/WS_SIM.eps}
+	\includegraphics[width= 0.8\hsize, height=0.43\vsize]{./figures/WS_SIM.eps}
 	\vspace{-0.35cm}
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.45\vsize]{./figures/initial_alpha.eps}
+	\includegraphics[width= 1.\hsize, height=0.6\vsize]{./figures/initial_alpha.eps}
 	\vspace{-0.75cm}
@@
 
-\begin{table}[t]
-	\centering
-	\begin{tabular}{|p{1cm}|p{0.5cm}|p{3cm}|}
-		\hline
-		\textbf{Space} & $n_k$ &\textbf{Control Mode Sets}  \\ \hline
-		$\mathbb{R}^2$ & $2$ & $\{[1],[2]\}$ \\ \hline
-		$\mathbb{R}^3$ & $3$ & $\{[1],[2]\}$, $\{[1,2], [3]\}$ \\ \hline
-		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
-		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
-	\end{tabular}
-	\vspace{.2cm}
-	\caption{Predefined control space partition sets for each of the simulation spaces.} 
-	\label{tbl:cmp}
-	\vspace{-.5cm}
-\end{table}
-
 \subsection{MICO Robot Simulation Setup}
 We also evaluated our system in a real robot simulation environment (MICO robotic arm from Kinova Robotics).
-The end effector of the robot lives in $\mathbb{SE}(3)$; however, the physical constraints of the robot make the kinematics highly nonlinear compared to that of a point robot in $\mathbb{SE}(3)$.
-We evaluated the system on two tasks: 1) Four goals with same orientation and 2) five goals with different orientations.
-Two mode switching schemes were tested: KL-divergence based disambiguation and the maximum potential based mode switching.
-For every trial, the robot autonomy was generated using a potential field as described in Section~\ref{ssec:blending}.
-However, unlike the point robot simulation in $\mathbb{SE}(3)$, the simulated human control command was made more realistic by adding noise to the magnitude and direction of the signal.
+The end effector of the robot lives in $\mathbb{SE}(3)$; however, the physical constraints of the robot make the kinematics highly nonlinear compared to a point robot in $\mathbb{SE}(3)$.
+We evaluated the system on two reaching tasks: 1) Four goals with same orientation and 2) five goals with different orientations.
+Two mode switching schemes were tested: KL divergence based disambiguation and the maximum potential based mode switching.
+For every trial, the robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy}.
+The control mapping used for the simulations corresponded to that of a 1D discrete switch-based headarray.
+Furthermore, a \textit{sparsity} factor was added to the simulated human control command $\boldsymbol{u^{sim}_h}$ to capture variability in command timing exhibited by humans.
+Ths sparsity factor captured the \textit{idle time} users had during task execution when teleoperating the robot.
+The sparsity was empirically set to be between 20-80\% as informed by the analysis of teleoperation data from previous experiments conducted in our lab.
 
@@
 Kruskal-Wallis test reveals that the group ranks are different for all simulation scenarios.
-Post-hoc analysis also reveals statistically significant differences between the baseline mode switch assistance scheme and at least one disambiguation scheme for all simulation scenarios (Figure~\ref{fig:initial_alpha}).
-This shows that when the disambiguation scheme is used, the system is able to provide assistance \textit{quicker} and \textit{earlier} during task execution.
+Post-hoc analysis also reveals statistically significant differences between the baseline mode switch assistance scheme and at least one of the disambiguation schemes for all simulation scenarios (Figure~\ref{fig:initial_alpha}).
+This shows that when the disambiguation scheme is used, the system is able to provide assistance \textit{earlier} during task execution.
+This is likely due to the fact that with disambiguation the system is able to elicit more informative control commands from the user and narrow down its prediction to the correct goal quicker during task execution.
+As a result, the confidence in the prediction becomes higher and the robot assistance is triggered earlier during a trial.
 
@@
 %The results in Figure~\ref{fig:num_mode} shows that the number of mode switches is significantly lower for the disambiguation paradigms.
-Furthermore, for all simulation scenarios except $\mathbb{R}^2$, using KL-divergence based disambiguation resulted in the lowest number of mode switches.
+Furthermore, for all simulation scenarios except $\mathbb{R}^2$, using KL divergence based disambiguation resulted in the lowest number of mode switches.
 
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.35\vsize]{./figures/correct_inference.eps}
+	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/correct_inference.eps}
 	\vspace{-0.75cm}
@@
 \section{Discussion}\label{sec:discussions}
+Success rate comments. 
+In our experiments a single type of mode switching scheme was utilized for the entire trial.
+Maybe a combination of both might be useful.
+disambiguation in the beginning to clarify intent.
+once intent is clarified use greedy schemes which will ensure reaching the goal.
+Earlier assistance is important for safety critical applications.
+Better tuning of the inference engine.
+Learning likelihood functions from data.
+Using DNNs for capturing the nonlinear filter in DFT.
+Improved kinematics model for the real robot to Real-time learning of user characteristics such as mean amplitude of control commands, how intermittent of persistent the user is issuing control commands.
+All of that can be incorporated into the forward projection to become as accurate as possible.
+Future work.
+More detailed analysis of data to expose the interactions between factors.
+Intent inference schemes that are amnesic might benefit from disambiguation schemes that capture informatoin gain as well as content to offset the lack of information in the probability distributions themselves.
+These simulated experiments have shed light on the efficacy of these systems.
+Full fledged human study will be done.
+Treating this as a mode-scheduling problem?
+Explore second order metrics to capture rate of change of information. Fisher information.
+
 \section{Conclusion}\label{sec:conclusions}

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/DATA_ANALYSIS/MATLAB/loadData_SIM.m

@@ -1,0 +1,105 @@
+initial_alpha = zeros(trials_per_task, length(tasks), total_subjects); %first column is going to be reaching and second column is pouring. each slice is a subject. Each row is one trial for a task
+percentage_correct_inference = zeros(trials_per_task, length(tasks), total_subjects);
+percentage_alpha = zeros(trials_per_task, length(tasks), total_subjects);
+total_time_all = zeros(trials_per_task, length(tasks), total_subjects);
+%%
+for i=1:total_subjects
+    user = subList{i};
+    subid = i;
+    trialId = trialList(i);
+    fnames = dir(user);
+    numfids = length(fnames);
+    for j=3:numfids
+        n = fnames(j).name;
+        load(n);
+        temp = n; n(end-3:end) = [];
+        if i < 10
+            if length(n) == 9
+                trialnum = str2double(n(end-1:end));
+            else
+                trialnum = str2double(n(end));
+            end
+            if strcmp(n(3:4), 'RE')
+                ta = 1;
+            elseif strcmp(n(3:4), 'PO')
+                ta = 2;
+            end
+            if strcmp(task_order{subid}, n(3:4))
+                intended_goal = ph1_trial_mat{trialnum, 4, subid};
+            else
+                intended_goal = ph2_trial_mat{trialnum, 4, subid};
+            end
+        else
+            if length(n) == 10
+                trialnum = str2double(n(end-1:end));
+            else
+                trialnum = str2double(n(end));
+            end
+            if strcmp(n(4:5), 'RE')
+                ta = 1;
+            elseif strcmp(n(4:5), 'PO')
+                ta = 2;
+            end
+            if strcmp(task_order{subid}, n(4:5))
+                intended_goal = ph1_trial_mat{trialnum, 4, subid};
+            else
+                intended_goal = ph2_trial_mat{trialnum, 4, subid};
+            end
+        end
+        
+        total_time_all(trialnum, ta, subid) = total_time;
+        
+        
+        alpha(1, :) = []; %REMOVE ZEROS FROM FIRST ROW. 
+        alpha(:, 2) = alpha(:, 2) - start_time;
+        alpha = trim_data(alpha, false);
+        
+        current_goal(1, :) = [];
+        current_goal(:, 2) = current_goal(:, 2) - start_time;
+        current_goal = trim_data(current_goal, false);
+        
[…]

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/DATA_ANALYSIS/MATLAB/parse_data_SIM.m

@@ -1,0 +1,216 @@
+%% THIS SCRIPT IS RESPONSIBLE FOR LOADING UP ALL DATA FROM THE MAT FILES, USING loadData.m AND STORING THE DATA IN APPROPRIATE
+%% MATRICES ACCORDING TO INTERFACE/CONDITION/TASK COMBINATION. 
+
+clear all; clc; close all;
+
+%%
+subList = {'H1','H2', 'H3', 'H4', 'H5', 'H6', 'H7', 'H8', 'H9', 'H10', 'H11', 'H12', 'H13', 'H14', 'H15', 'H16'};
+total_subjects = length(subList);
+trialList = (1:16)';
+interfaces = {'J2', 'HA'};
+tasks = {'RE','PO'}; %REACHING AND POURING. 
+assis = {'pot', 'kld'};
+task_order = {'RE','RE','RE','RE', 'RE', 'PO','RE', 'PO', 'RE', 'RE', 'PO', 'PO', 'RE', 'PO', 'PO', 'PO'};%,'PO','RE','PO','PO','RE'}; %Phase 1 tasks FOR EACH SUBJECTS. 
+trials_per_task = 16;
+skip_list = {'H3', 'H4', 'H8', 'H9'};
+load('trial_order_testing_32.mat'); % LOAD THE TRIAL ORDER. THIS IS FOR loadData TO CHECK FOR SOME CRITERION. 
+loadData_SIM;
+
+%%
+%percent ALPHA VALUES FOR EACH TRIAL.
+pa_re_jkld = [];
+pa_po_jkld = [];
+pa_re_jpot = [];
+pa_po_jpot = [];
+
+pa_re_hkld = [];
+pa_po_hkld = [];
+pa_re_hpot = [];
+pa_po_hpot = [];
+
+% initial alpha
+ia_re_jkld = [];
+ia_po_jkld = [];
+ia_re_jpot = [];
+ia_po_jpot = [];
+
+ia_re_hkld = [];
+ia_po_hkld = [];
+ia_re_hpot = [];
+ia_po_hpot = [];
+
+%percentage correct inference. 
+pc_re_jkld = [];
+pc_po_jkld = [];
+pc_re_jpot = [];
+pc_po_jpot = [];
+
+pc_re_hkld = [];
+pc_po_hkld = [];
+pc_re_hpot = [];
+pc_po_hpot = [];
+
+%success rate
+su_re_jkld = [];
[…]

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/DATA_ANALYSIS/MATLAB/plotting_script_SIM.m

@@ -1,0 +1,150 @@
+close all;
+%% percentage alpha
+parse_data_SIM;
+interfaces = {'j','h'};
+interface_cells = {'pa_re_jkld', 'pa_po_jkld', 'pa_re_jpot', 'pa_po_jpot';
+                    'pa_re_hkld', 'pa_po_hkld', 'pa_re_hpot', 'pa_po_hpot'};
+interface_cells = {'pc_re_jkld', 'pc_po_jkld', 'pc_re_jpot', 'pc_po_jpot';
+                    'pc_re_hkld', 'pc_po_hkld', 'pc_re_hpot', 'pc_po_hpot'};
+
+interface_cells = {'ia_re_jkld', 'ia_po_jkld', 'ia_re_jpot', 'ia_po_jpot';
+                    'ia_re_hkld', 'ia_po_hkld', 'ia_re_hpot', 'ia_po_hpot'};
+%                 
+% %only headarray data; 
+ha_cells = {'pa_re_hkld', 'pa_po_hkld', 'pa_re_hpot', 'pa_po_hpot'; %plot 1 -  percent assistance
+            'pc_re_hkld', 'pc_po_hkld', 'pc_re_hpot', 'pc_po_hpot';% plot 2 - percent correct inference
+            'ia_re_hkld', 'ia_po_hkld', 'ia_re_hpot', 'ia_po_hpot'}; %plot 3 - initial asistance
+%                
+y1 = 1.0; y2 = 2.0;
+ylims = 1.5*[1.0, 1.0, 1.0];
+
+%group tasks and interfaces. only across assistance conditions
+
+%% 
+v1 = [eval(interface_cells{1, 1}); eval(interface_cells{1, 2}); eval(interface_cells{2, 1}); eval(interface_cells{2, 1})]; %kld group, group tasks and interfaces
+v2 = [eval(interface_cells{1, 3}); eval(interface_cells{1, 4}); eval(interface_cells{2, 3}); eval(interface_cells{2, 4})]; %pot group, group tasks and interfaces
+figure; hold on; grid on;
+bh1 = boxplot(v1, 'positions', y1,'whisker', 50,'Widths', 0.3);set(bh1(:,1),'linewidth',2);
+bh2 = boxplot(v2, 'positions', y2,'whisker', 50,'Widths', 0.3);set(bh2(:,1),'linewidth',2);
+axis([0,3,0,1.0]);
+grid on;
+set(gca,  'fontWeight', 'normal', 'YTick', 0:0.2:1.0);
[…]

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/DATA_ANALYSIS/TRIALFOLDER/create_am_dr_list.m

@@ -1,0 +1,5 @@
+clear all; clc; close all;
+
+num_sub = 32;
+dr = round(0.6*rand(num_sub, 1) + 0.3, 2);
+am = round(0.1*rand(num_sub, 1) + 0.1, 2);

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/DATA_ANALYSIS/analysis_script.m

@@ -1,0 +1,205 @@
+%%
+% data_parser_new;
+before_timeout_trials = ~(trajectory_time == 11.9); %all trials that did not time out. 
+%% Trajectory Time Analysis. Almost Normal Distribution. Therefore use ANOVA. 
+title_list = {'R^2', 'R^3', 'SE(2)', 'SE(3)'};
+bins = 20;
+sps = cell(4,1);
+% for i=1:length(spaceList)
+%     data = trajectory_time(:, :, i);
+%     fprintf('*****************\n');
+%     fprintf('THE SPACE IS %s\n', spaceList{i});
+% %     close all;
+%      x = []; cond = {};
+%     for j=1:length(condList)
+%         fprintf('THE COND IS %s\n', condList{j});
+%         col = data(before_timeout_trials(:,j,i) == 1, j); %only those trials that did not timeout.
+%         x = [x; col(:)]; cond = cat(1, cond, cellstr(repmat(condList{j}, length(col), 1 )));
+% %         histogram(col, bins); hold on;
+% %         pause;
+%     end
+%     [p, tbl, stats] = anova1(x, cond, 'off');
+%     c = multcompare(stats, 'Display', 'off');
+%     sps{i} = subplot(2,2,i);
+%     bh1 = boxplot(x, cond); 
+%     set(bh1(:,1),'linewidth',2); set(bh1(:,2),'linewidth',2); set(bh1(:,3),'linewidth',2); set(bh1(:,4),'linewidth',2);
+%     title(sps{i}, title_list{i}); 
+%     grid on; xlabel('Mode Switch Assistance'); ylabel('Trial Completion Time');
+%     pvalues = c(:, 6);
+% %     [p,tbl,stats] = kruskalwallis(x, cond);
+%     
+%     
+% end
+
+%% Kruskal Wallis on Initial Alpha Distribution (R2 has no difference...R3, SE2, SE3 showing some difference). 
+% R2
+for i=1:length(spaceList) %R2, R3, SE2, SE3
+    data = initial_alpha(:, :, i);
+    fprintf('*****************\n');
+    fprintf('THE SPACE IS %s\n', spaceList{i});
+%     close all;
+    x = []; cond = {}; maxx = zeros(length(condList), 1);
+    for j=1:length(condList)
[…]

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/SE3/SimulateTraj_SE3_With_Blending.m

@@ -539,7 +539,7 @@ function isClose = compute_dist_to_goal(xg_T, xr_T_true)
     fracPosDiff = norm(xr_T(1:3, 4) - xg_T(1:3, 4))/norm(xr_T_true(1:3, 4) - xg_T(1:3, 4)); 
     Rg = xg_T(1:3, 1:3); Rr = xr_T(1:3, 1:3);
     Rdiff_w = Rg*(Rr^-1); 
-    [~,theta] = AxisAng3(MatrixLog3(Rdiff_w)); %If Rg and Rr are close to each other, Rdiff will be close to identity and theta will be close to 0. 
+    [~,theta] = AxisAng3(MatrixLog3(Rdiff_w)); %If Rg and Rr are close to each other, Rdiff wil l be close to identity and theta will be close to 0. 
     if fracPosDiff <= exit_threshold && theta < ori_threshold
         isClose = true;
     else

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/analysis_script.m

@@ -1,205 +1,0 @@
-%%
-% data_parser_new;
-before_timeout_trials = ~(trajectory_time == 11.9); %all trials that did not time out. 
-%% Trajectory Time Analysis. Almost Normal Distribution. Therefore use ANOVA. 
-title_list = {'R^2', 'R^3', 'SE(2)', 'SE(3)'};
-bins = 20;
-sps = cell(4,1);
-% for i=1:length(spaceList)
-%     data = trajectory_time(:, :, i);
-%     fprintf('*****************\n');
-%     fprintf('THE SPACE IS %s\n', spaceList{i});
-% %     close all;
-%      x = []; cond = {};
-%     for j=1:length(condList)
-%         fprintf('THE COND IS %s\n', condList{j});
-%         col = data(before_timeout_trials(:,j,i) == 1, j); %only those trials that did not timeout.
-%         x = [x; col(:)]; cond = cat(1, cond, cellstr(repmat(condList{j}, length(col), 1 )));
-% %         histogram(col, bins); hold on;
-% %         pause;
-%     end
-%     [p, tbl, stats] = anova1(x, cond, 'off');
-%     c = multcompare(stats, 'Display', 'off');
-%     sps{i} = subplot(2,2,i);
-%     bh1 = boxplot(x, cond); 
-%     set(bh1(:,1),'linewidth',2); set(bh1(:,2),'linewidth',2); set(bh1(:,3),'linewidth',2); set(bh1(:,4),'linewidth',2);
-%     title(sps{i}, title_list{i}); 
-%     grid on; xlabel('Mode Switch Assistance'); ylabel('Trial Completion Time');
-%     pvalues = c(:, 6);
-% %     [p,tbl,stats] = kruskalwallis(x, cond);
-%     
-%     
-% end
-
-%% Kruskal Wallis on Initial Alpha Distribution (R2 has no difference...R3, SE2, SE3 showing some difference). 
-% R2
-% for i=1:length(spaceList) %R2, R3, SE2, SE3
-%     data = initial_alpha(:, :, i);
-%     fprintf('*****************\n');
-%     fprintf('THE SPACE IS %s\n', spaceList{i});
-% %     close all;
-%     x = []; cond = {}; maxx = zeros(length(condList), 1);
-%     for j=1:length(condList)
[…]

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/data_parser_new.m

@@ -1,148 +1,0 @@
-clear all; close all; clc;
-%%
-spaceList = {'R22', 'R33', 'SE2', 'SE3'}; %R2, R3, SE2, SE3
-condList = {'POT', 'ENT', 'KL', 'DISAMB'};
-delta_t = 0.1;
-total_subjects = 5000;
-
-%% types of data to be looked at
-
-initial_alpha = -999*ones(total_subjects, length(condList), length(spaceList)); %initialize the alpha time as big negative. If it stays like this it means that the assistance was never triggered. 
-trajectory_time = -999*ones(total_subjects, length(condList), length(spaceList));
-percentage_correct_inference = zeros(total_subjects, length(condList), length(spaceList));
-percentage_alpha = zeros(total_subjects, length(condList), length(spaceList)); %for this the chattering has to be detected and snipped. 
-ng_array = zeros(total_subjects, length(spaceList)); %number of goals for each conditions. 
-intent_type_array = cell(total_subjects, length(spaceList));
-num_mode_switches = zeros(total_subjects, length(condList), length(spaceList));
-%%
-for i=1:length(spaceList)
-    dirname = strcat('NEW_',spaceList{i}, '_DATA');
-    fnames = dir(dirname);
-    numfids = length(fnames);
-    for index=3:3 + (total_subjects-1)
-        n = fnames(index).name;
-        disp(n);
-        load(n);
-        k = index - 2;
-        %% compute trajectory time. And trim all data points. 
-        if i < 4
-            %make traj and pgs the same length as everything else. 119 time
-            %steps. !!!!
-            traj_POT(:, end) = []; traj_ENT(:, end) = []; traj_KL(:, end) = []; traj_DISAMB(:, end) = [];
-            pgs_POT(:, end) = []; pgs_ENT(:, end) = []; pgs_KL(:, end) = []; pgs_DISAMB(:, end) = [];
-
-            % trim trajectories properly. 
-            traj_POT(:, ~any(traj_POT)) = []; l_POT = size(traj_POT, 2);
-            traj_ENT(:, ~any(traj_ENT)) = []; l_ENT = size(traj_ENT, 2);
[…]

### 2018-02-01 Code/Numerical_Fisher/SimulationCode/distribution_test.m

@@ -1,6 +1,6 @@
 clear all; clc; close all;
 %%
-N = 10000;
+N = 100;
 rs_array = zeros(N, 1); ds_array = zeros(N, 1);
 max_ng = 6;
 for i=1:N

### 2018-02-02 TexStuff/SecondDraft_TexFile/GopinathArgall_SecondDraftRSS2018.tex
Third Draft

@@
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-\def\bibfont{\footnotesize}
+%\def\bibfont{\footnotesize}
 \pdfinfo{
 	/Author (Deepak Gopinath, Brenna D. Argall)
-	/Title  (Mode Switch Assistance to Human Intent Disambiguation)
-	/CreationDate (January 31 2017)
+	/Title  (Information Theoretic Formulation of Intent Disambiguation)
+	/CreationDate (January 31 2018)
 	/Subject (Robots)
@@
 % paper title
-\title{Information Theoretic Formulation of Intent Disambiguation}
+\title{An Information Theoretic Formalism \\for Intent Disambiguation}
 \author{Author Names Omitted for Anonymous Review.}
@@
 \begin{abstract}
-The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately.
+The effectiveness of assistive robots is closely related to their ability to infer the user's needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately.
 In this paper, we formulate the problem of intent disambiguation in information theoretic terms.
 We propose two different methods for intent disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}.
-The proposed algorithms characterize the disambiguation capabilities of the system by the forward projection of probability distributions over goals utilizing an intent inference scheme and a kinematics model and computing the average information gain and content.
+The proposed algorithms characterize the disambiguation capabilities of the system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content.
 Previous studies have shown that the success of a disambiguation algorithm depends on a variety of factors and parameters.
-To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for point-like robots and a simulated robotic arm.
-Our results indicate that, compared to a baseline, the proposed disambiguation algorithms allow the robot to assist earlier during task execution.
-Additionally, we find that goal inference is more accurate and the total amount of assistance provided is higher.
+To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm.
+Our results indicate that, compared to a baseline, the proposed disambiguation algorithms do facilitate faster intent disambiguation, which in turn allows autonomy assistance to step in earlier during task execution.
+Additionally, we find that goal inference is more accurate and the total amount of time assistance is engaged is higher.
 \end{abstract}
@@
 \section{Introduction}
-Assistive machines such as robotic arms, smart wheelchairs  and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result injuries to the central nervous system~\citep{laplante1992assistive}.
+Assistive machines such as robotic arms and smart wheelchairs have the potential to transform the lives of millions of people with motor impairments.~\citep{laplante1992assistive}.
 These machines can promote independence, enhance the quality of lives and revolutionize the way people interact with society.
-They can also help extend the mobility and manipulation capabilities of individuals thereby helping motor-impaired people perform activities of daily living in a more effective manner.
+They can also help extend the mobility and manipulation capabilities of individuals, thereby helping motor-impaired people perform activities of daily living in a more effective manner.
 
-An assistive robotic machine is typically controlled using a control interface such as a joystick, a switch-based head array or a sip-and-puff.
+An assistive robotic machine is typically controlled using an interface such as a joystick, a switch-based head array or a sip-and-puff.
 These interfaces are low-dimensional, low-bandwidth and occasionally discrete.
 For this reason, they can often only operate in a subset of the entire control space.
-These subsets are referred to as \textit{control modes}.
-The efficacy of assistive machines rely on their ability to infer the users' needs and intentions and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately.
-Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, users are constrained to produce control commands that likely do not reveal their true intent.
-That is, the control interfaces act like filters that restrict the amount of information regarding the user's intent that gets passed through.
+These subsets are referred to as \textit{control modes}~\citep{simpson2008tooth}.
+To schedule and execute switches between control modes can be both mentally and physically demanding, and might be alleviated in part by the introduction of robotics autonomy.
+The efficacy of such autonomy-endowed machines relies on their ability to infer the users' needs and intentions, and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately.
+Due to the dimensionality mismatch between high-dimensional robots and low-dimensional interfaces, the user is constrained to produce control commands that likely do not reveal their true intent.
+That is, the control interfaces act like filters that restrict the amount of information regarding the user's intent that gets passed through to the machine and autonomy.
 %Furthermore, sparsity and noise in the control commands make the inference process even harder prompting the need for robust intent inference formalisms.
-In the context of assistive robotic manipulation, the first step of a task is often to reach for, and grasp, discrete objects in the environment.
+
+In the context of assistive robotic manipulation, the first step of a task is often to reach towards discrete objects in the environment.
 Therefore, \textit{intent inference} can be cast as a problem of computing the probability distributions over all possible discrete goals (objects) in the workspace.
-To estimate the most probable goal, intent inference mechanisms typically rely on various environmental cues and task-relevant features such as the robot and goal positions, human control commands and biometric measures.
+To estimate the most probable goal, intent inference mechanisms typically rely on various environmental cues and task-relevant features such as the robot and goal positions, human control commands and biometric measures~\citep{croft2003estimating}.
 In contrast, our system infers intent primarily based on the information contained in the constrained control commands issued to the assistive machine.
-This approach is more cost effective and more likely to be accepted by the users.
 
-Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the robot than others.
-Therefore, by having the human provide input in these modes, the robot can possibly infer the human's underlying intent unambiguously.
-This, in turn, allows the robot to \textit{help assist the human achieve their desired goal earlier}.
+Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the autonomy than others.
+Therefore, by having the human provide control input within these information-rich modes, the possibility of inferring the human's intent accurately and unambiguously is increased.
+This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.
 This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating.
-This can likely result lower user satisfaction often with significantly worse performance then either the human or robot could produce on their own.
-In this paper, we address this problem by utilizing our characterization of control modes to develop a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
-To formulate the problem of \textit{intent disambiguation}, we use information theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the intent disambiguation capabilities of each control mode.
+This can decrease user satisfaction and result in significantly worse performance than either the human or autonomy would produce on their own.
+In this paper, we address the problem of accurate intent inference by characterizing control modes according to the information content, and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
+We formalize the problem of intent inference within the framework of information theory.
+Specifically, we make use of the information theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the information content---with respect to intent disambiguation---of each control mode.
 
@@
 In Section~\ref{sec:related_work} we present an overview of relevant research.
-Section~\ref{sec:math} presents set theoretic treatment of control modes followed by intent disambiguation and intent inference in Section~\ref{sec:disamb}.
-The study design and experimental methods are discussed in Section~\ref{sec:ed} followed by results in Section~\ref{sec:results}.
+Section~\ref{sec:math} introduces our set theoretic treatment of control modes, followed by intent disambiguation and intent inference in Section~\ref{sec:disamb}.
+The study design and experimental methods are discussed in Section~\ref{sec:ed} followed, by results in Section~\ref{sec:results}.
 Discussion and conclusions are presented in Sections~\ref{sec:discussions} and~\ref{sec:conclusions} respectively.
@@
 \subsection{Probability Distribution Over Goals}\label{ssec:notation}
- In assistive robotic manipulation, intent inference is most commonly process of estimating the user's intended goal out of a set of discrete objects in the environment~\citep{calli2015ycb}.
+ In assistive robotic manipulation, intent inference is most commonly the process of estimating the user's intended goal out of a set of discrete objects in the environment~\citep{calli2015ycb}.
 The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$ and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$.
@@
 $\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots, p^{n_g}(t)]^{T}$ where $p^i(t)$ denotes the probability associated with goal $g^i$.
-The probability $p^i(t)$ represent the robot's \textit{confidence} that goal $g^i$ is the human's intended goal.
+The probability $p^i(t)$ also represents the robot's \textit{confidence} that goal $g^i$ is the human's intended goal.
 
@@
 Let $\mathcal{K}$ be the set of all controllable dimensions of the robot and $k^i$ represent the $i^{th}$ control dimension where $i \in [1,2,\dots,n_k]$ with $n_k = \vert\mathcal{K}\vert$.
-the number of controllable dimensions ($n_k$) depends on the robotic platform; for example, a 2D point robot that operates in $\mathbb{R}^2$ has $n_k = 2$ whereas $n_k =6$ for a 6DoF robotic manipulator.
+The number of controllable dimensions ($n_k$) depends on the robotic platform; for example, a 2D point robot that operates in $\mathbb{R}^2$ has $n_k = 2$ whereas $n_k =6$ for a 6-DoF robotic manipulator.
 %Lastly, let $\boldsymbol{u_h} \in \mathbb{R}^{n_k}$ denotes the human control command issued via the control interface and $\boldsymbol{u_r} \in \mathbb{R}^{n_k}$ denote the robot autonomy command.
@@
 Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i = \mathcal{K}$.
-The cardinality of each mode denoted by $\vert m \vert$ indicates the number of dimensions that can be controlled when operating in $m$.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+The cardinality of each mode $m \in \mathcal{M}$, denoted by $\vert m \vert$ indicates the number of dimensions that can be controlled when operating in $m$.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
 That is, for each $m \in \mathcal{M}$, the subspace of $\mathcal{R}^{n_k}$ that is accessible corresponds to $\mathcal{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
-Maximum velocity limits along each dimension imposes further constraints on the set of control commands that are available in each mode.
-The set of control commands denoted by $\mathcal{U}^m$, can be written as
+Maximum velocity limits along each dimension impose further constraints on the set of control commands that are available in each mode.
+This constrained set of control commands available in mode $m$, denoted by $\mathcal{U}^m$, can be written as
 \begin{equation*}
-\mathcal{U}^m = \{\boldsymbol{u} | \boldsymbol{u} \in \mathcal{R}^{\vert m \vert} ~ and ~ \norm{\boldsymbol{u}}_{\infty} \leq c \} 
+\mathcal{U}^m = \{\boldsymbol{u} | \boldsymbol{u} \in \mathcal{R}^{\vert m \vert} ~ and ~ \norm{\boldsymbol{u}}_{\infty} \leq v_{lim} \} 
 \end{equation*}
-where $c$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm. 
+where $v_{lim}$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm. 
 %Therefore, the set $\mathcal{U}^m$ corresponds to a hypercube of dimensionality $\vert m \vert$ embedded in $\mathcal{R}^{n_k}$.
@@
 
-This section describes our two proposed approaches for intent disambiguation using information theoretic concepts and the different intent inference schemes that work in conjunction with the disambiguation algorithms.
+This section describes our two proposed approaches for intent disambiguation using information theoretic concepts and the different intent inference schemes that work in conjunction with the disambiguation algorithm.
 
@@
 Our aim is to develop a metric that will capture the ``disambiguation capability'' of a control dimension/mode.
-Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely ``help'' the robot to perform better intent inference and may result in the robot providing appropriate kinds of assistance.
+Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely help the robot to perform better intent inference and may result in the robot providing more appropriate assistance.
 
 At any given time $t$, the probability distributions over goals encodes the human's underlying intent.
-The time evolution of the probability distribution, however, depends on the choice of the intent inference scheme and the various task relevant features and parameters that contribute to it.
+The time evolution of the probability distribution, however, depends on the choice of intent inference scheme and the various task relevant features and parameters that contribute to it.
 If the evolution is sensitive to the user control command (denoted by $\boldsymbol{u_h}$) then it is likely that the goal probabilities evolve differently as the user operates the robot in different control modes.
-User generated motion along certain control dimensions may reveal the human's intent with less ambiguity.
-That is, intent disambiguation serves as a mechanism that will enhance the accuracy of intent inference.
-Various types of intent inference schemes used in conjunction with the proposed disambiguation algorithms in our paper are described in detail in Section~\ref{ssec:inference}.
+User-generated motion along certain control dimensions therefore might reveal the human's intent with less ambiguity.
+That is, motion within maximally disambiguating control dimensions serves as a mechanism to enhance the accuracy of intent inference.
+Various types of intent inference schemes used in conjunction with the proposed disambiguation algorithm in our paper are described in detail in Section~\ref{ssec:inference}.
 
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.3\vsize]{./figures/Disamb_Compute.eps}
+	\includegraphics[width= 1.\hsize, height=0.26\vsize]{./figures/Disamb_Compute.eps}
 	\vspace{-0.35cm}
@@
   The disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms.
-The update rule for the probability distribution over goals is determined by the choice of inference schemes (Algorithm~\ref{alg:disamb}, Line 6) as a result of which the projected probability distributions, $\boldsymbol{p}(t_b)$ and the disambiguation metric $D_m$, likely are going to be different.
+The update rule for the probability distribution over goals is determined by the choice of inference schemes (Algorithm~\ref{alg:disamb}, Line 6) as a result of which the projected probability distributions, $\boldsymbol{p}(t_b)$ and the disambiguation metric $D_m$, likely are going to be different for different choices.
 This section describes the different types of intent inference schemes that work in conjunction with the disambiguation algorithms proposed in Section~\ref{sec:disamb}.
@@
 Dynamic neural fields are differential equations in time that governs the time evolution of dynamical state variables, with some specific properties such as recurrent interactions between the state variables, robustness to external noise and memory.
-Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner2008dynamical, schoner1995dynamics}.
+Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner2008dynamical}.
 When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$~\citep{gopinath2017disamb}.
@@
 \subsubsection{Baseline Mode Switch Assistance}\label{sssec:baseline}
-As a baseline for the simulation experiments described in Section~\ref{sec:ed} we also propose a simple greedy mode switch assistance scheme.
-At any given time $t$, the system selects the control mode which has the \textit{maximum attractive pull} or \textit{maximum potential} towards the goal.
+As a baseline for the simulation experiments described in Section~\ref{ssec:sim} we also propose a simple greedy mode switch assistance scheme.
+At any given time $t$, the system selects the control mode which has the \textit{maximum attractive pull} or \textit{maximum potential} towards the predicted goal.
 For each control dimension $k$, the magnitude of the $k^{th}$ dimension of $\dot{\boldsymbol{x}}_r^{attract}$ is a measure of the attractive potential along $k$.
@@
 
-\subsection{Point Robot Simulation Setup}
+\subsection{Point Robot Simulation Setup}\label{ssec:sim}
 \subsubsection{Robot Workspace}
@@
 Four different mode switching schemes were activated during each simulation trial, three of which performed intent disambiguation and one which served as a baseline for comparison.
-The disambiguation algorithms were entropy-based (Section~\ref{sssec:ent}), KL divergence based (Section~\ref{sssec:kl}) and a heuristic-based approach developed in an earlier work~\citep{gopinath2017mode}.
+The disambiguation algorithms were entropy-based (Section~\ref{sssec:ent}), KL divergence based (Section~\ref{sssec:kl}) and a heuristic-based approach developed in a related work~\citep{gopinath2017mode}.
 We used the mode switching scheme described in Section~\ref{sssec:baseline} as the baseline for comparison.
@@
 %	\item \textit{Number of Mode Switches}: This metric refers to the number of times the control mode switch from the current mode to a different mode. 
-	\item \textit{Initial Onset of Assistance (s)}: Earliest time at which assistance towards the intended goal was triggered.
+	\item \textit{Initial Onset of Assistance (s)}: Earliest time at which assistance  was triggered towards the intended goal.
 This measure captures how \textit{early} the robot was able to infer the correct goal  \textit{and} provide assistance.
-	\item \textit{Total Amount of Assistance (\%)}: Fraction of the total trial time for which assistance towards the intended goal was present.  
-	\item \textit{Inference Accuracy (\%)}: Fraction of the total trial time for which the intent inference mechanism correctly inferred the human's intended goal.
+	\item \textit{Total Amount of Assistance }: Fraction of the total trial time for which assistance towards the intended goal was present.  
+	\item \textit{Inference Accuracy }: Fraction of the total trial time for which the intent inference mechanism correctly inferred the human's intended goal.
 This is a measure of overall confidence of the system.
@@
 	\centering
-	\includegraphics[width= 0.8\hsize, height=0.43\vsize]{./figures/WS_SIM.eps}
+	\includegraphics[width= 0.8\hsize, height=0.3\vsize]{./figures/WS_SIM.eps}
 	\vspace{-0.35cm}
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.6\vsize]{./figures/initial_alpha.eps}
+	\includegraphics[width= 1.\hsize, height=0.4\vsize]{./figures/initial_alpha.eps}
 	\vspace{-0.75cm}
@@
 We also evaluated our system in a real robot simulation environment (MICO robotic arm from Kinova Robotics).
-The end effector of the robot lives in $\mathbb{SE}(3)$; however, the physical constraints of the robot make the kinematics highly nonlinear compared to a point robot in $\mathbb{SE}(3)$.
+Although the end effector of the robot lives in $\mathbb{SE}(3)$, the physical constraints of the robot make the kinematics highly nonlinear compared to a point-like robot in $\mathbb{SE}(3)$.
+
 We evaluated the system on two reaching tasks: 1) Four goals with same orientation and 2) five goals with different orientations.
 Two mode switching schemes were tested: KL divergence based disambiguation and the maximum potential based mode switching.
-For every trial, the robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy}.
-The control mapping used for the simulations corresponded to that of a 1D discrete switch-based headarray.
-Furthermore, a \textit{sparsity} factor was added to the simulated human control command $\boldsymbol{u^{sim}_h}$ to capture variability in command timing exhibited by humans.
-Ths sparsity factor captured the \textit{idle time} users had during task execution when teleoperating the robot.
-The sparsity was empirically set to be between 20-80\% as informed by the analysis of teleoperation data from previous experiments conducted in our lab.
+During each trial, the mode-switch algorithm was activated every $5s$ and the maximum trial duration was set at $40s$.
+The robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy} and the control interface mapping was that of a 1D discrete switch-based headarray.
+ Additionally, a \textit{sparsity} factor was added to the simulated human control command $\boldsymbol{u^{sim}_h}$ to capture the variability in command timing exhibited by humans during robot teleoperation.
+This sparsity factor captured the \textit{idle time} users have during task execution when teleoperating a robot and was randomly set between 20\% and 80\% as informed by the analysis of teleoperation data from previous experiments conducted in our lab.
 
@@
 
-In this section we present the results from the simulation studies conducted on point-like robots in different spaces.
-One way analysis of variance was performed using Kruskal-Wallis test and post-hoc analysis between groups was conducted using a multiple comparison test that used Tukey's HSD criterion.
+In this section we present results from our simulation studies conducted on point-like robots and a simulated robotic arm. 
+\subsection{Point-like Robot Simulation}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width= 1.\hsize, height=0.55\vsize]{./figures/total_assistance.eps}
+	\vspace{-0.8cm}
+	\caption{Group differences for total amount of assistance for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\label{fig:total_assistance}
+\end{figure}
+One way analysis of variance was performed using Kruskal-Wallis procedure to test for group effects.
+Post-hoc analysis between groups was conducted using a multiple comparison test that used Tukey's HSD criterion.
 All analysis was performed in MATLAB.
 In all the data plots, (*) indicates $p < 0.05$, (**) indicates $p < 0.01$ and (***) indicates $p < 0.001$.
-\subsection{Initial Onset of Assistance}
-
+\subsubsection{Initial Onset of Assistance}
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width= 1.\hsize, height=1.3\vsize]{./figures/correct_inference.eps}
+	\vspace{-0.75cm}
+	\caption{Group differences for fractional time for correct goal inference for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\label{fig:correct_inference}
+\end{figure}
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width= 1.\hsize, height=1.3\vsize]{./figures/mico_sim_res.eps}
+	\vspace{-0.5cm}
+	\caption{Top Left: Fraction of total time for which assistance towards intended goal was present.
+Top Right: Accuracy of intent inference procedure measured in fraction of total trial time.
+Bottom: Onset of initial assistance as a fraction of total trial time.
+Statistical significance was computed using the Wilcoxon Rank-Sum test, where(*) indicates $p < 0.05$, (**) indicates $p < 0.01$ and (***) indicates $p < 0.001$.
+}
+	\label{fig:mico_results}
+\end{figure}
 Kruskal-Wallis test reveals that the group ranks are different for all simulation scenarios.
@@
 
-\subsection{Amount of Total Assistance}
+\subsubsection{Amount of Total Assistance}
 %\vspace*{-0.7cm}
-\begin{figure}[t]
-	\centering
-	\includegraphics[width= 1.\hsize, height=0.6\vsize]{./figures/total_assistance.eps}
-	\vspace{-0.8cm}
-	\caption{Group differences for total amount of assistance for different simulation scenarios. Box plots show the median and the quartiles.} 
-	\label{fig:total_assistance}
-\end{figure}
+
 For all simulation scenarios, Figure~\ref{fig:total_assistance} shows a statistically significant increase in the total amount of assistance when disambiguation schemes are active compared to the baseline.
-This is possibly because disambiguation modes help to \textit{reveal} the intent more clearly \textit{to} the robot.
-As a result the overall confidence in the system's prediction of intended goal increases, thereby resulting in more assistance.
+The shared control paradigm used in our setup is designed in such a way that the robot assistance gets triggered when the confidence associated with the goal prediction passes a predefined threshold.
+These results indicate that with disambiguation the system is able to maintain the confidence in its prediction of the correct goal above the threshold for a longer duration during the trial resulting in greater overall assistance during the course of the task.
 %\subsection{Number of Mode Switches}
@@
 
-\subsection{Inference Accuracy}
-\begin{figure}[t!]
-	\centering
-	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/correct_inference.eps}
-	\vspace{-0.75cm}
-	\caption{Group differences for fractional time for correct goal inference for different simulation scenarios. Box plots show the median and the quartiles.} 
-	\label{fig:correct_inference}
-\end{figure}
-As shown in Figure~\ref{fig:correct_inference}, for all simulation scenarios, except $\mathbb{SE}(2)$, the accuracy of intent inference was higher for the disambiguation schemes compared to the baseline.
-This is likely because of the fact that, disambiguating modes elicit control commands that carry more information regarding the intended goal thereby helping the system to perform accurate intent inference.
+\subsubsection{Inference Accuracy}
+
+As shown in Figure~\ref{fig:correct_inference}, for all simulation scenarios, the accuracy of intent inference is higher for at least one disambiguation scheme compared to the baseline.
+This is likely because of the fact that robot operation in disambiguating modes results in higher information gain regarding the underlying intent thereby helping the system to perform accurate intent inference.
+
+\subsection{MICO Robot Simulation}
+Figure~\ref{fig:mico_results} reveals that for the simulations conducted on a simulated robotic arm, the onset of initial assistance towards the correct goal is earlier compared to that of the baseline ($p~=~0.049$).
+Similarly, the accuracy of the intent inference procedure is higher when disambiguation algorithm is deployed ($p~=~1.57e$-$4$).
+Although not statistically significant, with disambiguation the total amount of assistance provided by the system is slightly higher compared to the baseline mode-switching scheme.
+These results indicates that even with a low-dimensional and discrete control interface that exhibited signal dropouts (due to the sparsity factor), robot operation in control modes selected by the disambiguation algorithm helps the robot to elicit more intent-revealing control commands thereby helping the robot predict the intended goal more accurately and provide assistance earlier.
 \section{Discussion}\label{sec:discussions}
-Success rate comments. 
-In our experiments a single type of mode switching scheme was utilized for the entire trial.
-Maybe a combination of both might be useful.
-disambiguation in the beginning to clarify intent.
-once intent is clarified use greedy schemes which will ensure reaching the goal.
-Earlier assistance is important for safety critical applications.
-Better tuning of the inference engine.
-Learning likelihood functions from data.
-Using DNNs for capturing the nonlinear filter in DFT.
-Improved kinematics model for the real robot to Real-time learning of user characteristics such as mean amplitude of control commands, how intermittent of persistent the user is issuing control commands.
-All of that can be incorporated into the forward projection to become as accurate as possible.
-Future work.
+
+The effectiveness of an assistive machine in a shared control setting is closely related to its ability to infer the user's intent accurately and unambiguously.
+Accurate goal inference can improve the trust and communication between the human and the robot and can result in seamless and fluid human robot interaction.
+On the other hand, incorrect goal inference can likely lead to frustrating user experience and can often have a detrimental effect on task performance.
+Our results indicate that disambiguation helps to enhance the accuracy of the intent inference procedure and results in an increase in overall assistance provided to the user.
+Yet another factor that is crucial for the success of a shared control system, especially for safety-critical applications, is \textit{when} during task execution the assistance gets activated.
+For example, in shared control of complex systems that exhibit highly nonlinear and unstable dynamics typically the role of autonomy is to maintain stability and safety.
+In such scenarios, if the user operation leads to the destabilization of the system, failure to intervene earlier during task execution can lead to catastrophic results.
+From our simulation results, we can see that intent disambiguation algorithms enhances the inference capabilities of the system and help the robot to provide assistance earlier.
+
+The utility value of a mode-switching scheme can vary during the time course of a single trial.
+For instance, in the beginning stages of task execution when the intent is unclear and the probability distribution over goals is uniform (due to the absence of any cues from the user) disambiguation algorithms are likely to be more useful.
+Once task execution gets underway and intent is clarified, a time-optimal mode switching scheme can be used to lead the user towards successful task completion.
+That is, unlike the simulation experiments in which we used only one type of mode switching scheme during each trial, a more optimal strategy might be one which is adaptive and chooses different schemes depending on the context.
+This could possibly be cast within a control theoretic framework as a mode-scheduling problem in which the question of \textit{when} to deploy \textit{which} mode-switching paradigm can be solved concurrently.
+
+High fidelity models for how a user teleoperates a robot and robot kinematics can be learned from data using machine learning tools such as deep neural networks~\citep{nagabandi2017neural}, Gaussian processes~\citep{wang2013probabilistic}.
+With sufficient data, these techniques have the capability to capture the inherent nonlinearities in human-robot systems.
+Characterization of the disambiguation capabilities of different control modes can benefit a great deal from more accurate models.
+Furthermore, the disambiguation algorithm can be customized to specific users using real-time learning algorithms that capture individual teleoperation characteristics during task execution.
+
+%Future work.
 More detailed analysis of data to expose the interactions between factors.
@@
 Treating this as a mode-scheduling problem?
-Explore second order metrics to capture rate of change of information. Fisher information.
+%Explore second order metrics to capture rate of change of information. Fisher information.
 
 \section{Conclusion}\label{sec:conclusions}
+In this paper, we have formulated the problem of intent disambiguation in information theoretic terms.
+We introduced two different methods for intent disambiguation using the information theoretic concepts of entropy and KL divergence to characterize the disambiguation capabilities of different control modes.
+The algorithm seeks to elicit more informative control commands from the human by placing the control in those modes that will maximally disambiguate their intent.
+We also present results from an extensive simulation-based study for point-like robots and a simulated robotic arm.
+Results from the study indicate that, compared to the baseline, the proposed disambiguation algorithms result in more accurate goal inference.
+Furthermore, the robot is able to assist earlier during task execution and the overall amount of assistance provided is higher.
+In our future work, we plan to perform an in-depth analysis of the data to expose the interactions between various factors.
+Knowledge of how different components interact and influence each other is critical for the design of a successful shared control system.
+Furthermore, as informed by the simulation results, we plan to evaluate our system with an extensive user study.
 

### 2018-02-02 Code/Numerical_Fisher/SimulationCode/DATA_ANALYSIS/MATLAB/parse_data_SIM.m

@@ -4,13 +4,13 @@
 clear all; clc; close all;
 
 %%
-subList = {'H1','H2', 'H3', 'H4', 'H5', 'H6', 'H7', 'H8', 'H9', 'H10', 'H11', 'H12', 'H13', 'H14', 'H15', 'H16'};
+subList = {'H1','H2', 'H3', 'H4', 'H5', 'H6', 'H7', 'H8', 'H9', 'H10', 'H11', 'H12', 'H13', 'H14', 'H15', 'H16', 'H17', 'H18', 'H19', 'H20', 'H21', 'H22'};%, 'H23', 'H24'};
 total_subjects = length(subList);
-trialList = (1:16)';
+trialList = (1:length(subList))';
 interfaces = {'J2', 'HA'};
 tasks = {'RE','PO'}; %REACHING AND POURING. 
 assis = {'pot', 'kld'};
-task_order = {'RE','RE','RE','RE', 'RE', 'PO','RE', 'PO', 'RE', 'RE', 'PO', 'PO', 'RE', 'PO', 'PO', 'PO'};%,'PO','RE','PO','PO','RE'}; %Phase 1 tasks FOR EACH SUBJECTS. 
+task_order = {'RE','RE','RE','RE', 'RE', 'PO','RE', 'PO', 'RE', 'RE', 'PO', 'PO', 'RE', 'PO', 'PO', 'PO', 'PO', 'RE', 'RE', 'PO', 'PO', 'RE', 'RE', 'PO'};%,'PO','RE','PO','PO','RE'}; %Phase 1 tasks FOR EACH SUBJECTS. 
 trials_per_task = 16;
 skip_list = {'H3', 'H4', 'H8', 'H9'};
 load('trial_order_testing_32.mat'); % LOAD THE TRIAL ORDER. THIS IS FOR loadData TO CHECK FOR SOME CRITERION. 
@@ -71,9 +71,14 @@ for i=1:total_subjects
     ph1_trial_list = ph1_trial_mat(:,:,trialId);
     ph2_trial_list = ph2_trial_mat(:,:,trialId);
     
-    if strcmp(user, 'H6') %fix human errors
+    %fix human errors
+    if strcmp(user, 'H6') 
         ph1_trial_list{6, 5} = 2;
     end
+    if strcmp(user, 'H22')
+        ph1_trial_list{9, 4} = 4;
+    end
+    
     
     %index
     j_ph1_ind = find(strcmp(ph1_trial_list(:,2), 'j'));

### 2018-02-02 TexStuff/SecondDraft_TexFile/GopinathArgall_SecondDraftRSS2018.tex
Final Submission - First round. Feb 1

@@
 \title{An Information Theoretic Formalism \\for Intent Disambiguation}
-\author{Author Names Omitted for Anonymous Review.}
+\author{Author Names Omitted for Anonymous Review. [Paper ID: \textbf{187}]}
 % You will get a Paper-ID when submitting a pdf file to the conference system
@@
 Previous studies have shown that the success of a disambiguation algorithm depends on a variety of factors and parameters.
-To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm.
+To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm.
 Our results indicate that, compared to a baseline, the proposed disambiguation algorithms do facilitate faster intent disambiguation, which in turn allows autonomy assistance to step in earlier during task execution.
@@
 In this paper, we address the problem of accurate intent inference by characterizing control modes according to the information content, and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
-We formalize the problem of intent inference within the framework of information theory.
+We formalize the problem of intent disambiguation within the framework of information theory.
 Specifically, we make use of the information theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the information content---with respect to intent disambiguation---of each control mode.
@@
 Intent acquisition can leverage the underlying synergies and shared intentionality~\citep{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions (for example, selecting a control mode or executing a robot motion) that will nudge the human to reveal her/his intent more clearly~\cite{sadigh2016information, sadigh2016planning}.
-Information theoretic metrics such as a KL divergence can be utilized to identify regions of the sample space that will maximize information gain~\citep{tong2001active} and subsequently guide the data sampling process.
+Information theoretic metrics such as KL divergence can be utilized to identify regions of the sample space that will maximize information gain~\citep{tong2001active} and subsequently guide the data sampling process.
 Sensing robots designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\citep{atanasov2014information}.
@@
 For an assistive machine to provide appropriate kinds of assistance accurately and at the right time, it needs to have a good estimate of the human's underlying intent.
-Intent inference algorithms, therefore, play a vital role in the success of a assistive system.
+Intent inference algorithms, therefore, play a vital role in the success of an assistive system.
 Intent inference and recognition can be classified into two broad categories: heuristic approaches and model-based approaches.
@@
 Our aim is to develop a metric that will capture the ``disambiguation capability'' of a control dimension/mode.
-Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely help the robot to perform better intent inference and may result in the robot providing more appropriate assistance.
+Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely help the system to perform better intent inference and may result in the autonomy providing more appropriate assistance.
 
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.26\vsize]{./figures/Disamb_Compute.eps}
-	\vspace{-0.35cm}
+	\includegraphics[width= 1.\hsize, height=0.28\vsize]{./figures/Disamb_Compute.eps}
+	\vspace{-0.55cm}
 	\caption{Illustration of computation of $D_m$ in $\mathbb{R}^2$.
@@
 
-\subsection{Entropy Based Disambiguation Metric}\label{sssec:ent}
-The entropy of the probability distribution captures the average information content of a stochastic source of data.
+\subsection{Entropy Disambiguation Metric}\label{sssec:ent}
+The entropy of a probability distribution captures the average information content of a stochastic source of data.
 Lower entropy indicates higher certainty in the value of the random variable and vice-versa.
@@
 That is
-\begin{equation}
+\begin{equation*}
 D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)}  ENT(\boldsymbol{p}(t_b; \boldsymbol{u_h}))
-\end{equation}
+\end{equation*}
 where $\boldsymbol{p}(t_b; \boldsymbol{u_h})$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is $\boldsymbol{u_h}$.
-\subsection{KL divergence Based Metric}\label{sssec:kl}
+\subsection{KL Divergence Disambiguation}\label{sssec:kl}
 Although entropy can capture information \textit{content}, intent disambiguation can likely benefit from the quantification of the information \textit{gain} regarding the human's intended goal as a result of user-initiated motion in a control mode $m$.
-KL divergence, also known as relative entropy, measures how one probability distribution differs from another distribution.
+KL divergence, also known as relative entropy, measures how a probability distribution differs from another distribution.
 KL divergence is widely used in the context of Bayesian inference to compute the information gain when the prior is updated to the posterior in the light of new evidence.
-In the context of disambiguation we can treat the projected probability distribution as the posterior and distribution at time $t_a$ to be the prior.
+In the context of disambiguation we can treat the projected probability distribution at time $t_b$ as the posterior and the distribution at time $t_a$ to be the prior.
 KL divergence can then be used to characterize the \textit{information gain} regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
@@
 Disambiguation mode $m^*$ is the control mode that system chooses \textit{for} the human to better estimate their intent.
-Any control command issued by the human when operating in $m^*$ is likely to be more beneficial for the robot to determine the human's intended goal.
+Any control command issued by the human when operating in $m^*$ is likely to be more beneficial for the system to determine the human's intended goal.
 
@@
 For example, a simple proximity-based confidence function used extensively in literature is
-\begin{equation}
+\begin{equation*}
 c(\boldsymbol{x_r}, \boldsymbol{x_g}) = max\Big(0, 1 - \frac{\norm{\boldsymbol{x_r} - \boldsymbol{x_g}}}{r}\Big)
-\end{equation}
+\end{equation*}
 where $\boldsymbol{x_r}$ is the robot position, $\boldsymbol{x_g}$ is the goal position, $r$ is the radius beyond which the confidence function is always 0 and $\norm{\cdot}$ is an appropriate distance metric.
@@
 \subsubsection{Bayesian Approaches}
-Bayesian approaches to intent inference consists of iteratively updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
+Bayesian approaches for intent inference consist of iteratively updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
 The Bayesian update equation for the probability distribution over goals is given by
@@
 \end{equation*}
-where $\eta$ is the normalization factor, $\boldsymbol{u}^{1:t}_{\boldsymbol{h}}$ is the entire history of control commands and $\boldsymbol{\Theta}$ denoted all other task-relevant and environment features that informs the inference process.
+where $\eta$ is the normalization factor, $\boldsymbol{u}^{1:t}_{\boldsymbol{h}}$ is the entire history of control commands and $\boldsymbol{\Theta}$ denoted all other task-relevant and environment features that inform the inference process.
 The likelihood function is related to how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed utilizing domain knowledge.
-Under first-order Markovian assumption the equation can be simplified by only considering the control command at the current time step $t$.
-\subsubsection{Dynamic Neural Field Based Approaches}
+Under first-order Markovian assumption the update equation can be simplified by only considering the control command at the current time step $t$.
+\subsubsection{Dynamic Neural Field Approaches}
 Dynamic neural fields are differential equations in time that governs the time evolution of dynamical state variables, with some specific properties such as recurrent interactions between the state variables, robustness to external noise and memory.
@@
 \end{multline}
-where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector containing all ones of dimension $n_g \times 1$, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters that affect the time-evolution of the probability distribution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
+where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector of dimension $n_g \times 1$ containing all ones, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters that affect the time-evolution of the probability distribution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
 %In the absence of any information or cues, the probability distribution settles to a resting state which is a uniform distribution, that is whenever $\boldsymbol{u}_h = 0$, $\boldsymbol{\xi} = \vec{0}$.
@@
 \section{Experimental Evaluation}\label{sec:ed}
-We evaluate the efficacy of the proposed disambiguation algorithm on simulated point-like robots and a simulated robotic manipulator that operates in a \textit{shared-control} setting.
+We evaluate the efficacy of the proposed disambiguation algorithm on simulated point robots and a simulated robotic manipulator that operates in a \textit{shared-control} setting.
 This section describes the shared-control paradigm used in our experiments and the details of the simulation experiment protocol.
@@
 Therefore, intent inference and disambiguation play a vital role in the seamless operation and success of a shared control system.
-In our experimental evaluation, control-sharing is achieved with a blending-based paradigm in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
+In our experimental evaluation, control sharing is achieved with a blending-based paradigm in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
 \subsubsection{Robot Autonomy}\label{sssec:autonomy}
@@
 
-The robot control command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field which is defined in all parts of the state space~\citep{khatib1986real}.
+The robot autonomy command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field which is defined in all parts of the state space~\citep{khatib1986real}.
 Every goal $g$ is associated with a potential field $\gamma_g$ which treats $g$ as an attractor and all the other goals in the scene as repellers.
@@
 In our implementation, we empirically set $\rho_1 = \frac{1.2}{n_g}, \rho_2 = \frac{1.4}{n_g}$ and $ \rho_3 = 0.7$.
-\subsubsection{Baseline Mode Switch Assistance}\label{sssec:baseline}
-As a baseline for the simulation experiments described in Section~\ref{ssec:sim} we also propose a simple greedy mode switch assistance scheme.
+\subsubsection{Maximum Potential Mode Switch Assistance}\label{sssec:baseline}
+As a baseline for the simulation experiments described in Section~\ref{ssec:sim} we utilize a simple greedy mode switch assistance scheme.
 At any given time $t$, the system selects the control mode which has the \textit{maximum attractive pull} or \textit{maximum potential} towards the predicted goal.
 For each control dimension $k$, the magnitude of the $k^{th}$ dimension of $\dot{\boldsymbol{x}}_r^{attract}$ is a measure of the attractive potential along $k$.
-Each control mode $m \in \mathcal{M}$ is summarized by the total attractive potential of all control dimensions $k \in m$.
+The attractive potential of each control mode $m \in \mathcal{M}$ is computed as the total attractive potential of all control dimensions $k \in m$.
 
@@
 \subsubsection{Robot Workspace}
-Our simulations were performed on point-like robots that reside in $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$ spaces.
-The translational workspace limits were set at $[-0.4m, 0.4m]$ along each translational dimension and the orientation limits were set at $[0, 2\pi]$ along each rotational axis.
-Table~\ref{tbl:manip} lists all the factors there were randomized and manipulated for each trial.
+Our simulations were performed on point robots that reside in $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$ spaces.
+The translational workspace limits were set at $[-0.6m, 0.6m]$ along each translational dimension and the orientation limits were set at $[0, 2\pi]$ along each rotational axis.
+Table~\ref{tbl:manip} lists all the factors there were manipulated for each trial.
 \begin{table}[t]
@@
 		$\mathcal{M}$ & Randomly selected from Table~\ref{tbl:cmp} conditioned on the space\\ \hline
-		Intent Inference & [`Confidence', `Bayes', `DFT'] \\ \hline
+		Intent Inference & [`Confidence', `Bayes', `Dynamic Neural Field'] \\ \hline
 		Initial Robot Position & Randomized within workspace limits \\ \hline
@@
 Four different mode switching schemes were activated during each simulation trial, three of which performed intent disambiguation and one which served as a baseline for comparison.
-The disambiguation algorithms were entropy-based (Section~\ref{sssec:ent}), KL divergence based (Section~\ref{sssec:kl}) and a heuristic-based approach developed in a related work~\citep{gopinath2017mode}.
+The disambiguation algorithms were entropy disambiguation  metric (Section~\ref{sssec:ent}), KL divergence disambiguation metric (Section~\ref{sssec:kl}) and a heuristic approach developed in a related work~\citep{gopinath2017mode}.
 We used the mode switching scheme described in Section~\ref{sssec:baseline} as the baseline for comparison.
@@
 \end{equation*}
-where $\boldsymbol{x_g}^{intended}$ is the position of the human's intended goal which is known only to the human and the system tries to infer using the inference scheme.
+where $\boldsymbol{x_g}^{intended}$ is the position of the human's intended goal which is known only to the human and the system tries to infer using the inference mechanism.
 This model of simulated human control command assumes that the user issues control commands at all times and always tries to optimize for distance and time.
@@
 %	\item \textit{Number of Mode Switches}: This metric refers to the number of times the control mode switch from the current mode to a different mode. 
-	\item \textit{Initial Onset of Assistance (s)}: Earliest time at which assistance  was triggered towards the intended goal.
+	\item \textit{Initial Onset of Assistance}: Earliest time (normalized with respect to individual trial time) at which assistance  was triggered towards the intended goal.
 This measure captures how \textit{early} the robot was able to infer the correct goal  \textit{and} provide assistance.
@@
 The trial was ended prematurely if the robot reached within the intended goal as determined by a pre-specified distance threshold.
-Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point-like robot in $\mathbb{R}^2$.
+Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
  \begin{figure}[h!]
 	\centering
-	\includegraphics[width= 0.8\hsize, height=0.3\vsize]{./figures/WS_SIM.eps}
+	\includegraphics[width= 0.8\hsize, height=0.28\vsize]{./figures/WS_SIM.eps}
 	\vspace{-0.35cm}
-	\caption{Example of point-like robot simulation in $\mathbb{R}^2$.
+	\caption{Example of point robot simulation in $\mathbb{R}^2$.
 The goals are represented in black, the initial robot position in red and the human's intended goal in magenta.
 The different colored trajectories correspond to different mode switching schemes.
-Potential-based (Black), Entropy-based (Red), KL Divergence-based (Blue) and Heuristic-based (Green).}
+Greedy (Black), Entropy (Red), KL Divergence (Blue) and Heuristic (Green).}
 	\label{fig:ws_sim}
@@
 	\vspace{-0.75cm}
-	\caption{Group differences for initial onset of assistance for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\caption{Initial onset of assistance.
+Group differences between mode switch assistance schemes (GRD, ENT, KL, HEU), in four operational spaces $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
+Box plots show the median and the quartiles.}
 	\label{fig:initial_alpha}
@@
 
-\subsection{MICO Robot Simulation Setup}
-We also evaluated our system in a real robot simulation environment (MICO robotic arm from Kinova Robotics).
-Although the end effector of the robot lives in $\mathbb{SE}(3)$, the physical constraints of the robot make the kinematics highly nonlinear compared to a point-like robot in $\mathbb{SE}(3)$.
+\subsection{Robotic Arm	 Simulation Setup}
+We also evaluated our system in a physics-based simulation of a 6-DoF robotic arm (MICO robotic arm from Kinova Robotics).
+Although the end effector of the robot lives in $\mathbb{SE}(3)$, the physical constraints of the robot make the kinematics highly nonlinear compared to a point robot in $\mathbb{SE}(3)$.
 
 We evaluated the system on two reaching tasks: 1) Four goals with same orientation and 2) five goals with different orientations.
-Two mode switching schemes were tested: KL divergence based disambiguation and the maximum potential based mode switching.
-During each trial, the mode-switch algorithm was activated every $5s$ and the maximum trial duration was set at $40s$.
-The robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy} and the control interface mapping was that of a 1D discrete switch-based headarray.
+Two mode switching schemes were tested: KL divergence disambiguation and the maximum potential mode switching.
+During each trial, the mode switching algorithm was activated every $5s$ and the maximum trial duration was set at $40s$.
+The robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy} and the control interface mapping was 1D and discrete.
  Additionally, a \textit{sparsity} factor was added to the simulated human control command $\boldsymbol{u^{sim}_h}$ to capture the variability in command timing exhibited by humans during robot teleoperation.
@@
 
-In this section we present results from our simulation studies conducted on point-like robots and a simulated robotic arm. 
-\subsection{Point-like Robot Simulation}
+In this section we present results from our simulation studies conducted on a simulated 6-DoF robotic arm and point robots in $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$. 
+\subsection{Point Robot Simulation}
 \begin{figure}[t]
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.55\vsize]{./figures/total_assistance.eps}
+	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/total_assistance.eps}
 	\vspace{-0.8cm}
-	\caption{Group differences for total amount of assistance for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\caption{Total amount of assistance.
+Group differences between mode switch assistance schemes (GRD, ENT, KL, HEU), in four operational spaces $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
+Box plots show the median and the quartiles.}
 	\label{fig:total_assistance}
 \end{figure}
-One way analysis of variance was performed using Kruskal-Wallis procedure to test for group effects.
+One way analysis of variance was performed using Kruskal-Wallis procedure to test for group effects  between the four mode switch assistance schemes: greedy (GRD), entropy (ENT), KL-Divergence (KL) and heuristic (HEU).
 Post-hoc analysis between groups was conducted using a multiple comparison test that used Tukey's HSD criterion.
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=1.3\vsize]{./figures/correct_inference.eps}
+	\includegraphics[width= 1.\hsize, height=0.31\vsize]{./figures/correct_inference.eps}
 	\vspace{-0.75cm}
-	\caption{Group differences for fractional time for correct goal inference for different simulation scenarios. Box plots show the median and the quartiles.} 
+	\caption{Inference Accuracy.
+Group differences between mode switch assistance schemes (GRD, ENT, KL, HEU), in four operational spaces $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
+Box plots show the median and the quartiles.}
 	\label{fig:correct_inference}
 \end{figure}
-\begin{figure}[t!]
-	\centering
-	\includegraphics[width= 1.\hsize, height=1.3\vsize]{./figures/mico_sim_res.eps}
-	\vspace{-0.5cm}
-	\caption{Top Left: Fraction of total time for which assistance towards intended goal was present.
-Top Right: Accuracy of intent inference procedure measured in fraction of total trial time.
-Bottom: Onset of initial assistance as a fraction of total trial time.
-Statistical significance was computed using the Wilcoxon Rank-Sum test, where(*) indicates $p < 0.05$, (**) indicates $p < 0.01$ and (***) indicates $p < 0.001$.
-}
-	\label{fig:mico_results}
-\end{figure}
-Kruskal-Wallis test reveals that the group ranks are different for all simulation scenarios.
-Post-hoc analysis also reveals statistically significant differences between the baseline mode switch assistance scheme and at least one of the disambiguation schemes for all simulation scenarios (Figure~\ref{fig:initial_alpha}).
-This shows that when the disambiguation scheme is used, the system is able to provide assistance \textit{earlier} during task execution.
+
+The Kruskal-Wallis test reveals that the group ranks are different for simulations in all operational spaces.
+Post-hoc analysis also reveals statistically significant differences between the baseline mode switch assistance scheme and at least one of the disambiguation schemes for all operational spaces (Figure~\ref{fig:initial_alpha}).
+This shows that when the disambiguation scheme is used, the autonomy is able to provide assistance \textit{earlier} during task execution.
 This is likely due to the fact that with disambiguation the system is able to elicit more informative control commands from the user and narrow down its prediction to the correct goal quicker during task execution.
@@
 
-For all simulation scenarios, Figure~\ref{fig:total_assistance} shows a statistically significant increase in the total amount of assistance when disambiguation schemes are active compared to the baseline.
-The shared control paradigm used in our setup is designed in such a way that the robot assistance gets triggered when the confidence associated with the goal prediction passes a predefined threshold.
-These results indicate that with disambiguation the system is able to maintain the confidence in its prediction of the correct goal above the threshold for a longer duration during the trial resulting in greater overall assistance during the course of the task.
+For all operational spaces, Figure~\ref{fig:total_assistance} shows a statistically significant increase in the total amount of assistance when disambiguation schemes are active compared to the baseline.
+ The shared control paradigm used in our setup is designed in such a way that the robot assistance gets triggered when the confidence associated with the goal prediction crosses a predefined threshold.
+These results indicate that with disambiguation the system is able to maintain the confidence in its prediction of the correct goal above the threshold for a longer duration during the trial, resulting in greater overall assistance during the course of the task.
 %\subsection{Number of Mode Switches}
@@
 
-As shown in Figure~\ref{fig:correct_inference}, for all simulation scenarios, the accuracy of intent inference is higher for at least one disambiguation scheme compared to the baseline.
+As shown in Figure~\ref{fig:correct_inference}, for all operational spaces, the accuracy of intent inference is higher for at least one disambiguation scheme compared to the baseline.
 This is likely because of the fact that robot operation in disambiguating modes results in higher information gain regarding the underlying intent thereby helping the system to perform accurate intent inference.
-
-\subsection{MICO Robot Simulation}
-Figure~\ref{fig:mico_results} reveals that for the simulations conducted on a simulated robotic arm, the onset of initial assistance towards the correct goal is earlier compared to that of the baseline ($p~=~0.049$).
-Similarly, the accuracy of the intent inference procedure is higher when disambiguation algorithm is deployed ($p~=~1.57e$-$4$).
-Although not statistically significant, with disambiguation the total amount of assistance provided by the system is slightly higher compared to the baseline mode-switching scheme.
-These results indicates that even with a low-dimensional and discrete control interface that exhibited signal dropouts (due to the sparsity factor), robot operation in control modes selected by the disambiguation algorithm helps the robot to elicit more intent-revealing control commands thereby helping the robot predict the intended goal more accurately and provide assistance earlier.
+\begin{figure}[t]
+	\centering
+	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/mico_sim_res.eps}
+	\vspace{-0.5cm}
+	\caption{Results with the simulated 6-DoF robotic arm.
+Top Left: Fraction of total time for which assistance towards the intended goal was engaged.
+Top Right: Accuracy of intent inference procedure measured in fraction of total trial time.
+Bottom: Onset of initial assistance as a fraction of total trial time.
+Statistical significance was computed using the Wilcoxon Rank-Sum test.
+}
+	\label{fig:mico_results}
+\end{figure}
+\subsection{Robotic Arm Simulation}
+Figure~\ref{fig:mico_results} reveals that for the simulations conducted on a simulated robotic arm, the onset of initial assistance towards the correct goal is earlier compared to that of the baseline ($p < 0.05$).
+Similarly, the accuracy of the intent inference procedure is higher when disambiguation algorithm is deployed ($p < 0.001$).
+With disambiguation the total amount of assistance provided by the system also is slightly higher, though not significantly so, compared to the baseline mode-switching scheme.
+These results indicate that even with a low-dimensional and discrete control interface that exhibits signal dropouts (due to the sparsity factor), robot operation in control modes selected by the disambiguation algorithm helps the autonomy to elicit more intent-revealing control commands thereby helping the system predict the intended goal more accurately and provide assistance earlier.
 \section{Discussion}\label{sec:discussions}
@@
 Yet another factor that is crucial for the success of a shared control system, especially for safety-critical applications, is \textit{when} during task execution the assistance gets activated.
-For example, in shared control of complex systems that exhibit highly nonlinear and unstable dynamics typically the role of autonomy is to maintain stability and safety.
-In such scenarios, if the user operation leads to the destabilization of the system, failure to intervene earlier during task execution can lead to catastrophic results.
-From our simulation results, we can see that intent disambiguation algorithms enhances the inference capabilities of the system and help the robot to provide assistance earlier.
+For example, in the shared control of complex systems that exhibit highly nonlinear and unstable dynamics typically the role of autonomy is to maintain stability and safety.
+In such situations, if the user operation leads to the destabilization of the system, failure to intervene earlier during task execution can lead to catastrophic results.
+From our simulation results, we can see that intent disambiguation enhances the inference capabilities of the system and helps the autonomy to provide assistance earlier.
 
-The utility value of a mode-switching scheme can vary during the time course of a single trial.
-For instance, in the beginning stages of task execution when the intent is unclear and the probability distribution over goals is uniform (due to the absence of any cues from the user) disambiguation algorithms are likely to be more useful.
-Once task execution gets underway and intent is clarified, a time-optimal mode switching scheme can be used to lead the user towards successful task completion.
-That is, unlike the simulation experiments in which we used only one type of mode switching scheme during each trial, a more optimal strategy might be one which is adaptive and chooses different schemes depending on the context.
+The utility value of a mode-switching scheme can vary during the time course of task execution.
+For instance, in the beginning stages of task execution when the intent is unclear, disambiguation algorithms are likely to be more useful.
+Once task execution gets underway and intent is clarified, a greedy time-optimal mode switching scheme can be used to lead the user towards successful task completion.
+That is, a more optimal strategy might be one which is adaptive and chooses different schemes depending on the context.
 This could possibly be cast within a control theoretic framework as a mode-scheduling problem in which the question of \textit{when} to deploy \textit{which} mode-switching paradigm can be solved concurrently.
@@
 High fidelity models for how a user teleoperates a robot and robot kinematics can be learned from data using machine learning tools such as deep neural networks~\citep{nagabandi2017neural}, Gaussian processes~\citep{wang2013probabilistic}.
-With sufficient data, these techniques have the capability to capture the inherent nonlinearities in human-robot systems.
-Characterization of the disambiguation capabilities of different control modes can benefit a great deal from more accurate models.
-Furthermore, the disambiguation algorithm can be customized to specific users using real-time learning algorithms that capture individual teleoperation characteristics during task execution.
+With sufficient data these techniques have the capability to capture the inherent nonlinearities in human-robot systems.
+Characterization of the disambiguation capabilities of different control modes can benefit a great deal from more accurate models of robot kinematics and user teleoperation.
+Furthermore, the disambiguation algorithm can be customized to specific users using real-time learning algorithms that capture individual teleoperation characteristics.
 
@@
 
+%\vspace{-0.4cm}
 \section{Conclusion}\label{sec:conclusions}
-In this paper, we have formulated the problem of intent disambiguation in information theoretic terms.
-We introduced two different methods for intent disambiguation using the information theoretic concepts of entropy and KL divergence to characterize the disambiguation capabilities of different control modes.
-The algorithm seeks to elicit more informative control commands from the human by placing the control in those modes that will maximally disambiguate their intent.
-We also present results from an extensive simulation-based study for point-like robots and a simulated robotic arm.
-Results from the study indicate that, compared to the baseline, the proposed disambiguation algorithms result in more accurate goal inference.
-Furthermore, the robot is able to assist earlier during task execution and the overall amount of assistance provided is higher.
+In this paper, we formalized the problem of intent disambiguation within the framework of information theory.
+We introduced two different methods for intent disambiguation using the information theoretic concepts of entropy and KL divergence.
+We also present results from an extensive simulation-based study for point robots and a physics-based simulation of a robotic arm.
+Results from the study indicate that, compared to the baseline, the proposed disambiguation algorithms facilitated faster intent disambiguation which in turn allowed the autonomy to assist earlier during task execution.
+Goal inference was more accurate and the total amount of assistance engaged was also higher.
 In our future work, we plan to perform an in-depth analysis of the data to expose the interactions between various factors.

### 2018-02-02 Code/Numerical_Fisher/SimulationCode/DATA_ANALYSIS/MATLAB/plotting_script_SIM.m

@@ -98,14 +98,14 @@ for kk=1:3
     end
     if kk==1
 %     bh1 = boxplot([v1,v2], 'whisker', 50);
-        bh1 = boxplot(v1, 'positions', y1,'whisker', 50,'Widths', 0.3);set(bh1(:,1),'linewidth',2);
-        bh2 = boxplot(v3, 'positions', y2,'whisker', 50,'Widths', 0.3);set(bh2(:,1),'linewidth',2);
+        bh1 = boxplot(v3, 'positions', y1,'whisker', 50,'Widths', 0.3);set(bh1(:,1),'linewidth',2);
+        bh2 = boxplot(v1, 'positions', y2,'whisker', 50,'Widths', 0.3);set(bh2(:,1),'linewidth',2);
     elseif kk==2
-        bh3 = boxplot(v1, 'positions', y1,'whisker', 50,'Widths', 0.3);set(bh3(:,1),'linewidth',2);
-        bh4 = boxplot(v3, 'positions', y2,'whisker', 50,'Widths', 0.3);set(bh4(:,1),'linewidth',2);
+        bh3 = boxplot(v3, 'positions', y1,'whisker', 50,'Widths', 0.3);set(bh3(:,1),'linewidth',2);
+        bh4 = boxplot(v1, 'positions', y2,'whisker', 50,'Widths', 0.3);set(bh4(:,1),'linewidth',2);
     else
-        bh5 = boxplot(v1, 'positions', y1,'whisker', 50,'Widths', 0.3);set(bh5(:,1),'linewidth',2);
-        bh6 = boxplot(v3, 'positions', y2,'whisker', 50,'Widths', 0.3);set(bh6(:,1),'linewidth',2);
+        bh5 = boxplot(v3, 'positions', y1,'whisker', 50,'Widths', 0.3);set(bh5(:,1),'linewidth',2);
+        bh6 = boxplot(v1, 'positions', y2,'whisker', 50,'Widths', 0.3);set(bh6(:,1),'linewidth',2);
     end
     axis([0,3,0,ylims(kk)]);
     grid on;
@@ -114,14 +114,14 @@ for kk=1:3
         title('\bf \fontsize{8} Total Assistance');
         set(gca,'fontWeight','bold','Xtick',1:1:2);
 %         set(gca,'DefaultTextInterpreter', 'tex')
-        set(gca, 'XTickLabel', {'KLD','POT'});
+        set(gca, 'XTickLabel', {'GRD','KL'});
[…]

### 2019-01-28 TexStuff/IROS2018_ResubmitTex/GopinathArgall_IROS2019_2.tex
IROS 2019 commit 1. incorporated human model into forward projection.

--- 2018-02-02 TexStuff/SecondDraft_TexFile/GopinathArgall_SecondDraftRSS2018.tex
@@
 % numbers option provides compact numerical references in the text. 
+\usepackage{changes}
 \usepackage[numbers]{natbib}
@@
 The effectiveness of assistive robots is closely related to their ability to infer the user's needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately.
-In this paper, we formulate the problem of intent disambiguation in information theoretic terms.
+\added{In this paper, we proposed a mode selection paradigm that enhances autonomy's intent inference capabilities by exploiting the fact that how the human operates the robot and reveals his/her intent is conditioned on the current control mode.
+We formulate this as a problem of intent disambiguation in information theoretic terms.
+}In this paper, we formulate the problem of intent disambiguation in information theoretic terms.
 We propose two different methods for intent disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}.
-The proposed algorithms characterize the disambiguation capabilities of the system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content.
+The proposed algorithms characterize the disambiguation capabilities of the \added{different control modes?} system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content.
 Previous studies have shown that the success of a disambiguation algorithm depends on a variety of factors and parameters.
@@
 Therefore, by having the human provide control input within these information-rich modes, the possibility of inferring the human's intent accurately and unambiguously is increased.
-This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.
+\added{Talk about this specifically in terms of how mode selection can improve intent inference.
+}This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.
 This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating.
@@
 
+\added{Rewrite this section in terms of math of Bayesian inference.
+And don't talk about need for intent disambiguation, but instead make a case for how inference can be affected by the control mode.Write basic equation.
+Under the constrain that user can only operate the robot in one mode at a time rewrite the equation conditioned on mode.
+Isolate the likelihood and explain the meaning of it.
+And how the fact that the likelihood differs for different modes can be exploited to come up with a mode selection paradigm.
+To characterize which one is good we use information gain and entropy measures.
+Check out Siddarths paper for recursive bayesian formulation.
+This is general to any recursive situation.
+Talk about human following a policy that noisily optimizes shortest distance in Cartesian space.
+Talk about counterfactual reasoning?
+That is, we are asking the question what if, the human operated in so and so mode, how would the probabilities update.}
 Our aim is to develop a metric that will capture the ``disambiguation capability'' of a control dimension/mode.

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/IROS2019_Sim/script_simulate.m

@@ -1,0 +1,97 @@
+clear all; clc; close all;
+
+N = 400; %number of simulations
+vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
+types = {'POT', 'ENT', 'KL', 'DISAMB'};
+%for R2 case
+for ii=1:N
+    %define global variables
+   tic;
+   fprintf('R2 sim run %d\n', ii);
+   SimulateTraj_R2_With_Blending;
+   filename = strcat('R22_DATA/DATAR22_', num2str(ii), '.mat');
+   save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
+   for jj=1:length(vars)
+        for kk=1:length(types)
+            save(filename, strcat(vars{jj}, types{kk}), '-append');
+        end
+   end
+   clear all; clc; close all;
+   N = 400; %number of simulations
+   vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
+   types = {'POT', 'ENT', 'KL', 'DISAMB'};
+   toc;  
+end
+
+%% R3 simulation.
+
+N = 400;
+vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
+types = {'POT', 'ENT', 'KL', 'DISAMB'};
+for ii=1:N
+    tic;
+    fprintf('R3 sim run %d\n', ii);
+    %define global variables
+   SimulateTraj_R3_With_Blending;
+   filename = strcat('R33_DATA/DATAR33_', num2str(ii), '.mat');
+   save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
+   for jj=1:length(vars)
+        for kk=1:length(types)
+            save(filename, strcat(vars{jj}, types{kk}), '-append');
+        end
+   end
+   
+   clear all; clc; close all;
+   N = 400; %number of simulations
+   vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
[…]

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/R2/SimulateTraj_R2_With_Blending.m

@@ -1,4 +1,4 @@
-clear all; close all; clc;
+% clear all; close all; clc;
 
 %% SPAWN GOAL CONFIGURATION AND ROBOT POSITION. RANDOMLY IN THE WORKSPACE. 
 
@@ -7,57 +7,71 @@ xrange = [-0.5, 0.5];
 yrange = [-0.5, 0.5];
 
 %global variables.
-global cm num_modes ng nd xg xr sig delta_t conf_thresh conf_max alpha_max;
+global cm num_modes ng nd xg xr sig delta_t conf_thresh conf_max alpha_max sparsity_factor amp_sparsity_factor kappa projection_time;
 
 %workspace parameters
 max_ng = 6;
-ng = datasample(2:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
+ng = datasample(3:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 2
 nd = 2; %num of dimensions. by definition R^2
 cm = {1,2}; %only control mode settings. 
 num_modes = length(cm); %or 1 depending on whether the modes are [x, y] or [{x,y}]
+init_mode_index = datasample(1:num_modes, 1);
+
 
 %spawn random goals and random robot positions
 xg = [rand(1,ng)*range(xrange) + xrange(1); rand(1,ng)*range(yrange) + yrange(1)]; %random goal positions. These will be treated as fixed parameters.
 xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1)];
-xr_true = xr; %store away random position in a variable for reuse.
+xr_true = xr; %store away random  robot position in a variable for reuse.
 
+%human parameters
+sparsity_factor = rand/4; %how often would the human control command be zero.
+amp_sparsity_factor = rand/8; % how often the amplitude wiull be less that maximum. 
+kappa = 20.0; % concentration paarameter for vonMisesFisher distribution
+fprintf('The sparsity and amp factor are %f, %f\n', sparsity_factor, amp_sparsity_factor);
 
-%disambiguation related params
+%disambiguation related params %UNUSED
 sig = 0.01; %For Fisher information
+
+%% Projection paramaters
+projection_time = 4;
[…]

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/R2/compute_optimal_mode_ENT_R2.m

@@ -33,6 +33,7 @@ for i=1:length(cm)
 end
 
 best_mode = compute_best_mode(EID_AR);
+
 end
 
 

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/R3/SimulateTraj_R3_With_Blending.m

@@ -1,4 +1,4 @@
-clear all; close all; clc;
+% clear all; close all; clc;
 %% 
 %workspace limits
 xrange = [-0.5, 0.5];
@@ -6,59 +6,72 @@ yrange = [-0.5, 0.5];
 zrange = [-0.5, 0.5];
 
 %global variables. 
-global num_modes cm ng nd xg xr sig delta_t conf_thresh conf_max alpha_max;
+global num_modes cm ng nd xg xr sig delta_t conf_thresh conf_max alpha_max sparsity_factor amp_sparsity_factor kappa projection_time;
 
 %workspace params.
 % ng = 3; %num of goals
 max_ng = 6;
 % ng = 4; %num of goals
-ng = datasample(2:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
+ng = datasample(3:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
 nd = 3; %num of dimensions. by definition R^3
 cm_options = {{1,2,3}, {[1,2], 3}};
 max_nm = length(cm_options);
 cm = cm_options{datasample(1:max_nm, 1)};
 % cm = {1,2,3}; %{1,2,3}, %{[1,3], 2} %{[2,3], 1};
 num_modes = length(cm); %
+init_mode_index = datasample(1:num_modes, 1);
 
 %spawn random goals and robot position. 
 xg = [rand(1,ng)*range(xrange) + xrange(1); rand(1,ng)*range(yrange) + yrange(1); rand(1,ng)*range(zrange) + zrange(1)]; %random goal positions. These will be treated as fixed parameters.
 xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1); rand(1,1)*range(zrange) + zrange(1)];
 xr_true = xr;
 
+%human parameters
+sparsity_factor = rand/4;
+amp_sparsity_factor = rand/8; % how often the amplitude wiull be less that maximum. 
+kappa = 20.0; % concentration paarameter for vonMisesFisher distribution
+fprintf('The sparsity and amp factor are %f, %f\n', sparsity_factor, amp_sparsity_factor);
+
 %disamb parameters.
 sig = 0.01; %For Fisher information
+%% Projection paramaters
+projection_time = 4;
 delta_t = 0.1; %For compute projections. 
 
[…]

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/R3/human_model/compute_optimal_mode_KL_R3_human_model.m

@@ -1,0 +1,21 @@
+function [ best_mode ] = compute_optimal_mode_KL_R3_human_model( intent_type, xr_T, pg )
+%COMPUTE_OPTIMAL_MODE_KL_R2_HUMAN_MODEL Summary of this function goes here
+%   Detailed explanation goes here
+
+global cm xg ng;
+
+%for each mode in cm forward project using full human model and alpha value
+%etc. 
+EID_AR = zeros(length(cm), 1);
+for i=1:length(cm)
+    curr_mode = cm{i};
+    for j=1:ng
+        curr_goal = xg(:, j);
+        EID_AR(i) = EID_AR(i) + (1/ng)*(compute_projected_kl_R3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg));
+    end
+end
+best_mode = compute_best_mode(EID_AR);
+end
+
+
+

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/SE2/SimulateTraj_SE2_With_Blending.m

@@ -1,67 +1,78 @@
-clear all; close all; clc;
-
-
+% clear all; close all; clc;
 %% SPAWN GOAL CONFIGURATION AND ROBOT POSITION. RANDOMLY IN THE WORKSPACE. 
 
 %Define workspace limits. All in metres. 
 xrange = [-0.5, 0.5];
 yrange = [-0.5, 0.5];
-th_range = [0, 2*pi];
+th_range = [0, 2*pi]; %counter clockwise rotation with 0 as x-axis aligned with left-right directions of the plane. 
 
-global num_modes cm ng nd xg xr sig delta_t conf_thresh conf_max alpha_max;
+global num_modes cm ng nd xg xr sig delta_t conf_thresh conf_max alpha_max sparsity_factor amp_sparsity_factor kappa projection_time;
 max_ng = 6;
-% ng = 4; %num of goals
-ng = datasample(2:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
-nd = 3; %num of dimensions. by definition R^3
+ng = datasample(3:max_ng, 1); %spawn random number of goals. Maximum number is 6. At least 
+nd = 3; %num of dimensions. by definition SE2
 cm_options = {{1,2,3}, {[1,2], 3}};
 max_nm = length(cm_options);
 cm = cm_options{datasample(1:max_nm, 1)};
 num_modes = length(cm);
+init_mode_index = datasample(1:num_modes, 1);
 
 xg = [rand(1,ng)*range(xrange) + xrange(1); rand(1,ng)*range(yrange) + yrange(1); rand(1,ng)*range(th_range) + th_range(1)]; %random goal positions. These will be treated as fixed parameters.
 xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1); rand(1,1)*range(th_range) + th_range(1)];
 xr_true = xr;
 
+%human parameters
+sparsity_factor = rand/4.0;
+amp_sparsity_factor = rand/8; % how often the amplitude wiull be less that maximum. 
+kappa = 20.0; % concentration paarameter for vonMisesFisher distribution
+fprintf('The sparsity and amp factor are %f, %f\n', sparsity_factor, amp_sparsity_factor);
+
+%disamb parameters.
 sig = 0.01; %For Fisher information
[…]

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/SE2/human_model/compute_optimal_mode_KL_SE2_human_model.m

@@ -1,0 +1,21 @@
+function [ best_mode ] = compute_optimal_mode_KL_SE2_human_model( intent_type, xr_T, pg )
+%COMPUTE_OPTIMAL_MODE_KL_R2_HUMAN_MODEL Summary of this function goes here
+%   Detailed explanation goes here
+
+global cm xg ng;
+
+%for each mode in cm forward project using full human model and alpha value
+%etc. 
+EID_AR = zeros(length(cm), 1);
+for i=1:length(cm)
+    curr_mode = cm{i};
+    for j=1:ng
+        curr_goal = xg(:, j);
+        EID_AR(i) = EID_AR(i) + (1/ng)*(compute_projected_kl_SE2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg));
+    end
+end
+best_mode = compute_best_mode(EID_AR);
+end
+
+
+

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/SE3/human_model/compute_optimal_mode_ENT_SE3_human_model.m

@@ -1,0 +1,19 @@
+function [ best_mode ] = compute_optimal_mode_ENT_SE3_human_model( intent_type, xr_T, pg)
+%COMPUTE_OPTIMAL_MODE_FULL_MODEL Summary of this function goes here
+%   Detailed explanation goes here
+
+global cm xg_T ng;
+
+%for each mode in cm forward project using full human model and alpha value
+%etc. 
+EID_AR = zeros(length(cm), 1);
+for i=1:length(cm)
+    curr_mode = cm{i};
+    for j=1:ng
+        curr_goal = xg_T(:,:,j);
+        EID_AR(i) = EID_AR(i) + (1/ng)*compute_projected_entropy_SE3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+    end
+end
+best_mode = compute_best_mode(EID_AR);
+end
+

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/Tests/vonMises_vs_GaussianNoise.m

@@ -1,0 +1,39 @@
+clear all; clc; close all;
+
+%%
+N = 1000;
+%% Create von Mises Fisher distribution on a circle along a direction
+
+nd = 3;
+xg = ones(nd, 1); %45 degtree angle
+xr = zeros(nd,1); %robot is always at origin. 
+
+mu = [-0.1226,
+    0.0310,
+   -0.0997];
+kappa = 20; %concentration parameters
+vonmises_samples = randvonMisesFisherm(nd, N, kappa, mu);
+
+%%
+% mean = 0;
+% std = 0.5;
+% gaussian_noise = normrnd(mean, std, nd, N);
+% gaussian_noise_samples = repmat(mu, 1, N) + gaussian_noise;
+% for i=1:N
+%     gaussian_noise_samples(:, i) = gaussian_noise_samples(:, i)./norm(gaussian_noise_samples(:, i));
+% end
+
+%%
+figure;
+scatter3(vonmises_samples(1, :), vonmises_samples(2, :), vonmises_samples(3,:), 'r', 'filled'); grid on; hold on;
+xlabel('X'); ylabel('Y'); zlabel('Z'); axis([-2,2,-2,2,-2,2]); axis('square');
+
+% figure;
+%  histogram2(vonmises_samples(1, :), vonmises_samples(2, :))
+%  
+ %%
+% figure;
+% scatter(gaussian_noise_samples(1, :), gaussian_noise_samples(2, :), 'b', 'filled'); grid on; hold on;
+% xlabel('X'); ylabel('Y'); axis([-2,2,-2,2]); axis('square');
+% figure;
+% histogram2(gaussian_noise_samples(1, :), gaussian_noise_samples(2, :))

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/Utils/compute_pg_entropy.m

@@ -1,6 +1,6 @@
 function [ Upsilon ] = compute_pg_entropy( pg )
 %UNTITLED4 Summary of this function goes here
 %   Detailed explanation goes here
-Upsilon = nansum(pg.*log2(pg));
+Upsilon = -nansum(pg.*log2(pg+realmin));
 end
 

### 2019-01-28 Code/Numerical_Fisher/SimulationCode/script_simulate.m

@@ -1,85 +1,0 @@
-clear all; clc; close all;
-
-N = 400; %number of simulations
-vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
-types = {'POT', 'ENT', 'FI', 'DISAMB'};
-%for R2 case
-for ii=1:N
-    %define global variables
-   SimulateTraj_R2_With_Blending;
-   filename = strcat('R22_DATA/DATAR22_', num2str(ii), '.mat');
-   save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
-   for jj=1:length(vars)
-        for kk=1:length(types)
-            save(filename, strcat(vars{jj}, types{kk}), '-append');
-        end
-   end
-   clear all; clc; close all;
-   N = 400; %number of simulations
-   vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
-   types = {'POT', 'ENT', 'FI', 'DISAMB'};
-end
-
-%% R3 simulation.
-
-
-vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
-types = {'POT', 'ENT', 'FI', 'DISAMB'};
-for ii=1:N
-    %define global variables
-   SimulateTraj_R3_With_Blending;
-   filename = strcat('R33_DATA/DATAR33_', num2str(ii), '.mat');
-   save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
-   for jj=1:length(vars)
-        for kk=1:length(types)
-            save(filename, strcat(vars{jj}, types{kk}), '-append');
-        end
-   end
-   
-   clear all; clc; close all;
-   N = 400; %number of simulations
-   vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
-   types = {'POT', 'ENT', 'FI', 'DISAMB'};
-end
-
-%% SE2 SIMULATION
-
[…]

### 2019-02-08 TexStuff/IROS2018_ResubmitTex/GopinathArgall_IROS2019_2.tex
Updated draft. Update scripts. Expectation computed now.

--- 2018-02-02 TexStuff/SecondDraft_TexFile/GopinathArgall_SecondDraftRSS2018.tex
@@
 \usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
+
 \usepackage{amsmath} % assumes amsmath package installed  % assumes amsmath package installed
@@
 \DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator{\E}{\mathbb{E}}
 %\newcommand{\argmax}{\arg\!\max}
@@
 The effectiveness of assistive robots is closely related to their ability to infer the user's needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately.
-In this paper, we formulate the problem of intent disambiguation in information theoretic terms.
-We propose two different methods for intent disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}.
-The proposed algorithms characterize the disambiguation capabilities of the system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content.
-Previous studies have shown that the success of a disambiguation algorithm depends on a variety of factors and parameters.
+In this paper, we proposed a mode selection paradigm that enhances the autonomy's intent inference capabilities by exploiting the fact that how the human operates the robot and reveals his/her intent is intrinsically conditioned on the control mode in operation.
+We formulate this as a problem of intent disambiguation in information theoretic terms.
+We propose two different methods for enhancing intent inference via improved disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}.
+In our system, the autonomy maintain a probability distribution over goals (beliefs) and we characterize the disambiguation capabilities of the different control modes/dimensions utilizing a model-based approach to compute the average information gain and content.
+%The proposed algorithms characterize the disambiguation capabilities of the \added{different control modes?} system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content.
+Previous work has shown that the success of a disambiguation algorithm depends on a variety of factors and parameters.
 To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm.
-Our results indicate that, compared to a baseline, the proposed disambiguation algorithms do facilitate faster intent disambiguation, which in turn allows autonomy assistance to step in earlier during task execution.
-Additionally, we find that goal inference is more accurate and the total amount of time assistance is engaged is higher.
+Our results indicate that, compared to a baseline, the proposed disambiguation algorithms do enhance intent inference via faster intent disambiguation, which in turn allows autonomy assistance to step in earlier during task execution.
+We also find that goal inference is more accurate and the total amount of time assistance is engaged is higher.
 \end{abstract}
@@
 
-An assistive robotic machine is typically controlled using an interface such as a joystick, a switch-based head array or a sip-and-puff.
-These interfaces are low-dimensional, low-bandwidth and occasionally discrete.
-For this reason, they can often only operate in a subset of the entire control space.
+An assistive robotic machine is typically controlled using an interface such as a joystick, a switch-based head array or a sip-and-puff that.
+These interfaces are low-dimensional, low-bandwidth and occasionally discrete and typically motion commands.
+For this reason, at any given point in time during task execution they can only operate in a subset of the entire control space.
 These subsets are referred to as \textit{control modes}~\citep{simpson2008tooth}.
 To schedule and execute switches between control modes can be both mentally and physically demanding, and might be alleviated in part by the introduction of robotics autonomy.
-The efficacy of such autonomy-endowed machines relies on their ability to infer the users' needs and intentions, and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately.
-Due to the dimensionality mismatch between high-dimensional robots and low-dimensional interfaces, the user is constrained to produce control commands that likely do not reveal their true intent.
+The efficacy of such autonomy-endowed machines relies on their ability to infer the users' needs and intentions, and is often a bottleneck for providing appropriate assistance accurately, confidently and quickly.
+Due to the dimensionality mismatch between high-dimensional robots and low-dimensional interfaces, the user is constrained to produce control commands that likely do not express their true underlying intent unambiguously.
 That is, the control interfaces act like filters that restrict the amount of information regarding the user's intent that gets passed through to the machine and autonomy.
@@
 
-In the context of assistive robotic manipulation, the first step of a task is often to reach towards discrete objects in the environment.
-Therefore, \textit{intent inference} can be cast as a problem of computing the probability distributions over all possible discrete goals (objects) in the workspace.
-To estimate the most probable goal, intent inference mechanisms typically rely on various environmental cues and task-relevant features such as the robot and goal positions, human control commands and biometric measures~\citep{croft2003estimating}.
-In contrast, our system infers intent primarily based on the information contained in the constrained control commands issued to the assistive machine.
+In the context of assistive robotic manipulation, the first step of a task is often to \textit{reach} towards discrete objects in the environment.
+Therefore in this domain, \textit{intent inference} can be cast as a problem of maintaining and updating the probability distributions over all possible discrete goals (objects) in the workspace upon receiving fresh evidence from the human actions and environment.
+In Bayesian terminology, maintaining and updating the belief is the \textit{recursive Bayesian filtering} problem.
+Intent inference algorithms typically rely on various environmental cues and task-relevant features such as the robot and goal positions, human control commands and biometric measures~\citep{croft2003estimating} as their evidence variables.
+In contrast, due to reasons of user adoption and cost our system infers intent exclusively based on the information contained in the constrained control commands issued to the assistive machine.
 
-Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the autonomy than others.
+Our system is inspired by the following insights:
+\begin{enumerate}
+	\item At any given time, the user is constrained to operate the robot in a specific control mode.
+That is, the policy followed by the human while executing the reaching task is conditioned on the current active mode.
+	\item The posterior computation f the belief over goals depends on the human policy (treated as an evidence variable) which indirectly depends on the active control mode. 
+	\item Utilizing a model-based approach to forward project the beliefs over goals, the autonomy can \textit{counterfactually } reason about the information gain and content for different control modes.
+	\item Using this information theoretic characterization of control modes the autonomy chooses the control mode with the highest intent disambiguation capability \textit{for} the human.
+	\item By having the human provide control input within these information-rich control modes can likely improve the accuracy of intent inference. 
+\end{enumerate}
+%Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the autonomy than others.
 Therefore, by having the human provide control input within these information-rich modes, the possibility of inferring the human's intent accurately and unambiguously is increased.
+\added{Talk about this specifically in terms of how mode selection can improve intent inference.
+}
 This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.
-This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating.
-This can decrease user satisfaction and result in significantly worse performance than either the human or autonomy would produce on their own.
-In this paper, we address the problem of accurate intent inference by characterizing control modes according to the information content, and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
+This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating and can decrease user satisfaction and result in significantly worse performance.
+%than either the human or autonomy would produce on their own. 
+In this paper, we address the problem of accurate intent inference by characterizing control modes according to the information content and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
 We formalize the problem of intent disambiguation within the framework of information theory.
@@
 The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$ and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$.
-At any time $t$, the likelihood of goal $g$ being the desired goal follows a categorical probability distribution whose sample space is $\mathcal{G}$.
- That is, 
- \begin{equation*}
- g \sim \textbf{Cat}(n_g | \boldsymbol{p}(t)) = \prod_{i=1}^{n_g}p^{i}(t)^{[g = g^i]}
- \end{equation*}
-where, $[g = g^i]$ is the Iverson bracket and evaluates to 1 if $g = g^i$, 0 otherwise.
-$\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots, p^{n_g}(t)]^{T}$ where $p^i(t)$ denotes the probability associated with goal $g^i$.
-The probability $p^i(t)$ also represents the robot's \textit{confidence} that goal $g^i$ is the human's intended goal.
+% At any time $t$, the likelihood of goal $g$ being the desired goal follows a categorical probability distribution whose sample space is $\mathcal{G}$. 
+% That is, 
+% \begin{equation*}
+% g \sim \textbf{Cat}(n_g | \boldsymbol{p}(t)) = \prod_{i=1}^{n_g}p^{i}(t)^{[g = g^i]}
+% \end{equation*}
+%where, $[g = g^i]$ is the Iverson bracket and evaluates to 1 if $g = g^i$, 0 otherwise. 
+$\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p_{g_1}^t, p_{g_2}^t,\dots, p_{g_{n_g}}^t)]^{T}$ where $p_{g_i}^t$ denotes the probability associated with goal $g_i$ at time $t$.
+The probability $p_{g_i}^t$  also represents the robot's \textit{confidence} that goal $g_i$ is the human's intended goal at time $t$.
 
@@
 \section{Intent Disambiguation}\label{sec:disamb}
+This section describes how our autonomy counterfactually reasons about the intent disambiguation capabilities of different control modes by computing the information gain and content of the belief over goal utilizing a model-base approach in which the human is modeled is an adjustable rational agent that seeks to take the shortest distance path to the goal.
+We also describe the various types of intent inference schemes that we utilize in our experiements that work in conjunction with our disambiguation algorithm.
 
-This section describes our two proposed approaches for intent disambiguation using information theoretic concepts and the different intent inference schemes that work in conjunction with the disambiguation algorithm.
+%This section describes our two proposed approaches for intent disambiguation using information theoretic concepts and the different intent inference schemes that work in conjunction with the disambiguation algorithm.
 
-\subsection{Need For Intent Disambiguation}
+\subsection{Conditional Recursive Bayesian Belief Update}
+
+In this subsection we show how the recursive Bayesian update of the probability distribution over goals is explicitly conditioned on the current active control mode and therefore can be leveraged to counterfactually reason about the disambiguation capabilities.
+
+We treat the unknown goal $g$ as a random variable and  maintain a probability distribution $\boldsymbol{p}(t)$.
+We only consider a single evidence variable that corresponds to the human control command denoted as $\boldsymbol{u}_h$.
+The goal probability conditioned on the evidence variable can be written as
+\begin{equation}\label{eq:belief1}
+b^t_g = p(g^t \;|\; \boldsymbol{u}_h^{0:t}) \propto p(\boldsymbol{u}_h^t\;|\;g^t,\boldsymbol{u}_h^{0:t-1})p(g^t|\boldsymbol{u}_h^{0:t-1})
+\end{equation}
+under the Markovian assumption that $(\boldsymbol{u}_h^t \perp \boldsymbol{u}_h^{0:t-1} | g^t)$, that is, at current timestep the human control command is independent of control commands at previous timesteps given the current goal).
+Marginalizing over $g^{t-1}$ Equation~\ref{eq:belief1} becomes
+\begin{equation}\label{eq:belief2}
+b^t_g = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t, g^{t-1} \; | \; \boldsymbol{u}_h^{0:t-1})
+\end{equation}
+and under the assumption that the conditional transition probability of changing to goal $g^t$ given that the goal is $g^{t-1}$ is independent of the control command history.
+Equation~\ref{eq:belief2}, therefore simplifies to
+\begin{equation} \label{eq:recursive_belief}
+\begin{split}
+b^t_g & = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t | g^{t-1})  p(g^{t-1} | \boldsymbol{u}_h^{0:t-1})  \\
+& = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t | g^{t-1}) b^{t-1}_{g}
+\end{split}
+\end{equation}
+Marginalizing over $m$, the control mode variable, the human policy can be written as 
+\begin{equation} \label{eq:marginal_mode}
+p(\boldsymbol{u}_h^t \;|\; g^t) = \sum_{m \in \mathcal{M}}^{} p(\boldsymbol{u}_h^t \;|\; g^t, m)p(m)
+\end{equation}
+We can simplify Equation~\ref{eq:marginal_mode} using the critical piece of information that due to constrain of the control interface at any given time $t$ only one of the control modes in $\mathcal{M}$ can be active.
+That is, the probability distribution over modes at any given time $t$ reduces to a delta function.
+This can be written as
+\begin{equation}\label{eq:mode_prob}
+\begin{split}
+p(m) & = 1 \;\;\;\; \text{if} \;\; m = m^t \\
+& = 0 \;\;\;\; \text{otherwise}
+\end{split}
+\end{equation}
+Using Equations~\ref{eq:marginal_mode} and \ref{eq:mode_prob} and under the assumption that user does not change the goal during task execution, Equation~\ref{eq:recursive_belief} can be further simplified as
+\begin{equation}\label{eq:final_belief}
+	b^t_g = \underbrace{p(\boldsymbol{u}_h^t \;|\; g^t, m^t )}_{\substack{\text{policy conditioned} \\ \text{on mode}}}\;\underbrace{b^{t-1}_{g}}_{\substack{\text{belief at}\\ \text{$t-1$}}}
+\end{equation}
+
+From Equation~\ref{eq:final_belief} we can see that the belief at time $t$ depends on the current mode $m^t$.
+This is due to the fact that the mode at time $t$ has a direct influence on how the human chooses to operate the robot to accomplish the task.
+
+%\added{Rewrite this section in terms of math of Bayesian inference.
+And don't talk about need for intent disambiguation, but instead make a case for how inference can be affected by the control mode.Write basic equation.
+Under the constrain that user can only operate the robot in one mode at a time rewrite the equation conditioned on mode.
+Isolate the likelihood and explain the meaning of it.
+And how the fact that the likelihood differs for different modes can be exploited to come up with a mode selection paradigm.
+To characterize which one is good we use information gain and entropy measures.
+Check out Siddarths paper for recursive bayesian formulation.
+This is general to any recursive situation.
+Talk about human following a policy that noisily optimizes shortest distance in Cartesian space.
+Talk about counterfactual reasoning?
+That is, we are asking the question what if, the human operated in so and so mode, how would the probabilities update.
+}
+%
+%\added{Write the math in terms of mode conditioned recursive Bayesian update, under the constrain that the goal is not changing, and under the constrain that at any point in time only mode can be operative.
+%}
 
@@
 Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely help the system to perform better intent inference and may result in the autonomy providing more appropriate assistance.
-
 At any given time $t$, the probability distributions over goals encodes the human's underlying intent.
 The time evolution of the probability distribution, however, depends on the choice of intent inference scheme and the various task relevant features and parameters that contribute to it.
-If the evolution is sensitive to the user control command (denoted by $\boldsymbol{u_h}$) then it is likely that the goal probabilities evolve differently as the user operates the robot in different control modes.
-User-generated motion along certain control dimensions therefore might reveal the human's intent with less ambiguity.
+
+From Equation~\ref{eq:final_belief} we can see that the time evolution of the probability distribution is sensitive to the user control command (denoted by $\boldsymbol{u_h}$) and that they will evolve differently as the user controls the robot in different control modes.
+User-generated motion along certain control dimensions/modes therefore might reveal the human's intent with less ambiguity to the autonomy.
+By utilizing a model-based approach the autonomy can then counterfactually reason about how the belief over goals will evolve in time for all control modes $m \in \mathcal{M}$ and then select the control that offers the highest information gain and content.
 That is, motion within maximally disambiguating control dimensions serves as a mechanism to enhance the accuracy of intent inference.
@@
 
-\subsection{Forward Projection of $\boldsymbol{p}(t)$}
+\subsection{Model-based Projection of $\boldsymbol{p}(t)$}
+%\added{Replace this whole section with what is actually happening.
+Talk about Boltzmann distributed human that noisily optimizes a shortest distance noise function.
+subsection for human model.
+Talk about vonMisesFisher distribution?
+We perform model-based forward projection and counterfactually reason about different scenarios (scenarios here correspond to different modes and different possible goals.
+).
+We can possibly simulate a person who randomly changes goal with some finite probabilit.
+This would be similar to Sid's paper.
+The forward projection will take into account the probability of changing goal.
+Replace Algorithm 1 in a more formal manner?
+with what is actually happening in the code.
+Maybe talk about how information theoretric notions can in general be used for making better decisions?
+Tie it to active inference notions?
+Select action (switch mode) such that 'most information' regarding the use goal is extracted.
+}
+
 The first step towards the computation of the disambiguation metric $D_m$ for each $m \in \mathcal{M}$ is the forward projection of the probability distribution $\boldsymbol{p}(t)$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
-The exact computation of the projected probability distribution will depend on the underlying intent inference computation---for example, whether it depends on the robot position ($\boldsymbol{x_r}$), which can be computed from the human control command (denoted by $\boldsymbol{u}_h$) applied to the robot kinematics model or $\boldsymbol{u}_h$.
+We rely on a model-based approach in which the human policy under Boltzmann rationality assumption is modeled as a von Mises Fisher distribution.
+That is,
+\begin{equation}
+	p(\boldsymbol{u}_h \;| \;g ) = C_p(\kappa)\text{e}^{(\kappa\cdot Q_g(\boldsymbol{u}_h, \boldsymbol{x}_g, \boldsymbol{x_r}))}
+\end{equation}
+where $C_p(\kappa)$ is the normalization constant, $\kappa$ is the concentration parameter, $p$ is the dimensionality of the space and $Q_g(\boldsymbol{u}_h, \boldsymbol{x}_g, \boldsymbol{x_r})$ is modeled as the cost of taking action $\boldsymbol{u}_h$ towards goal $g$ at robot configuration $\boldsymbol{x}_r$ when acting optimally.
+We compute this cost as the \textit{agreement} between the human control command $\boldsymbol{u}_h$ and the vector connecting the current robot configuration $\boldsymbol{x}_r$ and the goal configuration $\boldsymbol{x}_g$.
+The human policy conditioned on control mode $m$, $p(\boldsymbol{u}_h \;| \;g, m )$ is then computed as the projection of $p(\boldsymbol{u}_h \;| \;g )$ onto the subspace $\mathbb{R}^{|m|}$ spanned by the control mode $m$.
+Given this human model for each control mode $m \in \mathcal{M}$, the autonomy adopts a sampling-based approach to estimate the time evolution of belief for all goals $g \in \mathcal{G}$.
+This model-based projection enables the autonomy to counterfactually reason about how much information gain is likely to happen when users operate the robot towards different goals in each of the control modes.
+The full algorithm is presented in Algorithm~\ref{alg:disamb}.
+We use two different information theoretic measures to capture the disambiguation capability of a control mode: 1) information content in the projected probability distributions over goal as encoded by the \textit{entropy} of the distribution and 2) information gain as a result of the time evolution of the belief as encoded by the \textit{KL divergence} between the posterior and the prior distributions.
+
+%The exact computation of the projected probability distribution will depend on the underlying intent inference computation---for example, whether it depends on the robot position ($\boldsymbol{x_r}$), which can be computed from the human control command (denoted by $\boldsymbol{u}_h$) applied to the robot kinematics model or $\boldsymbol{u}_h$.
 All parameters and features which affect the computation of $\boldsymbol{p}(t)$ are denoted as $\boldsymbol{\Theta}$.
 If the inference mechanism depend on the control command, the projected probability distribution at time $t_b$ given by $\boldsymbol{p}(t_b)$ depends on $\boldsymbol{u_h}$.
-For the purposes of computation of the disambiguation metric, in each mode $m \in \mathcal{M}$, we only consider a subset of control commands from $\mathcal{U}^m$, and is denoted by $Vert(\mathcal{U}^m)$.
+%For the purposes of computation of the disambiguation, for each mode $m \in \mathcal{M}$ 
+%For the purposes of computation of the disambiguation metric, in each mode $m \in \mathcal{M}$, we only consider a subset of control commands from $\mathcal{U}^m$, and is denoted by $Vert(\mathcal{U}^m)$.
 The set $Vert(\mathcal{U}^m)$ is given by
-\begin{equation*}
-Vert(\mathcal{U}^m) = \{\boldsymbol{u} \in \mathcal{U}^m ~|~ \boldsymbol{u} = \argmax_{\boldsymbol{u} \in \mathcal{U}^m} \norm{\boldsymbol{u}}_{2}\}
-\end{equation*}
-where $\norm{\cdot}_2$ is the Euclidean norm.\footnote{$Vert(\mathcal{U}^m)$ corresponds to the ``vertices'' of the $|m|$-dimensional hypercube that is the space of control commands accessible from mode $m$.}
-
-The probabilities are forward projected for each of the possible control commands available in $Vert(\mathcal{U}^m)$ and a weighted average of the disambiguation metric computations on each of the projected probabilities is used to characterize the control mode $m$ (Algorithm~\ref{alg:disamb}, Lines 3-11).
+%\begin{equation*}
+%Vert(\mathcal{U}^m) = \{\boldsymbol{u} \in \mathcal{U}^m ~|~ \boldsymbol{u} = \argmax_{\boldsymbol{u} \in \mathcal{U}^m} \norm{\boldsymbol{u}}_{2}\}
+%\end{equation*}
+%where $\norm{\cdot}_2$ is the Euclidean norm.\footnote{$Vert(\mathcal{U}^m)$ corresponds to the ``vertices'' of the $|m|$-dimensional hypercube that is the space of control commands accessible from mode $m$.}
+%
+%The probabilities are forward projected for each of the possible control commands available in $Vert(\mathcal{U}^m)$ and a weighted average of the disambiguation metric computations on each of the projected probabilities is used to characterize the control mode $m$ (Algorithm~\ref{alg:disamb}, Lines 3-11).
 In the following sub-sections we present two different methods to compute the disambiguation metric for a given mode $m$.
@@
 \begin{equation*}
-ENT(P(X)) = -\sum_{i = 1}^{n} P(x_i)log_{2}P(x_i)
+ENT(p(X)) = -\sum_{i = 1}^{n} p(x_i)log_2(p(x_i))
 \end{equation*}
-where $P(X)$ denotes the probability mass function.
-The disambiguation capability of a control mode $m$ is characterized by computing a weighted average of the entropies of projected probability distributions for all possible control commands $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
-That is
-\begin{equation*}
-D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)}  ENT(\boldsymbol{p}(t_b; \boldsymbol{u_h}))
-\end{equation*}
-where $\boldsymbol{p}(t_b; \boldsymbol{u_h})$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is $\boldsymbol{u_h}$.
+where $p(X)$ denotes the probability mass function.
+The disambiguation capability of a control mode $m$ is characterized by computing a weighted average of the entropies of projected probability distributions. That is, 
+\begin{equation}
+	D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_g^{t_b})\Big]
+\end{equation}
+
+%\begin{equation*}
+%D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)}  ENT(\boldsymbol{p}(t_b; \boldsymbol{u_h}))
+%\end{equation*}
+where $b_g^{t_b}$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is sampled from the mode conditioned human policy. 
 \subsection{KL Divergence Disambiguation}\label{sssec:kl}
@@
 \begin{equation*}
-KL(P||Q) = -\sum_{i=1}^{n}P(x_i)log_2\frac{Q(x_i)}{P(x_i)}
+KL(P||Q) = -\sum_{i=1}^{n}p(x_i)log_2\frac{q(x_i)}{p(x_i)}
 \end{equation*}
-where $P(X)$ and $Q(X)$ are two different probability mass distributions. 
-  More specifically, the disambiguation capability of control mode $m$ is computed by averaging the information gain for all possible control commands $\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$.
-That is the disambiguation metric can be computed as
-\begin{equation*}
-D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)} KL(\boldsymbol{p}(t_b; \boldsymbol{u_h})||\boldsymbol{p}(t_a))~~~~.
-\end{equation*}
+where $p(X)$ and $q(X)$ are two different probability mass distributions. 
+ More specifically, the disambiguation capability of control mode $m$ is computed by averaging the information gain for all projections of probability distributions $b_g^{t_b}$ That is the disambiguation metric can be computed as
+
+ \begin{equation}
+ D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_g^{t_b}||b_g^{t_a})\Big]
+ \end{equation}
+% 
+%\begin{equation*}
+%D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)} KL(\boldsymbol{p}(t_b; \boldsymbol{u_h})||\boldsymbol{p}(t_a))~~~~.
+%\end{equation*}
 \begin{algorithm}[t]
@@
 	 \begin{algorithmic}[1]
-		\REQUIRE $\boldsymbol{p}(t_a), \boldsymbol{x}_r(t_a), \Delta t, t_a < t_b, \boldsymbol{\Theta}$
-		\FOR{$m=1\dots n_m$}
+	 	\REQUIRE $b^{t_a}_g, \boldsymbol{x}_r^{t_a}, \Delta t, t_a < t_b$
+	 	\FOR{$m \in \mathcal{M}$}
 	 	\STATE Initialize $D_m = 0$
+	 	\FOR{$g \in \mathcal{G}$}
 
-		\FOR{$\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$}
-		\STATE Initialize $t = t_a, \boldsymbol{x_r}(t) = \boldsymbol{x_r}(t_a), \boldsymbol{p}(t) = \boldsymbol{p}(t_a)$
+	 	\STATE Initialize $t = t_a, \boldsymbol{x}_r^{t} = \boldsymbol{x}_r^{t_a}, b^t_g = b^{t_a}_g$
 	 	\WHILE{$t \leq t_b$}
-		\STATE $\boldsymbol{p}(t + \Delta t) \leftarrow \text{UpdateIntent}(\boldsymbol{p}(t), \boldsymbol{u}_h; \boldsymbol{\Theta})$
-		\STATE $\boldsymbol{x}_r(t + \Delta t) \leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r(t), \boldsymbol{u}_h)$
-		\STATE $t \leftarrow t + \Delta t$
+	 	\STATE $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\; g, m)$ 
+	 	\STATE $b^{t + \Delta t}_g \leftarrow \text{BeliefUpdate}(b^t_g, \boldsymbol{u}_h^t)$
+	 	\STATE $\boldsymbol{x}_r^{t + \Delta t}\leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r^{t}, \boldsymbol{u}_h^t)$
 	 	\ENDWHILE
-
-		\STATE $D_m \leftarrow D_m + \frac{1}{\vert Vert(\mathcal{U}^m) \vert} ENT(\boldsymbol{p}(t_b)) $
+	 	\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_g^{t_b})\Big] $
 
@@
 
-		\STATE $D_m \leftarrow D_m + \frac{1}{\vert Vert(\mathcal{U}^m) \vert} KL(\boldsymbol{p}(t_b) \vert\vert \boldsymbol{p}(t_a)) $
-
+	 	\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_g^{t_b}||b_g^{t_a})\Big] $
 	 	\ENDFOR
@@
 \end{algorithm}
+
+%\begin{algorithm}[t]
+%	\caption{Calculate $\boldsymbol{p}(t_b)$, $D_m$}
+%	\label{alg:disamb}
+%	\begin{algorithmic}[1]
+%		\REQUIRE $\boldsymbol{p}(t_a), \boldsymbol{x}_r(t_a), \Delta t, t_a < t_b, \boldsymbol{\Theta}$
+%		\FOR{$m=1\dots n_m$}
+%		\STATE Initialize $D_m = 0$
+%		
+%		\FOR{$\boldsymbol{u_h} \in Vert(\mathcal{U}^m)$}
+%		\STATE Initialize $t = t_a, \boldsymbol{x_r}(t) = \boldsymbol{x_r}(t_a), \boldsymbol{p}(t) = \boldsymbol{p}(t_a)$
+%		\WHILE{$t \leq t_b$}
+%		\STATE $\boldsymbol{p}(t + \Delta t) \leftarrow \text{UpdateIntent}(\boldsymbol{p}(t), \boldsymbol{u}_h; \boldsymbol{\Theta})$
+%		\STATE $\boldsymbol{x}_r(t + \Delta t) \leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r(t), \boldsymbol{u}_h)$
+%		\STATE $t \leftarrow t + \Delta t$
+%		\ENDWHILE
+%		
+%		\STATE $D_m \leftarrow D_m + \frac{1}{\vert Vert(\mathcal{U}^m) \vert} ENT(\boldsymbol{p}(t_b)) $
+%		
+%		or
+%		
+%		\STATE $D_m \leftarrow D_m + \frac{1}{\vert Vert(\mathcal{U}^m) \vert} KL(\boldsymbol{p}(t_b) \vert\vert \boldsymbol{p}(t_a)) $
+%		
+%		\ENDFOR
+%		\ENDFOR
+%	\end{algorithmic}
+%\end{algorithm}
 The control mode with highest disambiguation capability $m^*$ is given by $\argmax_m D_m$.
@@
 \subsection{Intent inference}\label{ssec:inference}
-  The disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms.
-The update rule for the probability distribution over goals is determined by the choice of inference schemes (Algorithm~\ref{alg:disamb}, Line 6) as a result of which the projected probability distributions, $\boldsymbol{p}(t_b)$ and the disambiguation metric $D_m$, likely are going to be different for different choices.
+%  The disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms. 
+  The exact update rule for the recursive belief updates is determined by the choice of inference schemes (Algorithm~\ref{alg:disamb}, Line 6) as a result of which the projected probability distributions, $b_g^{t_b}$ and the disambiguation metric $D_m$, likely are going to be different for different choices.
 This section describes the different types of intent inference schemes that work in conjunction with the disambiguation algorithms proposed in Section~\ref{sec:disamb}.
@@
 These confidence functions rely on instantaneous features and therefore are amnesic and can exhibit chatter behavior~\citep{dragan2012formalizing}.
+Using the above-mentioned confidence functions, we have
+\begin{equation}
+	p_g^t = c(\boldsymbol{x}_r^t, \boldsymbol{x}_g^t, \boldsymbol{u}_h^t)
+\end{equation}
+where $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\;g, m)$.
 
@@
 Bayesian approaches for intent inference consist of iteratively updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
-The Bayesian update equation for the probability distribution over goals is given by
-\begin{equation*}
-\underbrace{p(g_t| \boldsymbol{u}^{1:t}_{\boldsymbol{h}}, \boldsymbol{\Theta})}_{posterior} = \eta \underbrace{p(\boldsymbol{u}^{1:t}_{\boldsymbol{h}} | g_t, \boldsymbol{\Theta})}_{likelihood}\underbrace{p(g_{t-1})}_{prior}
-\end{equation*}
-where $\eta$ is the normalization factor, $\boldsymbol{u}^{1:t}_{\boldsymbol{h}}$ is the entire history of control commands and $\boldsymbol{\Theta}$ denoted all other task-relevant and environment features that inform the inference process.
-The likelihood function is related to how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed utilizing domain knowledge.
+The Bayesian update equation for the probability distribution over goals directly uses Equation~\ref{eq:final_belief} for belief propagation.
+%\begin{equation*}
+%\underbrace{p(g_t| \boldsymbol{u}^{1:t}_{\boldsymbol{h}}, \boldsymbol{\Theta})}_{posterior} = \eta \underbrace{p(\boldsymbol{u}^{1:t}_{\boldsymbol{h}} | g_t, \boldsymbol{\Theta})}_{likelihood}\underbrace{p(g_{t-1})}_{prior}
+%\end{equation*}
+%where $\eta$ is the normalization factor, $\boldsymbol{u}^{1:t}_{\boldsymbol{h}}$ is the entire history of control commands and $\boldsymbol{\Theta}$ denoted all other task-relevant and environment features that inform the inference process.
+%The likelihood function is related to how the human teleoperates the robot in order to accomplish a goal and can be either learned from data, or be hand-designed utilizing domain knowledge.
 Under first-order Markovian assumption the update equation can be simplified by only considering the control command at the current time step $t$.
+
+%\added{add mode conditioning?}
+
 \subsubsection{Dynamic Neural Field Approaches}
@@
 Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
+\added{modify the simulation parameters.
+Talk about projection time.
+}
  \begin{figure}[h!]

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/IROS2019_Sim/DATA_ANALYSIS/data_parser_new.m

@@ -3,21 +3,22 @@ clear all; close all; clc;
 spaceList = {'R22', 'R33', 'SE2', 'SE3'}; %R2, R3, SE2, SE3
 condList = {'POT', 'ENT', 'KL', 'DISAMB'};
 delta_t = 0.1;
-total_subjects = 5000;
+total_subjects = 800;
 
 %% types of data to be looked at
 
 initial_alpha = -999*ones(total_subjects, length(condList), length(spaceList)); %initialize the alpha time as big negative. If it stays like this it means that the assistance was never triggered. 
 trajectory_time = -999*ones(total_subjects, length(condList), length(spaceList));
-percentage_correct_inference = zeros(total_subjects, length(condList), length(spaceList));
-percentage_alpha = zeros(total_subjects, length(condList), length(spaceList)); %for this the chattering has to be detected and snipped. 
-ng_array = zeros(total_subjects, length(spaceList)); %number of goals for each conditions. 
-intent_type_array = cell(total_subjects, length(spaceList));
-num_mode_switches = zeros(total_subjects, length(condList), length(spaceList));
-
+percentage_correct_inference = -999*ones(total_subjects, length(condList), length(spaceList));
+percentage_alpha = -999*ones(total_subjects, length(condList), length(spaceList)); %for this the chattering has to be detected and snipped. 
+ng_array = -999*ones(total_subjects, length(spaceList)); %number of goals for each conditions. 
+intent_type_array = -999*ones(total_subjects, length(spaceList));
+num_mode_switches = -999*ones(total_subjects, length(condList), length(spaceList));
+trajectory_length = -999*ones(total_subjects, length(condList), length(spaceList));
+intent_type_dict = containers.Map({'dft', 'bayes', 'conf'}, [1,2,3]);
 %%
 for i=1:length(spaceList)
-    dirname = strcat('NEW_',spaceList{i}, '_DATA');
+    dirname = strcat(spaceList{i}, '_DATA_IROS_EXP');
     fnames = dir(dirname);
     numfids = length(fnames);
     for index=3:3 + (total_subjects-1)
@@ -58,6 +59,75 @@ for i=1:length(spaceList)
                 l_DISAMB = 119; traj_DISAMB(end) = [];
             end
             
+        end
+%         if ~strcmp(intent_type, 'conf')
+%             continue
+%         end
+        
[…]

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/IROS2019_Sim/script_simulate.m

@@ -1,55 +1,56 @@
 clear all; clc; close all;
 
-N = 400; %number of simulations
-vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
-types = {'POT', 'ENT', 'KL', 'DISAMB'};
-%for R2 case
-for ii=1:N
-    %define global variables
-   tic;
-   fprintf('R2 sim run %d\n', ii);
-   SimulateTraj_R2_With_Blending;
-   filename = strcat('R22_DATA/DATAR22_', num2str(ii), '.mat');
-   save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
-   for jj=1:length(vars)
-        for kk=1:length(types)
-            save(filename, strcat(vars{jj}, types{kk}), '-append');
-        end
-   end
-   clear all; clc; close all;
-   N = 400; %number of simulations
-   vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
-   types = {'POT', 'ENT', 'KL', 'DISAMB'};
-   toc;  
-end
+%% R2 simulation
+% N = 800; %number of simulations
+% vars = {'alpha_', 'curr_goal_', 'optimal_modes_', 'pgs_', 'traj_', 'uh_', 'ur_', 'blend_vel_'};
+% types = {'POT', 'ENT', 'KL', 'DISAMB'};
+% %for R2 case
+% for ii=1:N
+%     %define global variables
+%    tic;
+%    fprintf('R2 sim run %d\n', ii);
+%    SimulateTraj_R2_With_Blending;
+%    filename = strcat('R22_DATA/RUN_2_DATAR22_', num2str(ii), '.mat');
+%    save(filename, 'ng', 'nd', 'cm', 'num_modes', 'xg', 'xr_true', 'intent_type','random_goal_index');
+%    for jj=1:length(vars)
+%         for kk=1:length(types)
+%             save(filename, strcat(vars{jj}, types{kk}), '-append');
+%         end
+%    end
+%    clear all; clc; close all;
+%    N = 800; %number of simulations
[…]

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/R2/SimulateTraj_R2_With_Blending.m

@@ -7,7 +7,7 @@ xrange = [-0.5, 0.5];
 yrange = [-0.5, 0.5];
 
 %global variables.
-global cm num_modes ng nd xg xr sig delta_t conf_thresh conf_max alpha_max sparsity_factor amp_sparsity_factor kappa projection_time;
+global cm num_modes ng nd xg xr sig delta_t conf_thresh conf_max num_samples alpha_max sparsity_factor amp_sparsity_factor kappa projection_time;
 
 %workspace parameters
 max_ng = 6;
@@ -24,7 +24,7 @@ xr = [rand(1,1)*range(xrange) + xrange(1); rand(1,1)*range(yrange) + yrange(1)];
 xr_true = xr; %store away random  robot position in a variable for reuse.
 
 %human parameters
-sparsity_factor = rand/4; %how often would the human control command be zero.
+sparsity_factor = rand/8; %how often would the human control command be zero.
 amp_sparsity_factor = rand/8; % how often the amplitude wiull be less that maximum. 
 kappa = 20.0; % concentration paarameter for vonMisesFisher distribution
 fprintf('The sparsity and amp factor are %f, %f\n', sparsity_factor, amp_sparsity_factor);
@@ -34,7 +34,8 @@ sig = 0.01; %For Fisher information
 
 %% Projection paramaters
 projection_time = 4;
-delta_t = 0.1; %For compute projections. 
+delta_t = 0.1; %For compute projections.
+num_samples = 5;
 
 %% simulation params
 mode_comp_timesteps = 10; %time step gap between optimal mode computation. delta_t*mode_comp_timesteps is the time in seconds
@@ -49,7 +50,7 @@ conf_max = (1.1/ng);
 alpha_max = 0.7;
 
 %% PLOT GOALS AND CURRENT ROBOT POSITION. 
-% 
+% % 
 % figure;
 % scatter(xg(1,1:ng), xg(2,1:ng), 180, 'k', 'filled'); grid on; hold on;
 % scatter(xr(1), xr(2), 140, 'r', 'filled');
@@ -69,7 +70,7 @@ random_goal = xg(:, random_goal_index);
 %% SAMPLE AN INTENT INFERENCE MECHANISM FOR THE CURRENT SIMULATION
 intent_types = {'dft', 'conf', 'bayes'};
[…]

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/R2/compute_bayes_R2.m

@@ -1,7 +1,7 @@
 function [ posterior ] = compute_bayes_R2( uh, xr, prior )
 %UNTITLED Summary of this function goes here
 %   Detailed explanation goes here
-    global ng
+    global ng;
     ll = likelihood_func(uh, xr);
     prior = prior + 0.01*rand(ng, 1); %to avoid collapse of posterior. 
     prior = prior/sum(prior);
@@ -10,7 +10,7 @@ function [ posterior ] = compute_bayes_R2( uh, xr, prior )
 end
 
 function likelihood = likelihood_func(uh, xr)
-    global ng xg;
+    global ng xg kappa;
     likelihood = zeros(ng, 1);
     if norm(uh)~=0
         uh = uh/norm(uh);
@@ -22,6 +22,7 @@ function likelihood = likelihood_func(uh, xr)
         dir_vec = xg(:, i) - xr; %vector joining the robot position and the goal_x. 
         dir_vec = dir_vec/norm(dir_vec); %as long as xr is not xg, this would be nonzero;
         likelihood(i) = p_of_u_given_g(uh, dir_vec);
+%         likelihood(i) = vonMisesFisherPdf(uh, dir_vec, kappa);
     end
 end
 

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/R2/human_model/compute_optimal_mode_ENT_R2_human_model.m

@@ -2,7 +2,7 @@ function [ best_mode ] = compute_optimal_mode_ENT_R2_human_model( intent_type, x
 %COMPUTE_OPTIMAL_MODE_FULL_MODEL Summary of this function goes here
 %   Detailed explanation goes here
 
-global cm xg ng;
+global cm xg ng num_samples;
 
 %for each mode in cm forward project using full human model and alpha value
 %etc. 
@@ -10,8 +10,13 @@ EID_AR = zeros(length(cm), 1);
 for i=1:length(cm)
     curr_mode = cm{i};
     for j=1:ng
-        curr_goal = xg(:, j);
-        EID_AR(i) = EID_AR(i) + (1/ng)*compute_projected_entropy_R2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        projected_ent = zeros(num_samples, 1);
+        for k=1:num_samples
+            curr_goal = xg(:, j);
+            projected_ent(k) = compute_projected_entropy_R2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        end
+        expected_projected_entropy = mean(projected_ent);
+        EID_AR(i) = EID_AR(i) + (1/ng)*expected_projected_entropy;
     end
 end
 best_mode = compute_best_mode(EID_AR);

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/R2/human_model/compute_optimal_mode_KL_R2_human_model.m

@@ -2,7 +2,7 @@ function [ best_mode ] = compute_optimal_mode_KL_R2_human_model( intent_type, xr
 %COMPUTE_OPTIMAL_MODE_KL_R2_HUMAN_MODEL Summary of this function goes here
 %   Detailed explanation goes here
 
-global cm xg ng;
+global cm xg ng num_samples;
 
 %for each mode in cm forward project using full human model and alpha value
 %etc. 
@@ -10,8 +10,13 @@ EID_AR = zeros(length(cm), 1);
 for i=1:length(cm)
     curr_mode = cm{i};
     for j=1:ng
-        curr_goal = xg(:, j);
-        EID_AR(i) = EID_AR(i) + (1/ng)*(compute_projected_kl_R2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg));
+        projected_kl = zeros(num_samples, 1);
+        for k=1:num_samples
+            curr_goal = xg(:, j);
+            projected_kl(k) = compute_projected_kl_R2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        end
+        expected_projected_kl = mean(projected_kl);
+        EID_AR(i) = EID_AR(i) + (1/ng)*expected_projected_kl;
     end
 end
 best_mode = compute_best_mode(EID_AR);

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/R2/human_model/compute_pg_projection_R2_human_model.m

@@ -72,7 +72,12 @@ end
 function uh = generate_model_uh(xg, xr) %full unnomralized uh
     global nd kappa;
     mu = xg - xr; %noiseless human velocity model. 
-    uh = randvonMisesFisherm(nd, 1, kappa, mu);
+    if ~any(mu)
+        uh = zeros(nd, 1);
+    else
+        uh = randvonMisesFisherm(nd, 1, kappa, mu);
+    end
+%     uh = randvonMisesFisherm(nd, 1, kappa, mu);
 end
 
 %% simple potential field type of autonomy. 

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/R3/human_model/compute_optimal_mode_ENT_R3_human_model.m

@@ -2,7 +2,7 @@ function [ best_mode ] = compute_optimal_mode_ENT_R3_human_model( intent_type, x
 %COMPUTE_OPTIMAL_MODE_FULL_MODEL Summary of this function goes here
 %   Detailed explanation goes here
 
-global cm xg ng;
+global cm xg ng num_samples;
 
 %for each mode in cm forward project using full human model and alpha value
 %etc. 
@@ -10,8 +10,13 @@ EID_AR = zeros(length(cm), 1);
 for i=1:length(cm)
     curr_mode = cm{i};
     for j=1:ng
-        curr_goal = xg(:, j);
-        EID_AR(i) = EID_AR(i) + (1/ng)*compute_projected_entropy_R3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        projected_ent = zeros(num_samples, 1);
+        for k=1:num_samples
+            curr_goal = xg(:, j);
+            projected_ent(k) = compute_projected_entropy_R3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        end
+        expected_projected_entropy = mean(projected_ent);
+        EID_AR(i) = EID_AR(i) + (1/ng)*expected_projected_entropy;
     end
 end
 best_mode = compute_best_mode(EID_AR);

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/R3/human_model/compute_optimal_mode_KL_R3_human_model.m

@@ -2,7 +2,7 @@ function [ best_mode ] = compute_optimal_mode_KL_R3_human_model( intent_type, xr
 %COMPUTE_OPTIMAL_MODE_KL_R2_HUMAN_MODEL Summary of this function goes here
 %   Detailed explanation goes here
 
-global cm xg ng;
+global cm xg ng num_samples;
 
 %for each mode in cm forward project using full human model and alpha value
 %etc. 
@@ -10,8 +10,13 @@ EID_AR = zeros(length(cm), 1);
 for i=1:length(cm)
     curr_mode = cm{i};
     for j=1:ng
-        curr_goal = xg(:, j);
-        EID_AR(i) = EID_AR(i) + (1/ng)*(compute_projected_kl_R3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg));
+        projected_kl = zeros(num_samples, 1);
+        for k=1:num_samples
+            curr_goal = xg(:, j);
+            projected_kl(k) = compute_projected_kl_R3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        end
+        expected_projected_kl = mean(projected_kl);
+        EID_AR(i) = EID_AR(i) + (1/ng)*expected_projected_kl;
     end
 end
 best_mode = compute_best_mode(EID_AR);

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/SE2/human_model/compute_optimal_mode_ENT_SE2_human_model.m

@@ -2,7 +2,7 @@ function [ best_mode ] = compute_optimal_mode_ENT_SE2_human_model( intent_type, 
 %COMPUTE_OPTIMAL_MODE_FULL_MODEL Summary of this function goes here
 %   Detailed explanation goes here
 
-global cm xg ng;
+global cm xg ng num_samples;
 
 %for each mode in cm forward project using full human model and alpha value
 %etc. 
@@ -10,8 +10,13 @@ EID_AR = zeros(length(cm), 1);
 for i=1:length(cm)
     curr_mode = cm{i};
     for j=1:ng
-        curr_goal = xg(:, j);
-        EID_AR(i) = EID_AR(i) + (1/ng)*compute_projected_entropy_SE2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        projected_ent = zeros(num_samples, 1);
+        for k=1:num_samples
+            curr_goal = xg(:, j);
+            projected_ent(k) = compute_projected_entropy_SE2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        end
+        expected_projected_entropy = mean(projected_ent);
+        EID_AR(i) = EID_AR(i) + (1/ng)*expected_projected_entropy;
     end
 end
 best_mode = compute_best_mode(EID_AR);

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/SE2/human_model/compute_optimal_mode_KL_SE2_human_model.m

@@ -2,7 +2,7 @@ function [ best_mode ] = compute_optimal_mode_KL_SE2_human_model( intent_type, x
 %COMPUTE_OPTIMAL_MODE_KL_R2_HUMAN_MODEL Summary of this function goes here
 %   Detailed explanation goes here
 
-global cm xg ng;
+global cm xg ng num_samples;
 
 %for each mode in cm forward project using full human model and alpha value
 %etc. 
@@ -10,8 +10,13 @@ EID_AR = zeros(length(cm), 1);
 for i=1:length(cm)
     curr_mode = cm{i};
     for j=1:ng
-        curr_goal = xg(:, j);
-        EID_AR(i) = EID_AR(i) + (1/ng)*(compute_projected_kl_SE2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg));
+        projected_kl = zeros(num_samples, 1);
+        for k=1:num_samples
+            curr_goal = xg(:, j);
+            projected_kl(k) = compute_projected_kl_SE2_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        end
+        expected_projected_kl = mean(projected_kl);
+        EID_AR(i) = EID_AR(i) + (1/ng)*expected_projected_kl;
     end
 end
 best_mode = compute_best_mode(EID_AR);

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/SE3/human_model/compute_optimal_mode_KL_SE3_human_model.m

@@ -1,8 +1,8 @@
-function [ best_mode ] = compute_optimal_mode_KL_SE3_human_model( intent_type, xr_T, pg )
-%COMPUTE_OPTIMAL_MODE_KL_R2_HUMAN_MODEL Summary of this function goes here
+function [ best_mode ] = compute_optimal_mode_KL_SE3_human_model( intent_type, xr_T, pg)
+%COMPUTE_OPTIMAL_MODE_FULL_MODEL Summary of this function goes here
 %   Detailed explanation goes here
 
-global cm xg_T ng;
+global cm xg_T ng num_samples;
 
 %for each mode in cm forward project using full human model and alpha value
 %etc. 
@@ -10,12 +10,15 @@ EID_AR = zeros(length(cm), 1);
 for i=1:length(cm)
     curr_mode = cm{i};
     for j=1:ng
-        curr_goal = xg_T(:,:,j);
-        EID_AR(i) = EID_AR(i) + (1/ng)*(compute_projected_kl_SE3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg));
+        projected_kl = zeros(num_samples, 1);
+        for k=1:num_samples
+            curr_goal = xg_T(:,:,j);
+            projected_kl(k) = compute_projected_kl_SE3_human_model(curr_mode, curr_goal, intent_type, xr_T, pg);
+        end
+        expected_projected_kl = mean(projected_kl);
+        EID_AR(i) = EID_AR(i) + (1/ng)*expected_projected_kl;
     end
 end
 best_mode = compute_best_mode(EID_AR);
 end
-
-
 

### 2019-02-08 Code/Numerical_Fisher/SimulationCode/Tests/vonMisesPDFTest.m

@@ -1,0 +1,23 @@
+clear all; close all; clc;
+
+%%
+N = 1000;
+nd = 3;
+xg = ones(nd, 1); %45 degtree angle
+xr = zeros(nd,1); %robot is always at origin. 
+
+mu = xg -xr;
+kappa = 2; %concentration parameters
+vonmises_samples = randvonMisesFisherm(nd, N, kappa, mu);
+pdf = zeros(N, 1);
+for i=1:N
+    x = vonmises_samples(:, i);
+    pdf(i) = vonMisesFisherPdf(x, mu, kappa);
+end
+
+figure;
+scatter3(vonmises_samples(1, :), vonmises_samples(2, :), vonmises_samples(3,:), 'r', 'filled'); grid on; hold on;
+xlabel('X'); ylabel('Y'); zlabel('Z'); axis([-2,2,-2,2,-2,2]); axis('square');
+
+figure;
+histogram(pdf);

### 2019-02-22 TexStuff/IROS2018_ResubmitTex/GopinathArgall_IROS2019_2.tex
Version final - 2

@@
 Previous work has shown that the success of a disambiguation algorithm depends on a variety of factors and parameters. 
-To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm.
+%To thoroughly investigate the impact of these various components, 
+We present results from an extensive simulation-based study for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm.
 Our results indicate that, compared to a baseline, the proposed disambiguation algorithms do enhance intent inference via faster intent disambiguation, which in turn allows autonomy assistance to step in earlier during task execution.
@@
 \section{Introduction}
-Assistive machines such as robotic arms and smart wheelchairs have the potential to transform the lives of millions of people with motor impairments.~\citep{laplante1992assistive}.
-These machines can promote independence, enhance the quality of lives and revolutionize the way people interact with society.
-They can also help extend the mobility and manipulation capabilities of individuals, thereby helping motor-impaired people perform activities of daily living in a more effective manner.
+Assistive machines such as robotic arms and smart wheelchairs have the potential to transform the lives of millions of people with motor impairments~\citep{laplante1992assistive}.
+These machines can promote independence, enhance the quality of lives, extend the mobility and manipulation capabilities of individuals and revolutionize the way people interact with society.
+%They can also help , thereby helping motor-impaired people perform activities of daily living in a more effective manner.
 
-An assistive robotic machine is typically controlled using an interface such as a joystick, a switch-based head array or a sip-and-puff that.
-These interfaces are low-dimensional, low-bandwidth and occasionally discrete and typically motion commands.
+An assistive robotic machine is typically controlled using an interface such as a joystick, a switch-based head array or a sip-and-puff.
+These interfaces are low-dimensional, low-bandwidth and occasionally discrete.
 For this reason, at any given point in time during task execution they can only operate in a subset of the entire control space.
@@
 To schedule and execute switches between control modes can be both mentally and physically demanding, and might be alleviated in part by the introduction of robotics autonomy.
-The efficacy of such autonomy-endowed machines relies on their ability to infer the users' needs and intentions, and is often a bottleneck for providing appropriate assistance accurately, confidently and quickly.
+The efficacy of such autonomy-endowed machines relies on their ability to infer the users' needs and intentions, which is often a bottleneck for providing appropriate assistance accurately, confidently and quickly.
 Due to the dimensionality mismatch between high-dimensional robots and low-dimensional interfaces, the user is constrained to produce control commands that likely do not express their true underlying intent unambiguously.
-That is, the control interfaces act like filters that restrict the amount of information regarding the user's intent that gets passed through to the machine and autonomy.
+That is, the control interfaces act like filters that restrict the amount of information regarding the user's intent that is passed through to the autonomy.
 %Furthermore, sparsity and noise in the control commands make the inference process even harder prompting the need for robust intent inference formalisms.
@@
 Intent inference algorithms typically rely on various environmental cues and task-relevant features such as the robot and goal positions, human control commands and biometric measures~\citep{croft2003estimating} as their evidence variables.
-In contrast, due to reasons of user adoption and cost our system infers intent exclusively based on the information contained in the constrained control commands issued to the assistive machine.
+In contrast, due to reasons of user adoption and cost, our system matches the interfaces available on typical commercial assistive machines (such as powered wheelchairs) and so infers intent exclusively based on the information contained in the constrained control commands issued to the assistive machine.
 
 Our system is inspired by the following insights:
-\begin{enumerate}
+\begin{itemize}
 	\item At any given time, the user is constrained to operate the robot in a specific control mode.
 That is, the policy followed by the human while executing the reaching task is conditioned on the current active mode.
-	\item The posterior computation f the belief over goals depends on the human policy (treated as an evidence variable) which indirectly depends on the active control mode. 
+	\item The posterior computation of the belief over goals depends on the human policy which indirectly depends on the active control mode. 
 	\item Utilizing a model-based approach to forward project the beliefs over goals, the autonomy can \textit{counterfactually } reason about the information gain and content for different control modes.
-	\item Using this information theoretic characterization of control modes the autonomy chooses the control mode with the highest intent disambiguation capability \textit{for} the human.
-	\item By having the human provide control input within these information-rich control modes can likely improve the accuracy of intent inference. 
-\end{enumerate}
+	\item Using this information theoretic characterization of control modes, the autonomy chooses the control mode with the highest intent disambiguation capability \textit{for} the human.
+	\item Having the human provide control input within these information-rich control modes can likely improve the accuracy of intent inference.
+This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.
+\end{itemize}
 %Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the autonomy than others.
@@
 }
-This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.
-This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating and can decrease user satisfaction and result in significantly worse performance.
+
+%Having the autonomy to step in earlier and provide accurate assistance is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating and can decrease user satisfaction and result in significantly worse performance.
 %than either the human or autonomy would produce on their own.
-In this paper, we address the problem of accurate intent inference by characterizing control modes according to the information content and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
+
+In this paper, we address the problem of accurate intent inference by characterizing control modes according to their information content and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
 We formalize the problem of intent disambiguation within the framework of information theory.
@@
 
-Information theoretic approaches are widely utilized in the field of machine learning and robotics for optimal experiment design, for efficient data collection processes and for informing search strategies.
+%Information theoretic approaches are widely utilized in the field of machine learning and robotics for optimal experiment design, for efficient data collection processes and for informing search strategies.
 Robot assistance schemes that seek to elicit more informative cues \textit{from} the human to clarify the underlying intent can be thought of as an information acquisition problem.
-Intent acquisition can leverage the underlying synergies and shared intentionality~\citep{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions (for example, selecting a control mode or executing a robot motion) that will nudge the human to reveal her/his intent more clearly~\cite{sadigh2016information, sadigh2016planning}.
+Intent acquisition can leverage the underlying synergies and shared intentionality~\citep{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions
+%(for example, selecting a control mode or executing a robot motion) 
+that will nudge the human to reveal her/his intent more clearly~\cite{sadigh2016information}.
 Information theoretic metrics such as KL divergence can be utilized to identify regions of the sample space that will maximize information gain~\citep{tong2001active} and subsequently guide the data sampling process.
-Sensing robots designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\citep{atanasov2014information}.
-If the spatial distribution of information density is known \textit{a priori}, information maximization can be accomplished by maximizing the ergodicity of the robot's trajectory with respect to the underlying information density map~\citep{miller2013trajectory, miller2016ergodic}.
+%Sensing robots designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\citep{atanasov2014information}. 
+If the spatial distribution of information density is known \textit{a priori}, information maximization can be accomplished by maximizing the ergodicity of the robot's trajectory with respect to the underlying information density~\citep{miller2016ergodic}.
 
-For an assistive machine to provide appropriate kinds of assistance accurately and at the right time, it needs to have a good estimate of the human's underlying intent.
-Intent inference algorithms, therefore, play a vital role in the success of an assistive system.
+%For an assistive machine to provide appropriate kinds of assistance accurately and at the right time, it needs to have a good estimate of the human's underlying intent.
+ Intent inference algorithms play a vital role in the success of an assistive system.
 Intent inference and recognition can be classified into two broad categories: heuristic approaches and model-based approaches.
-Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features (such as motion cues) and the human's underlying intention~\citep{baker2007goal, baker2009action}.
+Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features (such as motion cues) and the human's underlying intention~\citep{baker2007goal}.
 On the other hand, in model-based approaches the system maintains a model of how a human maps states to control actions.
 The model can either be learned from data or can be hand-designed based on domain knowledge.
-For example, the human can be modeled within the Partially Observable Markov Decision Process (POMDP)~\citep{dragan2013policy, taha2011pomdp} framework and is assumed to behave according to a control policy that maps states to actions.
+For example, the human can be modeled within the Partially Observable Markov Decision Process (POMDP)~\citep{taha2011pomdp} framework and is assumed to behave according to a control policy that maps states to actions.
 However, in model-based approaches incorporating the entire history of states requires estimation of joint probability distributions over past states which can become computationally expensive and intractable quickly.
@@
 When there is a mismatch between the dimensionality of the problem and the control interface users have to continuously shift their focus from the task at hand to the choice of control mode during task execution, thereby resulting in a higher cognitive load.
-To solve this problem, various mode switching assistance paradigms have been proposed to alleviate task effort.
+Various mode switching assistance paradigms have been proposed to alleviate task effort.
 For example, an automatic time-optimal mode switch assistance has been proposed which has shown to significantly improve user satisfaction~\citep{herlant2016assistive}.
@@
  In assistive robotic manipulation, intent inference is most commonly the process of estimating the user's intended goal out of a set of discrete objects in the environment~\citep{calli2015ycb}.
-The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$ and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$.
+The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$.
+% and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$. 
 % At any time $t$, the likelihood of goal $g$ being the desired goal follows a categorical probability distribution whose sample space is $\mathcal{G}$. 
@@
 %where, $[g = g^i]$ is the Iverson bracket and evaluates to 1 if $g = g^i$, 0 otherwise. 
-$\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p_{g_1}^t, p_{g_2}^t,\dots, p_{g_{n_g}}^t)]^{T}$ where $p_{g_i}^t$ denotes the probability associated with goal $g_i$ at time $t$.
-The probability $p_{g_i}^t$  also represents the robot's \textit{confidence} that goal $g_i$ is the human's intended goal at time $t$.
+At time $t$ the random variable $g^t \in \mathcal{G}$ denotes the user's intended goal and $b_{g^t}$ denotes the belief over the goals. 
+% The probability $b_{g^t}$  also represents the robot's \textit{confidence} that goal $g$ is the human's intended goal at time $t$. 
+%$\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p_{g_1}^t, p_{g_2}^t,\dots, p_{g_{n_g}}^t)]^{T}$ where $p_{g_i}^t$ denotes the probability associated with goal $g_i$ at time $t$.
 
@@
 Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i = \mathcal{K}$.
-The cardinality of each mode $m \in \mathcal{M}$, denoted by $\vert m \vert$ indicates the number of dimensions that can be controlled when operating in $m$.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+The cardinality of each mode $m \in \mathcal{M}$, denoted by $\vert m \vert$, indicates the number of dimensions that can be controlled when operating in $m$.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes and so it is possible that $m^i \cap m^j \neq \emptyset$.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
 That is, for each $m \in \mathcal{M}$, the subspace of $\mathcal{R}^{n_k}$ that is accessible corresponds to $\mathcal{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
 Maximum velocity limits along each dimension impose further constraints on the set of control commands that are available in each mode.
-This constrained set of control commands available in mode $m$, denoted by $\mathcal{U}^m$, can be written as
-\begin{equation*}
-\mathcal{U}^m = \{\boldsymbol{u} | \boldsymbol{u} \in \mathcal{R}^{\vert m \vert} ~ and ~ \norm{\boldsymbol{u}}_{\infty} \leq v_{lim} \} 
-\end{equation*}
-where $v_{lim}$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm. 
+% This constrained set of control commands available in mode $m$, denoted by $\mathcal{U}^m$, can be written as 
+%\begin{equation*}
+%\mathcal{U}^m = \{\boldsymbol{u} | \boldsymbol{u} \in \mathcal{R}^{\vert m \vert} ~ and ~ \norm{\boldsymbol{u}}_{\infty} \leq v_{lim} \} 
+%\end{equation*}
+%where $v_{lim}$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm. 
 %Therefore, the set $\mathcal{U}^m$ corresponds to a hypercube of dimensionality $\vert m \vert$ embedded in $\mathcal{R}^{n_k}$.
@@
 \section{Intent Disambiguation}\label{sec:disamb}
-This section describes how our autonomy counterfactually reasons about the intent disambiguation capabilities of different control modes by computing the information gain and content of the belief over goal utilizing a model-base approach in which the human is modeled is an adjustable rational agent that seeks to take the shortest distance path to the goal.
-We also describe the various types of intent inference schemes that we utilize in our experiements that work in conjunction with our disambiguation algorithm.
+This section describes how our autonomy reasons about the intent disambiguation capabilities of different control modes by computing the information gain and content of the belief over goals.
+We utilize a model-based approach in which the human is modeled as an adjustable rational agent that seeks to take the shortest distance path to the goal.
+We also describe the various intent inference schemes that we utilize in our experiments, that work in conjunction with our disambiguation algorithm.
 
@@
 
-In this subsection we show how the recursive Bayesian update of the probability distribution over goals is explicitly conditioned on the current active control mode and therefore can be leveraged to counterfactually reason about the disambiguation capabilities.
+In this subsection we show how the recursive Bayesian update of the probability distribution over goals is explicitly conditioned on the current active control mode and therefore can be leveraged to reason about disambiguation.
+%the disambiguation capabilities.
 
-We treat the unknown goal $g$ as a random variable and  maintain a probability distribution $\boldsymbol{p}(t)$.
-We only consider a single evidence variable that corresponds to the human control command denoted as $\boldsymbol{u}_h$.
-The goal probability conditioned on the evidence variable can be written as
+%We treat the unknown goal $g$ as a random variable and  maintain a belief over the goals denoted as $b^t_g$. 
+We only consider a single evidence variable that corresponds to the human control command denoted as $\boldsymbol{u}_h$. The goal probability conditioned on the evidence variable can be written as 
 \begin{equation}\label{eq:belief1}
-b^t_g = p(g^t \;|\; \boldsymbol{u}_h^{0:t}) \propto p(\boldsymbol{u}_h^t\;|\;g^t,\boldsymbol{u}_h^{0:t-1})p(g^t|\boldsymbol{u}_h^{0:t-1})
+b_{g^t} = p(g^t \;|\; \boldsymbol{u}_h^{0:t}) \propto p(\boldsymbol{u}_h^t\;|\;g^t,\boldsymbol{u}_h^{0:t-1})p(g^t|\boldsymbol{u}_h^{0:t-1}) \;\;\;\;\;.
 \end{equation}
-under the Markovian assumption that $(\boldsymbol{u}_h^t \perp \boldsymbol{u}_h^{0:t-1} | g^t)$, that is, at current timestep the human control command is independent of control commands at previous timesteps given the current goal).
-Marginalizing over $g^{t-1}$ Equation~\ref{eq:belief1} becomes
+Assuming that $(\boldsymbol{u}_h^t \perp \boldsymbol{u}_h^{0:t-1} | g^t)$ (Markovian assumption that the control command at the current timestep is independent of previous timesteps given the current goal)and marginalizing over $g^{t-1}$, Equation~\ref{eq:belief1} becomes
 \begin{equation}\label{eq:belief2}
-b^t_g = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t, g^{t-1} \; | \; \boldsymbol{u}_h^{0:t-1})
+b_{g^t} = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t, g^{t-1} \; | \; \boldsymbol{u}_h^{0:t-1})
 \end{equation}
-and under the assumption that the conditional transition probability of changing to goal $g^t$ given that the goal is $g^{t-1}$ is independent of the control command history.
-Equation~\ref{eq:belief2}, therefore simplifies to
-\begin{equation} \label{eq:recursive_belief}
-\begin{split}
-b^t_g & = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t | g^{t-1})  p(g^{t-1} | \boldsymbol{u}_h^{0:t-1})  \\
-& = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t | g^{t-1}) b^{t-1}_{g}
-\end{split}
+We also assume that the conditional transition probability of changing to goal $g^t$ given that the goal is $g^{t-1}$ is independent of the control command history.
+Equation~\ref{eq:belief2}, therefore, simplifies to
+\begin{equation}\label{eq:recursive_belief}
+	b_{g^t} = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t | g^{t-1}) b_{g^{t-1}}
 \end{equation}
-Marginalizing over $m$, the control mode variable, the human policy can be written as 
+%\begin{equation} \label{eq:recursive_belief}
+%\begin{split}
+%b^t_g & = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t | g^{t-1})  p(g^{t-1} | \boldsymbol{u}_h^{0:t-1})  \\
+%& = p(\boldsymbol{u}_h^t \;|\; g^t) \sum_{g^{t-1} \in \mathcal{G}}^{} p(g^t | g^{t-1}) b^{t-1}_{g}
+%\end{split}
+%\end{equation}
+Marginalizing over $m$, the control mode variable, the human policy $p(\boldsymbol{u}_h^t \;|\; g^t)$ can be written as 
 \begin{equation} \label{eq:marginal_mode}
@@
 \end{equation}
-We can simplify Equation~\ref{eq:marginal_mode} using the critical piece of information that due to constrain of the control interface at any given time $t$ only one of the control modes in $\mathcal{M}$ can be active.
+We can simplify Equation~\ref{eq:marginal_mode} using the critical piece of information that, due to constraint of the control interface, at any given time $t$ only one of the control modes in $\mathcal{M}$ can be active.
 That is, the probability distribution over modes at any given time $t$ reduces to a delta function.
@@
 \begin{equation}\label{eq:mode_prob}
-\begin{split}
-p(m) & = 1 \;\;\;\; \text{if} \;\; m = m^t \\
-& = 0 \;\;\;\; \text{otherwise}
-\end{split}
+	p(m) = \begin{cases}
+			1 \;\;\;\; \text{if} \;\; m = m^t \\
+			0 \;\;\;\; \text{otherwise}
+			\end{cases}
 \end{equation}
+%\begin{equation}\label{eq:mode_prob}
+%\begin{split}
+%p(m) & = 1 \;\;\;\; \text{if} \;\; m = m^t \\
+%& = 0 \;\;\;\; \text{otherwise}
+%\end{split}
+%\end{equation}
 Using Equations~\ref{eq:marginal_mode} and \ref{eq:mode_prob} and under the assumption that user does not change the goal during task execution, Equation~\ref{eq:recursive_belief} can be further simplified as
 \begin{equation}\label{eq:final_belief}
-	b^t_g = \underbrace{p(\boldsymbol{u}_h^t \;|\; g^t, m^t )}_{\substack{\text{policy conditioned} \\ \text{on mode}}}\;\underbrace{b^{t-1}_{g}}_{\substack{\text{belief at}\\ \text{$t-1$}}}
+	b_{g^t} = \underbrace{p(\boldsymbol{u}_h^t \;|\; g^t, m^t )}_{\substack{\text{human policy} \\ \text{conditioned on mode}}}\;\underbrace{b_{g^{t-1}}}_{\substack{\text{belief at}\\ \text{$t-1$}}}
 \end{equation}
@@
 
-%\added{Rewrite this section in terms of math of Bayesian inference.
-And don't talk about need for intent disambiguation, but instead make a case for how inference can be affected by the control mode.Write basic equation.
-Under the constrain that user can only operate the robot in one mode at a time rewrite the equation conditioned on mode.
-Isolate the likelihood and explain the meaning of it.
-And how the fact that the likelihood differs for different modes can be exploited to come up with a mode selection paradigm.
-To characterize which one is good we use information gain and entropy measures.
-Check out Siddarths paper for recursive bayesian formulation.
-This is general to any recursive situation.
-Talk about human following a policy that noisily optimizes shortest distance in Cartesian space.
-Talk about counterfactual reasoning?
-That is, we are asking the question what if, the human operated in so and so mode, how would the probabilities update.
-}
-%
-%\added{Write the math in terms of mode conditioned recursive Bayesian update, under the constrain that the goal is not changing, and under the constrain that at any point in time only mode can be operative.
-%}
+\subsection{Algorithm: Information Theoretic Intent Disambiguation}
 
 Our aim is to develop a metric that will capture the ``disambiguation capability'' of a control dimension/mode. 
-Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely help the system to perform better intent inference and may result in the autonomy providing more appropriate assistance.
-At any given time $t$, the probability distributions over goals encodes the human's underlying intent.
-The time evolution of the probability distribution, however, depends on the choice of intent inference scheme and the various task relevant features and parameters that contribute to it.
+From Equation~\ref{eq:final_belief} we can see that the time evolution of the probability distribution is sensitive to the user control command (denoted by $\boldsymbol{u_h}$), and that it will evolve differently as the user controls the robot in different control modes.
+By utilizing a model-based approach, the autonomy can reason about the time evolution of the belief $b_{g^t}$ for all control modes $m \in \mathcal{M}$ and then select the mode that offers the highest information gain and content.
+That is, motion within maximally disambiguating control dimensions serves as a mechanism to enhance the accuracy of intent inference.
 
-From Equation~\ref{eq:final_belief} we can see that the time evolution of the probability distribution is sensitive to the user control command (denoted by $\boldsymbol{u_h}$) and that they will evolve differently as the user controls the robot in different control modes.
-User-generated motion along certain control dimensions/modes therefore might reveal the human's intent with less ambiguity to the autonomy.
-By utilizing a model-based approach the autonomy can then counterfactually reason about how the belief over goals will evolve in time for all control modes $m \in \mathcal{M}$ and then select the control that offers the highest information gain and content.
-That is, motion within maximally disambiguating control dimensions serves as a mechanism to enhance the accuracy of intent inference.
-Various types of intent inference schemes used in conjunction with the proposed disambiguation algorithm in our paper are described in detail in Section~\ref{ssec:inference}.
+The full algorithm is presented in Algorithm~\ref{alg:disamb}.
+We first perform a model-based projection of the probability distribution over goals (lines 5-9, Section~\ref{ssec:model_based}).
+We then compute the disambiguation capability $D_m$ of a control mode using information theoretic measures (lines 10-11) We present two different information theoretic measures for disambiguation: 1) information content in the projected probability distributions over goal as encoded by the \textit{entropy} of the distribution (Section~\ref{sssec:ent}) and 2) information gain as a result of the time evolution of the belief as encoded by the \textit{KL divergence} between the posterior and the prior distributions (Section~\ref{sssec:kl}).
 
-\subsection{Model-based Projection of $\boldsymbol{p}(t)$}
-%\added{Replace this whole section with what is actually happening.
-Talk about Boltzmann distributed human that noisily optimizes a shortest distance noise function.
-subsection for human model.
-Talk about vonMisesFisher distribution?
-We perform model-based forward projection and counterfactually reason about different scenarios (scenarios here correspond to different modes and different possible goals.
-).
-We can possibly simulate a person who randomly changes goal with some finite probabilit.
-This would be similar to Sid's paper.
-The forward projection will take into account the probability of changing goal.
-Replace Algorithm 1 in a more formal manner?
-with what is actually happening in the code.
-Maybe talk about how information theoretric notions can in general be used for making better decisions?
-Tie it to active inference notions?
-Select action (switch mode) such that 'most information' regarding the use goal is extracted.
-}
-
-The first step towards the computation of the disambiguation metric $D_m$ for each $m \in \mathcal{M}$ is the forward projection of the probability distribution $\boldsymbol{p}(t)$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
-We rely on a model-based approach in which the human policy under Boltzmann rationality assumption is modeled as a von Mises Fisher distribution.
+The control mode with highest disambiguation capability $m^*$ is then given by $\argmax_m D_m$.
+Disambiguation mode $m^*$ is the control mode that system chooses \textit{for} the human to better estimate their intent.
+Any control command issued by the human when operating in $m^*$ is likely to be more beneficial for the system to determine the human's intended goal.
+\subsection{Model-based Projection of $b_{g^t}$}\label{ssec:model_based}
+The first step towards the computation of the disambiguation metric $D_m$ for each $m \in \mathcal{M}$ is the forward projection of the probability distribution $b_{g^t}$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
+We rely on a model-based approach in which the human policy under the Boltzmann rationality assumption [] is modeled as a von Mises Fisher distribution [].
 That is,
@@
 \end{equation}
-where $C_p(\kappa)$ is the normalization constant, $\kappa$ is the concentration parameter, $p$ is the dimensionality of the space and $Q_g(\boldsymbol{u}_h, \boldsymbol{x}_g, \boldsymbol{x_r})$ is modeled as the cost of taking action $\boldsymbol{u}_h$ towards goal $g$ at robot configuration $\boldsymbol{x}_r$ when acting optimally.
+where $C_p(\kappa)$ is the normalization constant, $\kappa$ is the concentration parameter, $p$ is the dimensionality of the control space and $Q_g(\boldsymbol{u}_h, \boldsymbol{x}_g, \boldsymbol{x_r})$ is modeled as the cost of taking action $\boldsymbol{u}_h$ towards goal $g$ at robot configuration $\boldsymbol{x}_r$ when acting optimally.
 We compute this cost as the \textit{agreement} between the human control command $\boldsymbol{u}_h$ and the vector connecting the current robot configuration $\boldsymbol{x}_r$ and the goal configuration $\boldsymbol{x}_g$.
-The human policy conditioned on control mode $m$, $p(\boldsymbol{u}_h \;| \;g, m )$ is then computed as the projection of $p(\boldsymbol{u}_h \;| \;g )$ onto the subspace $\mathbb{R}^{|m|}$ spanned by the control mode $m$.
+The human thus is modeled as attempting the straight line path to the goal.
+The human policy conditioned on control mode $m$, $p(\boldsymbol{u}_h \;| \;g, m )$, is the projection of $p(\boldsymbol{u}_h \;| \;g )$ onto the subspace $\mathbb{R}^{|m|}$ spanned by the control mode $m$.
+
 Given this human model for each control mode $m \in \mathcal{M}$, the autonomy adopts a sampling-based approach to estimate the time evolution of belief for all goals $g \in \mathcal{G}$.
 This model-based projection enables the autonomy to counterfactually reason about how much information gain is likely to happen when users operate the robot towards different goals in each of the control modes.
-The full algorithm is presented in Algorithm~\ref{alg:disamb}.
-We use two different information theoretic measures to capture the disambiguation capability of a control mode: 1) information content in the projected probability distributions over goal as encoded by the \textit{entropy} of the distribution and 2) information gain as a result of the time evolution of the belief as encoded by the \textit{KL divergence} between the posterior and the prior distributions.
 
@@
 
- \begin{figure}[h]
-	\centering
-	\includegraphics[width= 1.\hsize, height=0.28\vsize]{./figures/Disamb_Compute.eps}
-	\vspace{-0.55cm}
-	\caption{Illustration of computation of $D_m$ in $\mathbb{R}^2$.
+% \begin{figure}[h]
+%	\centering
+%	\includegraphics[width= 1.\hsize, height=0.28\vsize]{./figures/Disamb_Compute.eps}
+%	\vspace{-0.55cm}
+%	\caption{Illustration of computation of $D_m$ in $\mathbb{R}^2$.
 The goals are shown in red, green and blue and the robot in black.
@@
 The entropy of $\boldsymbol{p}(t_b)$ captures the information \textit{content} in the projected distribution.}
-	\label{fig:disamb_compute}
-\end{figure}
+%	\label{fig:disamb_compute}
+%\end{figure}
 
@@
 The entropy of a probability distribution captures the average information content of a stochastic source of data.
-Lower entropy indicates higher certainty in the value of the random variable and vice-versa.
-Therefore, in the context of intent disambiguation entropy of the projected probability distribution, $\boldsymbol{p}(t_b)$, can be used as a measure of how confident the system is in its prediction of human intent.
-That is, entropy can be used a measure of disambiguation.
-Lower the entropy better the disambiguation due to higher certainty in the human's intended goal.
+Lower entropy indicates higher certainty in the value of the random variable, and vice-versa.
+Therefore, in the context of intent disambiguation, the entropy of the projected probability distribution, $b_{g^{t_b}}$, can be used as a measure of how confident the system is in its prediction of human intent.
+%This implies that entropy can be used a measure of disambiguation. 
+That is, lower the entropy better the disambiguation, due to higher certainty in the human's intended goal.
 For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$, the Shannon entropy is defined as
@@
 The disambiguation capability of a control mode $m$ is characterized by computing a weighted average of the entropies of projected probability distributions. That is, 
-\begin{equation}
-	D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_g^{t_b})\Big]
+\begin{equation}\label{eq:ent}
+	D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_{g^{t_b}})\Big]
 \end{equation}
@@
 %\end{equation*}
-where $b_g^{t_b}$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is sampled from the mode conditioned human policy. 
+where $b_{g^{t_b}}$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is sampled from the mode conditioned human policy $p(\boldsymbol{u}_h \; |\; g, m)$.
 \subsection{KL Divergence Disambiguation}\label{sssec:kl}
@@
 In the context of disambiguation we can treat the projected probability distribution at time $t_b$ as the posterior and the distribution at time $t_a$ to be the prior.
-KL divergence can then be used to characterize the \textit{information gain} regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
+KL divergence can be used to characterize the \textit{information gain} regarding the human's intended goal as a result of the application of $\boldsymbol{u_h}$.
+
 For a discrete random variable $X$ with possible values $\{x_1, x_2,\dots x_n\}$ the KL divergence is defined by
@@
 where $p(X)$ and $q(X)$ are two different probability mass distributions. 
- More specifically, the disambiguation capability of control mode $m$ is computed by averaging the information gain for all projections of probability distributions $b_g^{t_b}$ That is the disambiguation metric can be computed as
+ More specifically, the disambiguation capability of control mode $m$ is computed by averaging the information gain for all projections of probability distributions $b_{g^{t_b}}$.
+The disambiguation metric can be computed as
 
- \begin{equation}
- D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_g^{t_b}||b_g^{t_a})\Big]
+ \begin{equation}\label{eq:kldiv}
+ D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_{g^{t_b}}||b_{g^{t_a}})\Big]
  \end{equation}
@@
 \begin{algorithm}[t]
-	\caption{Calculate $\boldsymbol{p}(t_b)$, $D_m$}
+	\caption{Information Theoretic Intent Disambiguation}
 	\label{alg:disamb}
 	 \begin{algorithmic}[1]
-	 	\REQUIRE $b^{t_a}_g, \boldsymbol{x}_r^{t_a}, \Delta t, t_a < t_b$
+	 	\REQUIRE $b_{g^{t_a}}, \boldsymbol{x}_r^{t_a}, \Delta t, t_a < t_b$
 	 	\FOR{$m \in \mathcal{M}$}
@@
 
-	 	\STATE Initialize $t = t_a, \boldsymbol{x}_r^{t} = \boldsymbol{x}_r^{t_a}, b^t_g = b^{t_a}_g$
+	 	\STATE Initialize $t = t_a, \boldsymbol{x}_r^{t} = \boldsymbol{x}_r^{t_a}, b_{g^{t}} = b_{g^{t_a}}$
 	 	\WHILE{$t \leq t_b$}
 	 	\STATE $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\; g, m)$ 
-	 	\STATE $b^{t + \Delta t}_g \leftarrow \text{BeliefUpdate}(b^t_g, \boldsymbol{u}_h^t)$
+	 	\STATE $b_{g^{t + \Delta t}} \leftarrow \text{BeliefUpdate}(b_{g^{t}}, \boldsymbol{u}_h^t)$
 	 	\STATE $\boldsymbol{x}_r^{t + \Delta t}\leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r^{t}, \boldsymbol{u}_h^t)$
+	 	\STATE $t \leftarrow t + \Delta t$
 	 	\ENDWHILE
-	 	\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_g^{t_b})\Big] $
+	 	\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_{g^{t_b}})\Big] $
 
@@
 
-	 	\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_g^{t_b}||b_g^{t_a})\Big] $
+	 	\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_{g^{t_b}}||b_{g^{t_a}})\Big] $
 	 	\ENDFOR
@@
 %\end{algorithm}
-The control mode with highest disambiguation capability $m^*$ is given by $\argmax_m D_m$.
-Disambiguation mode $m^*$ is the control mode that system chooses \textit{for} the human to better estimate their intent.
-Any control command issued by the human when operating in $m^*$ is likely to be more beneficial for the system to determine the human's intended goal.
 
-\subsection{Intent inference}\label{ssec:inference}
+\section{Intent inference}\label{sec:inference}
 %  The disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms. 
-  The exact update rule for the recursive belief updates is determined by the choice of inference schemes (Algorithm~\ref{alg:disamb}, Line 6) as a result of which the projected probability distributions, $b_g^{t_b}$ and the disambiguation metric $D_m$, likely are going to be different for different choices.
-This section describes the different types of intent inference schemes that work in conjunction with the disambiguation algorithms proposed in Section~\ref{sec:disamb}.
+At any given time $t$, the probability distributions over goals encodes the human's underlying intent.
+The time evolution of the probability distribution, however, depends on the choice of intent inference scheme, and the various task relevant features and parameters that contribute to it.
+
+More specifically, the exact update rule for the recursive belief update is determined by the choice of inference scheme (Algorithm~\ref{alg:disamb}, Line 6) which impacts the projected probability distributions, $b_g^{t_b}$, and the disambiguation metric, $D_m$.
+Here we present the multiple intent schemes evaluated in conjunction with our disambiguation algorithm.
 %This is because, during the forward projection step, different intent update schemes result in different projections and affects the computation of the disambiguation metric.
@@
 Heuristic approaches based on \textit{confidence} functions~\citep{dragan2013policy} seek to find direct mappings between instantaneous cues and underlying human intentions. 
-For every goal $g \in \mathcal{G}$, the system maintains an associated set of confidences denoted by $\mathcal{C}$.
-The system designer has the freedom to choose the set of features that will inform the confidence functions.
-For example, a simple proximity-based confidence function used extensively in literature is
+%For every goal $g \in \mathcal{G}$, the system maintains an associated set of confidences denoted by $\mathcal{C}$. 
+%The system designer has the freedom to choose the set of features that will inform the confidence functions.
+For example, a confidence function that captures the ``directedness" of the human control command to a particular goal position can be written as 
+% 
+%For example, a simple proximity-based confidence function used extensively [] in literature is
+%\begin{equation*}
+%c(\boldsymbol{x}_r, \boldsymbol{x}_g) = max\Big(0, 1 - \frac{\norm{\boldsymbol{x}_r - \boldsymbol{x}_g}}{r}\Big)
+%\end{equation*}
+%where $\boldsymbol{x}_r$ is the robot position, $\boldsymbol{x}_g$ is the goal position, $r$ is the radius beyond which the confidence function is always 0 and $\norm{\cdot}$ is an appropriate distance metric.
+%A slightly more information-rich variant that aims to capture the ``directedness'' of the human control command to a particular goal position is
+%c({\boldsymbol{x}_r^t,\boldsymbol{x}_g^t, \boldsymbol{u}_{h}^t}) =
 \begin{equation*}
-c(\boldsymbol{x_r}, \boldsymbol{x_g}) = max\Big(0, 1 - \frac{\norm{\boldsymbol{x_r} - \boldsymbol{x_g}}}{r}\Big)
+b_{g^t} =  \boldsymbol{u}_h^t\cdot(\boldsymbol{x}_{g}^t - \boldsymbol{x_r}^t)
 \end{equation*}
-where $\boldsymbol{x_r}$ is the robot position, $\boldsymbol{x_g}$ is the goal position, $r$ is the radius beyond which the confidence function is always 0 and $\norm{\cdot}$ is an appropriate distance metric.
-A slightly more information-rich variant that aims to capture the ``directedness'' of the human control command to a particular goal position is
-\begin{equation*}
-c({\boldsymbol{x_r},\boldsymbol{x_g}, \boldsymbol{u}_{h}}) = \boldsymbol{u}_h\cdot(\boldsymbol{x}_{g} - \boldsymbol{x_r})
-\end{equation*}
-where $\boldsymbol{u_h}$ is the human control command.
+where $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\;g, m)$ is the human control command.
 These confidence functions rely on instantaneous features and therefore are amnesic and can exhibit chatter behavior~\citep{dragan2012formalizing}.
-Using the above-mentioned confidence functions, we have
-\begin{equation}
-	p_g^t = c(\boldsymbol{x}_r^t, \boldsymbol{x}_g^t, \boldsymbol{u}_h^t)
-\end{equation}
-where $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\;g, m)$.
+%Using the above-mentioned confidence functions, we have 
+%\begin{equation}
+%	p_g^t = c(\boldsymbol{x}_r^t, \boldsymbol{x}_g^t, \boldsymbol{u}_h^t)
+%\end{equation}
+%where $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\;g, m)$.
 
@@
 Bayesian approaches for intent inference consist of iteratively updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
-The Bayesian update equation for the probability distribution over goals directly uses Equation~\ref{eq:final_belief} for belief propagation.
+The Bayesian update procedure directly uses Equation~\ref{eq:final_belief} for belief propagation.
 %\begin{equation*}
@@
 \subsubsection{Dynamic Neural Field Approaches}
-Dynamic neural fields are differential equations in time that governs the time evolution of dynamical state variables, with some specific properties such as recurrent interactions between the state variables, robustness to external noise and memory.
+%Dynamic neural fields are differential equations in time that governs the time evolution of dynamical state variables, with some specific properties such as recurrent interactions between the state variables, robustness to external noise and memory.
 Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner2008dynamical}.
-When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$~\citep{gopinath2017disamb}.
+When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$, where $p^i(t)$ denotes the probability associated with the $i^{th}$ goal at time $t$~\citep{gopinath2017disamb} and $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots,p^{n_g}(t) ]^{T}$.
 %Recurrent interactions between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
@@
 \begin{multline}\label{eq:dft}
-\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} + \\ \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
+\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} + \\ \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h^t;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
 \end{multline}
@@
 %In the absence of any information or cues, the probability distribution settles to a resting state which is a uniform distribution, that is whenever $\boldsymbol{u}_h = 0$, $\boldsymbol{\xi} = \vec{0}$.
-Given the initial probability distribution at time $t_a$ Equation~\ref{eq:dft} can be solved numerically from $t \in [t_a, t_b]$ using a simple Euler algorithm with a fixed time-step $\Delta t$.
+%Given the initial probability distribution at time $t_a$, Equation~\ref{eq:dft} can be solved numerically from $t \in [t_a, t_b]$ using a simple Euler algorithm with a fixed time-step $\Delta t$. 
 The design of $\boldsymbol{\xi}$ is informed by what features of the human control input and environment capture the human's underlying intent most effectively.
-We rely on the \textit{directedness} of the human control commands towards a goal, the \textit{proximity} to a goal and the \textit{agreement} between the human commands and robot autonomy.
+Our implementation relies on the \textit{directedness} of the human control commands towards a goal, the \textit{proximity} to a goal and the \textit{agreement} between the human commands and robot autonomy.
 
@@
 We evaluate the efficacy of the proposed disambiguation algorithm on simulated point robots and a simulated robotic manipulator that operates in a \textit{shared-control} setting.
-This section describes the shared-control paradigm used in our experiments and the details of the simulation experiment protocol.
+This section describes the shared-control paradigm used in our experiments and the details of the simulation experiment.
 %In this section we describe our simulation experiments conducted on simulated point-like robots and a simulated robotic manipulator to evaluate the effectiveness of our disambiguation algorithm. 
 \subsection{Shared Control}\label{ssec:shared-control}
-Shared autonomy in assistive robotics aims to reduce the human's physical and cognitive burden during task execution without having the user to completely cede manual control.
-Some common shared-control approaches include (a) hierarchical paradigms in which the choice of a high-level goal is entrusted to the user and the autonomy generates low-level control~\citep{kim2012autonomy} and (b) signal-level paradigms in which the user and robot's control commands are blended together~\citep{muelling2017autonomy}.
-Shared control systems often require a good estimate of the human's intent to determine when and how to share control.
+Shared autonomy in assistive robotics aims to reduce the human's physical and cognitive burden during task execution without having the user to completely cede manual control~\citep{kim2012autonomy, muelling2017autonomy}.
+%Some common shared-control approaches include (a) hierarchical paradigms in which the choice of a high-level goal is entrusted to the user and the autonomy generates low-level control~\citep{kim2012autonomy} and (b) signal-level paradigms in which the user and robot's control commands are blended together~\citep{muelling2017autonomy}.
+%Shared control systems often require a good estimate of the human's intent to determine when and how to share control.
 Therefore, intent inference and disambiguation play a vital role in the seamless operation and success of a shared control system.
@@
 Every goal $g$ is associated with a potential field $\gamma_g$ which treats $g$ as an attractor and all the other goals in the scene as repellers.
-That is,
-\begin{equation*}
-\dot{\boldsymbol{x}}_r^{attract} = \boldsymbol{x}_{g} - \boldsymbol{x_r}
-\end{equation*}
- where $\dot{\boldsymbol{x}}_r$ indicates the velocity of the robot, $\boldsymbol{x}_{g}$ is the location of goal $g$.
+%That is,
+%\begin{equation*}
+%\dot{\boldsymbol{x}}_r^{attract} = \boldsymbol{x}_{g} - \boldsymbol{x_r}
+%\end{equation*}
+% where $\dot{\boldsymbol{x}}_r$ indicates the velocity of the robot, $\boldsymbol{x}_{g}$ is the location of goal $g$.
 Each dimension of $\dot{\boldsymbol{x}}_r^{attract}$ can be interpreted as the magnitude of the \textit{attractive pull} towards the goal along that dimension.
-The repeller velocity is given by
-\begin{equation*}
-\dot{\boldsymbol{x}}_r^{repel} = \sum_{i \in \mathcal{G} \setminus g} \frac{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}{\mu(\norm{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}^2)}
-\end{equation*}
- $\mu$ controls the magnitude of the repeller velocity. The autonomy command $\boldsymbol{u}_{r,g}$ is computed as a summation of the attractor and repeller velocities.
+%The repeller velocity is given by
+%\begin{equation*}
+%\dot{\boldsymbol{x}}_r^{repel} = \sum_{i \in \mathcal{G} \setminus g} \frac{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}{\mu(\norm{\boldsymbol{x_r} - \boldsymbol{x}_{g^i}}^2)}
+%\end{equation*}
+% $\mu$ controls the magnitude of the repeller velocity.
+%  The autonomy command $\boldsymbol{u}_{r,g}$ is computed as a summation of the attractor and repeller velocities.
 %\begin{equation*}
@@
 \subsubsection{Blending Paradigm}\label{sssec:blending}
-The final control command $\boldsymbol{u_f}$ issued to the robot then is given by
+The final control command $\boldsymbol{u}_f$ issued to the robot then is given by
 \begin{equation*}
-\boldsymbol{u_f} = \alpha\cdot \boldsymbol{u}_{r,g^*} + (1 - \alpha)\cdot \boldsymbol{u}_h
+\boldsymbol{u}_f = \alpha\cdot \boldsymbol{u}_{r,g^*} + (1 - \alpha)\cdot \boldsymbol{u}_h
 \end{equation*}
-where $g^*$ is the most confident goal and corresponds to the mode of $\boldsymbol{p}(t)$. The blending parameter, $\alpha$ is a piecewise linear function of the $p(g^*)$ and is specified as
-$$
-\alpha = \left\{
-\begin{array}{ll}
-0 & \quad\quad~~~ p(g^*) \leq \rho_1 \\
-\frac{\rho_3}{\rho_2 - \rho_1}\cdot p(g^*) &  \quad \text{if}\quad \rho_1 < p(g^*) \leq \rho_2  \\
-\rho_3 & \quad\quad~~~ p(g^*) > \rho_2 	
-\end{array}
-\right.
-$$
-with $\rho_i \in [0, 1] \;\forall\; i \in [1,2,3]$ and $ \rho_2 > \rho_1$. 
-In our implementation, we empirically set $\rho_1 = \frac{1.2}{n_g}, \rho_2 = \frac{1.4}{n_g}$ and $ \rho_3 = 0.7$.
+where $g^*$ is the most confident goal and corresponds to the mode of $b_{g^t}$. 
+The blending parameter, $\alpha$ is a piecewise linear function of the $p(g^*)$.
+%and is specified as
+%$$
+%\alpha = \left\{
+%\begin{array}{ll}
+%0 & \quad\quad~~~ p(g^*) \leq \rho_1 \\
+%\frac{\rho_3}{\rho_2 - \rho_1}\cdot p(g^*) &  \quad \text{if}\quad \rho_1 < p(g^*) \leq \rho_2  \\
+%\rho_3 & \quad\quad~~~ p(g^*) > \rho_2 	
+%\end{array}
+%\right.
+%$$
+%with $\rho_i \in [0, 1] \;\forall\; i \in [1,2,3]$ and $ \rho_2 > \rho_1$. 
+%In our implementation, we empirically set $\rho_1 = \frac{1.2}{n_g}, \rho_2 = \frac{1.4}{n_g}$ and $ \rho_3 = 0.7$.
 \subsubsection{Maximum Potential Mode Switch Assistance}\label{sssec:baseline}
@@
 At any given time $t$, the system selects the control mode which has the \textit{maximum attractive pull} or \textit{maximum potential} towards the predicted goal.
-For each control dimension $k$, the magnitude of the $k^{th}$ dimension of $\dot{\boldsymbol{x}}_r^{attract}$ is a measure of the attractive potential along $k$.
+%For each control dimension $k$, the magnitude of the $k^{th}$ dimension of $\dot{\boldsymbol{x}}_r^{attract}$ is a measure of the attractive potential along $k$. 
 The attractive potential of each control mode $m \in \mathcal{M}$ is computed as the total attractive potential of all control dimensions $k \in m$.
@@
 We used the mode switching scheme described in Section~\ref{sssec:baseline} as the baseline for comparison.
-\subsubsection{Simulated $\boldsymbol{u_r}$ and $\boldsymbol{u_h}$}
-The simulated robot autonomy $\boldsymbol{u^{sim}_r}$ is generated using a repeller-free potential field.
-In a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u^{sim}_h}$ is given by
-\begin{equation*}
-\boldsymbol{u^{sim}_h} = \argmax_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)} \boldsymbol{u_h}\cdot(\boldsymbol{x_g}^{intended} - \boldsymbol{x_r})
-\end{equation*}
-where $\boldsymbol{x_g}^{intended}$ is the position of the human's intended goal which is known only to the human and the system tries to infer using the inference mechanism.
-This model of simulated human control command assumes that the user issues control commands at all times and always tries to optimize for distance and time.
+\subsubsection{$\boldsymbol{u}_r$ and $\boldsymbol{u}_h$}
+The simulated robot autonomy $\boldsymbol{u}^{sim}_r$ is generated using a repeller-free potential field.
+For an intended goal $g^{intended}$ and a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u}^{sim}_h$ is sampled from the $p(\boldsymbol{u}_h\;|\;g^{intended}, m)$.
+%\begin{equation*}
+%\boldsymbol{u}^{sim}_h = \argmax_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)} \boldsymbol{u_h}\cdot(\boldsymbol{x_g}^{intended} - \boldsymbol{x_r})
+%\end{equation*}
+%where $\boldsymbol{x_g}^{intended}$ is the position of the human's intended goal which is known only to the human and the system tries to infer using the inference mechanism. 
+%This model of simulated human control command assumes that the user issues control commands at all times and always tries to optimize for distance and time.
 The final control command issued to the point robot was determined by the blending-based shared control scheme described in Section~\ref{sssec:blending}.
@@
 	\item \textit{Inference Accuracy }: Fraction of the total trial time for which the intent inference mechanism correctly inferred the human's intended goal.
-This is a measure of overall confidence of the system.
+This is a measure of overall accuracy of the system.
 \end{itemize}
-\begin{table}[t]
-	\centering
-	\begin{tabular}{|p{1cm}|p{0.5cm}|p{3cm}|}
-		\hline
-		\textbf{Space} & $n_k$ &\textbf{Control Mode Sets}  \\ \hline
-		$\mathbb{R}^2$ & $2$ & $\{[1],[2]\}$ \\ \hline
-		$\mathbb{R}^3$ & $3$ & $\{[1],[2], [3]\}$, $\{[1,2], [3]\}$ \\ \hline
-		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
-		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
-	\end{tabular}
-	\vspace{.2cm}
-	\caption{Predefined control space partition sets for each of the simulation spaces.} 
-	\label{tbl:cmp}
-	\vspace{-.5cm}
-\end{table}
+%\begin{table}[t]
+%	\centering
+%	\begin{tabular}{|p{1cm}|p{0.5cm}|p{3cm}|}
+%		\hline
+%		\textbf{Space} & $n_k$ &\textbf{Control Mode Sets}  \\ \hline
+%		$\mathbb{R}^2$ & $2$ & $\{[1],[2]\}$ \\ \hline
+%		$\mathbb{R}^3$ & $3$ & $\{[1],[2], [3]\}$, $\{[1,2], [3]\}$ \\ \hline
+%		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
+%		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
+%	\end{tabular}
+%	\vspace{.2cm}
+%	\caption{Predefined control space partition sets for each of the simulation spaces. The numbers in the control mode sets indicate the dimensions. } 
+%	\label{tbl:cmp}
+%	\vspace{-.5cm}
+%\end{table}
 \subsubsection{Simulation Protocol}
-5000 simulation runs were performed for each of the scenarios. 
+8000 simulation runs were performed for each of the scenarios. 
 The maximum trial duration was set at $12s$ or equivalently $120$ time-steps with $\Delta t = 0.1$.
-The mode switch assistance algorithm was activated once every $4$ time-steps.
+The forward projection time was set to be $4$ seconds and the mode switch assistance algorithm was activated once every $10$ time-steps.
 The trial was ended prematurely if the robot reached within the intended goal as determined by a pre-specified distance threshold.
-Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
-\added{modify the simulation parameters.
-Talk about projection time.
-}
- \begin{figure}[h!]
-	\centering
-	\includegraphics[width= 0.8\hsize, height=0.28\vsize]{./figures/WS_SIM.eps}
-	\vspace{-0.35cm}
-	\caption{Example of point robot simulation in $\mathbb{R}^2$.
+The expectation in Equations~\ref{eq:ent} and \ref{eq:kldiv} was computed by averaging over five samples.
+A \textit{sparsity} factor was added to the human control command to capture the dropouts exhibited by humans during robot teleoperation.
+%Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
+% \added{modify the simulation parameters. Talk about projection time. }
+% \begin{figure}[h!]
+%	\centering
+%	\includegraphics[width= 0.8\hsize, height=0.28\vsize]{./figures/WS_SIM.eps}
+%	\vspace{-0.35cm}
+%	\caption{Example of point robot simulation in $\mathbb{R}^2$.
 The goals are represented in black, the initial robot position in red and the human's intended goal in magenta.
@@
 Greedy (Black), Entropy (Red), KL Divergence (Blue) and Heuristic (Green).}
-	\label{fig:ws_sim}
-\end{figure}
+%	\label{fig:ws_sim}
+%\end{figure}
  \begin{figure}[t!]
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.4\vsize]{./figures/initial_alpha.eps}
+	\includegraphics[width= 1.\hsize, height=0.3\vsize]{./figures/initial_alpha.eps}
 	\vspace{-0.75cm}
@@
 The robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy} and the control interface mapping was 1D and discrete.
- Additionally, a \textit{sparsity} factor was added to the simulated human control command $\boldsymbol{u^{sim}_h}$ to capture the variability in command timing exhibited by humans during robot teleoperation.
-This sparsity factor captured the \textit{idle time} users have during task execution when teleoperating a robot and was randomly set between 20\% and 80\% as informed by the analysis of teleoperation data from previous experiments conducted in our lab.
+% This sparsity factor captured the \textit{idle time} users have during task execution when teleoperating a robot and was randomly set between 20\% and 80\% as informed by the analysis of teleoperation data from previous experiments conducted in our lab.
 
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/total_assistance.eps}
+	\includegraphics[width= 1.\hsize, height=0.3\vsize]{./figures/total_assistance.eps}
 	\vspace{-0.8cm}
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.31\vsize]{./figures/correct_inference.eps}
+	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/correct_inference.eps}
 	\vspace{-0.75cm}
@@
 This shows that when the disambiguation scheme is used, the autonomy is able to provide assistance \textit{earlier} during task execution.
-This is likely due to the fact that with disambiguation the system is able to elicit more informative control commands from the user and narrow down its prediction to the correct goal quicker during task execution.
+This implies that with disambiguation the system is able to elicit more informative control commands from the user and narrow down its prediction to the correct goal quicker during task execution.
 As a result, the confidence in the prediction becomes higher and the robot assistance is triggered earlier during a trial.

### 2019-02-27 TexStuff/IROS2018_ResubmitTex/GopinathArgall_IROS2019_2.tex
After submission

@@
 \title{An Information Theoretic Formalism \\for Intent Disambiguation}
-\author{Author Names Omitted for Anonymous Review. [Paper ID: \textbf{187}]}
+%\author{Author Names Omitted for Anonymous Review. [Paper ID: \textbf{187}]}
 % You will get a Paper-ID when submitting a pdf file to the conference system
-%\author{Deepak Gopinath and Brenna D. Argall}
+\author{Deepak Gopinath and Brenna D. Argall}
 
@@
 For example, an automatic time-optimal mode switch assistance has been proposed which has shown to significantly improve user satisfaction~\citep{herlant2016assistive}.
-In the area of myoelectric prosthetics, dynamic switching approaches that learn the most effective control option during task execution using temporal difference and reinforcement learning have also been proposed~\cite{pilarski2012dynamic}.
+%In the area of myoelectric prosthetics, dynamic switching approaches that learn the most effective control option during task execution using temporal difference and reinforcement learning have also been proposed~\cite{pilarski2012dynamic}.
 
@@
 This section describes how our autonomy reasons about the intent disambiguation capabilities of different control modes by computing the information gain and content of the belief over goals.
-We utilize a model-based approach in which the human is modeled as an adjustable rational agent that seeks to take the shortest distance path to the goal.
+We utilize a model-based approach in which the human is modeled as a rational agent that seeks to take the shortest distance path to the goal.
 We also describe the various intent inference schemes that we utilize in our experiments, that work in conjunction with our disambiguation algorithm.
@@
 The first step towards the computation of the disambiguation metric $D_m$ for each $m \in \mathcal{M}$ is the forward projection of the probability distribution $b_{g^t}$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
-We rely on a model-based approach in which the human policy under the Boltzmann rationality assumption [] is modeled as a von Mises Fisher distribution [].
-That is,
+We rely on a model-based approach in which the human policy under the Boltzmann rationality assumption [] is modeled as
 \begin{equation}
@@
  \begin{equation}\label{eq:kldiv}
- D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_{g^{t_b}}||b_{g^{t_a}})\Big]
+ D_m = \frac{1}{\vert n_g \vert} \sum_{g \in \mathcal{G}}^{} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_{g^{t_b}}||b_{g^{t_a}})\Big] \;\;\;\;.
  \end{equation}
@@
 %Dynamic neural fields are differential equations in time that governs the time evolution of dynamical state variables, with some specific properties such as recurrent interactions between the state variables, robustness to external noise and memory.
-Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics, based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing~\citep{schoner2008dynamical}.
-When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$, where $p^i(t)$ denotes the probability associated with the $i^{th}$ goal at time $t$~\citep{gopinath2017disamb} and $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots,p^{n_g}(t) ]^{T}$.
+Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics~\citep{schoner2008dynamical}. 
+%based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing
+When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$, where $p^i(t)$ denotes the probability associated with the $i^{th}$ goal at time $t$ and $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots,p^{n_g}(t) ]^{T}$.
 %Recurrent interactions between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
@@
 \end{multline}
-where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector of dimension $n_g \times 1$ containing all ones, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a function that encodes the nonlinearity through which human control commands and task features affect the time evolution, $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters that affect the time-evolution of the probability distribution, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
+where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector of dimension $n_g \times 1$ containing all ones, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a nonlinear function through which human control commands and task features affect the time evolution, $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
 %In the absence of any information or cues, the probability distribution settles to a resting state which is a uniform distribution, that is whenever $\boldsymbol{u}_h = 0$, $\boldsymbol{\xi} = \vec{0}$.
@@
 \end{table}
+\begin{table}[t]
+	\centering
+	\begin{tabular}{|p{1cm}|p{0.5cm}|p{3cm}|}
+		\hline
+		\textbf{Space} & $n_k$ &\textbf{Control Mode Sets}  \\ \hline
+		$\mathbb{R}^2$ & $2$ & $\{[1],[2]\}$ \\ \hline
+		$\mathbb{R}^3$ & $3$ & $\{[1],[2], [3]\}$, $\{[1,2], [3]\}$ \\ \hline
+		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
+		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
+	\end{tabular}
+	\vspace{.2cm}
+	\caption{Predefined control space partition sets for each of the simulation spaces. The numbers in the control mode sets indicate the dimensions. } 
+	\label{tbl:cmp}
+	\vspace{-.5cm}
+\end{table}
 
@@
 We used the mode switching scheme described in Section~\ref{sssec:baseline} as the baseline for comparison.
-\subsubsection{$\boldsymbol{u}_r$ and $\boldsymbol{u}_h$}
+\subsubsection{$\boldsymbol{u}_r$ and $\boldsymbol{u}_h^{sim}$}
 The simulated robot autonomy $\boldsymbol{u}^{sim}_r$ is generated using a repeller-free potential field.
-For an intended goal $g^{intended}$ and a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u}^{sim}_h$ is sampled from the $p(\boldsymbol{u}_h\;|\;g^{intended}, m)$.
+For an intended goal $g^{intended}$ and a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u}^{sim}_h$ is sampled from the mode-conditioned policy, $p(\boldsymbol{u}_h\;|\;g^{intended}, m)$.
 %\begin{equation*}
@@
 \end{itemize}
-%\begin{table}[t]
-%	\centering
-%	\begin{tabular}{|p{1cm}|p{0.5cm}|p{3cm}|}
-%		\hline
-%		\textbf{Space} & $n_k$ &\textbf{Control Mode Sets}  \\ \hline
-%		$\mathbb{R}^2$ & $2$ & $\{[1],[2]\}$ \\ \hline
-%		$\mathbb{R}^3$ & $3$ & $\{[1],[2], [3]\}$, $\{[1,2], [3]\}$ \\ \hline
-%		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
-%		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
-%	\end{tabular}
-%	\vspace{.2cm}
-%	\caption{Predefined control space partition sets for each of the simulation spaces. The numbers in the control mode sets indicate the dimensions. } 
-%	\label{tbl:cmp}
-%	\vspace{-.5cm}
-%\end{table}
+
 \subsubsection{Simulation Protocol}
@@
 The expectation in Equations~\ref{eq:ent} and \ref{eq:kldiv} was computed by averaging over five samples.
-A \textit{sparsity} factor was added to the human control command to capture the dropouts exhibited by humans during robot teleoperation.
+A \textit{dropout} factor was added to the human control command to capture the signal sparsity exhibited by humans during robot teleoperation.
 %Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.3\vsize]{./figures/initial_alpha.eps}
+	\includegraphics[width= 1.\hsize, height=0.3\vsize, center]{./figures/onset_time.eps}
 	\vspace{-0.75cm}
@@
 During each trial, the mode switching algorithm was activated every $5s$ and the maximum trial duration was set at $40s$.
-The robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy} and the control interface mapping was 1D and discrete.
+The robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy} and the control interface mapping was 1D and discrete (similar to that of a headarray).
 % This sparsity factor captured the \textit{idle time} users have during task execution when teleoperating a robot and was randomly set between 20\% and 80\% as informed by the analysis of teleoperation data from previous experiments conducted in our lab.
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/correct_inference.eps}
+	\includegraphics[width= 1.1\hsize, height=0.5\vsize]{./figures/correct_inference.eps}
 	\vspace{-0.75cm}
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/mico_sim_res.eps}
+	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/mico_sim.eps}
 	\vspace{-0.5cm}
@@
 Figure~\ref{fig:mico_results} reveals that for the simulations conducted on a simulated robotic arm, the onset of initial assistance towards the correct goal is earlier compared to that of the baseline ($p < 0.05$).
-Similarly, the accuracy of the intent inference procedure is higher when disambiguation algorithm is deployed ($p < 0.001$).
-With disambiguation the total amount of assistance provided by the system also is slightly higher, though not significantly so, compared to the baseline mode-switching scheme.
+Similarly, the accuracy of the intent inference procedure is higher when disambiguation algorithm is deployed, although not statistically significant.
+However, the total amount of assistance provided by the autonomy is comparable between the mode-switching schemes.
 These results indicate that even with a low-dimensional and discrete control interface that exhibits signal dropouts (due to the sparsity factor), robot operation in control modes selected by the disambiguation algorithm helps the autonomy to elicit more intent-revealing control commands thereby helping the system predict the intended goal more accurately and provide assistance earlier.
@@
 The effectiveness of an assistive machine in a shared control setting is closely related to its ability to infer the user's intent accurately and unambiguously.
-Accurate goal inference can improve the trust and communication between the human and the robot and can result in seamless and fluid human robot interaction.
-On the other hand, incorrect goal inference can likely lead to frustrating user experience and can often have a detrimental effect on task performance.
-Our results indicate that disambiguation helps to enhance the accuracy of the intent inference procedure and results in an increase in overall assistance provided to the user.
+Accurate goal inference can improve the trust in human-robot interaction.
+On the other hand, incorrect goal inference can likely lead to frustrating user experience and often result in poor task performance.
+Our results indicate that disambiguation helps to enhance the accuracy of the intent inference and leads to an increase in the overall assistance provided to the user.
 Yet another factor that is crucial for the success of a shared control system, especially for safety-critical applications, is \textit{when} during task execution the assistance gets activated.
@@
 For instance, in the beginning stages of task execution when the intent is unclear, disambiguation algorithms are likely to be more useful.
-Once task execution gets underway and intent is clarified, a greedy time-optimal mode switching scheme can be used to lead the user towards successful task completion.
 That is, a more optimal strategy might be one which is adaptive and chooses different schemes depending on the context.
-This could possibly be cast within a control theoretic framework as a mode-scheduling problem in which the question of \textit{when} to deploy \textit{which} mode-switching paradigm can be solved concurrently.
+This could possibly be cast within a control theoretic framework as a mode-scheduling problem in which the question of \textit{when} to deploy \textit{which} mode-switching paradigm can be tackled.
 
-High fidelity models for how a user teleoperates a robot and robot kinematics can be learned from data using machine learning tools such as deep neural networks~\citep{nagabandi2017neural}, Gaussian processes~\citep{wang2013probabilistic}.
-With sufficient data these techniques have the capability to capture the inherent nonlinearities in human-robot systems.
-Characterization of the disambiguation capabilities of different control modes can benefit a great deal from more accurate models of robot kinematics and user teleoperation.
-Furthermore, the disambiguation algorithm can be customized to specific users using real-time learning algorithms that capture individual teleoperation characteristics.
+Disambiguation algorithms can benefit from high fidelity models of robot kinematics and user teleoperation that can be learned from data using machine learning techniques such as deep neural networks~\citep{nagabandi2017neural}.
+Furthermore, parallel computation on GPU can also be leveraged for more accurate estimation of the expectation in Equations~\ref{eq:ent} and \ref{eq:kldiv}.
+Lastly, the disambiguation algorithm can be customized to specific users using real-time learning algorithms that capture individual teleoperation characteristics.
 
@@
 In our future work, we plan to perform an in-depth analysis of the data to expose the interactions between various factors.
-Knowledge of how different components interact and influence each other is critical for the design of a successful shared control system.
 Furthermore, as informed by the simulation results, we plan to evaluate our system with an extensive user study.

### 2019-02-27 TexStuff/IROS_2019_propertex_file/GopinathArgall_IROS2019_Disamb.tex
After submission

--- 2019-02-27 TexStuff/IROS2018_ResubmitTex/GopinathArgall_IROS2019_2.tex
@@
-\documentclass[conference]{IEEEtran}
-\usepackage{times}
-% numbers option provides compact numerical references in the text. 
-\usepackage{changes}
-\usepackage[numbers]{natbib}
-\usepackage{multicol}
-\usepackage{tabularx}
-\usepackage[bookmarks=true]{hyperref}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%2345678901234567890123456789012345678901234567890123456789012345678901234567890
+%        1         2         3         4         5         6         7         8
+
+\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
+
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
+
+\IEEEoverridecommandlockouts                              % This command is only needed if 
+                                                          % you want to use the \thanks command
+
+\overrideIEEEmargins                                      % Needed to meet printer requirements.
+
+%In case you encounter the following error:
+%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
+%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
+%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
+%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
+%\pdfobjcompresslevel=0
+%\pdfminorversion=4
+
+% See the \addtolength command later in the file to balance the column lengths
+% on the last page of the document
+
+% The following packages can be found on http:\\www.ctan.org
 \usepackage{graphics} % for pdf, bitmapped graphics files
+\usepackage{epsfig} % for postscript graphics files
+\usepackage{mathptmx} % assumes new font selection scheme installed
+\usepackage{times} % assumes new font selection scheme installed
+\usepackage{amsmath} % assumes amsmath package installed
+\usepackage{amssymb}  % assumes amsmath package installed
 \usepackage{graphicx}
-\usepackage[numbers]{natbib}
-\usepackage{multicol}
-\usepackage[bookmarks=true]{hyperref}
+\usepackage{amssymb}
+\usepackage{graphicx}
 \usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
-
-\usepackage{amsmath} % assumes amsmath package installed  % assumes amsmath package installed
 \usepackage{mathtools, bbm}
+\usepackage{amsmath} % assumes amsmath package installed
+\usepackage{amssymb}  % assumes amsmath package installed
 \usepackage{lipsum}
+\usepackage{dsfont}
 \usepackage[export]{adjustbox}
@@
 \usepackage{url}
-\usepackage{booktabs}
-\usepackage{pifont}
+\usepackage{microtype}
 \usepackage{algorithm, algorithmic}
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator{\E}{\mathbb{E}}
-%\newcommand{\argmax}{\arg\!\max}
+\usepackage{breqn}
+\usepackage[bottom]{footmisc}
+
+%\usepackage{times}
+%% numbers option provides compact numerical references in the text. 
+%\usepackage{changes}
+%\usepackage[numbers]{natbib}
+%\usepackage{multicol}
+%\usepackage{tabularx}
+%\usepackage[bookmarks=true]{hyperref}
+%\usepackage{graphics} % for pdf, bitmapped graphics files
+%\usepackage{graphicx}
+%\usepackage[numbers]{natbib}
+%\usepackage{multicol}
+%\usepackage[bookmarks=true]{hyperref}
+%\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
+%
+%\usepackage{amsmath} % assumes amsmath package installed  % assumes amsmath package installed
+%\usepackage{mathtools, bbm}
+%\usepackage{lipsum}
+%\usepackage[export]{adjustbox}
+%\usepackage[normalem]{ulem} % underline
+%\usepackage{wrapfig}
+%\usepackage{multirow}
+%\usepackage{balance}
+%\usepackage{color}
+%\usepackage{url}
+%\usepackage{booktabs}
+%\usepackage{pifont}
+%\usepackage{algorithm, algorithmic}
+\newcommand{\argmax}{\arg\!\max}
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-%\def\bibfont{\footnotesize}
-\pdfinfo{
-	/Author (Deepak Gopinath, Brenna D. Argall)
-	/Title  (Information Theoretic Formulation of Intent Disambiguation)
-	/CreationDate (January 31 2018)
-	/Subject (Robots)
-	/Keywords (Robots)
+
+\title{\LARGE \bf
+Information-Theoretic Characterization of Control Modes for\\ Intent Disambiguation
 }
-% numbers option provides compact numerical references in the text.
 
-\pdfinfo{
-   /Author (Homer Simpson)
-   /Title  (Robots: Our new overlords)
-   /CreationDate (D:20101201120000)
-   /Subject (Robots)
-   /Keywords (Robots;Overlords)
+\author{Deepak Gopinath$^{1}$ and Brenna D. Argall$^{2}$% <-this % stops a space
+\thanks{This material is based upon work supported by the National Science Foundation under Grant CNS 1544741. Any opinions, findings and conclusions or
+	recommendations expressed in this material are those of the authors and do
+	not necessarily reflect the views of the aforementioned institutions. 
+}% <-this % stops a space
+\thanks{$^{1}$Deepak Gopinath is with the Department of Mechanical Engineering, Northwestern University, Evanston, IL, USA and Shirley Ryan AbilityLab, Chicago, IL, USA
+        {\tt\small deepak.gopinath@u.northwestern.edu}}%
+\thanks{$^{2}$Brenna D.
+Argall is with the Department of Mechanical Engineering, Department of Electrical Engineering and Computer Science, Northwestern University, Evanston, IL, Department of Physical Medicine and Rehabilitation, Northwestern University, Chicago, IL and Shirley Ryan AbilityLab, Chicago, IL.
+        {\tt\small brenna.argall@northwestern.edu}}%
 }
@@
 
-% paper title
-\title{An Information Theoretic Formalism \\for Intent Disambiguation}
-%\author{Author Names Omitted for Anonymous Review. [Paper ID: \textbf{187}]}
-% You will get a Paper-ID when submitting a pdf file to the conference system
-\author{Deepak Gopinath and Brenna D. Argall}
+\maketitle
+\thispagestyle{empty}
+\pagestyle{empty}
 
-%\author{\authorblockN{Deepak Gopinath}
-%\authorblockA{Department of Mechanical\\Engineering,
-%Northwestern University\\
-%Evanston, Illinois 30332\\
-%Email: deepakedakkattilgopinath2015\\@u.northwestern.edu}
-%\and
-%\authorblockN{Brenna D. Argall}
-%\authorblockA{Department of Mechanical\\Engineering,
-%		Northwestern University\\
-%		Evanston, Illinois 30332\\
-%		Email: brenna.argall@northwestern.edu}
-%	}
-
-%\author{Deepak Gopinath$^{1}$ and Brenna D. Argall$^{2}$
-%	\thanks{Manuscript received: March, 1, 2016; Revised June,
-%		7, 2016; Accepted June, 29, 2016.}
-%}
-% avoiding spaces at the end of the author lines is not a problem with
-% conference papers because we don't use \thanks or \IEEEmembership
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\authorblockN{Deepak E. Gopinath\authorrefmark{1}\authorrefmark{2},
-%		Brenna D. Argall\authorrefmark{1}\authorrefmark{2}\authorrefmark{3}\authorrefmark{4}
-%	}
-%	\authorblockA{
-%		\authorrefmark{1}Department of Mechanical Engineering, Northwestern University, Evanston, IL}
-%	
-%	\authorblockA{\authorrefmark{2}Rehabilitation Institute of Chicago, Chicago, IL}
-%	
-%	\authorblockA{\authorrefmark{3}Department of Physical Medicine and Rehabilitation, Northwestern University, Chicago, IL}
-%	
-%	\authorblockA{\authorrefmark{4}Department of Electrical Engineering and Computer Science, Northwestern University, Evanston, IL}
-%	
-%	\authorblockA{{\tt\small deepakgopinath@u.northwestern.edu}}
-%	\authorblockA{{\tt\small brenna.argall@northwestern.edu}}
-%}
-
-\maketitle
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
 The effectiveness of assistive robots is closely related to their ability to infer the user's needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately.
-In this paper, we proposed a mode selection paradigm that enhances the autonomy's intent inference capabilities by exploiting the fact that how the human operates the robot and reveals his/her intent is intrinsically conditioned on the control mode in operation.
-We formulate this as a problem of intent disambiguation in information theoretic terms.
-We propose two different methods for enhancing intent inference via improved disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}.
-In our system, the autonomy maintain a probability distribution over goals (beliefs) and we characterize the disambiguation capabilities of the different control modes/dimensions utilizing a model-based approach to compute the average information gain and content.
+In this paper, we propose a mode selection paradigm that enhances the autonomy's intent inference capabilities by exploiting the fact that how the human operates the robot and reveals his/her intent is intrinsically conditioned on the control mode in operation.
+We formulate this as a problem of intent disambiguation in information-theoretic terms.
+We propose two different methods for enhancing intent inference via improved disambiguation using the information-theoretic concepts of \textit{entropy} and \textit{KL divergence}.
+In our system, the autonomy maintains a probability distribution over goals (beliefs) and we characterize the disambiguation capabilities of the different control modes/dimensions utilizing a model-based approach to compute the average information gain and content.
 %The proposed algorithms characterize the disambiguation capabilities of the \added{different control modes?} system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content.
@@
 
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-Assistive machines such as robotic arms and smart wheelchairs have the potential to transform the lives of millions of people with motor impairments~\citep{laplante1992assistive}.
-These machines can promote independence, enhance the quality of lives, extend the mobility and manipulation capabilities of individuals and revolutionize the way people interact with society.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{INTRODUCTION}
+Assistive machines such as robotic arms and smart wheelchairs have the potential to transform the lives of people with motor impairments~\cite{laplante1992assistive}.
+These machines can promote independence, enhance quality of lives, extend the mobility and manipulation capabilities of individuals, and revolutionize the way people interact with society.
 %They can also help , thereby helping motor-impaired people perform activities of daily living in a more effective manner.
@@
 For this reason, at any given point in time during task execution they can only operate in a subset of the entire control space.
-These subsets are referred to as \textit{control modes}~\citep{simpson2008tooth}.
+These subsets are referred to as \textit{control modes}~\cite{simpson2008tooth}.
 To schedule and execute switches between control modes can be both mentally and physically demanding, and might be alleviated in part by the introduction of robotics autonomy.
@@
 In Bayesian terminology, maintaining and updating the belief is the \textit{recursive Bayesian filtering} problem.
-Intent inference algorithms typically rely on various environmental cues and task-relevant features such as the robot and goal positions, human control commands and biometric measures~\citep{croft2003estimating} as their evidence variables.
+Intent inference algorithms typically rely on various task-relevant features such as the robot and goal positions, human control commands and biometric measures~\cite{croft2003estimating} as their evidence variables.
 In contrast, due to reasons of user adoption and cost, our system matches the interfaces available on typical commercial assistive machines (such as powered wheelchairs) and so infers intent exclusively based on the information contained in the constrained control commands issued to the assistive machine.
@@
 	\item The posterior computation of the belief over goals depends on the human policy which indirectly depends on the active control mode. 
-	\item Utilizing a model-based approach to forward project the beliefs over goals, the autonomy can \textit{counterfactually } reason about the information gain and content for different control modes.
-	\item Using this information theoretic characterization of control modes, the autonomy chooses the control mode with the highest intent disambiguation capability \textit{for} the human.
+	\item Utilizing a model-based approach to project the beliefs over goals forward in time, the autonomy can \textit{counterfactually } reason about the information gain and content for different control modes.
+	\item Using this information-theoretic characterization of control modes, the autonomy chooses the control mode with the highest intent disambiguation capability \textit{for} the human.
 	\item Having the human provide control input within these information-rich control modes can likely improve the accuracy of intent inference.
@@
 
-In this paper, we address the problem of accurate intent inference by characterizing control modes according to their information content and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
+In this paper, we address how to enhance the accuracy of intent inference by characterizing control modes according to their information content and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
 We formalize the problem of intent disambiguation within the framework of information theory.
-Specifically, we make use of the information theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the information content---with respect to intent disambiguation---of each control mode.
+Specifically, we make use of the information-theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the information content---with respect to intent disambiguation---of each control mode.
 
@@
 In Section~\ref{sec:related_work} we present an overview of relevant research.
-Section~\ref{sec:math} introduces our set theoretic treatment of control modes, followed by intent disambiguation and intent inference in Section~\ref{sec:disamb}.
+Section~\ref{sec:math} introduces our set theoretic treatment of control modes, followed by intent disambiguation and intent inference in Sections~\ref{sec:disamb} and \ref{sec:inference} respectively.
 The study design and experimental methods are discussed in Section~\ref{sec:ed} followed, by results in Section~\ref{sec:results}.
@@
 Robot assistance schemes that seek to elicit more informative cues \textit{from} the human to clarify the underlying intent can be thought of as an information acquisition problem.
-Intent acquisition can leverage the underlying synergies and shared intentionality~\citep{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions
+Intent acquisition can leverage the underlying synergies and shared intentionality~\cite{tomasello2007shared} of human-robot teams and can be an active process in which the robot performs actions
 %(for example, selecting a control mode or executing a robot motion) 
 that will nudge the human to reveal her/his intent more clearly~\cite{sadigh2016information}.
-Information theoretic metrics such as KL divergence can be utilized to identify regions of the sample space that will maximize information gain~\citep{tong2001active} and subsequently guide the data sampling process.
-%Sensing robots designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\citep{atanasov2014information}. 
-If the spatial distribution of information density is known \textit{a priori}, information maximization can be accomplished by maximizing the ergodicity of the robot's trajectory with respect to the underlying information density~\citep{miller2016ergodic}.
+Information-theoretic metrics such as KL divergence can be utilized to identify regions of the sample space that will maximize information gain~\cite{tong2001active} and subsequently guide the data sampling process.
+Sensing robots that are designed for automated exploration and data acquisition tasks can benefit from exploring more information-rich regions in the environment~\cite{atanasov2014information}. 
+If the spatial distribution of information density is known \textit{a priori}, information maximization can be accomplished by maximizing the ergodicity of the robot's trajectory with respect to the underlying information density~\cite{miller2016ergodic}.
 
@@
 Intent inference and recognition can be classified into two broad categories: heuristic approaches and model-based approaches.
-Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features (such as motion cues) and the human's underlying intention~\citep{baker2007goal}.
+Heuristic approaches are often simpler and computationally light-weight and seek to find direct mappings between various task relevant features (such as motion cues) and the human's underlying intention~\cite{baker2007goal}.
 On the other hand, in model-based approaches the system maintains a model of how a human maps states to control actions.
 The model can either be learned from data or can be hand-designed based on domain knowledge.
-For example, the human can be modeled within the Partially Observable Markov Decision Process (POMDP)~\citep{taha2011pomdp} framework and is assumed to behave according to a control policy that maps states to actions.
+For example, the human can be modeled within the Partially Observable Markov Decision Process (POMDP)~\cite{taha2011pomdp} framework and is assumed to behave according to a control policy that maps states to actions.
 However, in model-based approaches incorporating the entire history of states requires estimation of joint probability distributions over past states which can become computationally expensive and intractable quickly.
@@
 Various mode switching assistance paradigms have been proposed to alleviate task effort.
-For example, an automatic time-optimal mode switch assistance has been proposed which has shown to significantly improve user satisfaction~\citep{herlant2016assistive}.
-%In the area of myoelectric prosthetics, dynamic switching approaches that learn the most effective control option during task execution using temporal difference and reinforcement learning have also been proposed~\cite{pilarski2012dynamic}.
+For example, an automatic time-optimal mode switch assistance has been proposed which has shown to significantly improve user satisfaction~\cite{herlant2016assistive}.
+In the area of myoelectric prosthetics, dynamic switching approaches that learn the most effective control option during task execution using temporal difference and reinforcement learning have also been proposed~\cite{pilarski2012dynamic}.
 
@@
 \subsection{Probability Distribution Over Goals}\label{ssec:notation}
- In assistive robotic manipulation, intent inference is most commonly the process of estimating the user's intended goal out of a set of discrete objects in the environment~\citep{calli2015ycb}.
+In assistive robotic manipulation, intent inference is most commonly the process of estimating the user's intended goal out of a set of discrete objects in the environment~\cite{calli2015ycb}.
 The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$.
@@
 Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i = \mathcal{K}$.
-The cardinality of each mode $m \in \mathcal{M}$, denoted by $\vert m \vert$, indicates the number of dimensions that can be controlled when operating in $m$.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes and so it is possible that $m^i \cap m^j \neq \emptyset$.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
-That is, for each $m \in \mathcal{M}$, the subspace of $\mathcal{R}^{n_k}$ that is accessible corresponds to $\mathcal{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
+The cardinality of each mode $m \in \mathcal{M}$, denoted by $\vert m \vert$, indicates the number of dimensions that can be controlled when operating in $m$\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes and so it is possible that $m^i \cap m^j \neq \emptyset$.}.
+Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+That is, for each $m \in \mathcal{M}$, the subspace of $\mathbb{R}^{n_k}$ that is accessible corresponds to $\mathbb{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
 Maximum velocity limits along each dimension impose further constraints on the set of control commands that are available in each mode.
@@
 We utilize a model-based approach in which the human is modeled as a rational agent that seeks to take the shortest distance path to the goal.
-We also describe the various intent inference schemes that we utilize in our experiments, that work in conjunction with our disambiguation algorithm.
+We also describe the various intent inference schemes that we utilize in our experiments, which work in conjunction with our disambiguation algorithm.
 
@@
 %\end{equation}
-Using Equations~\ref{eq:marginal_mode} and \ref{eq:mode_prob} and under the assumption that user does not change the goal during task execution, Equation~\ref{eq:recursive_belief} can be further simplified as
+Using Equations~\ref{eq:marginal_mode} and \ref{eq:mode_prob} and under the assumption that the user does not change the goal during task execution, Equation~\ref{eq:recursive_belief} can be further simplified as
 \begin{equation}\label{eq:final_belief}
@@
 We first perform a model-based projection of the probability distribution over goals (lines 5-9, Section~\ref{ssec:model_based}).
-We then compute the disambiguation capability $D_m$ of a control mode using information theoretic measures (lines 10-11) We present two different information theoretic measures for disambiguation: 1) information content in the projected probability distributions over goal as encoded by the \textit{entropy} of the distribution (Section~\ref{sssec:ent}) and 2) information gain as a result of the time evolution of the belief as encoded by the \textit{KL divergence} between the posterior and the prior distributions (Section~\ref{sssec:kl}).
+We then compute the disambiguation capability $D_m$ of a control mode using information-theoretic measures (lines 10-11) We present two different information-theoretic measures for disambiguation: 1) information content in the projected probability distributions over goal as encoded by the \textit{entropy} of the distribution (Section~\ref{sssec:ent}) and 2) information gain as a result of the time evolution of the belief as encoded by the \textit{KL divergence} between the posterior and the prior distributions (Section~\ref{sssec:kl}).
 
@@
 The first step towards the computation of the disambiguation metric $D_m$ for each $m \in \mathcal{M}$ is the forward projection of the probability distribution $b_{g^t}$ from current time $t_a$ to $t_b$ such that $t_a < t_b$.
-We rely on a model-based approach in which the human policy under the Boltzmann rationality assumption [] is modeled as
+We rely on a model-based approach in which the human policy under the Boltzmann rationality assumption~\cite{hula2015monte} is modeled as a von Mises distribution~\cite{mardia1975statistics}.
+That is,
 \begin{equation}
@@
 where $b_{g^{t_b}}$ denotes the projected probability distribution at time $t_b$ when the control command used for forward projection is sampled from the mode conditioned human policy $p(\boldsymbol{u}_h \; |\; g, m)$.
+
 \subsection{KL Divergence Disambiguation}\label{sssec:kl}
@@
 \end{equation}
-% 
-%\begin{equation*}
-%D_m = \frac{1}{\vert Vert(\mathcal{U}^m) \vert}\sum_{\boldsymbol{u_h} \in Vert(\mathcal{U}^m)} KL(\boldsymbol{p}(t_b; \boldsymbol{u_h})||\boldsymbol{p}(t_a))~~~~.
-%\end{equation*}
-\begin{algorithm}[t]
-	\caption{Information Theoretic Intent Disambiguation}
+
+\begin{algorithm}[h]
+	\caption{Information-Theoretic Intent Disambiguation}
 	\label{alg:disamb}
@@
 \subsubsection{Heuristic Approaches}
-Heuristic approaches based on \textit{confidence} functions~\citep{dragan2013policy} seek to find direct mappings between instantaneous cues and underlying human intentions. 
+Heuristic approaches based on \textit{confidence} functions~\cite{gopinath2017human} seek to find direct mappings between instantaneous cues and underlying human intentions. 
 %For every goal $g \in \mathcal{G}$, the system maintains an associated set of confidences denoted by $\mathcal{C}$. 
@@
 where $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\;g, m)$ is the human control command.
-These confidence functions rely on instantaneous features and therefore are amnesic and can exhibit chatter behavior~\citep{dragan2012formalizing}.
+These confidence functions rely on instantaneous features and therefore are amnesic and can exhibit chatter behavior~\cite{dragan2012formalizing}.
 %Using the above-mentioned confidence functions, we have 
@@
 As a result, the inference is not robust to external noise and can exhibit chatter behavior.
+
 \subsubsection{Bayesian Approaches}
@@
 %Dynamic neural fields are differential equations in time that governs the time evolution of dynamical state variables, with some specific properties such as recurrent interactions between the state variables, robustness to external noise and memory.
-Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics~\citep{schoner2008dynamical}. 
+Dynamic neural fields were originally conceived to explain cortical population neuronal dynamics~\cite{schoner2008dynamical}. 
 %based on the hypothesis that the excitatory and inhibitory neural interactions between local neuronal pools form the basis of cortical information processing
-When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$, where $p^i(t)$ denotes the probability associated with the $i^{th}$ goal at time $t$ and $\boldsymbol{p}(t) = [p^1(t), p^2(t),\dots,p^{n_g}(t) ]^{T}$.
+When applied to the problem of intent inference, the individual goal probabilities are treated as constrained dynamical state variables whose time evolution is determined by a dynamic neural field such that $p^i(t) \in [0, 1]$ and $\Sigma_{1}^{n_g}p^{i}(t) = 1$, where $p^i(t)$ denotes the probability associated with the $i^{th}$ goal at time $t$ and $\textit{\textbf{p}}(t) = [p^1(t), p^2(t),\dots,p^{n_g}(t) ]^{T}$.
 %Recurrent interactions between the state variables, robustness to external noise and inherent memory make dynamic neural fields an ideal candidate for an intent inference engine.
@@
 \begin{multline}\label{eq:dft}
-\frac{\partial \boldsymbol{p}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\boldsymbol{p}(t) + \underbrace{\frac{1}{n_g}\cdot\mathbbm{1}_{n_g}\bigg]}_{\text{rest state}} + \\ \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h^t;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
+	\frac{\partial \textit{\textbf{p}}(t)}{\partial t} = \frac{1}{\tau}\bigg[-\mathbb{I}_{n_g\times n_g}\cdot\textit{\textbf{p}}(t) + \underbrace{\frac{1}{n_g}\cdot\mathds{1}_{n_g}\bigg]}_{\text{rest state}} + \\ \underbrace{\boldsymbol{\lambda}_{n_g\times n_g}\cdot\sigma(\boldsymbol{\xi}(\boldsymbol{u}_h^t;\boldsymbol{\Theta}))}_{\text{excitatory + inhibitory}}
 \end{multline}
-where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathbbm{1}_{n_g}$ is a vector of dimension $n_g \times 1$ containing all ones, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a nonlinear function through which human control commands and task features affect the time evolution, $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
+where time-scale parameter $\tau$ determines the memory capacity of the system, $\mathbb{I}_{n_g\times n_g}$ is the identity matrix, $\mathds{1}_{n_g}$ is a vector of dimension $n_g \times 1$ containing all ones, $\boldsymbol{\lambda}$ is the control matrix that controls the excitatory and inhibitory aspects, $\boldsymbol{\xi}$ is a nonlinear function through which human control commands and task features affect the time evolution, $\boldsymbol{\Theta}$ represents all other task-relevant features and parameters, and $\sigma$ is a biased sigmoidal nonlinearity given by $\sigma(\boldsymbol{\xi}) = \frac{1}{1 + e^{-\boldsymbol{\xi}}} - 0.5$.
 %In the absence of any information or cues, the probability distribution settles to a resting state which is a uniform distribution, that is whenever $\boldsymbol{u}_h = 0$, $\boldsymbol{\xi} = \vec{0}$.
@@
 \section{Experimental Evaluation}\label{sec:ed}
-We evaluate the efficacy of the proposed disambiguation algorithm on simulated point robots and a simulated robotic manipulator that operates in a \textit{shared-control} setting.
+We evaluate the efficacy of the proposed disambiguation algorithm on simulated point robots and a simulated robotic manipulator that operates in a \textit{shared control} setting.
 This section describes the shared-control paradigm used in our experiments and the details of the simulation experiment.
@@
 \subsection{Shared Control}\label{ssec:shared-control}
-Shared autonomy in assistive robotics aims to reduce the human's physical and cognitive burden during task execution without having the user to completely cede manual control~\citep{kim2012autonomy, muelling2017autonomy}.
+Shared autonomy in assistive robotics aims to reduce the human's physical and cognitive burden during task execution without having the user to completely cede manual control~\cite{muelling2017autonomy}.
 %Some common shared-control approaches include (a) hierarchical paradigms in which the choice of a high-level goal is entrusted to the user and the autonomy generates low-level control~\citep{kim2012autonomy} and (b) signal-level paradigms in which the user and robot's control commands are blended together~\citep{muelling2017autonomy}.
@@
 Therefore, intent inference and disambiguation play a vital role in the seamless operation and success of a shared control system.
-In our experimental evaluation, control sharing is achieved with a blending-based paradigm in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
+In our experimental evaluation, control sharing is achieved with a blending-based paradigm, in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
 \subsubsection{Robot Autonomy}\label{sssec:autonomy}
@@
 
-The robot autonomy command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field which is defined in all parts of the state space~\citep{khatib1986real}.
+The robot autonomy command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field, which is defined in all parts of the state space~\cite{khatib1986real}.
 Every goal $g$ is associated with a potential field $\gamma_g$ which treats $g$ as an attractor and all the other goals in the scene as repellers.
@@
 %$\gamma_g$ operates in the full six dimensional Cartesian space, and treats position and orientation as independent potential fields.
+
 \subsubsection{Blending Paradigm}\label{sssec:blending}
@@
 The blending parameter, $\alpha$ is a piecewise linear function of the $p(g^*)$.
-%and is specified as
-%$$
-%\alpha = \left\{
-%\begin{array}{ll}
-%0 & \quad\quad~~~ p(g^*) \leq \rho_1 \\
-%\frac{\rho_3}{\rho_2 - \rho_1}\cdot p(g^*) &  \quad \text{if}\quad \rho_1 < p(g^*) \leq \rho_2  \\
-%\rho_3 & \quad\quad~~~ p(g^*) > \rho_2 	
-%\end{array}
-%\right.
-%$$
-%with $\rho_i \in [0, 1] \;\forall\; i \in [1,2,3]$ and $ \rho_2 > \rho_1$. 
-%In our implementation, we empirically set $\rho_1 = \frac{1.2}{n_g}, \rho_2 = \frac{1.4}{n_g}$ and $ \rho_3 = 0.7$.
+and is specified as
+$$
+\alpha = \left\{
+\begin{array}{ll}
+0 & \quad\quad~~~ p(g^*) \leq \rho_1 \\
+\frac{\rho_3}{\rho_2 - \rho_1}\cdot p(g^*) &  \quad \text{if}\quad \rho_1 < p(g^*) \leq \rho_2  \\
+\rho_3 & \quad\quad~~~ p(g^*) > \rho_2 	
+\end{array}
+\right.
+$$
+with $\rho_i \in [0, 1] \;\forall\; i \in [1,2,3]$ and $ \rho_2 > \rho_1$. 
+In our implementation, we empirically set $\rho_1 = \frac{1.05}{n_g}, \rho_2 = \frac{1.1}{n_g}$ and $ \rho_3 = 0.7$.
 \subsubsection{Maximum Potential Mode Switch Assistance}\label{sssec:baseline}
@@
 Table~\ref{tbl:manip} lists all the factors there were manipulated for each trial.
-\begin{table}[t]
+\begin{table}[h]
 	\centering
@@
 	\label{tbl:manip}
-	\vspace{-.5cm}
 \end{table}
-\begin{table}[t]
+\begin{table}[h]
 	\centering
@@
 	\vspace{.2cm}
-	\caption{Predefined control space partition sets for each of the simulation spaces. The numbers in the control mode sets indicate the dimensions. } 
+	\caption{Predefined control space partition sets for each of the simulation spaces. The numbers in the rightmost column indicate the control dimensions. } 
 	\label{tbl:cmp}
-	\vspace{-.5cm}
 \end{table}
@@
 \subsubsection{Mode Switch Schemes}
-Four different mode switching schemes were activated during each simulation trial, three of which performed intent disambiguation and one which served as a baseline for comparison.
-The disambiguation algorithms were entropy disambiguation  metric (Section~\ref{sssec:ent}), KL divergence disambiguation metric (Section~\ref{sssec:kl}) and a heuristic approach developed in a related work~\citep{gopinath2017mode}.
+Four different mode switching schemes were activated during each simulation trial, three of which performed intent disambiguation, and one which served as a baseline for comparison.
+The disambiguation algorithms were entropy disambiguation  metric (Section~\ref{sssec:ent}), KL divergence disambiguation metric (Section~\ref{sssec:kl}) and a heuristic approach developed in a related work~\cite{gopinath2017mode}.
 We used the mode switching scheme described in Section~\ref{sssec:baseline} as the baseline for comparison.
@@
 The simulated robot autonomy $\boldsymbol{u}^{sim}_r$ is generated using a repeller-free potential field.
-For an intended goal $g^{intended}$ and a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u}^{sim}_h$ is sampled from the mode-conditioned policy, $p(\boldsymbol{u}_h\;|\;g^{intended}, m)$.
+For an intended goal $g^{intended}$ and a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u}^{sim}_h$ is sampled from the mode conditioned policy, $p(\boldsymbol{u}_h\;|\;g^{intended}, m)$.
 %\begin{equation*}
@@
 The expectation in Equations~\ref{eq:ent} and \ref{eq:kldiv} was computed by averaging over five samples.
-A \textit{dropout} factor was added to the human control command to capture the signal sparsity exhibited by humans during robot teleoperation.
-%Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
-% \added{modify the simulation parameters. Talk about projection time. }
-% \begin{figure}[h!]
-%	\centering
-%	\includegraphics[width= 0.8\hsize, height=0.28\vsize]{./figures/WS_SIM.eps}
-%	\vspace{-0.35cm}
-%	\caption{Example of point robot simulation in $\mathbb{R}^2$.
+A \textit{dropout} factor was added to the human control command to mimic the signal sparsity exhibited by humans during robot teleoperation.
+Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
+ \begin{figure}[h!]
+	\centering
+	\includegraphics[width= \hsize, height=0.25\vsize]{./figures/WS_SIM.eps}
+	\vspace{-0.35cm}
+	\caption{Example of point robot simulation in $\mathbb{R}^2$.
 The goals are represented in black, the initial robot position in red and the human's intended goal in magenta.
@@
 Greedy (Black), Entropy (Red), KL Divergence (Blue) and Heuristic (Green).}
-%	\label{fig:ws_sim}
-%\end{figure}
+	\label{fig:ws_sim}
+\end{figure}
 \begin{figure}[t!]
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.3\vsize, center]{./figures/onset_time.eps}
+	\includegraphics[width= 1.01\hsize, height=0.3\vsize, center]{./figures/onset_time.eps}
 	\vspace{-0.75cm}
@@
 The robot autonomy was generated using a potential field as described in Section~\ref{sssec:autonomy} and the control interface mapping was 1D and discrete (similar to that of a headarray).
+A total of 128 trials were collected for each task.
 % This sparsity factor captured the \textit{idle time} users have during task execution when teleoperating a robot and was randomly set between 20\% and 80\% as informed by the analysis of teleoperation data from previous experiments conducted in our lab.
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.3\vsize]{./figures/total_assistance.eps}
+	\includegraphics[width= 1.1\hsize, height=1\vsize, center]{./figures/total_assistance.eps}
 	\vspace{-0.8cm}
@@
 \end{figure}
-One way analysis of variance was performed using Kruskal-Wallis procedure to test for group effects  between the four mode switch assistance schemes: greedy (GRD), entropy (ENT), KL-Divergence (KL) and heuristic (HEU).
+One way ANOVA was performed using Kruskal-Wallis procedure to test for group effects between the four mode switch schemes: greedy (GRD), entropy (ENT), KL-Divergence (KL) and heuristic (HEU).
 Post-hoc analysis between groups was conducted using a multiple comparison test that used Tukey's HSD criterion.
@@
 	\centering
-	\includegraphics[width= 1.1\hsize, height=0.5\vsize]{./figures/correct_inference.eps}
+	\includegraphics[width= 1.1\hsize, height=0.46\vsize, center]{./figures/correct_inference.eps}
 	\vspace{-0.75cm}
@@
 The shared control paradigm used in our setup is designed in such a way that the robot assistance gets triggered when the confidence associated with the goal prediction crosses a predefined threshold.
-These results indicate that with disambiguation the system is able to maintain the confidence in its prediction of the correct goal above the threshold for a longer duration during the trial, resulting in greater overall assistance during the course of the task.
+These results indicate that with disambiguation the system is able to maintain the confidence in its prediction of the correct goal above the threshold for a longer duration during the trial, resulting in greater overall assistance during the task.
 %\subsection{Number of Mode Switches}
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.5\vsize]{./figures/mico_sim.eps}
+	\includegraphics[width= 1.\hsize, height=0.28\vsize, center]{./figures/mico_sim.eps}
 	\vspace{-0.5cm}
@@
 Accurate goal inference can improve the trust in human-robot interaction.
-On the other hand, incorrect goal inference can likely lead to frustrating user experience and often result in poor task performance.
+On the other hand, incorrect goal inference can likely lead to suboptimal user experience and result in poor task performance.
 Our results indicate that disambiguation helps to enhance the accuracy of the intent inference and leads to an increase in the overall assistance provided to the user.
-Yet another factor that is crucial for the success of a shared control system, especially for safety-critical applications, is \textit{when} during task execution the assistance gets activated.
+Another factor that is crucial for the success of a shared control system, especially for safety-critical applications, is \textit{when} during task execution the assistance gets activated.
 For example, in the shared control of complex systems that exhibit highly nonlinear and unstable dynamics typically the role of autonomy is to maintain stability and safety.
@@
 
-Disambiguation algorithms can benefit from high fidelity models of robot kinematics and user teleoperation that can be learned from data using machine learning techniques such as deep neural networks~\citep{nagabandi2017neural}.
+Disambiguation algorithms can benefit from high fidelity models of robot kinematics and user teleoperation that can be learned from data using machine learning techniques such as deep neural networks.
 Furthermore, parallel computation on GPU can also be leveraged for more accurate estimation of the expectation in Equations~\ref{eq:ent} and \ref{eq:kldiv}.
@@
 \section{Conclusion}\label{sec:conclusions}
-In this paper, we formalized the problem of intent disambiguation within the framework of information theory.
-We introduced two different methods for intent disambiguation using the information theoretic concepts of entropy and KL divergence.
+ In this paper, we proposed a mode selection
+paradigm that enhances the autonomy’s intent inference capabilities by exploiting the fact that how the human operates the robot is intrinsically conditioned on
+the control mode in operation.
+We introduced two different methods for intent disambiguation using the information-theoretic concepts of entropy and KL divergence.
 We also present results from an extensive simulation-based study for point robots and a physics-based simulation of a robotic arm.
@@
 
-\section*{Acknowledgments}
-Funding source omitted for review. 
-%% Use plainnat to work nicely with natbib. 
+%\section*{Acknowledgments}
+%Funding source omitted for review.
+
 \balance	
-\bibliographystyle{plainnat}
+\bibliographystyle{IEEEtran}
 \bibliography{references}

### 2019-05-31 TexStuff/IROS_2019_propertex_file_resubmit/RAL_Reviews/information_on_response_to_reviewers/paper_review_response_template/reviewresponse_example.tex
RAL resubmit

% Copyright Javier Sánchez-Monedero.
% Please report bugs and suggestions to (jsanchezm at uco.es)
%
% This document is released under a Creative Commons Licence 
% CC-BY-SA (http://creativecommons.org/licenses/by-sa/3.0/) 
%
% BASIC INSTRUCTIONS: 
% 1. Load and set up proper language packages
% 2. Complete the paper data commands
% 3. Use commands \rcomment and \newtext as shown in the example

\documentclass[a4paper,twoside,11pt]{reviewresponse}

% 1. Load and set up proper language packages
%\usepackage[utf8x]{inputenc}
\usepackage[latin9]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}  % assumes amsmath package installed

% 2. Complete the paper data
\newcommand{\myAuthors}{{Deepak E. Gopinath$^{\displaystyle 1, 3}$, ~Brenna D. Argall$^{\displaystyle 1,2,3}$, }}
\newcommand{\myAuthorsShort}{John.~Doe et. al}
\newcommand{\myEmail}{deepak.gopinath@u.northwestern.edu}
\newcommand{\myTitle}{Information-Theoretic Characterization of Control Modes for Intent Disambiguation - Response to Reviewers}
\newcommand{\myShortTitle}{Response to reviewers}
\newcommand{\myJournal}{IEEE Robotics And Automation Letters (RA-L)}
\newcommand{\myDept}{{$^{\displaystyle 1}$Department of Mechanical Engineering, Northwestern University, Evanston, IL}\\
{$^{\displaystyle 2}$ Departments of Computer Science and Physical Medicine and Rehabilitation, Northwestern University, Evanston, IL  }\\
{$^{\displaystyle 3}$ Shirley Ryan AbilityLab, Chicago, IL }\\}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage[linktoc=all]{hyperref}
\usepackage[linktoc=all,bookmarks,bookmarksopen=true,bookmarksnumbered=true]{hyperref}

\hypersetup{
pdfauthor = {\myAuthorsShort},
pdftitle = {\myTitle},
pdfsubject = {\myJournal\xspace},
colorlinks = true,
linkcolor=black!70!green,          % color of internal links
citecolor=black!70!green,        % color of links to bibliography
filecolor=magenta,      % color of file links
urlcolor=black!70!green           % color of external links
}

\begin{document}

\thispagestyle{plain}

\begin{center}
 {\LARGE\myTitle} \vspace{1cm} \\
 {\large\myJournal} \vspace{0.5cm} \\
 \today \vspace{0.5cm} \\
 \myAuthors \\
 \url{\myEmail} \vspace{1cm} \\
 \myDept
\end{center}

%\tableofcontents

%\begin{abstract}
We sincerely thank the reviewers for their valuable efforts and feedback. We have made every effort to address all the major points raised by the reviewers and have modified the manuscript accordingly. For added ease of reading, we are also submitting a version of the revised manuscript in which the modifications are highlighted in orange color. Detailed responses to the comments follow.  
%\end{abstract}

\section{Reviewer 3}

\rcomment{- I think it is better to define certain terms such as "belief over
	goals" and "intention disambiguation/inference" in the introduction.}

We thank the reviewer for this comment and have modified the text to make the meaning of intent disambiguation and inference more clear to the reader.

\rcomment{As I understand Algorithm 1 explains how intentions are obtained,however it does not explain how this intentions are embedded in the
	robot assistive controller. }

If we are correctly interpreting the reviewer's comment, we believe 
there is a point of misinterpretation here: Algorithm 1 in fact is about 
computing the disambiguation mode, which is different from predicting 
the intent itself (if that is what the reviewer meant by "how intentions 
are obtained"). This distinction is indeed a potential point of 
confusion, and we have included a new figure (Figure 1) that explicitly 
calls out these various components as well as clarifying text throughout 
the document.

%
%We apologize the confusion that arose to the reviewer, but we would like to point that computing the disambiguation mode is different from predicting the intent itself. Algorithm 1 is about characterizing intent disambiguation capabilities of each control mode. 
%
%We would like to emphasize that the robot assistance, intent inference and intent disambiguation all are working in tandem as the human (simulated) interacts with the robot. In order to bring this point across, we have added a new figure which depicts how the different components interact with each other. We sincerely hope that this will clarify how the output of Algorithm 1 is integrated within the robot assistance system.

\rcomment{Simulation methods are not described with sufficient details. It is
	hard to reproduce this. Could you add equations for human and robot
	control behaviour ($u_h$ and $u_r$)? Adding detailed equations and
	parameters to Appendix and supplementary material will be helpful.}

Tables I and II now provide all simulation parameters and their ranges. 
The specification of $u_h$ is given in Equation 7, and $u_r$ in Section 
V.A.1. (RA-L does not allow Appendix and supplementary material, we 
therefore were unable to submit those.)

%We have made every attempt to make the simulation details clear. Tables I and II provides all the simulation parameters and their ranges. We had already specified how $u_h$ (Equation 7) and $u_r$ were generated (Section V.A.1). We have modified Section V.B.3 to back reference Equation 7 and V.A.1. RA-L does not allow Appendix and supplementary material and therefore we won't be able to submit those.

\rcomment{
	- I am not sure if it is valid to do statistical analysis of simulated
	data? }

We would like to respectfully argue that statistical analyses of 
simulated data is indeed valid (and happens often within the field of 
robotics). The goal with our simulation was to be able to control for 
various confounding factors that can potentially arise in real human subjects studies (such as fatigue, lack of attention etc.) and perform a more 
extensive evaluation (8000 trials for each metric space) than could ever be possible on real 
hardware and with real subjects. We do not believe that this replaces hardware evaluation, but 
rather that it complements it. In this work we chose to do the more 
exhaustive simulation evaluation first.

%
%We would like to respectfully disagree with the reviewer on this point. The goal with our simulation is to be able to control for various confounding factors and be able to randomize them properly so that the analysis can focus on the factor of interest, which in our case is efficacy of our intent disambiguation algorithms. Simulated data serve as a proxy/an approximation of what real data might look like. for example, this is similar to how modern deep learning techniques use data augmentation methods to create `synthetic data' to train their systems which can then be deployed in real scenarios. Training on simulated data does not invalidate the models learned but only improves their performance in the real world. 
\clearpage

\section{Reviewer 4}

\rcomment{One unclear issue is the presence of Dynamic Neural Field (DNF)
	approaches. Because the KL and Entropy algorithm utilizes the intent
	inference algorithms of heuristic, Bayesian, and dynamic neural field
	approaches. The other two algorithms were applied in this paper, but
	the usage of the DNS approach is not explicitly written.}

We apologize for this confusion. For the simulations we indeed utilized all three approaches (heuristic, Bayesian and DNF). Table I, Row 3 indicates the different intent inference approaches utilized in the simulations.

\rcomment{, most of terms are salient but I suggest changing
	one of those terms to improve the readability. }

We thank the reviewer for this valuable suggestion and have modified the terms used for describing the different metrics accordingly for improved readability throughout the paper as well as in the figures. `Total Amount of Assistance' has been changed to `Temporal Ratio of Assistance'.

\rcomment{ unclear selection of test
	condition in the second experiment... KL and ENT should be compared to
	GRD or ENT should be compared to GRD at least because it showed better
	performance...}

We agree with the reviewer that a full comprehensive experiment would need to compare both ENT and KLD against GRD condition. As the reviewer rightly spotted, this paper is an extension to our earlier paper [21] which just relied on hand-crafted heuristic features to perform intent disambiguation. 
Our goal was to identify at least one 
information-theoretic approach that was better than the heuristic 
approach (if one existed). That KLD-based intent disambiguation system 
was found to be more effective than the GRD condition validated the use 
of information theoretic approaches for intent disambiguation. Having 
validated the promise of the information-theorectic approaches, we are 
now in the process of preparing a full-fledged human subject study in 
which one of the conditions indeed will be to test both ENT and KLD 
against the GRD.

%Our goal was to identify at least one information-theoretic approach than could possibly be better than the heuristic approach. We are in the process of extending the current study into a full fledged human subject study in which we will be testing both ENT and KLD against the GRD. We were however, unable to finish the experiment in time for the submission deadline.

%We would still like to point out that the KLD-based intent disambiguation system was still more effective than the GRD condition thereby marking an improvement over a heuristic based approach and validates the use of information theoretic approaches for intent disambiguation.

%We would also like to emphasize that the major difference between the point robot simulations and the robotic arm simulation setup is the nonlinear kinematics. The robot autonomy was still generated using the potential field approach.

\clearpage
\section{Reviewer 9}

\rcomment{It seems that the approach is specialised for a specific task, i.e. for
	a reaching task where goals are discrete. The authors claim that this
	type of task is the most common which seems to be an overstatement.}

We sincerely believe that this is not an overstatement, given the 
capabilities of today's assistive robotic arms. In the domain of assistive robotic manipulations,  robotic arms are typically used by motor-impaired subjects for performance activities of daily living (ADL) tasks. Various types of ADL tasks such feeding, picking up objects from shelves, tabletops and the ground, reaching for doorknobs all involve reaching toward objects in the world. We have added text to the introduction where we clarify this point. Numerous videos of use-cases (available online) in which motor impaired people use robotic arms in their daily lives will further illustrate our point.

\rcomment{There are many tasks in robot assistance or HRI that may benefit from
	assistance, e.g. obstacle avoidance, trajectory tracking, force
	tracking, etc. The authors are encouraged to discuss how does the
	proposed approach generalise to these tasks.
}

We thank the reviewer for this suggestion and accordingly we have added some text in the discussion section addressing how generalizable our algorithm is. We make further reference to the generalizability in the introduction section where we state that intent inference is crucial for the success for many shared-autonomy human machine systems. Any human-robot system that has an intent inference mechanism under-the-hood can potentially utilize our intent disambiguation algorithm with respect to relevant parameters that affect intent inference (control modes, in our specific example) to enhance the efficacy of the inference mechanism.
\rcomment{
	Related work rather lists some scarce examples instead of being a
	structured summation of the most important works related to this paper.
	There are many approaches for intent inference found in the literature,
	see the works of e.g. Anca Dragan. Also, the related work should be
	linked to the present work in a meaningful way. }

We thank the reviewer for this suggestion and have accordingly made our related work section more comprehensive. We hope this modification will help the reader to make the connection between past work and the work presented in the paper more clear as well.

\rcomment{It is unnecessary to devote the whole section to mathematical notation.
	It should only be a paragraph in the introduction. It is highly
	advisable to rather give a problem setting, with accompanying figure of
	the task considered where the notation is usefully presented}

We have taken this suggestion into account and have accordingly deleted the section devoted to mathematical notation. The content has been integrated with the new Section IV. 
\rcomment{Please list all the assumptions you impose on the problem in one place,
	e.g. that the human doesn't change the goal, that at any given time
	only one control mode can be activated, etc. Mentioning assumptions "on
	the fly" is not suitable.}

We thank the reviewer for the comment, but we have respectfully chosen not to change the way we present the math. We believe that it is important to start with the most general form of 
the equations and to introduce simplifications based on different 
assumptions as the problem specification becomes less general. In our 
experience such an approach helps the reader to better follow the 
progression of ideas and makes clear the simplifications.

\rcomment{Can you explain what would happen with the proposed approach if there
	is an obstacle to a goal?}

This is an important observation by the reviewer. An obstacle to a goal can indeed cause 'unintuitive changes' to the direct path to a goal. However, we would like to emphasize that, how well the autonomy is able to reason about these kinds of changes in motion direction depends on the features (directedness, proximity, agreement etc) used by the \textbf{intent inference} module. That ability of the intent disambiguation system to disambiguate intent is only as effective as the underlying intent inference mechanism. This is because, during the forward projection of beliefs (Line 7 in Algorithm 1), the BeliefUpdate() utilizes the same inference algorithm that is active during task execution. If the choice of intent inference algorithm ignores the presence of obstacles (probably not the best choice!), intent disambiguation will not be able to reason about the presence of obstacles.

One can think of the intent disambiguation as an add-on module to whichever intent inference scheme is used, such that the disambiguation system is able to rank order the (discrete) parameters on which the inference depends on according to their ability to extract information that will help to enhance inference accuracy.

%his is an interesting question and we would like to point out that the `intent disambiguation' algorithm is designed to improve the accuracy of the intent inference module. The robot autonomy is generated from a policy that is \textbf{independent} of the intent disambiguation algorithm. In our case, we utilize a potential field based approach to generate robot autonomy signals. The potential field generator utilizes the intent inference module's prediction of what the current goal and treats the predicted goal as the sole `attractor in the world'. All the other objects in the world are then treated as obstacles and therefore will have associated repeller fields. We have modified Section V.A.1 to include this information and we hope this would clarify this point.

\rcomment{..Where are the results for the dynamic neural field approach?  A
	multitude of different approaches is proposed which is exceptionally
	confusing and it is very hard to follow what is relevant in this paper.
	Or to rephrase, how disambiguation, inference, and assistance concepts
	participate in the evaluation..?}

We have cited one of our other works which does a qualitative comparison of dynamic neural field approach to other standard approaches for intent inference.

The reason why we have used a multitude of approaches for each 
component of the overall system was to more rigorously evaluate the 
robustness of our proposed intent disambiguation approach---by 
demonstrating that its effectiveness was not contingent on a particular 
choice of intent inference algorithm, shared control algorithm or 
disambiguation metric. We hope that Figure 1 helps to clarify how all of 
the different components interact with each other.

% We would like to argue that the reason why we have used a multitude of approaches for each component of the overall system is that, in simulation we wanted to ensure the robustness of our proposed intent disambiguation approach to the choice of different algorithms for other components of the system. We would like to point out that the intent inference, intent disambiguation and shared control assistance are all working in tandem as the human interacts with the robot. This is exemplified in the Figure 1, that depicts how the different components work together. We hope this clarifies how all the different components `participate in the evaluation'.

\rcomment{..The simulation environment, task, and the complete evaluation setup
	need to be thoroughly explained. Since the actual user study is
	missing, it is very important to describe in detail (with equations)
	how is the human simulated.}

\textbf{Response}

Thank you for the suggestion. We have described the simulation 
environment in greater detail, and hope that the modifications in the 
current version make the simulation setup more comprehensible to the 
reader. In particular, Section V.B.3 describes how the human actions are simulated. Further details of how the simulations were conducted are also described in Section V.B.5 and in simulation parameters and their ranges are presented were also presented in Tables I and II. Furthermore, we are also making the point robot simulation code open source and is now available on GitHub. The paper contains the link to the repo as well.

\end{document}

### 2019-05-31 TexStuff/IROS_2019_propertex_file_resubmit/GopinathArgall_IROS2019_Disamb_Resubmit.tex
RAL resubmit

--- 2019-02-27 TexStuff/IROS_2019_propertex_file/GopinathArgall_IROS2019_Disamb.tex
@@
 \usepackage{amssymb}
+%\usepackage{xcolor}
+\usepackage[xcolor=yellow]{changes}
+\colorlet{Changes@Color}{orange}
 \usepackage{graphicx}
@@
 \thanks{$^{2}$Brenna D.
-Argall is with the Department of Mechanical Engineering, Department of Electrical Engineering and Computer Science, Northwestern University, Evanston, IL, Department of Physical Medicine and Rehabilitation, Northwestern University, Chicago, IL and Shirley Ryan AbilityLab, Chicago, IL.
+Argall is with the Departments of Mechanical Engineering ,Computer Science, Physical Medicine and Rehabilitation, Northwestern University, Chicago, IL and Shirley Ryan AbilityLab, Chicago, IL.
         {\tt\small brenna.argall@northwestern.edu}}%
@@
 We formulate this as a problem of intent disambiguation in information-theoretic terms.
-We propose two different methods for enhancing intent inference via improved disambiguation using the information-theoretic concepts of \textit{entropy} and \textit{KL divergence}.
+We propose two different methods for enhancing intent inference via improved disambiguation using the information-theoretic concepts of \textit{entropy} and \added{\textit{Kullback-Leibler} (KL) divergence}.
 In our system, the autonomy maintains a probability distribution over goals (beliefs) and we characterize the disambiguation capabilities of the different control modes/dimensions utilizing a model-based approach to compute the average information gain and content.
@@
 
-An assistive robotic machine is typically controlled using an interface such as a joystick, a switch-based head array or a sip-and-puff.
+An assistive robotic machine is typically controlled using an interface such as a joystick, a switch-based head array\footnote{\added{Adaptive Switch Laboratories:} \url{http://www.asl-inc.com}} or a sip-and-puff\footnote{\added{Therafin Corporation} \url{ http://www.therafin.com}}.
 These interfaces are low-dimensional, low-bandwidth and occasionally discrete.
@@
 To schedule and execute switches between control modes can be both mentally and physically demanding, and might be alleviated in part by the introduction of robotics autonomy.
-The efficacy of such autonomy-endowed machines relies on their ability to infer the users' needs and intentions, which is often a bottleneck for providing appropriate assistance accurately, confidently and quickly.
-Due to the dimensionality mismatch between high-dimensional robots and low-dimensional interfaces, the user is constrained to produce control commands that likely do not express their true underlying intent unambiguously.
+\added{The ability of such autonomy-endowed machines to infer the users' needs and intentions, also known as \textit{intent inference,} is often a bottleneck for providing appropriate assistance accurately, confidently and quickly.} Due to the dimensionality mismatch between high-dimensional robots and low-dimensional interfaces, the user is constrained to produce control commands that likely do not express their true underlying intent unambiguously.
 That is, the control interfaces act like filters that restrict the amount of information regarding the user's intent that is passed through to the autonomy.
@@
 
-In the context of assistive robotic manipulation, the first step of a task is often to \textit{reach} towards discrete objects in the environment.
-Therefore in this domain, \textit{intent inference} can be cast as a problem of maintaining and updating the probability distributions over all possible discrete goals (objects) in the workspace upon receiving fresh evidence from the human actions and environment.
+In the context of \added{performing activities of daily living using assistive robotic manipulators}, the first step of a task is often to \textit{reach} towards discrete objects in the environment, \added{for example, picking up food, reaching for door knobs, tabletop manipulation \textit{et cetera}}\footnote{\url{https://www.youtube.com/watch?v=r3yWmf8blz0}}.
+Therefore in this domain, \textit{intent inference} can be cast as a problem of maintaining and updating the probability distributions over all possible goals (\added{also known as \textit{belief}}) in the workspace upon receiving fresh evidence from the human actions and environment.
 In Bayesian terminology, maintaining and updating the belief is the \textit{recursive Bayesian filtering} problem.
 Intent inference algorithms typically rely on various task-relevant features such as the robot and goal positions, human control commands and biometric measures~\cite{croft2003estimating} as their evidence variables.
-In contrast, due to reasons of user adoption and cost, our system matches the interfaces available on typical commercial assistive machines (such as powered wheelchairs) and so infers intent exclusively based on the information contained in the constrained control commands issued to the assistive machine.
+However, due to reasons of user adoption and cost, our system matches the interfaces available on typical commercial assistive machines (such as powered wheelchairs) and so infers intent exclusively based on the information contained in the constrained control commands issued to the assistive machine.
 
-Our system is inspired by the following insights:
+Our system is inspired by the following \added{observations}:
 \begin{itemize}
-	\item At any given time, the user is constrained to operate the robot in a specific control mode.
-That is, the policy followed by the human while executing the reaching task is conditioned on the current active mode.
-	\item The posterior computation of the belief over goals depends on the human policy which indirectly depends on the active control mode. 
-	\item Utilizing a model-based approach to project the beliefs over goals forward in time, the autonomy can \textit{counterfactually } reason about the information gain and content for different control modes.
-	\item Using this information-theoretic characterization of control modes, the autonomy chooses the control mode with the highest intent disambiguation capability \textit{for} the human.
+	\item \added{At any given time, the policy followed by the human while controlling the robotic arm is conditioned on the current active mode.
+As a result, the belief update that depends on the human policy implicitly depends on the active control mode.
+}
+	\item Utilizing a model-based approach to project the beliefs over goals forward in time, the autonomy can \textit{counterfactually} reason about the information gain and content for different control modes.
+	\item Using this information-theoretic characterization of control modes, the autonomy can choose the control mode with the highest intent disambiguation capability \textit{for} the human.
 	\item Having the human provide control input within these information-rich control modes can likely improve the accuracy of intent inference.
@@
 
+We formalize this as a problem of intent disambiguation within the framework of information theory.
 In this paper, we address how to enhance the accuracy of intent inference by characterizing control modes according to their information content and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent.
-We formalize the problem of intent disambiguation within the framework of information theory.
 Specifically, we make use of the information-theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the information content---with respect to intent disambiguation---of each control mode.
@@
 In Section~\ref{sec:related_work} we present an overview of relevant research.
-Section~\ref{sec:math} introduces our set theoretic treatment of control modes, followed by intent disambiguation and intent inference in Sections~\ref{sec:disamb} and \ref{sec:inference} respectively.
+Sections~\ref{sec:disamb} and \ref{sec:inference} introduces our set theoretic treatment of control modes, followed by intent disambiguation and intent inference respectively.
 The study design and experimental methods are discussed in Section~\ref{sec:ed} followed, by results in Section~\ref{sec:results}.
@@
 The model can either be learned from data or can be hand-designed based on domain knowledge.
-For example, the human can be modeled within the Partially Observable Markov Decision Process (POMDP)~\cite{taha2011pomdp} framework and is assumed to behave according to a control policy that maps states to actions.
-However, in model-based approaches incorporating the entire history of states requires estimation of joint probability distributions over past states which can become computationally expensive and intractable quickly.
+\added{For example, the human can be modeled as a rational agent within a Partially Observable Markov Decision Process (POMDP) such that the uncertainty is over user's goal~\cite{taha2011pomdp} framework.
+The autonomy can then use these models to either take a \textit{predict-then-act}~\cite{dragan2013policy} approach or generate robot control commands that will \textit{minimize the expected user cost}~\cite{javdani2015shared} so that assistance is effective even in cases where the goal uncertainty is very high.
+The intent disambiguation algorithm presented in this paper can be stacked on top of any parametric intent inference scheme as a mechanism to further improve the accuracy of the inference scheme}.
 
@@
 
-\section{Mathematical Notation}\label{sec:math}
-This section describes the mathematical notation used in our intent disambiguation algorithm that computes a control mode that maximally disambiguates between the various goals.
-We develop this algorithm specifically for robotic manipulation scenarios in which the user is controlling a robotic arm to reach for and interact with various discrete objects in the environment.
-
-% Section~\ref{ssec:notation} outlines the mathematical notation used in this paper.
+%%\section{Mathematical Notation}\label{sec:math}
+%%This section describes the mathematical notation used in our intent disambiguation algorithm that computes a control mode that maximally disambiguates between the various goals.
+%%We develop this algorithm specifically for robotic manipulation scenarios in which the user is controlling a robotic arm to reach for and interact with various discrete objects in the environment.
+%%
+%%% Section~\ref{ssec:notation} outlines the mathematical notation used in this paper.
 Section~\ref{ssec:set_modes} presents a set-theoretic treatment of control modes and Section~\ref{ssec:disamb} describes the disambiguation algorithm.
 The mathematical details of the intent inference paradigms are outlined in detail in Section~\ref{ssec:inference}.
-\subsection{Probability Distribution Over Goals}\label{ssec:notation}
-In assistive robotic manipulation, intent inference is most commonly the process of estimating the user's intended goal out of a set of discrete objects in the environment~\cite{calli2015ycb}.
+%%\subsection{Probability Distribution Over Goals}\label{ssec:notation}
+%%In assistive robotic manipulation, intent inference is most commonly the process of estimating the user's intended goal out of a set of discrete objects in the environment~\cite{calli2015ycb}.
 The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$.
-% and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$. 
-% At any time $t$, the likelihood of goal $g$ being the desired goal follows a categorical probability distribution whose sample space is $\mathcal{G}$. 
-% That is, 
-% \begin{equation*}
-% g \sim \textbf{Cat}(n_g | \boldsymbol{p}(t)) = \prod_{i=1}^{n_g}p^{i}(t)^{[g = g^i]}
-% \end{equation*}
-%where, $[g = g^i]$ is the Iverson bracket and evaluates to 1 if $g = g^i$, 0 otherwise. 
-At time $t$ the random variable $g^t \in \mathcal{G}$ denotes the user's intended goal and $b_{g^t}$ denotes the belief over the goals. 
-% The probability $b_{g^t}$  also represents the robot's \textit{confidence} that goal $g$ is the human's intended goal at time $t$. 
-%$\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p_{g_1}^t, p_{g_2}^t,\dots, p_{g_{n_g}}^t)]^{T}$ where $p_{g_i}^t$ denotes the probability associated with goal $g_i$ at time $t$.
+%%% and let $g^i$ refer to the $i^{th}$ goal with $i \in [1,2,\dots, n_g]$. 
+%%% At any time $t$, the likelihood of goal $g$ being the desired goal follows a categorical probability distribution whose sample space is $\mathcal{G}$. 
+%%% That is, 
+%%% \begin{equation*}
+%%% g \sim \textbf{Cat}(n_g | \boldsymbol{p}(t)) = \prod_{i=1}^{n_g}p^{i}(t)^{[g = g^i]}
+%%% \end{equation*}
+%%%where, $[g = g^i]$ is the Iverson bracket and evaluates to 1 if $g = g^i$, 0 otherwise. 
+%%At time $t$ the random variable $g^t \in \mathcal{G}$ denotes the user's intended goal and $b_{g^t}$ denotes the belief over the goals. 
+%%% The probability $b_{g^t}$  also represents the robot's \textit{confidence} that goal $g$ is the human's intended goal at time $t$. 
+%%%$\boldsymbol{p}(t)$ denotes the probability distribution over goals such that $\boldsymbol{p}(t) = [p_{g_1}^t, p_{g_2}^t,\dots, p_{g_{n_g}}^t)]^{T}$ where $p_{g_i}^t$ denotes the probability associated with goal $g_i$ at time $t$.
+%%
+%%\subsection{Set Theoretic Treatment of Control Modes}\label{ssec:set_modes}
+%%%
+%%%The limitations of the control interfaces necessitate the control space $\mathcal{K}$ to be partitioned into control modes.
+Let $\mathcal{M}$ denote the set of all control modes with $n_m = \vert\mathcal{M}\vert$.
+Additionally, let $m^i$ refer to the $i^{th}$ control mode where $i \in [1,2,\dots,n_m]$.
+Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i$ spans all of the controllable dimensions.\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes.} Let $\boldsymbol{e}^i$ be the standard basis vectors that denote the unit velocity vector along the $i^{th}$ control dimension.\footnote{For the rotational control dimensions, the velocity is specified with respect to the end-effector of the robotic frame.} Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+Therefore, the user can only access smaller subsets of $\mathbb{R}^{n_k}$ via the control interface with $\mathcal{U}_{m^i}$ denoting the subset of $\mathbb{R}^{n_k}$ accessible from control mode $m^i$.
+Figure 1 represents this in a pictorial fashion for a robot residing in $\mathbb{R}^2$.
+%%The low dimensionality of the control interfaces necessitates the control space to be partitioned into control modes.
+%%Let $\mathcal{K}$ be the set of all controllable dimensions of the robot and $k^i$ represent the $i^{th}$ control dimension where $i \in [1,2,\dots,n_k]$ with $n_k = \vert\mathcal{K}\vert$.
+The number of controllable dimensions ($n_k$) depends on the robotic platform; for example, a 2D point robot that operates in $\mathbb{R}^2$ has $n_k = 2$ whereas $n_k =6$ for a 6-DoF robotic manipulator.
+%%%Lastly, let $\boldsymbol{u_h} \in \mathbb{R}^{n_k}$ denotes the human control command issued via the control interface and $\boldsymbol{u_r} \in \mathbb{R}^{n_k}$ denote the robot autonomy command.
+%%
+%%Let $\mathcal{M}$ denote the set of all control modes with $n_m = \vert\mathcal{M}\vert$.
+Additionally, let $m^i$ refer to the $i^{th}$ control mode where $i \in [1,2,\dots,n_m]$.
+Each control mode $m^i$ is a subset of $\mathcal{K}$ such that $\bigcup\limits_{i=1}^{n_m} m^i = \mathcal{K}$.
+The cardinality of each mode $m \in \mathcal{M}$, denoted by $\vert m \vert$, indicates the number of dimensions that can be controlled when operating in $m$\footnote{Note that a dimension $k \in \mathcal{K}$ can be an element of multiple control modes and so it is possible that $m^i \cap m^j \neq \emptyset$.}.
+Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
+That is, for each $m \in \mathcal{M}$, the subspace of $\mathbb{R}^{n_k}$ that is accessible corresponds to $\mathbb{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
+Maximum velocity limits along each dimension impose further constraints on the set of control commands that are available in each mode.
+%%% This constrained set of control commands available in mode $m$, denoted by $\mathcal{U}^m$, can be written as 
+%%%\begin{equation*}
+%%%\mathcal{U}^m = \{\boldsymbol{u} | \boldsymbol{u} \in \mathcal{R}^{\vert m \vert} ~ and ~ \norm{\boldsymbol{u}}_{\infty} \leq v_{lim} \} 
+%%%\end{equation*}
+%%%where $v_{lim}$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm. 
+%%%Therefore, the set $\mathcal{U}^m$ corresponds to a hypercube of dimensionality $\vert m \vert$ embedded in $\mathcal{R}^{n_k}$.
+In other words $\mathcal{U}^m$ is a $\vert m \vert$-cube with edge length equals $2c$.
+Without loss of generality, the velocity limits can be different for different control dimensions in which case $\mathcal{U}^m$ will correspond to a hypercuboid.
+Figure 1 represents this in a pictorial fashion for $\mathbb{R}^2$.
+%%% \begin{figure}[h]
+%%%	\centering
+%%%	\includegraphics[width= 0.8\hsize, height=0.2\vsize]{./figures/R2_ControlModes.eps}
+%%%	\vspace{-0.35cm}
+%%%	\caption{Illustration of 1D and 2D control modes in a two-dimensional control space, $\mathbb{R}^2$.
+Note that this space can be embedded in a higher dimensional space such as $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
+The 1D control modes are shown in blue and orange and the 2D control mode is shown as the green shaded area within the red square.
+The vertex set denotes the maximum magnitude control commands that can be issued when operating in a control mode.
+}
+%%%	\label{fig:r2_modes}
+%%%\end{figure}
+%%
+%%% The disambiguation formalism developed in Section~\ref{ssec:disamb} is agnostic to the particular form of intent inference.
+However, the algorithm assumes that $\boldsymbol{p}(t)$ can be forward projected in time by iteratively applying the intent inference algorithm.
+
+\section{Intent Disambiguation}\label{sec:disamb}
+\added{This section introduces a set-theoretic treatment of control modes and how our autonomy reasons about the intent disambiguation capabilities of different control modes by computing the information gain and content of the belief over goals.} We utilize a model-based approach in which the human is modeled as a rational agent that seeks to take the shortest distance path to the goal.
+We also describe the various intent inference schemes that we utilize in our experiments, which work in conjunction with our disambiguation algorithm.
+
+%This section describes our two proposed approaches for intent disambiguation using information theoretic concepts and the different intent inference schemes that work in conjunction with the disambiguation algorithm.
 
@@
 Furthermore, the user can only operate in one of the $n_m$ control modes at any given time $t$.
-That is, for each $m \in \mathcal{M}$, the subspace of $\mathbb{R}^{n_k}$ that is accessible corresponds to $\mathbb{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$.
-Maximum velocity limits along each dimension impose further constraints on the set of control commands that are available in each mode.
-% This constrained set of control commands available in mode $m$, denoted by $\mathcal{U}^m$, can be written as 
-%\begin{equation*}
-%\mathcal{U}^m = \{\boldsymbol{u} | \boldsymbol{u} \in \mathcal{R}^{\vert m \vert} ~ and ~ \norm{\boldsymbol{u}}_{\infty} \leq v_{lim} \} 
-%\end{equation*}
-%where $v_{lim}$ denotes the maximum velocity along any dimension $k$ and $\norm{\cdot}_{\infty}$ denotes the $L_\infty$ norm. 
-%Therefore, the set $\mathcal{U}^m$ corresponds to a hypercube of dimensionality $\vert m \vert$ embedded in $\mathcal{R}^{n_k}$.
-In other words $\mathcal{U}^m$ is a $\vert m \vert$-cube with edge length equals $2c$.
-Without loss of generality, the velocity limits can be different for different control dimensions in which case $\mathcal{U}^m$ will correspond to a hypercuboid.
-Figure 1 represents this in a pictorial fashion for $\mathbb{R}^2$.
-% \begin{figure}[h]
-%	\centering
-%	\includegraphics[width= 0.8\hsize, height=0.2\vsize]{./figures/R2_ControlModes.eps}
-%	\vspace{-0.35cm}
-%	\caption{Illustration of 1D and 2D control modes in a two-dimensional control space, $\mathbb{R}^2$.
-Note that this space can be embedded in a higher dimensional space such as $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
-The 1D control modes are shown in blue and orange and the 2D control mode is shown as the green shaded area within the red square.
-The vertex set denotes the maximum magnitude control commands that can be issued when operating in a control mode.
-}
-%	\label{fig:r2_modes}
-%\end{figure}
-
-% The disambiguation formalism developed in Section~\ref{ssec:disamb} is agnostic to the particular form of intent inference.
-However, the algorithm assumes that $\boldsymbol{p}(t)$ can be forward projected in time by iteratively applying the intent inference algorithm.
-\section{Intent Disambiguation}\label{sec:disamb}
-This section describes how our autonomy reasons about the intent disambiguation capabilities of different control modes by computing the information gain and content of the belief over goals.
-We utilize a model-based approach in which the human is modeled as a rational agent that seeks to take the shortest distance path to the goal.
-We also describe the various intent inference schemes that we utilize in our experiments, which work in conjunction with our disambiguation algorithm.
-
-%This section describes our two proposed approaches for intent disambiguation using information theoretic concepts and the different intent inference schemes that work in conjunction with the disambiguation algorithm.
-
+That is, for each $m \in \mathcal{M}$, the subspace of $\mathbb{R}^{n_k}$ that is accessible corresponds to $\mathbb{R}^{\vert m \vert}$ whose orthonormal basis vectors are given by $\boldsymbol{e}^k \;\; \forall \;\; k \in m$  \footnote{\added{Table~\ref{tbl:cmp} presents some examples for control space partitions.}}.
+%Maximum velocity limits along each dimension impose further constraints on the set of control commands that are available in each mode. 
 \subsection{Conditional Recursive Bayesian Belief Update}
 
-In this subsection we show how the recursive Bayesian update of the probability distribution over goals is explicitly conditioned on the current active control mode and therefore can be leveraged to reason about disambiguation.
+In this subsection we show how the recursive Bayesian belief update is explicitly conditioned on the current active control mode and therefore can be leveraged to reason about disambiguation.
 %the disambiguation capabilities.
 
+In assistive robotic manipulation, intent inference is most commonly the process of estimating the user's intended goal out of a set of discrete objects in the environment~\cite{calli2015ycb}.
+The set of all candidate goals is denoted by $\mathcal{G}$ with $n_g = \vert\mathcal{G}\vert$.
+At time $t$ the random variable $g^t \in \mathcal{G}$ denotes the user's intended goal and $b_{g^t}$ denotes the belief over the goals. 
 %We treat the unknown goal $g$ as a random variable and  maintain a belief over the goals denoted as $b^t_g$. 
@@
 \end{equation}
-Assuming that $(\boldsymbol{u}_h^t \perp \boldsymbol{u}_h^{0:t-1} | g^t)$ (Markovian assumption that the control command at the current timestep is independent of previous timesteps given the current goal)and marginalizing over $g^{t-1}$, Equation~\ref{eq:belief1} becomes
+Assuming that $(\boldsymbol{u}_h^t \perp \boldsymbol{u}_h^{0:t-1} | g^t)$ (Markovian assumption that the control command at the current timestep is independent of previous timesteps given the current goal) and marginalizing over $g^{t-1}$, Equation~\ref{eq:belief1} becomes
 \begin{equation}\label{eq:belief2}
@@
 
+\begin{algorithm}[h]
+	\caption{Information-Theoretic Intent Disambiguation}
+	\label{alg:disamb}
+	\begin{algorithmic}[1]
+		\REQUIRE $b_{g^{t_a}}, \boldsymbol{x}_r^{t_a}, \Delta t, t_a < t_b$
+		\FOR{$m \in \mathcal{M}$}
+		\STATE Initialize $D_m = 0$
+		\FOR{$g \in \mathcal{G}$}
+
+		\STATE Initialize $t = t_a + \Delta t, \boldsymbol{x}_r^{t - \Delta t} = \boldsymbol{x}_r^{t_a}, b_{g^{t - \Delta t}} = b_{g^{t_a}}$
+		\WHILE{$t \leq t_b$}
+		\STATE $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\; g, m)$ 
+		\STATE $b_{g^{t}} \leftarrow \text{BeliefUpdate}(b_{g^{t-\Delta t}}, \boldsymbol{u}_h^t)$
+		\STATE $\boldsymbol{x}_r^{t}\leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r^{t-\Delta t}, \boldsymbol{u}_h^t)$
+		\STATE $t \leftarrow t + \Delta t$
+		\ENDWHILE
+		\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_{g^{t_b}})\Big]$
+
+		or
+
+		\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_{g^{t_b}}||b_{g^{t_a}})\Big]$
+		\ENDFOR
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
 The control mode with highest disambiguation capability $m^*$ is then given by $\argmax_m D_m$.
@@
 
-\begin{algorithm}[h]
-	\caption{Information-Theoretic Intent Disambiguation}
-	\label{alg:disamb}
-	\begin{algorithmic}[1]
-		\REQUIRE $b_{g^{t_a}}, \boldsymbol{x}_r^{t_a}, \Delta t, t_a < t_b$
-		\FOR{$m \in \mathcal{M}$}
-		\STATE Initialize $D_m = 0$
-		\FOR{$g \in \mathcal{G}$}
-
-		\STATE Initialize $t = t_a, \boldsymbol{x}_r^{t} = \boldsymbol{x}_r^{t_a}, b_{g^{t}} = b_{g^{t_a}}$
-		\WHILE{$t \leq t_b$}
-		\STATE $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\; g, m)$ 
-		\STATE $b_{g^{t + \Delta t}} \leftarrow \text{BeliefUpdate}(b_{g^{t}}, \boldsymbol{u}_h^t)$
-		\STATE $\boldsymbol{x}_r^{t + \Delta t}\leftarrow \text{SimulateKinematics}(\boldsymbol{x}_r^{t}, \boldsymbol{u}_h^t)$
-		\STATE $t \leftarrow t + \Delta t$
-		\ENDWHILE
-		\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[ENT(b_{g^{t_b}})\Big] $
-
-		or
-
-		\STATE $D_m \leftarrow D_m + \frac{1}{n_g} \mathbb{E}_{\boldsymbol{u}_h \sim p(\boldsymbol{u}_h \; | \; g, m)}\Big[KL(b_{g^{t_b}}||b_{g^{t_a}})\Big] $
-		\ENDFOR
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-
 %\begin{algorithm}[t]
@@
 %  The disambiguation power of our algorithm is closely linked to the inference power of different choices of inference mechanisms. 
-At any given time $t$, the probability distributions over goals encodes the human's underlying intent.
-The time evolution of the probability distribution, however, depends on the choice of intent inference scheme, and the various task relevant features and parameters that contribute to it.
+\added{The exact update rule for the recursive belief update (Algorithm~\ref{alg:disamb}, Line 7) directly impacts the projected probability distributions, $b_g^{t_b}$, and the disambiguation metric, $D_m$.
+At any given time $t$, the probability distributions over goals encodes the human's underlying intent and the time evolution of the probability distribution \added{i.e., belief update}, depends on the choice of intent inference scheme.
+Here we present the different belief update schemes (intent inference block in Figure~\ref{fig:sc}) evaluated in our experimental evaluation.
+}
+% and the various task relevant features and parameters that contribute to it.
 
-More specifically, the exact update rule for the recursive belief update is determined by the choice of inference scheme (Algorithm~\ref{alg:disamb}, Line 6) which impacts the projected probability distributions, $b_g^{t_b}$, and the disambiguation metric, $D_m$.
-Here we present the multiple intent schemes evaluated in conjunction with our disambiguation algorithm.
 %This is because, during the forward projection step, different intent update schemes result in different projections and affects the computation of the disambiguation metric.
@@
 \end{equation*}
-where $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\;g, m)$ is the human control command.
+\added{where $\boldsymbol{u}_h^t \sim p(\boldsymbol{u}_h\;|\;g^{intended}, m)$ is the human control command}.
 These confidence functions rely on instantaneous features and therefore are amnesic and can exhibit chatter behavior~\cite{dragan2012formalizing}.
@@
 \subsubsection{Bayesian Approaches}
-Bayesian approaches for intent inference consist of iteratively updating of the belief (probability distribution over goals) as new evidence arrives at every time-step.
+Bayesian approaches for intent inference consist of iteratively updating of the belief as new evidence arrives at every time-step.
 The Bayesian update procedure directly uses Equation~\ref{eq:final_belief} for belief propagation.
@@
 The design of $\boldsymbol{\xi}$ is informed by what features of the human control input and environment capture the human's underlying intent most effectively.
-Our implementation relies on the \textit{directedness} of the human control commands towards a goal, the \textit{proximity} to a goal and the \textit{agreement} between the human commands and robot autonomy.
+Our implementation relies on the \textit{directedness} of the human control commands towards a goal, the \textit{proximity} to a goal and the \textit{agreement} between the human commands and robot autonomy\footnote{We refer the reader to~\cite{gopinath2018dnf} for a more in-depth evaluation of dynamic neural approach approach for intent inference.}.
 
@@
 Therefore, intent inference and disambiguation play a vital role in the seamless operation and success of a shared control system.
-In our experimental evaluation, control sharing is achieved with a blending-based paradigm, in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
+In our evaluation, control sharing is achieved with a blending-based paradigm, in which the final control command issued to the robot is a weighted linear combination of the user control command and robot autonomy.
 \subsubsection{Robot Autonomy}\label{sssec:autonomy}
@@
 
-The robot autonomy command $\boldsymbol{u}_{r,g}$ is generated using a simple potential field, which is defined in all parts of the state space~\cite{khatib1986real}.
-Every goal $g$ is associated with a potential field $\gamma_g$ which treats $g$ as an attractor and all the other goals in the scene as repellers.
+The robot autonomy command $\boldsymbol{u}_{r,g^*}$ is generated using a simple potential field, which is defined in all parts of the state space~\cite{khatib1986real}.
+\added{The potential field worked in conjunction with the intent inference module which generated the goal prediction $g^*$ at every time step.
+$g^*$ is then associated with a potential field $\gamma_{g^*}$ which treated $g^*$ as an attractor and all the other goals in the scene as repellers.
+}
 %That is,
@@
 
-\subsubsection{Blending Paradigm}\label{sssec:blending}
+\subsubsection{Control Blending Paradigm}\label{sssec:blending}
 The final control command $\boldsymbol{u}_f$ issued to the robot then is given by
@@
 In our implementation, we empirically set $\rho_1 = \frac{1.05}{n_g}, \rho_2 = \frac{1.1}{n_g}$ and $ \rho_3 = 0.7$.
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width= \hsize, height=0.28\vsize]{./figures/SharedAutonomy.eps}
+	\vspace{-1cm}
+	\caption{\added{Components of a shared autonomy human-machine system.
+This illustrates how the different components work in tandem as the human and autonomy interact continually to control the robotic arm.
+The intent disambiguation module is activated upon user request and results in a control mode switch to the maximally disambiguating mode $m^*$.
+The intent inference block utilizes the different algorithms presented in Section~\ref{sec:inference}.
+The robot autonomy is generated using a potential field approach described in Section~\ref{sssec:autonomy} and the shared autonomy is implemented via a control blending approach described in Section~\ref{sssec:blending}.} }
+	\label{fig:sc}
+\end{figure}
+
 \subsubsection{Maximum Potential Mode Switch Assistance}\label{sssec:baseline}
@@
 		$\mathbb{SE}(2)$ & $3$ &  $\{[1],[2],[3]\}$, $\{[1,2], [3]\}$ \\ \hline
-		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$ \\ \hline
+		$\mathbb{SE}(3)$ & $6$ & $\{[1],[2],[3],[4],[5],[6]\}$, $\{[1,2,3],  [4,5,6]\}$, $\{[1,2], [1,3], [4,5], [6]\}$, $\{[1,2], [1,3], [4,5], [4,6]\}$ \\ \hline
 	\end{tabular}
@@
 \subsubsection{$\boldsymbol{u}_r$ and $\boldsymbol{u}_h^{sim}$}
-The simulated robot autonomy $\boldsymbol{u}^{sim}_r$ is generated using a repeller-free potential field.
-For an intended goal $g^{intended}$ and a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u}^{sim}_h$ is sampled from the mode conditioned policy, $p(\boldsymbol{u}_h\;|\;g^{intended}, m)$.
+The simulated robot autonomy $\boldsymbol{u}^{sim}_r$ is generated using a repeller-free potential field \added{introduced in Section~\ref{sssec:autonomy}}.
+For an intended goal $g^{intended}$ and a given control mode $m \in \mathcal{M}$, the simulated human control command denoted by $\boldsymbol{u}^{sim}_h$ is sampled from the mode conditioned policy, $p(\boldsymbol{u}_h\;|\;g^{intended}, m)$ \added{as described in Section~\ref{ssec:model_based}}.
 %\begin{equation*}
@@
 	%	\item \textit{Number of Mode Switches}: This metric refers to the number of times the control mode switch from the current mode to a different mode. 
-	\item \textit{Initial Onset of Assistance}: Earliest time (normalized with respect to individual trial time) at which assistance  was triggered towards the intended goal.
+	\item \textit{Onset Time}: Earliest time (normalized with respect to individual trial time) at which assistance  was triggered towards the intended goal.
 This measure captures how \textit{early} the robot was able to infer the correct goal  \textit{and} provide assistance.
-	\item \textit{Total Amount of Assistance }: Fraction of the total trial time for which assistance towards the intended goal was present.  
-	\item \textit{Inference Accuracy }: Fraction of the total trial time for which the intent inference mechanism correctly inferred the human's intended goal.
+	\item \textit{\added{Temporal Ratio of Assistance}}: Fraction of the total trial time for which assistance towards the intended goal was present.  
+	\item \textit{Inference Accuracy}: Fraction of the total trial time for which the intent inference mechanism correctly inferred the human's intended goal.
 This is a measure of overall accuracy of the system.
@@
 The expectation in Equations~\ref{eq:ent} and \ref{eq:kldiv} was computed by averaging over five samples.
-A \textit{dropout} factor was added to the human control command to mimic the signal sparsity exhibited by humans during robot teleoperation.
-Figure~\ref{fig:ws_sim} illustrates an example of the simulation for a point robot in $\mathbb{R}^2$.
- \begin{figure}[h!]
-	\centering
-	\includegraphics[width= \hsize, height=0.25\vsize]{./figures/WS_SIM.eps}
-	\vspace{-0.35cm}
-	\caption{Example of point robot simulation in $\mathbb{R}^2$.
+A \textit{dropout} factor was added to the human control command to mimic the signal sparsity exhibited by humans during robot teleoperation\footnote{Point robot simulation code available at \url{https://github.com/deepakgopinath/information_theoretic_intent_disambiguation}}.
+
+%\begin{figure}[ht!]
+%	\centering
+%	\includegraphics[width= \hsize, height=0.28\vsize]{./figures/SharedAutonomy.eps}
+%	\vspace{-0.35cm}
+%	\caption{\added{Components of a shared autonomy human-machine system.
+This illustrates how the different components work in tandem as the human and autonomy interact continually to control the robotic arm.
+The intent disambiguation module is activated upon user request and results in a control mode switch to the maximally disambiguating mode $m^*$.}}
+%	\label{fig:sc}
+%\end{figure}
+% \begin{figure}[h!]
+%	\centering
+%	\includegraphics[width= \hsize, height=0.25\vsize]{./figures/WS_SIM.eps}
+%	\vspace{-0.35cm}
+%	\caption{Example of point robot simulation in $\mathbb{R}^2$.
 The goals are represented in black, the initial robot position in red and the human's intended goal in magenta.
@@
 Greedy (Black), Entropy (Red), KL Divergence (Blue) and Heuristic (Green).}
-	\label{fig:ws_sim}
-\end{figure}
+%	\label{fig:ws_sim}
+%\end{figure}
 \begin{figure}[t!]
 	\centering
-	\includegraphics[width= 1.01\hsize, height=0.3\vsize, center]{./figures/onset_time.eps}
+	\includegraphics[width= 1.01\hsize, height=0.35\vsize, center]{./figures/onset_time.eps}
 	\vspace{-0.75cm}
@@
 \subsection{Robotic Arm	 Simulation Setup}
-We also evaluated our system in a physics-based simulation of a 6-DoF robotic arm (MICO robotic arm from Kinova Robotics).
+We also evaluated our system in a physics-based simulation of a 6-DoF robotic arm (MICO robot from Kinova Robotics).
 Although the end effector of the robot lives in $\mathbb{SE}(3)$, the physical constraints of the robot make the kinematics highly nonlinear compared to a point robot in $\mathbb{SE}(3)$.
@@
 	\centering
-	\includegraphics[width= 1.1\hsize, height=1\vsize, center]{./figures/total_assistance.eps}
+	\includegraphics[width= 1.1\hsize, height=0.42\vsize, center]{./figures/temporal_ratio_of_assistance.eps}
 	\vspace{-0.8cm}
-	\caption{Total amount of assistance.
+	\caption{Temporal ratio of assistance.
 Group differences between mode switch assistance schemes (GRD, ENT, KL, HEU), in four operational spaces $\mathbb{R}^2$, $\mathbb{R}^3$, $\mathbb{SE}(2)$ and $\mathbb{SE}(3)$.
@@
 In all the data plots, (*) indicates $p < 0.05$, (**) indicates $p < 0.01$ and (***) indicates $p < 0.001$.
-\subsubsection{Initial Onset of Assistance}
+\subsubsection{Onset Time}
 \begin{figure}[t!]
 	\centering
-	\includegraphics[width= 1.1\hsize, height=0.46\vsize, center]{./figures/correct_inference.eps}
+	\includegraphics[width= 1.1\hsize, height=0.45\vsize, center]{./figures/correct_inference.eps}
 	\vspace{-0.75cm}
@@
 
-\subsubsection{Amount of Total Assistance}
+\subsubsection{\added{Temporal Ratio of Assistance}}
 %\vspace*{-0.7cm}
@@
 	\centering
-	\includegraphics[width= 1.\hsize, height=0.28\vsize, center]{./figures/mico_sim.eps}
+	\includegraphics[width= 1.\hsize, height=0.24\vsize, center]{./figures/mico_sim_new.eps}
 	\vspace{-0.5cm}
@@
 Similarly, the accuracy of the intent inference procedure is higher when disambiguation algorithm is deployed, although not statistically significant.
-However, the total amount of assistance provided by the autonomy is comparable between the mode-switching schemes.
-These results indicate that even with a low-dimensional and discrete control interface that exhibits signal dropouts (due to the sparsity factor), robot operation in control modes selected by the disambiguation algorithm helps the autonomy to elicit more intent-revealing control commands thereby helping the system predict the intended goal more accurately and provide assistance earlier.
+However, the temporal ratio of assistance provided by the autonomy is comparable between the mode-switching schemes.
+These results indicate that even with a low-dimensional and discrete control interface that exhibits signal dropouts, robot operation in control modes selected by the disambiguation algorithm helps the autonomy to elicit more intent-revealing control commands thereby helping the system predict the intended goal more accurately and provide assistance earlier.
 \section{Discussion}\label{sec:discussions}
@@
 Our results indicate that disambiguation helps to enhance the accuracy of the intent inference and leads to an increase in the overall assistance provided to the user.
+\added{Our algorithm can be used for any human-robot system that utilizes a parametric intent inference system.
+The disambiguation algorithm can be used to rank order any discrete parameter set accordingly to their ability to better disambiguate intent.
+}
+
 Another factor that is crucial for the success of a shared control system, especially for safety-critical applications, is \textit{when} during task execution the assistance gets activated.
@@
 From our simulation results, we can see that intent disambiguation enhances the inference capabilities of the system and helps the autonomy to provide assistance earlier.
-
 The utility value of a mode-switching scheme can vary during the time course of task execution.
@@
 Furthermore, parallel computation on GPU can also be leveraged for more accurate estimation of the expectation in Equations~\ref{eq:ent} and \ref{eq:kldiv}.
-Lastly, the disambiguation algorithm can be customized to specific users using real-time learning algorithms that capture individual teleoperation characteristics.
+%Lastly, the disambiguation algorithm can be customized to specific users using real-time learning algorithms that capture individual teleoperation characteristics.
 
@@
  In this paper, we proposed a mode selection
-paradigm that enhances the autonomy’s intent inference capabilities by exploiting the fact that how the human operates the robot is intrinsically conditioned on
-the control mode in operation.
+paradigm that enhances the autonomy's intent inference capabilities by exploiting the fact that how the human operates the robot is intrinsically conditioned on the control mode in operation.
 We introduced two different methods for intent disambiguation using the information-theoretic concepts of entropy and KL divergence.
